### 2024-02-13 Manuscript_1.Rmd
Figure 3 done - Polish Figure 4

---
title: "Manuscript_1"
author: Deborah Gérard^[University of Luxembourg - FSTM - DLSM - Systems Biology group - Epigenetics team]
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    keep_md: true
    df_print: paged
    toc: true
    toc_depth: 6
  pdf_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE, 
                      results = "as.is", 
                      fig.height = 3, 
                      cache = TRUE, 
                      tidy = TRUE, 
                      fig.pos = "H")
```

#### *1. Create a Singularity container*

Work within a Singularity container to ensure reproducibility

```{bash Sing_crea, eval = FALSE, echo = TRUE}
# Initiate virtual box Vagrant
cd $HOME/Manuscript_1_vagrant

vagrant up --provision
# vagrant reload
vagrant ssh

# Check the number of allocated cores and memory
free -h
nproc

# Check singularity version
singularity version   # 3.9.0

# Prepare the singularity definition file
mkdir Manuscript_1_singularity && cd Manuscript_1_singularity
touch Manuscript_1_singularity.def

# Build the temporary container based on Ubuntu 20.04 from Docker for development 
sudo singularity build --sandbox Manuscript_1_singularity_tmp Manuscript_1_singularity.def

# Run the container in writable mode to make changes
sudo singularity shell --writable Manuscript_1_singularity_tmp

# Now that all necessay packages and library have been installed, build the container
sudo singularity build Manuscript_1_singularity.sif Manuscript_1_singularity_tmp

# Start R
singularity exec Manuscript_1_singularity.sif R

# Check R version
R.Version()
```

**Note**: R version is 4.2.3 (2023-03-15)

##### *1.1 Customize the Singularity container*

Install different R libraries

```{r cust, eval = FALSE, echo = TRUE}
# tidyverse, ggpubr, rstatix
install.packages(c("tidyverse", 
                   "ggpubr", 
                   "rstatix"))
# plotgardener
BiocManager::install("plotgardener")

# BSgenome.Hsapiens.UCSC.hg38
BiocManager::install("BSgenome.Hsapiens.UCSC.hg38")

# extrafont
install.packages("extrafont")

# showtext
install.packages("showtext")

# TxDb.Hsapiens.UCSC.hg38.knownGene
BiocManager::install("TxDb.Hsapiens.UCSC.hg38.knownGene")

# org.Hs.eg.db
BiocManager::install("org.Hs.eg.db")

# JASPAR2020
BiocManager::install("JASPAR2020")

# TFBSTools
BiocManager::install("TFBSTools")

# ggseqlogo
install.packages("ggseqlogo")

# TxDb.Hsapiens.UCSC.hg38.refGene
BiocManager::install("TxDb.Hsapiens.UCSC.hg38.refGene")

# LDlinkR
install.packages("LDlinkR")

# AllelicImbalance
BiocManager::install("AllelicImbalance")

# ggflowchart
install.packages("ggflowchart")

# Issue between dplyr, BiocFilrCache and biomaRt - > downgrade dbplyr
install.packages("devtools")
devtools::install_version("dbplyr", version = "2.3.4")
```

Load libraries and check their versions

```{r load_lib, eval = FALSE, echo = TRUE}
# Load
library("tidyverse")
library("rstatix")
library("ggpubr")
library("plotgardener")
#library("BSgenome.Hsapiens.UCSC.hg38")
#library("TxDb.Hsapiens.UCSC.hg38.knownGene")
library("TxDb.Hsapiens.UCSC.hg38.refGene")
library("org.Hs.eg.db")
library("extrafont")
library("showtext")
library("JASPAR2020")
library("TFBSTools")
library("ggseqlogo")
library("biomaRt")
library("LDlinkR")
library("AllelicImbalance")
library("png")
library("AnnotationDbi")
library("scales")
library("flowCore")
library("ggcyto")

# Check
packageVersion("tidyverse") #2.0.0
packageVersion("rstatix") #0.7.2
packageVersion("ggpubr")  #0.6.0
packageVersion("plotgardener")  #1.4.2
#packageVersion("BSgenome.Hsapiens.UCSC.hg38") #1.4.5
#packageVersion("TxDb.Hsapiens.UCSC.hg38.knownGene") #3.16.0
packageVersion("TxDb.Hsapiens.UCSC.hg38.refGene") #3.15.0
packageVersion("org.Hs.eg.db")  #3.16.0
packageVersion("extrafont") #0.19
packageVersion("showtext")  #0.9.6
packageVersion("JASPAR2020")  #0.99.10
packageVersion("TFBSTools") #1.36.0
packageVersion("ggseqlogo") #0.1
packageVersion("biomaRt") #2.54.1
packageVersion("LDlinkR") #1.3.0
packageVersion("AllelicImbalance")  #1.36.0
packageVersion("png") #0.1.8
packageVersion("AnnotationDbi") #1.60.2
packageVersion("dbplyr")  #2.3.4

# Import all available fonts
font_import()
```

# FIGURES
### FIGURE 1
```{r fig1, eval = FALSE, echo = TRUE}
########## FIGURE 1 ##########
##############################
# Save as a PDF
pdf("/home/vagrant/Manuscript_1/FIGURE1/FIGURE1.pdf",
    width = 8.3, 
    height = 11.7)

# Create a A4 blank page
pageCreate(width = 8.3, 
           height = 11.7, 
           default.units = "inches",
           showGuides = FALSE)

#### PANEL A - 
# text Figure 1
plotText(label = "Figure 1", 
         fontsize = 14,
         x = 0.25, 
         y = 0.25, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")
# text A
plotText(label = "A", 
         fontsize = 12,
         x = 0.25, 
         y = 0.5, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

# text B
plotText(label = "B", 
         fontsize = 12,
         x = 0.25, 
         y = 1.5, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

# text C
plotText(label = "C", 
         fontsize = 12,
         x = 0.25, 
         y = 4.5, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

# text D
plotText(label = "D", 
         fontsize = 12,
         x = 0.25, 
         y = 8.25, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

###################
#### Figure 1A ####
###################
Fig1A = readPNG("/home/vagrant/Manuscript_1/FIGURE1/Fig1A.png")

# Plot Figure 1A
plotRaster(image = Fig1A,
           x = 0.375,
           y = 0.625,
           width = 7.55,
           height = 1.0,
           just = c("left", 
                    "top"),
           interpolate = FALSE)

###################
#### Figure 1B ####
###################
# Load data obtained from Jochen
RNAseq_odd = read_delim("/home/vagrant/Manuscript_1/FIGURE1/REFORMAT_tpm_gene_sets.gsa.txt",
                        delim = "\t",
                        col_names = TRUE)

#RNAseq_odd = read_delim("/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/REFORMAT_tpm_gene_sets.gsa.txt",
#                        delim = "\t",
#                        col_names = TRUE)

# Calculate odd ratio
RNAseq_odd = RNAseq_odd %>% 
  dplyr::filter(!VARIABLE %in% c("microglia")) %>% 
  mutate(odd_R = exp(BETA)) %>% 
  mutate(VARIABLE = factor(VARIABLE, 
                           levels = c("smNPC",
                                      "D15negsort",
                                      "D15possort",
                                      "D30postsort",
                                      "D50negsort",
                                      "D50possort",
                                      "astrocytes")))

# Plot
fig1B = ggplot(RNAseq_odd,
       aes(x = odd_R,
           y = VARIABLE)) +
  geom_point(shape = 16, size = 3) +
  geom_errorbarh(aes(xmin = odd_R - SE, 
                     xmax = odd_R + SE), 
                 height = 0.25) +
  geom_vline(xintercept = 1.0, linetype = "dashed", color = "grey") +
  theme_classic() +
  theme(axis.title = element_text(face = "bold"),
        axis.text = element_text(face = "bold")) +
  scale_y_discrete(labels = c("smNPC" = "smNPC", 
                              "D15negsort" = "non-mDAN D15", 
                              "D15possort" = "mDAN D15", 
                              "D30postsort" = "mDAN D30", 
                              "D50negsort" = "non-mDAN D50",
                              "D50possort" = "mDAN D50",
                              "astrocytes" = "Astrocytes")) +
  geom_text(label = round(RNAseq_odd$P, 
                          digits = 3),
            nudge_y = 0.40) +
  xlab("Odds ratio (95% Confidence Interval)") +
  ylab("")

# Place
plotGG(plot = fig1B, 
       x = 0.375, 
       y = 1.75, 
       width = 3.0, 
       height = 2.5,
       just = c("left", "top"), 
       default.units = "inches")

###################
#### Figure 1C ####
###################
Fig1C_pip = readPNG("/home/vagrant/Manuscript_1/FIGURE1/Fig1C_pipeline.png")

Fig1C_tab1.1 = readPNG("/home/vagrant/Manuscript_1/FIGURE1/Fig1C_SNPs_tab1.png/Fig1C_SNPs_tab1.png-1.png")
Fig1C_tab1.2 = readPNG("/home/vagrant/Manuscript_1/FIGURE1/Fig1C_SNPs_tab1.png/Fig1C_SNPs_tab1.png-2.png")

# Plot Figure 1C
plotRaster(image = Fig1C_pip,
           x = 0.375,
           y = 5.25,
           width = 3.0,
           height = 2.5,
           just = c("left", 
                    "top"),
           interpolate = FALSE)

plotRaster(image = Fig1C_tab1.1,
           x = 3.375,
           y = 5.25,
           width = 2.3,
           height = 2.5,
           just = c("left", 
                    "top"),
           interpolate = FALSE)

plotRaster(image = Fig1C_tab1.2,
           x = 5.8,
           y = 5.25,
           width = 2.3,
           height = 2.5,
           just = c("left", 
                    "top"),
           interpolate = FALSE)

#diag_edge_data = tibble(from = c("~17x10^6\nPD GWAS SNPs",
#                                 "~3400 significant\nPD GWAS SNPs",
#                                 "28 significant\nPD rSNPs"),
#                        to = c("~3400 significant\nPD GWAS SNPs",
#                               "28 significant\nPD rSNPs",
#                               "3 significant\nPD rSNPs"))
#
#diag_node_data = tibble(name = c("~17x10^6\nPD GWAS SNPs",
#                                 "~3400 significant\nPD GWAS SNPs",
#                                 "28 significant\nPD rSNPs",
#                                "3 significant\nPD rSNPs"),
#                        label = name)

# Diagramme
# fig1C = ggflowchart(diag_edge_data,
#                    diag_node_data,
#                    text_size = 3.0,
#                    arrow_size = 0.2)

# Place the diagramme
#plotGG(plot = fig1C, 
#       x = 0.5, 
#       y = 4.5, 
#      width = 1.5, 
#       height = 3.0,
#       just = c("left", "top"), 
#      default.units = "inches")

###################
#### Figure 1D ####
###################

# Locus plot
# Load the Nalls et al. GWAS data
nalls_allSNPs.HG38.GR = readRDS(
  "/home/vagrant/Manuscript_1/FIGURE1/nalls_allSNPs.HG38.GR.rds")

#nalls_allSNPs.HG38.GR = readRDS(
#  "/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/nalls_allSNPs.HG38.GR.rds")

# Here our SNPs of interest and their location
snp = GRanges(seqnames = c("chr10", "chr4", "chr4"),
              ranges = IRanges(start = c(119651404, 987107, 76213716),
                               end = c(119651405, 987108, 76213717)))

# Retrieve them from Nalls et al data
snp_Nalls = subsetByOverlaps(nalls_allSNPs.HG38.GR, snp) %>% 
  as_tibble() %>% 
  dplyr::select(-width, -strand) %>% 
  mutate(rsID = c("rs144814361", "rs1465922", "rs11248061"))

# Visualise the genomic region per SNP (+- 400100 bp)
# rs144814361
r = 40100

# Filter for the SNP in BAG3 regulatory region
Nalls_sel_reg.BAG3 = nalls_allSNPs.HG38.GR %>% 
  as_tibble() %>% 
  dplyr::filter(seqnames == "chr10",
         between(base_pair_position, 119651405 - r, 119651405 + r)) %>% 
  mutate(minus_log_10_p = -log10(p),
         GWAS_p_sig = if_else(minus_log_10_p > -log10(5e-8), "yes", "no"),
         rsID = if_else(seqnames == "chr10" & base_pair_position == 119651405, "rs144814361", ""))

# Get SNPs info from Ensembl
snp.ensembl = useEnsembl(biomart = "snp", dataset = "hsapiens_snp")

# SNP info
query.snp = getBM(c("ensembl_gene_stable_id", 
                            "refsnp_id", 
                            "chr_name", 
                            "chrom_start", 
                            "chrom_end", 
                            "minor_allele", 
                            "minor_allele_freq"),
                          filters = "snp_filter",
                          values = c("rs144814361", "rs1465922", "rs11248061"),
                  mart = snp.ensembl)

# Get rsID of SNPs that are significant and append 
position_chr10 = Nalls_sel_reg.BAG3 %>% 
  mutate(chr = gsub("chr", "", seqnames)) %>% 
  unite(col = "position", c(chr, end, base_pair_position), sep = ":", remove = FALSE) %>% 
  filter(GWAS_p_sig != "no") %>%
  dplyr::select(position) %>% 
  pull()

rsID_sig_SNPs.chr10 = getBM(c("refsnp_id", "chr_name", "chrom_start", "chrom_end", "allele", "minor_allele"),
                      filters = "chromosomal_region",
                      values = position_chr10,
                      mart = snp.ensembl)

rsID_sig_SNPs.chr10 = rsID_sig_SNPs.chr10 %>% 
  unite(col = "position", chr_name:chrom_end, sep = ":", remove = FALSE)

Nalls_sel_reg.BAG3 = Nalls_sel_reg.BAG3 %>% 
  mutate(chr = gsub("chr", "", seqnames)) %>% 
  unite(col = "position", c(chr, end, base_pair_position),
        sep = ":", remove = FALSE) %>% 
  left_join(rsID_sig_SNPs.chr10, by = "position")

# Calculate R2 to check if SNPs are in LD
BAG3_SNPs_LD = Nalls_sel_reg.BAG3 %>% 
  dplyr::select(refsnp_id) %>% 
  drop_na()

BAG3_R2 = LDproxy(snp = "rs144814361",
                   pop = "EUR",
                   r2d = "r2",
                   token = "5bba40af90d7",
                   genome_build = "grch38_high_coverage")

BAG3_R2 = BAG3_R2 %>% 
  as_tibble() %>% 
  dplyr::select(RS_Number, Coord, R2) %>% 
  dplyr::rename(refsnp_id = RS_Number)

# Plot
BAG3.pl = Nalls_sel_reg.BAG3 %>% 
  unite("Coord", seqnames, base_pair_position, sep = ":", remove = FALSE) %>% 
  left_join(BAG3_R2, by = "Coord") %>% 
  dplyr::select(seqnames, base_pair_position, p, refsnp_id.x,R2) %>% 
  dplyr::rename(chrom = seqnames,
               pos = base_pair_position,
               snp = refsnp_id.x, 
               LD = R2) %>% 
  mutate(chrom = as.character(chrom)) %>% 
  group_by(LD) %>% 
  mutate(LD_grp = cut(LD, seq(0, 1.0, 0.2)))

BAG3.pl$LD_grp = addNA(BAG3.pl$LD_grp)

BAG3_leadSNP = "rs144814361"

BAG3_MP = plotManhattan(data = BAG3.pl,
              chrom = "chr10",
              chromstart = 119611405,
              chromend = 119691405,
              assembly = "hg38",
              fill = colorby("LD_grp",
                             palette = colorRampPalette(c("#35b779",
                                                          "#21918c", 
                                                          "#31688e",
                                                          "#443983", 
                                                          "#440154", 
                                                          "#CCCCCC"))),
        trans = "-log10", 
        sigLine = TRUE, col = "grey",
        lty = 2, range = c(0, 16),
        leadSNP = list(
        snp = BAG3_leadSNP,
        pch = 18,
        cex = 0.75,
        fill = "#990066",
        fontsize = 8),
              x = 0.5, 
              y = 8.5, 
              width = 1.5, 
              height = 2.5,
              just = c("left", "top"), 
              default.units = "inches")

## Annotate genome label
annoGenomeLabel(
    plot = BAG3_MP, x = 0.5, y = 11,
    fontsize = 8, scale = "Mb",
    just = c("left", "top"), default.units = "inches"
)

## Annotate y-axis
annoYaxis(
    plot = BAG3_MP,
    at = c(0, 2, 4, 6, 8, 10, 12),
    axisLine = TRUE, fontsize = 8
)

## Plot y-axis label
plotText(
    label = "-log10(p-value)", x = 0.125, y = 10.125, rot = 90,
    fontsize = 8, fontface = "bold", just = "center",
    default.units = "inches"
)

# Plot gene BAG3
plotGenes(
    chrom = "chr10", chromstart = 119611405, chromend = 119691405,
    x = 0.5, y = 8.5, width = 1.5, height = 0.5,
    just = c("left", "top"), default.units = "inches",
    fontcolor = "black",
    fill = "black",
    assembly = assembly(Genome = "hg38refGene", 
                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
                      OrgDb = "org.Hs.eg.db")
)

# Filter for the SNP in IDUA regulatory region
Nalls_sel_reg.IDUA = nalls_allSNPs.HG38.GR %>% 
  as_tibble() %>% 
  filter(seqnames == "chr4",
         between(base_pair_position, 987108 - r, 987108 + r)) %>% 
  mutate(minus_log_10_p = -log10(p),
         GWAS_p_sig = if_else(minus_log_10_p > -log10(5e-8), "yes", "no"),
         rsID = if_else(seqnames == "chr4" & base_pair_position == 987108, "rs11248061", ""))

# Get rsID of SNPs that significant and append 
position_chr4.IDUA = Nalls_sel_reg.IDUA %>% 
  mutate(chr = gsub("chr", "", seqnames)) %>% 
  unite(col = "position", c(chr, end, base_pair_position), sep = ":", remove = FALSE) %>% 
  filter(GWAS_p_sig != "no") %>%
  dplyr::select(position) %>% 
  pull()

rsID_sig_SNPs.chr4.IDUA = getBM(c("refsnp_id", "chr_name", "chrom_start", "chrom_end", "allele", "minor_allele",
                        "minor_allele_freq"),
                      filters = "chromosomal_region",
                      values = position_chr4.IDUA,
                      mart = snp.ensembl)

rsID_sig_SNPs.chr4.IDUA = rsID_sig_SNPs.chr4.IDUA %>% 
  unite(col = "position", chr_name:chrom_end, sep = ":", remove = FALSE)

Nalls_sel_reg.IDUA = Nalls_sel_reg.IDUA %>% 
  mutate(chr = gsub("chr", "", seqnames)) %>% 
  unite(col = "position", c(chr, end, base_pair_position),
        sep = ":", remove = FALSE) %>% 
  left_join(rsID_sig_SNPs.chr4.IDUA, by = "position")

# Calculate R2 to check if SNPs are in LD
IDUA_SNPs_LD = Nalls_sel_reg.IDUA %>% 
  dplyr::select(refsnp_id) %>% 
  drop_na()

IDUA_SNPs_LD = IDUA_SNPs_LD %>% 
  filter(!str_detect(refsnp_id, "^CR"))

IDUA_R2 = LDproxy(snp = "rs11248061",
                   pop = "EUR",
                   r2d = "r2",
                   token = "5bba40af90d7",
                   genome_build = "grch38_high_coverage")

IDUA_R2 = IDUA_R2 %>% 
  as_tibble() %>% 
  dplyr::select(RS_Number, Coord, R2) %>% 
  dplyr::rename(refsnp_id = RS_Number)

# Plot
IDUA.pl = Nalls_sel_reg.IDUA %>% 
  unite("Coord", seqnames, base_pair_position, sep = ":", remove = FALSE) %>% 
  distinct(Coord, .keep_all = TRUE) %>% 
  left_join(IDUA_R2, by = "Coord") %>% 
  dplyr::select(seqnames, base_pair_position, p, refsnp_id.x, R2) %>% 
  dplyr::rename(chrom = seqnames,
               pos = base_pair_position,
               snp = refsnp_id.x, 
               LD = R2) %>% 
  mutate(chrom = as.character(chrom)) %>% 
  group_by(LD) %>% 
  mutate(LD_grp = cut(LD, seq(0, 1.0, 0.2)))

IDUA.pl$LD_grp = addNA(IDUA.pl$LD_grp)

IDUA_leadSNP = "rs11248061"

IDUA_MP = plotManhattan(data = IDUA.pl,
              chrom = "chr4",
              chromstart = 947108,
              chromend = 1027108,
              assembly = "hg38",
              fill = colorby("LD_grp",
                             palette = colorRampPalette(c("#35b779",
                                                          "#21918c", 
                                                          "#31688e",
                                                          "#443983", 
                                                          "#440154", 
                                                          "#CCCCCC"))),
        trans = "-log10", 
        sigLine = TRUE, col = "grey",
        lty = 2, range = c(0, 16),
        leadSNP = list(
        snp = IDUA_leadSNP,
        pch = 18,
        cex = 0.75,
        fill = "#990066",
        fontsize = 8),
              x = 2.5, 
              y = 8.5, 
              width = 1.5, 
              height = 2.5,
              just = c("left", "top"), 
              default.units = "inches")

## Annotate genome label
annoGenomeLabel(
    plot = IDUA_MP, x = 2.5, y = 11,
    fontsize = 8, scale = "Mb",
    just = c("left", "top"), default.units = "inches"
)

## Annotate y-axis
annoYaxis(
    plot = IDUA_MP,
    at = c(0, 2, 4, 6, 8, 10, 12),
    axisLine = TRUE, fontsize = 8
)

## Plot y-axis label
plotText(
    label = "-log10(p-value)", x = 2.125, y = 10.125, rot = 90,
    fontsize = 8, fontface = "bold", just = "center",
    default.units = "inches"
)

# Plot gene IDUA
plotGenes(
    chrom = "chr4", chromstart = 947108, chromend = 1027108,
    x = 2.5, y = 8.5, width = 1.5, height = 0.5,
    just = c("left", "top"), default.units = "inches",
    fontcolor = "black",
    fill = "black",
    assembly = assembly(Genome = "hg38refGene", 
                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
                      OrgDb = "org.Hs.eg.db")
)

# Filter for the SNP in SCARB2 regulatory region
Nalls_sel_reg.SCARB2 = nalls_allSNPs.HG38.GR %>% 
  as_tibble() %>% 
  filter(seqnames == "chr4",
         between(base_pair_position, 76213717 - r, 76213717 + r)) %>% 
  mutate(minus_log_10_p = -log10(p),
         GWAS_p_sig = if_else(minus_log_10_p > -log10(5e-8), "yes", "no"),
         rsID = if_else(seqnames == "chr4" & base_pair_position == 76213717, "rs1465922", ""))

# Get rsID of SNPs that significant and append 
position_chr4.SCARB2 = Nalls_sel_reg.SCARB2 %>% 
  mutate(chr = gsub("chr", "", seqnames)) %>% 
  unite(col = "position", c(chr, end, base_pair_position), sep = ":", remove = FALSE) %>% 
  filter(GWAS_p_sig != "no") %>%
  dplyr::select(position) %>% 
  pull()

rsID_sig_SNPs.chr4.SCARB2 = getBM(c("refsnp_id", "chr_name", "chrom_start", "chrom_end", "allele", "minor_allele",
                        "minor_allele_freq"),
                      filters = "chromosomal_region",
                      values = position_chr4.SCARB2,
                      mart = snp.ensembl)

rsID_sig_SNPs.chr4.SCARB2 = rsID_sig_SNPs.chr4.SCARB2 %>% 
  unite(col = "position", chr_name:chrom_end, sep = ":", remove = FALSE)

Nalls_sel_reg.SCARB2 = Nalls_sel_reg.SCARB2 %>% 
  mutate(chr = gsub("chr", "", seqnames)) %>% 
  unite(col = "position", c(chr, end, base_pair_position),
        sep = ":", remove = FALSE) %>% 
  left_join(rsID_sig_SNPs.chr4.SCARB2, by = "position")

# Calculate R2 to check if SNPs are in LD
SCARB2_SNPs_LD = Nalls_sel_reg.SCARB2 %>% 
  dplyr::select(refsnp_id) %>% 
  drop_na()

SCARB2_R2 = LDproxy(snp = "rs1465922",
                   pop = "EUR",
                   r2d = "r2",
                   token = "5bba40af90d7",
                   genome_build = "grch38_high_coverage")

SCARB2_R2 = SCARB2_R2 %>% 
  as_tibble() %>% 
  dplyr::select(RS_Number, Coord, R2) %>% 
  dplyr::rename(refsnp_id = RS_Number)

# Plot
SCARB2.pl = Nalls_sel_reg.SCARB2 %>% 
  unite("Coord", seqnames, base_pair_position, sep = ":", remove = FALSE) %>% 
  left_join(SCARB2_R2, by = "Coord") %>% 
  dplyr::select(seqnames, base_pair_position, p, refsnp_id.x, R2) %>% 
  dplyr::rename(chrom = seqnames,
               pos = base_pair_position,
               snp = refsnp_id.x, 
               LD = R2) %>% 
  mutate(chrom = as.character(chrom)) %>% 
  group_by(LD) %>% 
  mutate(LD_grp = cut(LD, seq(0, 1.0, 0.2)))

SCARB2.pl$LD_grp = addNA(SCARB2.pl$LD_grp)

SCARB2_leadSNP = "rs1465922"

SCARB2_MP = plotManhattan(data = SCARB2.pl,
              chrom = "chr4",
              chromstart = 76173717,
              chromend = 76253717,
              assembly = "hg38",
              fill = colorby("LD_grp",
                             palette = colorRampPalette(c("#35b779",
                                                          "#21918c", 
                                                          "#31688e",
                                                          "#443983", 
                                                          "#440154", 
                                                          "#CCCCCC"))),
        trans = "-log10", 
        sigLine = TRUE, col = "grey",
        lty = 2, range = c(0, 16),
        leadSNP = list(
        snp = SCARB2_leadSNP,
        pch = 18,
        cex = 0.75,
        fill = "#990066",
        fontsize = 8),
              x = 4.5, 
              y = 8.5, 
              width = 1.5, 
              height = 2.5,
              just = c("left", "top"), 
              default.units = "inches")

## Annotate genome label
annoGenomeLabel(
    plot = SCARB2_MP, x = 4.5, y = 11,
    fontsize = 8, scale = "Mb",
    just = c("left", "top"), default.units = "inches"
)

## Annotate y-axis
annoYaxis(
    plot = SCARB2_MP,
    at = c(0, 2, 4, 6, 8, 10, 12),
    axisLine = TRUE, fontsize = 8
)

## Plot y-axis label
plotText(
    label = "-log10(p-value)", x = 4.125, y = 10.125, rot = 90,
    fontsize = 8, fontface = "bold", just = "center",
    default.units = "inches"
)

# Plot gene SCARB2
plotGenes(
    chrom = "chr4", chromstart = 76173717, chromend = 76253717,
    x = 4.5, y = 8.5, width = 1.5, height = 0.5,
    just = c("left", "top"), default.units = "inches",
    fontcolor = "black",
    fill = "black",
    assembly = assembly(Genome = "hg38refGene", 
                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
                      OrgDb = "org.Hs.eg.db")
)

# Legend LD score
plotLegend(
  legend = c("LD reference SNP",
             paste("0", "<", "r^2", "<= 0.2"),
             paste("0.2", "<", "r^2", "<= 0.4"),
             paste("0.4", "<", "r^2", "<= 0.6"),
             paste("0.6", "<", "r^2", "<= 0.8"),
             paste("0.8", "<", "r^2", "<= 1.0"),
             "no LD data"),
    fill = c("#990066", "#35b779", "#21918c", "#31688e", "#443983", "#440154", "#CCCCCC"), 
  cex = 0.75,
    pch = c(18, 19, 19, 19, 19, 19, 19), border = FALSE, x = 6.5, y = 9.25,
    width = 1.0, height = 1.0, just = c("left", "top"),
    default.units = "inches"
)

dev.off()
```

### FIGURE 2
Create the page layout that will contain all the necessary plots

```{r fig2, eval = FALSE, echo = TRUE}
########## FIGURE 2 ##########
##############################

# Save as a PDF
pdf("/home/vagrant/Manuscript_1/FIGURE2/FIGURE2.pdf",
    width = 8.3, 
    height = 11.7)

# Create a A4 blank page
pageCreate(width = 8.3, 
           height = 11.7, 
           default.units = "inches",
           showGuides = FALSE)

#### PANEL A - BAG3 locus
# text Figure 2
plotText(label = "Figure 2", 
         fontsize = 14,
         x = 0.25, 
         y = 0.25, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")
# text A
plotText(label = "A", 
         fontsize = 12,
         x = 0.25, 
         y = 0.5, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

# ATACseq signal BAG3
# path where bigwig files are
bw.path = "/home/vagrant/epifunc/"

# 1st bio replicate smNPC
bw.smNPC_1 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/smNPC_I.bw"),
                        chrom = "chr10",
                        chromstart = 119611305,
                        chromend = 119691505)

# 2nd bio replicate smNPC
bw.smNPC_2 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/smNPC_II.bw"),
                        chrom = "chr10",
                        chromstart = 119611305,
                        chromend = 119691505)

# 3rd bio replicate smNPC
bw.smNPC_3 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/smNPC_III.bw"),
                        chrom = "chr10",
                        chromstart = 119611305,
                        chromend = 119691505)

# 1st bio replicate TH positive neurons D15
bw.TH.pos_D15_1 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/D15_POS_I.bw"),
                        chrom = "chr10",
                        chromstart = 119611305,
                        chromend = 119691505)

# 2nd bio replicate TH positive neurons D15
bw.TH.pos_D15_2 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/D15_POS_II.bw"),
                        chrom = "chr10",
                        chromstart = 119611305,
                        chromend = 119691505)

# 3rd bio replicate TH positive neurons D15
bw.TH.pos_D15_3 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/D15_POS_III.bw"),
                        chrom = "chr10",
                        chromstart = 119611305,
                        chromend = 119691505)

# 1st bio replicate TH positive neurons D30
bw.TH.pos_D30_1 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/D30_POS_I.bw"),
                        chrom = "chr10",
                        chromstart = 119611305,
                        chromend = 119691505)

# 2nd bio replicate TH positive neurons D30
bw.TH.pos_D30_2 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/D30_POS_II.bw"),
                        chrom = "chr10",
                        chromstart = 119611305,
                        chromend = 119691505)

# 3rd bio replicate TH positive neurons D30
bw.TH.pos_D30_3 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/D30_POS_III.bw"),
                        chrom = "chr10",
                        chromstart = 119611305,
                        chromend = 119691505)

# 1st bio replicate TH positive neurons D50
bw.TH.pos_D50_1 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/HFFTHmCherry_D50_possort_S1.bw"),
                        chrom = "chr10",
                        chromstart = 119611305,
                        chromend = 119691505)

# 2nd bio replicate TH positive neurons D50
bw.TH.pos_D50_2 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/HFFTHmCherry_D50_possort_S3.bw"),
                        chrom = "chr10",
                        chromstart = 119611305,
                        chromend = 119691505)

# 3rd bio replicate TH positive neurons D50
bw.TH.pos_D50_3 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/HFFTHmCherry_D50_possort_S4.bw"),
                        chrom = "chr10",
                        chromstart = 119611305,
                        chromend = 119691505)

# Add a scale next to the bigwig files - check the maximum to choose
scale.BAG3.max = max(c(bw.smNPC_1$score,
                       bw.smNPC_2$score,
                       bw.smNPC_3$score,
                       bw.TH.pos_D15_1$score,
                       bw.TH.pos_D15_2$score,
                       bw.TH.pos_D15_3$score,
                       bw.TH.pos_D30_1$score,
                       bw.TH.pos_D30_2$score,
                       bw.TH.pos_D30_3$score,
                       bw.TH.pos_D50_1$score,
                       bw.TH.pos_D50_2$score,
                       bw.TH.pos_D50_3$score))

print(scale.BAG3.max)

# Define parameters for the regions
region.p.BAG3 = pgParams(chrom = "chr10",
                         chromstart = 119611405,
                         chromend = 119691405,
                         assembly = "hg38",
                         range = c(0, scale.BAG3.max))

# Add the genomic label
plotGenomeLabel(
  chrom = "chr10",
  chromstart = 119611405,
  chromend = 119691405,
  assembly = "hg38",
  x = 0.75,
  y = 0.625,
  length = 4.0,
  default.units = "inches",
  scale = "Mb")

# ATACseq signal smNPC_I and scale
ATAC_smNPC_I = plotSignal(
  data = bw.smNPC_1, 
  params = region.p.BAG3,
  fill = "#D3D3D3", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 0.875, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_smNPC_I, 
          at = c(0, scale.BAG3.max),
          fontsize = 6)

# ATACseq signal smNPC_II
ATAC_smNPC_II = plotSignal(
  data = bw.smNPC_2, 
  params = region.p.BAG3,
  fill = "#C0C0C0", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 0.875, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_smNPC_II, 
          at = c(0, scale.BAG3.max),
          fontsize = 6)

# ATACseq signal smNPC_III
ATAC_smNPC_III = plotSignal(
  data = bw.smNPC_3, 
  params = region.p.BAG3,
  fill = "#A9A9A9", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 0.875, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_smNPC_III, 
          at = c(0, scale.BAG3.max),
          fontsize = 6)

# ATACseq signal TH positive neurons D15 I
ATAC_TH.pos_D15_I = plotSignal(
  data = bw.TH.pos_D15_1, 
  params = region.p.BAG3,
  fill = "#B22222", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 1.25, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_TH.pos_D15_I, 
          at = c(0, scale.BAG3.max),
          fontsize = 6)

# ATACseq signal TH positive neurons D15 II
ATAC_TH.pos_D15_II = plotSignal(
  data = bw.TH.pos_D15_2, 
  params = region.p.BAG3,
  fill = "#A52A2A", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 1.25, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_TH.pos_D15_II, 
          at = c(0, scale.BAG3.max),
          fontsize = 6)

# ATACseq signal TH positive neurons D15 III
ATAC_TH.pos_D15_III = plotSignal(
  data = bw.TH.pos_D15_3, 
  params = region.p.BAG3,
  fill = "#8B0000", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 1.25, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_TH.pos_D15_III, 
          at = c(0, scale.BAG3.max),
          fontsize = 6)

# ATACseq signal TH positive neurons D30 I
ATAC_TH.pos_D30_I = plotSignal(
  data = bw.TH.pos_D30_1, 
  params = region.p.BAG3,
  fill = "#FF6347", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 1.625, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_TH.pos_D30_I, 
          at = c(0, scale.BAG3.max),
          fontsize = 6)

# ATACseq signal TH positive neurons D30 II
ATAC_TH.pos_D30_II = plotSignal(
  data = bw.TH.pos_D30_2, 
  params = region.p.BAG3,
  fill = "#FF0000", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 1.625, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_TH.pos_D30_II, 
          at = c(0, scale.BAG3.max),
          fontsize = 6)

# ATACseq signal TH positive neurons D30 III
ATAC_TH.pos_D30_III = plotSignal(
  data = bw.TH.pos_D30_3, 
  params = region.p.BAG3,
  fill = "#DC143C", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 1.625, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_TH.pos_D30_III, 
          at = c(0, scale.BAG3.max),
          fontsize = 6)

# ATACseq signal TH positive neurons D50 I
ATAC_TH.pos_D50_I = plotSignal(
  data = bw.TH.pos_D50_1, 
  params = region.p.BAG3,
  fill = "#FFA07A", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 2.0, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_TH.pos_D50_I, 
          at = c(0, scale.BAG3.max),
          fontsize = 6)

# ATACseq signal TH positive neurons D50 II
ATAC_TH.pos_D50_II = plotSignal(
  data = bw.TH.pos_D50_2, 
  params = region.p.BAG3,
  fill = "#FA8072", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 2.0, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_TH.pos_D50_II, 
          at = c(0, scale.BAG3.max),
          fontsize = 6)

# ATACseq signal TH positive neurons D50 III
ATAC_TH.pos_D50_III = plotSignal(
  data = bw.TH.pos_D50_3, 
  params = region.p.BAG3,
  fill = "#E9967A", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 2.0, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_TH.pos_D50_III, 
          at = c(0, scale.BAG3.max),
          fontsize = 6)

# Gene track
plotGenes(chrom = "chr10",
  chromstart = 119611405,
  chromend = 119691405,
  assembly = assembly(Genome = "hg38refGene", 
                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
                      OrgDb = "org.Hs.eg.db"),
  fontcolor = "black",
  fill = "black",
  x = 0.75,
  y = 2.375,
  width = 4.0,
  height = 0.375,
  just = c("left", "top"),
  default.units = "inches")

# Add the samples name
plotText(label = "smNPC", 
         fontsize = 6, 
         fontcolor = "#A9A9A9",
         x = 0.75, 
         y = 0.875, 
         just = c("left", "top"),
         default.units = "inches")

plotText(label = "mDAN D15", 
         fontsize = 6, 
         fontcolor = "#B22222",
         x = 0.75, 
         y = 1.25, 
         just = c("left", "top"),
         default.units = "inches")

plotText(label = "mDAN D30", 
         fontsize = 6, 
         fontcolor = "#DC143C",
         x = 0.75, 
         y = 1.625, 
         just = c("left", "top"),
         default.units = "inches")

plotText(label = "mDAN D50", 
         fontsize = 6, 
         fontcolor = "#E9967A",
         x = 0.75, 
         y = 2.0, 
         just = c("left", "top"),
         default.units = "inches")

#### PANEL B - BAG3 and LHX1 expression (RNAseq)
# text B
plotText(label = "B", 
         fontsize = 12,
         x = 5.0, 
         y = 0.5, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

# Load RPKM matrix obtained from Borja and rename columns
# dat.RPKM = read_delim("/home/vagrant/epifunc/RNAseq/RPKM_genename",
#                       delim = "\t", 
#                       col_names = TRUE)
# 
# dat.RPKM = dat.RPKM %>% 
#   dplyr::select(gene_id, gene_name, everything())

# RPKM data - Remove the negative sorted neurons and astrocytes
# dat.RPKM.filt = dat.RPKM %>% 
#   dplyr::select(!contains("negsort"), -starts_with("ASTRO")) %>% 
#   pivot_longer(cols = ends_with("bam"), names_to = "Sample", values_to = "RPKM") %>% 
#   mutate(Cond = case_when(str_detect(Sample, "D15_possort") ~ "Positively sorted neurons D15",
#                          str_detect(Sample, "D30_possort") ~ "Positively sorted neurons D30",
#                          str_detect(Sample, "D50_possort") ~ "Positively sorted neurons D50",
#                          TRUE ~ "smNPCs"),
#          Cond = factor(Cond, levels = c("smNPCs", "Positively sorted neurons D15",
#                                   "Positively sorted neurons D30", 
#                                   "Positively sorted neurons D50")),
#          gene_id = gsub("\\..*", "", gene_id))

# Save the matrix of expression
# write_rds(dat.RPKM.filt,
#           "/home/vagrant/Manuscript_1/FIGURE2/mat_RPKM.rds")

# Load it for making the plots
dat.RPKM.filt = read_rds("/home/vagrant/Manuscript_1/FIGURE2/mat_RPKM.rds")

# Expression for BAG3 and LHX1
BAG3.LHX1.exp = ggboxplot(dat.RPKM.filt %>% 
                            dplyr::filter(gene_name %in% c("BAG3", "LHX1")),
                          x = "Cond", 
                          y = "RPKM", 
                          add = "jitter", 
                          fill = "Cond", 
                          palette = c("#A9A9A9", "#B22222", "#DC143C", "#E9967A"),
                          facet.by = "gene_name",
                          xlab = "", 
                          ylab = "Reads Per Kilobase Million (RPKM)") +
  scale_x_discrete(labels = c("smNPC",
                              expression("mDAN D15"),
                              expression("mDAN D30"),
                              expression("mDAN D50"))) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))

# Place the plot
plotGG(plot = BAG3.LHX1.exp, 
       x = 5.25, 
       y = 0.625, 
       width = 2, 
       height = 3.5,
       just = c("left", "top"), 
       default.units = "inches")

# Add the transcription factor binding motif (TFBS) for LHX1
pfm.LHX1 = getMatrixByID(JASPAR2020, 
                         ID = "MA1518.1")
LHX1 = new.env()

LHX1$LHX1 = pfm.LHX1@profileMatrix

LHX1 = as.list(LHX1)
LHX1_TFBS = ggseqlogo(LHX1)

# Place the plot
plotGG(plot = LHX1_TFBS, 
       x = 1.7125, 
       y = 2.625, 
       width = 1.5, 
       height = 1.5,
       just = c("left", "top"), 
       default.units = "inches")

# Add the SNP position that zoom in the TFBS
SNP_param = pgParams(chrom = "chr10",
                     chromstart = 119651405,
                     chromend = 119651405,
                     assembly = "hg38")

annoHighlight(plot = ATAC_smNPC_I, 
              params = SNP_param,
              fill = "#404788FF",
              y = 0.875, 
              height = 1.75, 
              just = c("left", "top"), 
              default.units = "inches")

annoZoomLines(plot = ATAC_smNPC_I, 
              params = SNP_param,
              y0 = 2.625, 
              x1 = c(2.25, 3.25), 
              y1 = 2.75, 
              default.units = "inches")

# text C
plotText(label = "C", 
         fontsize = 12,
         x = 0.25, 
         y = 4.25, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

# ATACseq signal IDUA
# 1st bio replicate smNPC
bw.IDUA.smNPC_1 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/smNPC_I.bw"),
                        chrom = "chr4",
                        chromstart = 947008,
                        chromend = 1027208)

# 2nd bio replicate smNPC
bw.IDUA.smNPC_2 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/smNPC_II.bw"),
                        chrom = "chr4",
                        chromstart = 947008,
                        chromend = 1027208)

# 3rd bio replicate smNPC
bw.IDUA.smNPC_3 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/smNPC_III.bw"),
                        chrom = "chr4",
                        chromstart = 947008,
                        chromend = 1027208)

# 1st bio replicate TH positive neurons D15
bw.IDUA.TH.pos_D15_1 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/D15_POS_I.bw"),
                        chrom = "chr4",
                        chromstart = 947008,
                        chromend = 1027208)

# 2nd bio replicate TH positive neurons D15
bw.IDUA.TH.pos_D15_2 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/D15_POS_II.bw"),
                        chrom = "chr4",
                        chromstart = 947008,
                        chromend = 1027208)

# 3rd bio replicate TH positive neurons D15
bw.IDUA.TH.pos_D15_3 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/D15_POS_III.bw"),
                        chrom = "chr4",
                        chromstart = 947008,
                        chromend = 1027208)

# 1st bio replicate TH positive neurons D30
bw.IDUA.TH.pos_D30_1 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/D30_POS_I.bw"),
                        chrom = "chr4",
                        chromstart = 947008,
                        chromend = 1027208)

# 2nd bio replicate TH positive neurons D30
bw.IDUA.TH.pos_D30_2 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/D30_POS_II.bw"),
                        chrom = "chr4",
                        chromstart = 947008,
                        chromend = 1027208)

# 3rd bio replicate TH positive neurons D30
bw.IDUA.TH.pos_D30_3 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/D30_POS_III.bw"),
                        chrom = "chr4",
                        chromstart = 947008,
                        chromend = 1027208)

# 1st bio replicate TH positive neurons D50
bw.IDUA.TH.pos_D50_1 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/HFFTHmCherry_D50_possort_S1.bw"),
                        chrom = "chr4",
                        chromstart = 947008,
                        chromend = 1027208)

# 2nd bio replicate TH positive neurons D50
bw.IDUA.TH.pos_D50_2 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/HFFTHmCherry_D50_possort_S3.bw"),
                        chrom = "chr4",
                        chromstart = 947008,
                        chromend = 1027208)

# 3rd bio replicate TH positive neurons D50
bw.IDUA.TH.pos_D50_3 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/HFFTHmCherry_D50_possort_S4.bw"),
                        chrom = "chr4",
                        chromstart = 947008,
                        chromend = 1027208)

# Add a scale next to the bigwig files - check the maximum to choose
scale.IDUA.max = max(c(bw.IDUA.smNPC_1$score,
                       bw.IDUA.smNPC_2$score,
                       bw.IDUA.smNPC_3$score,
                       bw.IDUA.TH.pos_D15_1$score,
                       bw.IDUA.TH.pos_D15_2$score,
                       bw.IDUA.TH.pos_D15_3$score,
                       bw.IDUA.TH.pos_D30_1$score,
                       bw.IDUA.TH.pos_D30_2$score,
                       bw.IDUA.TH.pos_D30_3$score,
                       bw.IDUA.TH.pos_D50_1$score,
                       bw.IDUA.TH.pos_D50_2$score,
                       bw.IDUA.TH.pos_D50_3$score))

print(scale.IDUA.max)

# Define parameters for the regions
region.p.IDUA = pgParams(chrom = "chr4",
                         chromstart = 947108,
                         chromend = 1027108,
                         assembly = "hg38",
                         range = c(0, scale.IDUA.max))

# Add the genomic label
plotGenomeLabel(
  chrom = "chr4",
  chromstart = 947108,
  chromend = 1027108,
  assembly = "hg38",
  x = 0.75,
  y = 4.375,
  length = 4.0,
  default.units = "inches",
  scale = "Mb")

# ATACseq signal smNPC_I
ATAC_smNPC_I_IDUA = plotSignal(
  data = bw.IDUA.smNPC_1, 
  params = region.p.IDUA,
  fill = "#D3D3D3", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 4.625, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_smNPC_I_IDUA, 
          at = c(0, scale.IDUA.max),
          fontsize = 6)

# ATACseq signal smNPC_II
ATAC_smNPC_II_IDUA = plotSignal(
  data = bw.IDUA.smNPC_2, 
  params = region.p.IDUA,
  fill = "#C0C0C0", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 4.625, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_smNPC_II_IDUA, 
          at = c(0, scale.IDUA.max),
          fontsize = 6)

# Add the SNP position that zoom in the TFBS
SNP_param_IDUA = pgParams(chrom = "chr4",
                     chromstart = 987108,
                     chromend = 987108,
                     assembly = "hg38")

annoHighlight(plot = ATAC_smNPC_I_IDUA, 
              params = SNP_param_IDUA,
              fill = "#404788FF",
              y = 4.75, 
              height = 1.875, 
              just = c("left", "top"), 
              default.units = "inches")

annoZoomLines(plot = ATAC_smNPC_I_IDUA, 
              params = SNP_param_IDUA,
              y0 = 6.625, 
              x1 = c(2.25, 3.25), 
              y1 = 6.75, 
              default.units = "inches")

# ATACseq signal smNPC_III
ATAC_smNPC_III_IDUA = plotSignal(
  data = bw.IDUA.smNPC_3, 
  params = region.p.IDUA,
  fill = "#A9A9A9", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 4.625, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_smNPC_III_IDUA, 
          at = c(0, scale.IDUA.max),
          fontsize = 6)

# ATACseq signal TH positive neurons D15 I
ATAC_TH.pos_D15_I_IDUA = plotSignal(
  data = bw.IDUA.TH.pos_D15_1, 
  params = region.p.IDUA,
  fill = "#B22222", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 5.0, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_TH.pos_D15_I_IDUA, 
          at = c(0, scale.IDUA.max),
          fontsize = 6)

# ATACseq signal TH positive neurons D15 II
ATAC_TH.pos_D15_II_IDUA = plotSignal(
  data = bw.IDUA.TH.pos_D15_2, 
  params = region.p.IDUA,
  fill = "#A52A2A", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 5.0, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_TH.pos_D15_II_IDUA, 
          at = c(0, scale.IDUA.max),
          fontsize = 6)

# ATACseq signal TH positive neurons D15 III
ATAC_TH.pos_D15_III_IDUA = plotSignal(
  data = bw.IDUA.TH.pos_D15_3, 
  params = region.p.IDUA,
  fill = "#8B0000", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 5.0, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_TH.pos_D15_III_IDUA, 
          at = c(0, scale.IDUA.max),
          fontsize = 6)

# ATACseq signal TH positive neurons D30 I
ATAC_TH.pos_D30_I_IDUA = plotSignal(
  data = bw.IDUA.TH.pos_D30_1, 
  params = region.p.IDUA,
  fill = "#FF6347", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 5.375, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_TH.pos_D30_I_IDUA, 
          at = c(0, scale.IDUA.max),
          fontsize = 6)

# ATACseq signal TH positive neurons D30 II
ATAC_TH.pos_D30_II_IDUA = plotSignal(
  data = bw.IDUA.TH.pos_D30_2, 
  params = region.p.IDUA,
  fill = "#FF0000", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 5.375, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_TH.pos_D30_II_IDUA, 
          at = c(0, scale.IDUA.max),
          fontsize = 6)

# ATACseq signal TH positive neurons D30 III
ATAC_TH.pos_D30_III_IDUA = plotSignal(
  data = bw.IDUA.TH.pos_D30_3, 
  params = region.p.IDUA,
  fill = "#DC143C", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 5.375, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_TH.pos_D30_III_IDUA, 
          at = c(0, scale.IDUA.max),
          fontsize = 6)

# ATACseq signal TH positive neurons D50 I
ATAC_TH.pos_D50_I_IDUA = plotSignal(
  data = bw.IDUA.TH.pos_D50_1, 
  params = region.p.IDUA,
  fill = "#FFA07A", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 5.75, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_TH.pos_D50_I_IDUA, 
          at = c(0, scale.IDUA.max),
          fontsize = 6)

# ATACseq signal TH positive neurons D50 II
ATAC_TH.pos_D50_II_IDUA = plotSignal(
  data = bw.IDUA.TH.pos_D50_2, 
  params = region.p.IDUA,
  fill = "#FA8072", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 5.75, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_TH.pos_D50_II_IDUA, 
          at = c(0, scale.IDUA.max),
          fontsize = 6)

# ATACseq signal TH positive neurons D50 III
ATAC_TH.pos_D50_III_IDUA = plotSignal(
  data = bw.IDUA.TH.pos_D50_3, 
  params = region.p.IDUA,
  fill = "#E9967A", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 5.75, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_TH.pos_D50_III_IDUA, 
          at = c(0, scale.IDUA.max),
          fontsize = 6)

# Gene track
plotGenes(chrom = "chr4",
  chromstart = 947108,
  chromend = 1027108,
  assembly = assembly(Genome = "hg38refGene", 
                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
                      OrgDb = "org.Hs.eg.db"),
  fontcolor = "black",
  fill = "black",
  x = 0.75,
  y = 6.125,
  width = 4.0,
  height = 0.375,
  just = c("left", "top"),
  default.units = "inches")

# Add the samples name
plotText(label = "smNPC", 
         fontsize = 6, 
         fontcolor = "#A9A9A9",
         x = 0.75, 
         y = 4.625, 
         just = c("left", "top"),
         default.units = "inches")

plotText(label = "mDAN D15", 
         fontsize = 6, 
         fontcolor = "#B22222",
         x = 0.75, 
         y = 5.0, 
         just = c("left", "top"),
         default.units = "inches")

plotText(label = "mDAN D30", 
         fontsize = 6, 
         fontcolor = "#DC143C",
         x = 0.75, 
         y = 5.375, 
         just = c("left", "top"),
         default.units = "inches")

plotText(label = "mDAN D50", 
         fontsize = 6, 
         fontcolor = "#E9967A",
         x = 0.75, 
         y = 5.75, 
         just = c("left", "top"),
         default.units = "inches")

#### PANEL D - IDUA and ZBTB14 expression (RNAseq)
# text D
plotText(label = "D", 
         fontsize = 12,
         x = 5.0, 
         y = 4.25, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

IDUA.ZBTB14.exp = ggboxplot(dat.RPKM.filt %>% 
                            dplyr::filter(gene_name %in% c("IDUA", "ZBTB14", "SLC26A1")) %>% 
                              mutate(gene_name = factor(gene_name,
                                                        levels = c("IDUA", "ZBTB14", "SLC26A1"))),
                          x = "Cond", 
                          y = "RPKM", 
                          add = "jitter", 
                          fill = "Cond", 
                          palette = c("#A9A9A9", "#B22222", "#DC143C", "#E9967A"),
                          facet.by = "gene_name",
                          xlab = "", 
                          ylab = "Reads Per Kilobase Million (RPKM)") +
  scale_x_discrete(labels = c("smNPC",
                              "mDAN D15",
                              "mDAN D30",
                              "mDAN D50")) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))

# Place the plot
plotGG(plot = IDUA.ZBTB14.exp, 
       x = 5.25, 
       y = 4.25, 
       width = 3, 
       height = 3.5,
       just = c("left", "top"), 
       default.units = "inches")

# Add the transcription factor binding motif (TFBS) for ZBTB14
pfm.ZBTB14 = getMatrixByID(JASPAR2020, 
                         ID = "MA1650.1")
ZBTB14 = new.env()

ZBTB14$ZBTB14 = pfm.ZBTB14@profileMatrix

ZBTB14 = as.list(ZBTB14)
ZBTB14_TFBS = ggseqlogo(ZBTB14)

# Place the plot
plotGG(plot = ZBTB14_TFBS, 
       x = 1.7125, 
       y = 6.625, 
       width = 1.5, 
       height = 1.5,
       just = c("left", "top"), 
       default.units = "inches")

# text E
plotText(label = "E", 
         fontsize = 12,
         x = 0.25, 
         y = 8.0, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

# ATACseq signal SCARB2
# 1st bio replicate smNPC
bw.SCARB2.smNPC_1 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/smNPC_I.bw"),
                        chrom = "chr4",
                        chromstart = 76173617,
                        chromend = 76253817)

# 2nd bio replicate smNPC
bw.SCARB2.smNPC_2 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/smNPC_II.bw"),
                        chrom = "chr4",
                        chromstart = 76173617,
                        chromend = 76253817)

# 3rd bio replicate smNPC
bw.SCARB2.smNPC_3 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/smNPC_III.bw"),
                        chrom = "chr4",
                        chromstart = 76173617,
                        chromend = 76253817)

# 1st bio replicate TH positive neurons D15
bw.SCARB2.TH.pos_D15_1 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/D15_POS_I.bw"),
                        chrom = "chr4",
                        chromstart = 76173617,
                        chromend = 76253817)

# 2nd bio replicate TH positive neurons D15
bw.SCARB2.TH.pos_D15_2 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/D15_POS_II.bw"),
                        chrom = "chr4",
                        chromstart = 76173617,
                        chromend = 76253817)

# 3rd bio replicate TH positive neurons D15
bw.SCARB2.TH.pos_D15_3 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/D15_POS_III.bw"),
                        chrom = "chr4",
                        chromstart = 76173617,
                        chromend = 76253817)

# 1st bio replicate TH positive neurons D30
bw.SCARB2.TH.pos_D30_1 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/D30_POS_I.bw"),
                        chrom = "chr4",
                        chromstart = 76173617,
                        chromend = 76253817)

# 2nd bio replicate TH positive neurons D30
bw.SCARB2.TH.pos_D30_2 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/D30_POS_II.bw"),
                        chrom = "chr4",
                        chromstart = 76173617,
                        chromend = 76253817)

# 3rd bio replicate TH positive neurons D30
bw.SCARB2.TH.pos_D30_3 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/D30_POS_III.bw"),
                        chrom = "chr4",
                        chromstart = 76173617,
                        chromend = 76253817)

# 1st bio replicate TH positive neurons D50
bw.SCARB2.TH.pos_D50_1 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/HFFTHmCherry_D50_possort_S1.bw"),
                        chrom = "chr4",
                        chromstart = 76173617,
                        chromend = 76253817)

# 2nd bio replicate TH positive neurons D50
bw.SCARB2.TH.pos_D50_2 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/HFFTHmCherry_D50_possort_S3.bw"),
                        chrom = "chr4",
                        chromstart = 76173617,
                        chromend = 76253817)

# 3rd bio replicate TH positive neurons D50
bw.SCARB2.TH.pos_D50_3 = readBigwig(file = paste0(bw.path, 
                                      "BIGWIG/HFFTHmCherry_D50_possort_S4.bw"),
                        chrom = "chr4",
                        chromstart = 76173617,
                        chromend = 76253817)

# Add a scale next to the bigwig files - check the maximum to choose
scale.SCARB2.max = max(c(bw.SCARB2.smNPC_1$score,
                       bw.SCARB2.smNPC_2$score,
                       bw.SCARB2.smNPC_3$score,
                       bw.SCARB2.TH.pos_D15_1$score,
                       bw.SCARB2.TH.pos_D15_2$score,
                       bw.SCARB2.TH.pos_D15_3$score,
                       bw.SCARB2.TH.pos_D30_1$score,
                       bw.SCARB2.TH.pos_D30_2$score,
                       bw.SCARB2.TH.pos_D30_3$score,
                       bw.SCARB2.TH.pos_D50_1$score,
                       bw.SCARB2.TH.pos_D50_2$score,
                       bw.SCARB2.TH.pos_D50_3$score))

print(scale.SCARB2.max)

# Define parameters for the regions
region.p.SCARB2 = pgParams(chrom = "chr4",
                         chromstart = 76173717,
                         chromend = 76253717,
                         assembly = "hg38",
                         range = c(0, scale.SCARB2.max))

# Add the genomic label
plotGenomeLabel(
  chrom = "chr4",
  chromstart = 76173717,
  chromend = 76253717,
  assembly = "hg38",
  x = 0.75,
  y = 8.125,
  length = 4.0,
  default.units = "inches",
  scale = "Mb")

# ATACseq signal smNPC_I
ATAC_smNPC_I_SCARB2 = plotSignal(
  data = bw.SCARB2.smNPC_1, 
  params = region.p.SCARB2,
  fill = "#D3D3D3", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 8.375, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_smNPC_I_SCARB2, 
          at = c(0, scale.SCARB2.max),
          fontsize = 6)

# ATACseq signal smNPC_II
ATAC_smNPC_II_SCARB2 = plotSignal(
  data = bw.SCARB2.smNPC_2, 
  params = region.p.SCARB2,
  fill = "#C0C0C0", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 8.375, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_smNPC_II_SCARB2, 
          at = c(0, scale.SCARB2.max),
          fontsize = 6)

# ATACseq signal smNPC_III
ATAC_smNPC_III_SCARB2 = plotSignal(
  data = bw.SCARB2.smNPC_3, 
  params = region.p.SCARB2,
  fill = "#A9A9A9", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 8.375, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_smNPC_III_SCARB2, 
          at = c(0, scale.SCARB2.max),
          fontsize = 6)

# Add the SNP position that zoom in the TFBS
SNP_param_SCARB2 = pgParams(chrom = "chr4",
                     chromstart = 76213717,
                     chromend = 76213717,
                     assembly = "hg38")

annoHighlight(plot = ATAC_smNPC_I_SCARB2, 
              params = SNP_param_SCARB2,
              fill = "#404788FF",
              y = 8.375, 
              height = 1.875, 
              just = c("left", "top"), 
              default.units = "inches")

annoZoomLines(plot = ATAC_smNPC_I_SCARB2, 
              params = SNP_param_SCARB2,
              y0 = 10.25, 
              x1 = c(2.25, 3.25), 
              y1 = 10.5, 
              default.units = "inches")

# ATACseq signal TH positive neurons D15 I
ATAC_TH.pos_D15_I_SCARB2 = plotSignal(
  data = bw.SCARB2.TH.pos_D15_1, 
  params = region.p.SCARB2,
  fill = "#B22222", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 8.75, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_TH.pos_D15_I_SCARB2, 
          at = c(0, scale.SCARB2.max),
          fontsize = 6)

# ATACseq signal TH positive neurons D15 II
ATAC_TH.pos_D15_II_SCARB2 = plotSignal(
  data = bw.SCARB2.TH.pos_D15_2, 
  params = region.p.SCARB2,
  fill = "#A52A2A", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 8.75, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_TH.pos_D15_II_SCARB2, 
          at = c(0, scale.SCARB2.max),
          fontsize = 6)

# ATACseq signal TH positive neurons D15 III
ATAC_TH.pos_D15_III_SCARB2 = plotSignal(
  data = bw.SCARB2.TH.pos_D15_3, 
  params = region.p.SCARB2,
  fill = "#8B0000", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 8.75, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_TH.pos_D15_III_SCARB2, 
          at = c(0, scale.SCARB2.max),
          fontsize = 6)

# ATACseq signal TH positive neurons D30 I
ATAC_TH.pos_D30_I_SCARB2 = plotSignal(
  data = bw.SCARB2.TH.pos_D30_1, 
  params = region.p.SCARB2,
  fill = "#FF6347", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 9.125, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_TH.pos_D30_I_SCARB2, 
          at = c(0, scale.SCARB2.max),
          fontsize = 6)

# ATACseq signal TH positive neurons D30 II
ATAC_TH.pos_D30_II_SCARB2 = plotSignal(
  data = bw.SCARB2.TH.pos_D30_2, 
  params = region.p.SCARB2,
  fill = "#FF0000", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 9.125, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_TH.pos_D30_II_SCARB2, 
          at = c(0, scale.SCARB2.max),
          fontsize = 6)

# ATACseq signal TH positive neurons D30 III
ATAC_TH.pos_D30_III_SCARB2 = plotSignal(
  data = bw.SCARB2.TH.pos_D30_3, 
  params = region.p.SCARB2,
  fill = "#DC143C", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 9.125, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_TH.pos_D30_III_SCARB2, 
          at = c(0, scale.SCARB2.max),
          fontsize = 6)

# ATACseq signal TH positive neurons D50 I
ATAC_TH.pos_D50_I_SCARB2 = plotSignal(
  data = bw.SCARB2.TH.pos_D50_1, 
  params = region.p.SCARB2,
  fill = "#FFA07A", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 9.5, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_TH.pos_D50_I_SCARB2, 
          at = c(0, scale.SCARB2.max),
          fontsize = 6)

# ATACseq signal TH positive neurons D50 II
ATAC_TH.pos_D50_II_SCARB2 = plotSignal(
  data = bw.SCARB2.TH.pos_D50_2, 
  params = region.p.SCARB2,
  fill = "#FA8072", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 9.5, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_TH.pos_D50_II_SCARB2, 
          at = c(0, scale.SCARB2.max),
          fontsize = 6)

# ATACseq signal TH positive neurons D50 III
ATAC_TH.pos_D50_III_SCARB2 = plotSignal(
  data = bw.SCARB2.TH.pos_D50_3, 
  params = region.p.SCARB2,
  fill = "#E9967A", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 9.5, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = ATAC_TH.pos_D50_III_SCARB2, 
          at = c(0, scale.SCARB2.max),
          fontsize = 6)

# Gene track
plotGenes(
  chrom = "chr4",
  chromstart = 76173717,
  chromend = 76253717,
  assembly = assembly(Genome = "hg38refGene", 
                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
                      OrgDb = "org.Hs.eg.db"),
  fontcolor = "black",
  fill = "black",
  x = 0.75,
  y = 9.875,
  width = 4.0,
  height = 0.375,
  just = c("left", "top"),
  default.units = "inches")

# Add the samples name
plotText(label = "smNPC", 
         fontsize = 6, 
         fontcolor = "#A9A9A9",
         x = 0.75, 
         y = 8.375, 
         just = c("left", "top"),
         default.units = "inches")

plotText(label = "mDAN D15", 
         fontsize = 6, 
         fontcolor = "#B22222",
         x = 0.75, 
         y = 8.75, 
         just = c("left", "top"),
         default.units = "inches")

plotText(label = "mDAN D30", 
         fontsize = 6, 
         fontcolor = "#DC143C",
         x = 0.75, 
         y = 9.125, 
         just = c("left", "top"),
         default.units = "inches")

plotText(label = "mDAN D50", 
         fontsize = 6, 
         fontcolor = "#E9967A",
         x = 0.75, 
         y = 9.5, 
         just = c("left", "top"),
         default.units = "inches")

# text F
plotText(label = "F", 
         fontsize = 12,
         x = 5.0, 
         y = 8.0, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

SCARB2.NR2C2.exp = ggboxplot(dat.RPKM.filt %>% 
                            dplyr::filter(gene_name %in% c("SCARB2", "NR2C2", "FAM47E")) %>% 
                              mutate(gene_name = factor(gene_name,
                                                        levels = c("SCARB2", "NR2C2", "FAM47E"))),
                          x = "Cond", 
                          y = "RPKM", 
                          add = "jitter", 
                          fill = "Cond", 
                          palette = c("#A9A9A9", "#B22222", "#DC143C", "#E9967A"),
                          facet.by = "gene_name",
                          xlab = "", 
                          ylab = "Reads Per Kilobase Million (RPKM)") +
  scale_x_discrete(labels = c("smNPC",
                              "mDAN D15",
                              "mDAN D30",
                              "mDAN D50")) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))

# Place the plot
plotGG(plot = SCARB2.NR2C2.exp, 
       x = 5.25, 
       y = 7.875, 
       width = 3, 
       height = 3.5,
       just = c("left", "top"), 
       default.units = "inches")

# Add the transcription factor binding motif (TFBS) for NR2C2
pfm.NR2C2 = getMatrixByID(JASPAR2020, 
                         ID = "MA1536.1")

# Reverse to position weight matrix as the SNP is on the reverse strand
pfm.NR2C2 = reverseComplement(pfm.NR2C2)

NR2C2 = new.env()

NR2C2$NR2C2 = pfm.NR2C2@profileMatrix

NR2C2 = as.list(NR2C2)
NR2C2_TFBS = ggseqlogo(NR2C2)

# Place the plot
plotGG(plot = NR2C2_TFBS, 
       x = 1.6875, 
       y = 10.375, 
       width = 1.5, 
       height = 1.5,
       just = c("left", "top"), 
       default.units = "inches")

dev.off()
```

### FIGURE 3
```{r fig3, eval = FALSE, echo = TRUE}
########## FIGURE 3 ##########
##############################
# Save as a PDF and as TIF
pdf("/home/vagrant/Manuscript_1/FIGURE3/FIGURE3.pdf",
    paper = "a4",
    family = "Helvetica")

# Save as TIFF, 300 dpi
tiff("/home/vagrant/Manuscript_1/FIGURE3/FIGURE3.tiff",
     width = 8.27,
     height = 11.67,
     units = "in",
     res = 300)

# Create a A4 blank page
pageCreate(width = 8.27, 
           height = 11.67, 
           default.units = "inches",
           showGuides = TRUE)

# text Figure 3
plotText(label = "Figure 3", 
         fontsize = 14,
         fontface = "bold",
         fontfamily = "Helvetica",
         x = 0.25, 
         y = 0.25, 
         just = "left", 
         default.units = "inches")

#### PANEL A - Scheme of transduction for knockdown and luciferase
# text A
plotText(label = "A", 
         fontsize = 12,
         fontface = "bold",
         fontfamily = "Helvetica",
         x = 0.25, 
         y = 0.5, 
         just = "left", 
         default.units = "inches")

#### PANEL B - luciferase barplots with statistics
# text B
plotText(label = "B", 
         fontsize = 12,
         fontface = "bold",
         fontfamily = "Helvetica",
         x = 0.25, 
         y = 2.0, 
         just = "left", 
         default.units = "inches")

Gluc_signal = tibble(Sample = c("BAG3-WT", "BAG3-MUT", "IDUA-WT", "IDUA-MUT", "SCARB2-WT", "SCARB2-MUT", "miniCMV", "Neg_CTRL"),
                     GLUC_n1_rep1 = c(319, 240, 154, 196, 379, 211, 431, 33),
                     GLUC_n1_rep2 = c(323, 237, 161, 205, 371, 224, 459, 33),
                     GLUC_n2_rep1 = c(201, 143, 121, 128, 278, 172, 253, 31),
                     GLUC_n2_rep2 = c(191, 149, 119, 126, 278, 162, 249, 31),
                     GLUC_n3_rep1 = c(249, 146, 136, 142, 223, 175, 212, 32),
                     GLUC_n3_rep2 = c(203, 152, 121, 125, 209, 168, 190, 33),
                     GLUC_n4_rep1 = c(348, 333, 220, 185, 396, 244, 319, 31),
                     GLUC_n4_rep2 = c(322, 306, 229, 186, 369, 227, 294, 32),
                     SEAP_n1_rep1 = c(72, 78, 54, 67, 99, 75, 128, 32),
                     SEAP_n1_rep2 = c(69, 70, 49, 66, 97, 79, 132, 29),
                     SEAP_n2_rep1 = c(50, 52, 45, 45, 76, 64, 80, 32),
                     SEAP_n2_rep2 = c(50, 52, 45, 51, 85, 63, 80, 32),
                     SEAP_n3_rep1 = c(52, 50, 43, 50, 66, 55, 68, 32),
                     SEAP_n3_rep2 = c(49, 53, 48, 46, 66, 62, 69, 31),
                     SEAP_n4_rep1 = c(64, 75, 58, 54, 103, 75, 111, 33),
                     SEAP_n4_rep2 = c(61, 74, 62, 56, 108, 77, 111, 31)) %>% 
  pivot_longer(!Sample, names_to = "Meas", values_to = "Abs_val") %>% 
  mutate(Meas2 = gsub("^([^_]*_[^_]*)_.*", "\\1", Meas)) %>% 
  group_by(Sample, Meas2) %>% 
  mutate(AVG = mean(Abs_val, na.rm = TRUE))

# Calculate ratio Gluc over SEAP
Gluc_signal_ratio = Gluc_signal %>% 
  dplyr::select(-Meas, -Abs_val) %>% 
  distinct(Meas2, .keep_all = TRUE) %>% 
  pivot_wider(names_from = "Meas2", values_from = "AVG") %>% 
  mutate(Ratio_within_bio_rep1 = GLUC_n1/SEAP_n1,
         Ratio_within_bio_rep2 = GLUC_n2/SEAP_n2,
         Ratio_within_bio_rep3 = GLUC_n3/SEAP_n3,
         Ratio_within_bio_rep4 = GLUC_n4/SEAP_n4) %>% 
  dplyr::select(Sample, Ratio_within_bio_rep1:Ratio_within_bio_rep4) %>% 
  pivot_longer(cols = c("Ratio_within_bio_rep1", "Ratio_within_bio_rep2", "Ratio_within_bio_rep3",
                        "Ratio_within_bio_rep4"),
               names_to = "Ratio",
               values_to = "value") %>% 
  mutate(Genes = gsub("(.*)-.*", "\\1", Sample))

# Calculate statistics - T-test
GLUC_stat = compare_means(value ~ Sample,
                          data = Gluc_signal_ratio %>% 
                            ungroup(),
                          method = "t.test")

# Plot for BAG3
GLUC_BAG3 = ggbarplot(Gluc_signal_ratio %>% 
                        dplyr::filter(Sample %in% c("BAG3-WT",
                                                     "BAG3-MUT",
                                                     "miniCMV",
                                                     "Neg_CTRL")), 
                      x = "Sample", 
                      y = "value",
                      width = 0.25,
                      add = c("mean_se", 
                              "jitter"),
                      fill = "grey",
                      xlab = "",
                      ylab = "Ratio Gluc/SEAP",
                      position = position_dodge(0.9)) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90, hjust = 1.0, size = 9, face = "bold", family = "Helvetica"),
        axis.text.y = element_text(size = 9, face = "bold"),
        axis.title.y = element_text(size = 10, face = "bold")) +
  scale_y_continuous(expand = c(0, 0),
                     limits = c(0, 6.0)) +
  scale_x_discrete(labels = c("BAG3 other allele",
                              "BAG3 effect allele",
                              "Positive control",
                              "Negative control")) +
  stat_pvalue_manual(GLUC_stat %>% 
                       dplyr::filter(group1 == "BAG3-WT",
                              group2 == "BAG3-MUT"),
                     label = "p = {p.format}",
                     y.position = 5.6,
                     size = 3.0)

# Place the plot
plotGG(plot = GLUC_BAG3, 
       x = 0.50, 
       y = 2.25, 
       width = 2, 
       height = 4.25,
       just = c("left", "top"), 
       default.units = "inches")

# Plot for IDUA
GLUC_IDUA = ggbarplot(Gluc_signal_ratio %>% 
                        dplyr::filter(Sample %in% c("IDUA-WT",
                                                    "IDUA-MUT",
                                                    "miniCMV",
                                                    "Neg_CTRL")), 
                      x = "Sample", 
                      y = "value",
          width = 0.25,
          add = c("mean_se", 
                  "jitter"),
          fill = "grey",
          xlab = "",
          ylab = "Ratio Gluc/SEAP",
          position = position_dodge(0.9)) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90, hjust = 1.0, size = 9, face = "bold"),
        axis.text.y = element_text(size = 9, face = "bold"),
        axis.title.y = element_text(size = 10, face = "bold")) +
  scale_x_discrete(labels = c("IDUA other allele",
                              "IDUA effect allele",
                              "Positive control",
                              "Negative control")) +
  scale_y_continuous(expand = c(0, 0),
                     limits = c(0, 6.0)) +
  stat_pvalue_manual(GLUC_stat %>% 
                       dplyr::filter(group1 == "IDUA-WT",
                              group2 == "IDUA-MUT"),
                     label = "p = {p.format}",
                     y.position = 4.0,
                     size = 3.0)

# Place the plot
plotGG(plot = GLUC_IDUA, 
       x = 3.0, 
       y = 2.25, 
       width = 2, 
       height = 4.25,
       just = c("left", "top"), 
       default.units = "inches")

# Plot for SCARB2
GLUC_SCARB2 = ggbarplot(Gluc_signal_ratio %>% 
                          dplyr::filter(Sample %in% c("SCARB2-WT",
                                                     "SCARB2-MUT",
                                                     "miniCMV",
                                                     "Neg_CTRL")), 
                        x = "Sample", 
                        y = "value",
          width = 0.25,
          add = c("mean_se", 
                  "jitter"),
          fill = "grey",
          xlab = "",
          ylab = "Ratio Gluc/SEAP",
          position = position_dodge(0.9)) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90, hjust = 1.0, size = 9, face = "bold"),
        axis.text.y = element_text(size = 9, face = "bold"),
        axis.title.y = element_text(size = 10, face = "bold")) +
  scale_x_discrete(labels = c("SCARB2 other allele",
                              "SCARB2 effect allele",
                              "Positive control",
                              "Negative control")) +
  scale_y_continuous(expand = c(0, 0),
                     limits = c(0, 6.0)) +
  stat_pvalue_manual(GLUC_stat %>% 
                       dplyr::filter(group1 == "SCARB2-WT",
                              group2 == "SCARB2-MUT"),
                     label = "p = {p.format}",
                     y.position = 4.0,
                      size = 3.0)

# Place the plot
plotGG(plot = GLUC_SCARB2, 
       x = 5.5, 
       y = 2.25, 
       width = 2, 
       height = 4.25,
       just = c("left", "top"), 
       default.units = "inches")

#### PANEL C - knockdown barplots with statistics
# text C
plotText(label = "C", 
         fontsize = 12,
         x = 0.25, 
         y = 6.75, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

# Knockdown of LHX1 and quantification of LHX1 and BAG3 expression 3 days post transduction
KD.BAG3.LHX1.3days = tibble(Sple = rep("shLHX1", 6),
                            Gene = c(rep("LHX1", 3),
                                     rep("BAG3", 3)),
                            Exp = c(0.411253539,
                                    0.359459217,
                                    0.367190337,
                                    0.972688658,
                                    0.965902853,
                                    0.88813445))

# Stats
KD.BAG3.LHX1.3days.stats = tibble(Sple = c(rep("shLHX1", 6),
                                           rep("shCTRL", 6)),
                                  Gene = rep(c(rep("LHX1", 3),
                                           rep("BAG3", 3)), 2),
                                  Exp = c(9.5167,
                                          8.39675,
                                          8.1855,
                                          9.13605,
                                          8.33795,
                                          8.76415,
                                          8.2348,
                                          6.92065,
                                          6.7401,
                                          9.0961,
                                          8.2879,
                                          8.593))

stat_LHX1.KD = compare_means(Exp ~ Sple,
                          data = KD.BAG3.LHX1.3days.stats,
                          group.by = "Gene",
                          method = "t.test",
                          paired = TRUE)
# Plot
pl.KD_BAG3_LHX1 = KD.BAG3.LHX1.3days %>% 
  mutate(Gene = factor(Gene, levels = c("LHX1", "BAG3"))) %>% 
  ggbarplot(.,
            x = "Gene",
            y = "Exp",
            fill = c("Gene"),
            position = position_dodge(0.9),
            palette = c("#440154FF", "#287C8EFF"),
            add = c("mean_se", "jitter"),
            xlab = "",
            ylab = "Relative expression to shSCRAMBLE",
            title = "shLHX1 - 3 days") +
  geom_hline(yintercept = 1.0, lty = "dashed", color = "black") +
  theme(axis.title.y = element_text(face = "bold", size = 10),
        axis.text.x = element_text(face = "bold.italic", size = 10, angle = 90, family = "Helvetica"),
        axis.text.y = element_text(face = "bold", size = 10),
        legend.position = "none",
        plot.title = element_text(face = "bold", size = 10, hjust = 0.5)) +
  scale_y_continuous(expand = c(0, 0),
                     limits = c(0, 1.8)) +
  stat_pvalue_manual(stat_LHX1.KD,
                     label = "p = {p.format}",
                     x = "Gene",
                     y.position = 0.5,
                     size = 3.0,
                     hide.ns = TRUE)

plotGG(plot = pl.KD_BAG3_LHX1, 
       x = 0.5, 
       y = 7.0, 
       width = 1.75, 
       height = 4.25,
       just = c("left", "top"), 
       default.units = "inches")

# Knockdown of ZBTB14 and quantification of ZBTB14 and IDUA expression 3 days post transduction
KD.IDUA.ZBTB14.3days = tibble(Sple = rep("shZBTB14", 6),
                            Gene = c(rep("ZBTB14", 3),
                                     rep("IDUA", 3)),
                            Exp = c(0.334134302,
                                    0.316834205,
                                    0.294206291,
                                    0.663813558,
                                    1.259979272,
                                    1.774054093))

# Stats
KD.IDUA.ZBTB14.3days.stats = tibble(Sple = c(rep("shZBTB14", 6),
                                           rep("shCTRL", 6)),
                                  Gene = rep(c(rep("ZBTB14", 3),
                                           rep("IDUA", 3)), 2),
                                  Exp = c(11.39125,
                                          10.4813,
                                          10.5062,
                                          11.56275,
                                          10.1455,
                                          9.76485,
                                          9.80975,
                                          8.8231,
                                          8.7411,
                                          10.9716,
                                          10.4789,
                                          10.5919))

stat_ZBTB14.KD = compare_means(Exp ~ Sple,
                          data = KD.IDUA.ZBTB14.3days.stats,
                          group.by = "Gene",
                          method = "t.test",
                          paired = TRUE)

# Plot
pl.KD_IDUA_ZBTB14 = KD.IDUA.ZBTB14.3days %>% 
  mutate(Gene = factor(Gene, levels = c("ZBTB14", "IDUA"))) %>% 
  ggbarplot(.,
            x = "Gene",
            y = "Exp",
            fill = c("Gene"),
            position = position_dodge(0.9),
            palette = c("#440154FF", "#287C8EFF"),
            add = c("mean_se", "jitter"),
            xlab = "",
            ylab = "Relative expression to shSCRAMBLE",
            title = "shZBTB14 - 3 days") +
  geom_hline(yintercept = 1.0, lty = "dashed", color = "black") +
  theme(axis.title.y = element_text(face = "bold", size = 10),
        axis.text.x = element_text(face = "bold.italic", size = 10, angle = 90, family = "Helvetica"),
        axis.text.y = element_text(face = "bold", size = 10),
        legend.position = "none",
        plot.title = element_text(face = "bold", size = 10, hjust = 0.5)) +
  scale_y_continuous(expand = c(0, 0),
                     limits = c(0, 1.8)) +
  stat_pvalue_manual(stat_ZBTB14.KD,
                     label = "p = {p.format}",
                     x = "Gene",
                     y.position = 0.5,
                     size = 3.0,
                     hide.ns = TRUE)

plotGG(plot = pl.KD_IDUA_ZBTB14, 
       x = 2.375, 
       y = 7.0, 
       width = 1.75, 
       height = 4.25,
       just = c("left", "top"), 
       default.units = "inches")

# Knockdown of NR2C2 and quantification of NR2C2 and SCARB2 expression 3 days post transduction
KD.SCARB2.NR2C2.3days = tibble(Sple = rep("shNR2C2", 6),
                            Gene = c(rep("NR2C2", 3),
                                     rep("SCARB2", 3)),
                            Exp = c(0.345210918,
                                    0.512864636,
                                    0.548665969,
                                    1.239922544,
                                    1.130295504,
                                    1.170885498))

# Stats
KD.SCARB2.NR2C2.3days.stats = tibble(Sple = c(rep("shNR2C2", 6),
                                           rep("shCTRL", 6)),
                                  Gene = rep(c(rep("NR2C2", 3),
                                           rep("SCARB2", 3)), 2),
                                  Exp = c(9.43575,
                                          9.3043,
                                          9.263,
                                          5.6841,
                                          5.92295,
                                          5.9289,
                                          7.9013,
                                          8.34095,
                                          8.397,
                                          5.99435,
                                          6.09965,
                                          6.1565))

stat_NR2C2.KD = compare_means(Exp ~ Sple,
                          data = KD.SCARB2.NR2C2.3days.stats,
                          group.by = "Gene",
                          method = "t.test",
                          paired = TRUE)

# Plot
pl.KD_SCARB2_NR2C2 = KD.SCARB2.NR2C2.3days %>% 
  mutate(Gene = factor(Gene, levels = c("NR2C2", "SCARB2"))) %>% 
  ggbarplot(.,
            x = "Gene",
            y = "Exp",
            fill = c("Gene"),
            position = position_dodge(0.9),
            palette = c("#440154FF", "#287C8EFF"),
            add = c("mean_se", "jitter"),
            xlab = "",
            ylab = "Relative expression to shSCRAMBLE",
            title = "shNR2C2 - 3 days") +
  geom_hline(yintercept = 1.0, lty = "dashed", color = "black") +
  theme(axis.title.y = element_text(face = "bold", size = 10),
        axis.text.x = element_text(face = "bold.italic", size = 10, angle = 90, family = "Helvetica"),
        axis.text.y = element_text(face = "bold", size = 10),
        legend.position = "none",
        plot.title = element_text(face = "bold", size = 10, hjust = 0.5)) +
  scale_y_continuous(expand = c(0, 0),
                     limits = c(0, 1.8)) +
  stat_pvalue_manual(stat_NR2C2.KD,
                     label = "p = {p.format}",
                     x = "Gene",
                     y.position = 1.5,
                     size = 3.0)

plotGG(plot = pl.KD_SCARB2_NR2C2, 
       x = 4.25, 
       y = 7.0, 
       width = 1.75, 
       height = 4.25,
       just = c("left", "top"), 
       default.units = "inches")

# Knockdown of NR2C2 and quantification of NR2C2 and SCARB2 expression 6 days post transduction
KD.SCARB2.NR2C2.6days = tibble(Sple = rep("shNR2C2", 6),
                            Gene = c(rep("NR2C2", 3),
                                     rep("SCARB2", 3)),
                            Exp = c(0.662710186,
                                    0.456029798,
                                    0.787662775,
                                    1.410640142,
                                    1.425976296,
                                    1.332143962))

# Stats
KD.SCARB2.NR2C2.6days.stats = tibble(Sple = c(rep("shNR2C2", 6),
                                           rep("shCTRL", 6)),
                                  Gene = rep(c(rep("NR2C2", 3),
                                           rep("SCARB2", 3)), 2),
                                  Exp = c(8.34355,
                                          9.0917,
                                          8.32445,
                                          5.3595,
                                          5.19535,
                                          6.5266,
                                          7.75,
                                          7.9589,
                                          7.9801,
                                          5.85585,
                                          5.7073,
                                          6.94035))

stat_NR2C2.KD.6days = compare_means(Exp ~ Sple,
                          data = KD.SCARB2.NR2C2.6days.stats,
                          group.by = "Gene",
                          method = "t.test",
                          paired = TRUE)

# Plot
pl.KD_SCARB2_NR2C2_6days = KD.SCARB2.NR2C2.6days %>% 
  mutate(Gene = factor(Gene, levels = c("NR2C2", "SCARB2"))) %>% 
  ggbarplot(.,
            x = "Gene",
            y = "Exp",
            fill = c("Gene"),
            position = position_dodge(0.9),
            palette = c("#440154FF", "#287C8EFF"),
            add = c("mean_se", "jitter"),
            xlab = "",
            ylab = "Relative expression to shSCRAMBLE",
            title = "shNR2C2 - 6 days") +
  geom_hline(yintercept = 1.0, lty = "dashed", color = "black") +
  theme(axis.title.y = element_text(face = "bold", size = 10),
        axis.text.x = element_text(face = "bold.italic", size = 10, angle = 90, family = "Helvetica"),
        axis.text.y = element_text(face = "bold", size = 10),
        legend.position = "none",
        plot.title = element_text(face = "bold", size = 10, hjust = 0.5)) +
  scale_y_continuous(expand = c(0, 0),
                     limits = c(0, 1.8)) +
  stat_pvalue_manual(stat_NR2C2.KD.6days,
                     label = "p = {p.format}",
                     x = "Gene",
                     y.position = 1.5,
                     size = 3.0,
                     hide.ns = TRUE)

plotGG(plot = pl.KD_SCARB2_NR2C2_6days, 
       x = 6.125, 
       y = 7.0, 
       width = 1.75, 
       height = 4.25,
       just = c("left", "top"), 
       default.units = "inches")

dev.off()
```

### FIGURE 4
```{r fig4, eval = FALSE, echo = TRUE}
########## FIGURE 4 ##########
##############################
# Save as a PDF
pdf("/home/vagrant/Manuscript_1/FIGURE4/FIGURE4.pdf",
    width = 8.3, 
    height = 11.7)

# Save as TIFF, 300 dpi
tiff("/home/vagrant/Manuscript_1/FIGURE4/FIGURE4.tiff",
     width = 8.27,
     height = 11.67,
     units = "in",
     res = 300)

# Create a A4 blank page
pageCreate(width = 8.27, 
           height = 11.67, 
           default.units = "inches",
           showGuides = TRUE)

plotText(label = "Figure 4", 
         fontsize = 14,
         fontface = "bold",
         fontfamily = "Helvetica",
         x = 0.25, 
         y = 0.25, 
         just = "left", 
         default.units = "inches")

#### PANEL A - Chromatin imbalance in TH REP1 mCHERRY cell line at rs1465922 
# text A
plotText(label = "A", 
         fontsize = 12,
         fontface = "bold",
         fontfamily = "Helvetica",
         x = 0.25, 
         y = 0.5, 
         just = "left", 
         default.units = "inches")

#FIG 4A
AI_RNA = tibble(Samples = 
                  c("smNPCs", "Neurons positively sorted D15", "Neurons positively sorted D30",
                    "Neurons positively sorted D50", "Astrocytes"),
                A = c(5, 23, 77, 56, 30),
                G = c(8, 4, 62, 34, 47)) %>% 
  gather(-Samples, key = "Base", value = "Reads")

AI_ATAC = tibble(Samples = 
                  c("smNPCs", "mDAN D15", "mDAN D30",
                    "mDAN D50", "Astrocytes"),
                A = c(31, 195, 202, 118, 155),
                G = c(39, 263, 264, 196, 179)) %>% 
  gather(-Samples, key = "Base", value = "Reads")

AI = AI_ATAC %>% 
  bind_rows(AI_RNA) %>% 
  mutate(Cond = rep(c("ATAC", "RNA"), each = 10))

# Good looking plot
chrom_AI = ggbarplot(AI_ATAC, x = "Samples", y = "Reads",
          fill = "Base",
          position = position_dodge(0.7),
          xlab = "", ylab = "Reads",
          #title = "Allelic imbalance at chr4:76213717 - SNP in SCARB2 promoter",
          label = c(0.3, 0.001, 0.004, 1e-5, 0.2,
                    rep("", 5)),
          label.pos = "out",
          lab.size = 3) +
  theme(legend.position = "right",
        axis.text.x = element_text(angle = 45, hjust = 1.0, face = "bold", size = 10),
        axis.text.y = element_text(face = "bold", size = 10),
        axis.title.y = element_text(face = "bold", size = 10),
        legend.text = element_text(face = "bold", size = 10),
        legend.title = element_text(face = "bold", size = 10)) +
        # title = element_text(hjust = 0.5)) +
  scale_fill_manual(values = c("#80A44F", "#427F96"))

plotGG(plot = chrom_AI, 
       x = 0.5, 
       y = 0.75, 
       width = 6, 
       height = 4,
       just = c("left", "top"), 
       default.units = "inches")

# text B
plotText(label = "B", 
         fontsize = 12,
         x = 0.25, 
         y = 5.0, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

GTEX_SNPs_interest = read_delim("/home/vagrant/epifunc/eQTpLot/20230117_GTEX_data.csv",
               delim = ";",
               col_names = TRUE)

GTEX_SNPs_SCARB2_brain = GTEX_SNPs_interest %>% 
  mutate(GTEX_sig = if_else(P.Value < 0.05, "*", "")) %>% 
  filter(str_detect(Tissue, "Brain"),
         Gene.Symbol == "SCARB2")

GTEX_eqtl = ggplot(data = GTEX_SNPs_SCARB2_brain, mapping = aes(x = SNP.Id,
                                                y = Tissue,
                                                fill = NES)) + 
  geom_tile() +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1, face = "bold", size = 10),
        axis.title.x = element_blank(),
        axis.text.y = element_text(face = "bold", size = 10),
        axis.title.y = element_blank(),
        legend.text = element_text(face = "bold", size = 10),
        legend.title = element_text(face = "bold", size = 10)) +
  scale_fill_gradient2(
    low = muted("blue"),
    mid = "white",
    high = muted("red"),
    midpoint = 0,
    name = "eQTL \neffect size") +
  geom_text(aes(label = GTEX_sig))

plotGG(plot = GTEX_eqtl, 
       x = 0.5, 
       y = 5.25, 
       width = 7, 
       height = 6,
       just = c("left", "top"), 
       default.units = "inches")

dev.off()
```

### FIGURE 5
```{r fig5, eval = FALSE, echo = TRUE}
########## FIGURE 5 ##########
##############################
# Save as a PDF
pdf("/home/vagrant/Manuscript_1/FIGURE5/FIGURE5.pdf",
    width = 8.3, 
    height = 11.7)

# Create a A4 blank page
pageCreate(width = 8.3, 
           height = 11.7, 
           default.units = "inches",
           showGuides = FALSE)

#### PANEL A - 
# text Figure 5
plotText(label = "Figure 5", 
         fontsize = 14,
         x = 0.25, 
         y = 0.25, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")
# text A
plotText(label = "A", 
         fontsize = 12,
         x = 0.25, 
         y = 0.5, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

KD_TH_lev = tibble(Sple = rep("shNR2C2", 3),
                   Rep = 1:3,
                   days = "6 days",
                   Gene = "TH",
                   Exp = c(1.705920009,
                           2.196566231,
                           1.107610012))

#TH levels in knockdown of NR2C2 6 days#
TH_lev_KD = KD_TH_lev %>% 
  ggbarplot(.,
            x = "Gene",
            y = "Exp",
            fill = c("days"),
            facet.by = "Sple",
            position = position_dodge(0.9),
            palette = c("#287C8EFF"),
            add = c("mean_se"),
            xlab = "",
            ylab = "Relative expression to shSCRAMBLE") +
  geom_hline(yintercept = 1.0, lty = "dashed", color = "black") +
  theme(axis.title.y = element_text(face = "bold", size = 10),
        axis.text.x = element_text(face = "bold", size = 10, angle = 90),
        axis.text.y = element_text(face = "bold", size = 10),
        legend.position = "none")

plotGG(plot = TH_lev_KD, 
       x = 0.5, 
       y = 0.5, 
       width = 2, 
       height = 4.25,
       just = c("left", "top"), 
       default.units = "inches")

### DEXOMAG - 3 biological repliactes ###
GCase = read_excel("/Volumes/deborah.gerard/Documents/Wetlab/epifunc/DEXOMAG_shSCARB2_shNR2C2_shCTRL_N1_N2_N3/20231214_DEXOMAG_KD_SCARB2_NR2C2_SCRAMBLE_N1_N2_N3_ANALYSIS.xlsx")

GCase %>% 
  dplyr::select(GCase, `GCase MEAN`, ...10, ...11) %>% 
  drop_na() %>% 
  dplyr::rename(Sample = GCase,
                N1 = `GCase MEAN`,
                N2 = ...10,
                N3 = ...11) %>% 
  pivot_longer(N1:N3, names_to = "Rep.bio", values_to = "norm.fluo.value") %>% 
  mutate(norm.fluo.value = as.numeric(norm.fluo.value)) %>% 
  #dplyr::filter(Sample != "Whole Gcase NT") %>% 
  ggbarplot(.,
            x = "Sample",
            y = "norm.fluo.value",
            add = c("mean_se", "jitter"),
            xlab = "",
            ylab = "GCase activity (normalised fluorescence values)") +
  scale_x_discrete(labels = c("SCARB2 KD",
                              "NR2C2 KD",
                              "SCRAMBLE",
                              "Not transduced + dexomag",
                              "Not transduced - dexomag",
                              "Whole cell lysate")) +
  theme(axis.text.x = element_text(angle = 45, face = "bold", hjust = 1.0),
        axis.text.y = element_text(face = "bold"),
        axis.title.y = element_text(face = "bold")) +
  stat_compare_means(comparisons = list(c("shSCARB2", "shSCRAMBLE")),
                     method = "t.test",
                     size = 4,
                     label = "p.format") +
  stat_compare_means(comparisons = list(c("shNR2C2", "shSCRAMBLE")),
                     method = "t.test",
                     size = 4,
                     label = "p.format")

dev.off()
```

### SUPPLEMENTARY FIGURE 1
IHEC consortium has one sample of substantia nigra for H3K27me3, H3K9me3, H3K4me1, H3K4me3 and H3K36me3 from a healthy brain for BAG3, IDUA and SCARB2 loci
```{r suppFig1, eval = FALSE, echo = TRUE}
############################################
########## SUPPLEMENTARY FIGURE 1 ##########
############################################

# Save as a PDF
pdf("/home/vagrant/Manuscript_1/SUPPLEMENTARY_FIGURE1/SUPPLEMENTARY_FIGURE1.pdf",
    width = 8.3, 
    height = 11.7)

# Create a A4 blank page
pageCreate(width = 8.3, 
           height = 11.7, 
           default.units = "inches",
           showGuides = TRUE)

#### PANEL A - 
# text Supplementary Figure 1
plotText(label = "Supplementary Figure 1", 
         fontsize = 14,
         x = 0.25, 
         y = 0.25, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")
# text A
plotText(label = "A", 
         fontsize = 12,
         x = 0.25, 
         y = 0.5, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

# ChIP-seq signal BAG3
# path where bigwig files are
bw.IHEC.path = "/home/vagrant/Documents/IHEC/ChIP_Seq/BIGWIG/"

# Reads BIGWIG file at BAG3 location - H3K4me1
bw.BAG3.H3K4me1 = readBigwig(file = paste0(bw.IHEC.path,
                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6a1889bf-7312-4e41-b1cc-e2f3be7a8076.fc.signal.bigwig"),
                               chrom = "chr10",
                               chromstart = 119611305,
                               chromend = 119691505)

# Reads BIGWIG file at BAG3 location - H3K4me3
bw.BAG3.H3K4me3 = readBigwig(file = paste0(bw.IHEC.path,
                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.4cb9300f-9097-4374-8f2a-4afd8ff855fb.fc.signal.bigwig"),
                               chrom = "chr10",
                               chromstart = 119611305,
                               chromend = 119691505)

# Reads BIGWIG file at BAG3 location - H3K36me3
bw.BAG3.H3K36me3 = readBigwig(file = paste0(bw.IHEC.path,
                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6586e624-852f-4cac-83df-2325cee19699.fc.signal.bigwig"),
                               chrom = "chr10",
                               chromstart = 119611305,
                               chromend = 119691505)

# Reads BIGWIG file at BAG3 location - H3K9me3
bw.BAG3.H3K9me3 = readBigwig(file = paste0(bw.IHEC.path,
                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.e8fe7664-906e-4d87-8f3a-6ce88dbeadc6.fc.signal.bigwig"),
                               chrom = "chr10",
                               chromstart = 119611305,
                               chromend = 119691505)

# Reads BIGWIG file at BAG3 location - H3K27me3
bw.BAG3.H3K27me3 = readBigwig(file = paste0(bw.IHEC.path,
                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.5f5024a9-2e3f-4527-82ec-0ed04bf4a848.fc.signal.bigwig"),
                               chrom = "chr10",
                               chromstart = 119611305,
                               chromend = 119691505)

# Add a scale next to the bigwig files - check the maximum to choose
scale.IHEC.BAG3.max = max(c(bw.BAG3.H3K4me1$score,
                              bw.BAG3.H3K4me3$score,
                              bw.BAG3.H3K36me3$score,
                              bw.BAG3.H3K9me3$score,
                              bw.BAG3.H3K27me3$score)) %>% 
  round(.,
        digits = 1.0)

print(scale.IHEC.BAG3.max)

# Define parameters for the regions
region.p.IHEC.BAG3 = pgParams(chrom = "chr10",
                         chromstart = 119611405,
                         chromend = 119691405,
                         assembly = "hg38",
                         range = c(0, scale.IHEC.BAG3.max))

# Add the genomic label
plotGenomeLabel(
  chrom = "chr10",
  chromstart = 119611405,
  chromend = 119691405,
  assembly = "hg38",
  x = 0.75,
  y = 0.625,
  length = 4.0,
  default.units = "inches",
  scale = "Mb")

# ChIPseq signal H3K4me1
H3K4me1_BAG3 = plotSignal(
  data = bw.BAG3.H3K4me1, 
  params = region.p.IHEC.BAG3,
  fill = "#b5de2b", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 0.875, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = H3K4me1_BAG3, 
          at = c(0, scale.IHEC.BAG3.max),
          fontsize = 6)

# ChIPseq signal H3K4me3
H3K4me3_BAG3 = plotSignal(
  data = bw.BAG3.H3K4me3, 
  params = region.p.IHEC.BAG3,
  fill = "#35b779", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 1.25, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = H3K4me3_BAG3, 
          at = c(0, scale.IHEC.BAG3.max),
          fontsize = 6)

# ChIPseq signal H3K36me3
H3K36me3_BAG3 = plotSignal(
  data = bw.BAG3.H3K36me3, 
  params = region.p.IHEC.BAG3,
  fill = "#26828e", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 1.625, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = H3K36me3_BAG3, 
          at = c(0, scale.IHEC.BAG3.max),
          fontsize = 6)

# ChIPseq signal H3K9me3
H3K9me3_BAG3 = plotSignal(
  data = bw.BAG3.H3K9me3, 
  params = region.p.IHEC.BAG3,
  fill = "#3e4989", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 2.0, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = H3K9me3_BAG3, 
          at = c(0, scale.IHEC.BAG3.max),
          fontsize = 6)

# ChIPseq signal H3K27me3
H3K27me3_BAG3 = plotSignal(
  data = bw.BAG3.H3K27me3, 
  params = region.p.IHEC.BAG3,
  fill = "#440154", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 2.375, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = H3K27me3_BAG3, 
          at = c(0, scale.IHEC.BAG3.max),
          fontsize = 6)

# Gene track
plotGenes(
  chrom = "chr10",
  chromstart = 119611405,
  chromend = 119691405,
  assembly = assembly(Genome = "hg38refGene", 
                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
                      OrgDb = "org.Hs.eg.db"),
  fontcolor = "black",
  fill = "black",
  x = 0.75,
  y = 2.75,
  width = 4.0,
  height = 0.375,
  just = c("left", "top"),
  default.units = "inches")

# Add the samples name
plotText(label = "H3K4me1", 
         fontsize = 6, 
         fontcolor = "#b5de2b",
         x = 0.75,
         y = 0.875, 
         just = c("left", "top"),
         default.units = "inches")

# Add the samples name
plotText(label = "H3K4me3", 
         fontsize = 6, 
         fontcolor = "#35b779",
         x = 0.75,
         y = 1.25, 
         just = c("left", "top"),
         default.units = "inches")

# Add the samples name
plotText(label = "H3K36me3", 
         fontsize = 6, 
         fontcolor = "#26828e",
         x = 0.75,
         y = 1.625, 
         just = c("left", "top"),
         default.units = "inches")

# Add the samples name
plotText(label = "H3K9me3", 
         fontsize = 6, 
         fontcolor = "#3e4989",
         x = 0.75,
         y = 2.0, 
         just = c("left", "top"),
         default.units = "inches")

# Add the samples name
plotText(label = "H3K27me3", 
         fontsize = 6, 
         fontcolor = "#440154",
         x = 0.75,
         y = 2.375, 
         just = c("left", "top"),
         default.units = "inches")

# Reads BIGWIG file at IDUA location - H3K4me1
bw.IDUA.H3K4me1 = readBigwig(file = paste0(bw.IHEC.path,
                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6a1889bf-7312-4e41-b1cc-e2f3be7a8076.fc.signal.bigwig"),
                               chrom = "chr4",
                               chromstart = 947008,
                               chromend = 1027208)

# Reads BIGWIG file at IDUA location - H3K4me3
bw.IDUA.H3K4me3 = readBigwig(file = paste0(bw.IHEC.path,
                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.4cb9300f-9097-4374-8f2a-4afd8ff855fb.fc.signal.bigwig"),
                               chrom = "chr4",
                               chromstart = 947008,
                               chromend = 1027208)

# Reads BIGWIG file at IDUA location - H3K36me3
bw.IDUA.H3K36me3 = readBigwig(file = paste0(bw.IHEC.path,
                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6586e624-852f-4cac-83df-2325cee19699.fc.signal.bigwig"),
                               chrom = "chr4",
                               chromstart = 947008,
                               chromend = 1027208)

# Reads BIGWIG file at IDUA location - H3K9me3
bw.IDUA.H3K9me3 = readBigwig(file = paste0(bw.IHEC.path,
                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.e8fe7664-906e-4d87-8f3a-6ce88dbeadc6.fc.signal.bigwig"),
                               chrom = "chr4",
                               chromstart = 947008,
                               chromend = 1027208)

# Reads BIGWIG file at IDUA location - H3K27me3
bw.IDUA.H3K27me3 = readBigwig(file = paste0(bw.IHEC.path,
                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.5f5024a9-2e3f-4527-82ec-0ed04bf4a848.fc.signal.bigwig"),
                               chrom = "chr4",
                               chromstart = 947008,
                               chromend = 1027208)

# Add a scale next to the bigwig files - check the maximum to choose
scale.IHEC.IDUA.max = max(c(bw.IDUA.H3K4me1$score,
                              bw.IDUA.H3K4me3$score,
                              bw.IDUA.H3K36me3$score,
                              bw.IDUA.H3K9me3$score,
                              bw.IDUA.H3K27me3$score)) %>% 
  round(.,
        digits = 1.0)

print(scale.IHEC.IDUA.max)

# Define parameters for the regions
region.p.IHEC.IDUA = pgParams(chrom = "chr4",
                         chromstart = 947108,
                         chromend = 1027108,
                         assembly = "hg38",
                         range = c(0, scale.IHEC.IDUA.max))

# Add the genomic label
plotGenomeLabel(
  chrom = "chr4",
  chromstart = 947108,
  chromend = 1027108,
  assembly = "hg38",
  x = 0.75,
  y = 3.5,
  length = 4.0,
  default.units = "inches",
  scale = "Mb")

# ChIPseq signal H3K4me1
H3K4me1_IDUA = plotSignal(
  data = bw.IDUA.H3K4me1, 
  params = region.p.IHEC.IDUA,
  fill = "#b5de2b", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 3.75, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = H3K4me1_IDUA, 
          at = c(0, scale.IHEC.IDUA.max),
          fontsize = 6)

# ChIPseq signal H3K4me3
H3K4me3_IDUA = plotSignal(
  data = bw.IDUA.H3K4me3, 
  params = region.p.IHEC.IDUA,
  fill = "#35b779", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 4.125, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = H3K4me3_IDUA, 
          at = c(0, scale.IHEC.IDUA.max),
          fontsize = 6)

# ChIPseq signal H3K36me3
H3K36me3_IDUA = plotSignal(
  data = bw.IDUA.H3K36me3, 
  params = region.p.IHEC.IDUA,
  fill = "#26828e", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 4.5, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = H3K36me3_IDUA, 
          at = c(0, scale.IHEC.IDUA.max),
          fontsize = 6)

# ChIPseq signal H3K9me3
H3K9me3_IDUA = plotSignal(
  data = bw.IDUA.H3K9me3, 
  params = region.p.IHEC.IDUA,
  fill = "#3e4989", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 4.875, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = H3K9me3_IDUA, 
          at = c(0, scale.IHEC.IDUA.max),
          fontsize = 6)

# ChIPseq signal H3K27me3
H3K27me3_IDUA = plotSignal(
  data = bw.IDUA.H3K27me3, 
  params = region.p.IHEC.IDUA,
  fill = "#440154", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 5.25, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = H3K27me3_IDUA, 
          at = c(0, scale.IHEC.IDUA.max),
          fontsize = 6)

# Gene track
plotGenes(
  chrom = "chr4",
  chromstart = 947108,
  chromend = 1027108,
  assembly = assembly(Genome = "hg38refGene", 
                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
                      OrgDb = "org.Hs.eg.db"),
  fontcolor = "black",
  fill = "black",
  x = 0.75,
  y = 5.625,
  width = 4.0,
  height = 0.375,
  just = c("left", "top"),
  default.units = "inches")

# Add the samples name
plotText(label = "H3K4me1", 
         fontsize = 6, 
         fontcolor = "#b5de2b",
         x = 0.75,
         y = 3.75, 
         just = c("left", "top"),
         default.units = "inches")

# Add the samples name
plotText(label = "H3K4me3", 
         fontsize = 6, 
         fontcolor = "#35b779",
         x = 0.75,
         y = 4.125, 
         just = c("left", "top"),
         default.units = "inches")

# Add the samples name
plotText(label = "H3K36me3", 
         fontsize = 6, 
         fontcolor = "#26828e",
         x = 0.75,
         y = 4.5, 
         just = c("left", "top"),
         default.units = "inches")

# Add the samples name
plotText(label = "H3K9me3", 
         fontsize = 6, 
         fontcolor = "#3e4989",
         x = 0.75,
         y = 4.875, 
         just = c("left", "top"),
         default.units = "inches")

# Add the samples name
plotText(label = "H3K27me3", 
         fontsize = 6, 
         fontcolor = "#440154",
         x = 0.75,
         y = 5.25, 
         just = c("left", "top"),
         default.units = "inches")

# ChIP-seq signal SCARB2
# Reads BIGWIG file at SCARB2 location - H3K4me1
bw.SCARB2.H3K4me1 = readBigwig(file = paste0(bw.IHEC.path,
                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6a1889bf-7312-4e41-b1cc-e2f3be7a8076.fc.signal.bigwig"),
                               chrom = "chr4",
                               chromstart = 76173617,
                               chromend = 76253817)

# Reads BIGWIG file at SCARB2 location - H3K4me3
bw.SCARB2.H3K4me3 = readBigwig(file = paste0(bw.IHEC.path,
                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.4cb9300f-9097-4374-8f2a-4afd8ff855fb.fc.signal.bigwig"),
                               chrom = "chr4",
                               chromstart = 76173617,
                               chromend = 76253817)

# Reads BIGWIG file at SCARB2 location - H3K36me3
bw.SCARB2.H3K36me3 = readBigwig(file = paste0(bw.IHEC.path,
                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6586e624-852f-4cac-83df-2325cee19699.fc.signal.bigwig"),
                               chrom = "chr4",
                               chromstart = 76173617,
                               chromend = 76253817)

# Reads BIGWIG file at SCARB2 location - H3K9me3
bw.SCARB2.H3K9me3 = readBigwig(file = paste0(bw.IHEC.path,
                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.e8fe7664-906e-4d87-8f3a-6ce88dbeadc6.fc.signal.bigwig"),
                               chrom = "chr4",
                               chromstart = 76173617,
                               chromend = 76253817)

# Reads BIGWIG file at SCARB2 location - H3K27me3
bw.SCARB2.H3K27me3 = readBigwig(file = paste0(bw.IHEC.path,
                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.5f5024a9-2e3f-4527-82ec-0ed04bf4a848.fc.signal.bigwig"),
                               chrom = "chr4",
                               chromstart = 76173617,
                               chromend = 76253817)

# Add a scale next to the bigwig files - check the maximum to choose
scale.IHEC.SCARB2.max = max(c(bw.SCARB2.H3K4me1$score,
                              bw.SCARB2.H3K4me3$score,
                              bw.SCARB2.H3K36me3$score,
                              bw.SCARB2.H3K9me3$score,
                              bw.SCARB2.H3K27me3$score)) %>% 
  round(.,
        digits = 1.0)

print(scale.IHEC.SCARB2.max)

# Define parameters for the regions
region.p.IHEC.SCARB2 = pgParams(chrom = "chr4",
                         chromstart = 76173717,
                         chromend = 76253717,
                         assembly = "hg38",
                         range = c(0, scale.IHEC.SCARB2.max))

# Add the genomic label
plotGenomeLabel(
  chrom = "chr4",
  chromstart = 76173717,
  chromend = 76253717,
  assembly = "hg38",
  x = 0.75,
  y = 6.5,
  length = 4.0,
  default.units = "inches",
  scale = "Mb")

# ChIPseq signal H3K4me1
H3K4me1_SCARB2 = plotSignal(
  data = bw.SCARB2.H3K4me1, 
  params = region.p.IHEC.SCARB2,
  fill = "#b5de2b", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 6.75, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = H3K4me1_SCARB2, 
          at = c(0, scale.IHEC.SCARB2.max),
          fontsize = 6)

# ChIPseq signal H3K4me3
H3K4me3_SCARB2 = plotSignal(
  data = bw.SCARB2.H3K4me3, 
  params = region.p.IHEC.SCARB2,
  fill = "#35b779", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 7.125, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = H3K4me3_SCARB2, 
          at = c(0, scale.IHEC.SCARB2.max),
          fontsize = 6)

# ChIPseq signal H3K36me3
H3K36me3_SCARB2 = plotSignal(
  data = bw.SCARB2.H3K36me3, 
  params = region.p.IHEC.SCARB2,
  fill = "#26828e", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 7.5, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = H3K36me3_SCARB2, 
          at = c(0, scale.IHEC.SCARB2.max),
          fontsize = 6)

# ChIPseq signal H3K9me3
H3K9me3_SCARB2 = plotSignal(
  data = bw.SCARB2.H3K9me3, 
  params = region.p.IHEC.SCARB2,
  fill = "#3e4989", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 7.875, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = H3K9me3_SCARB2, 
          at = c(0, scale.IHEC.SCARB2.max),
          fontsize = 6)

# ChIPseq signal H3K27me3
H3K27me3_SCARB2 = plotSignal(
  data = bw.SCARB2.H3K27me3, 
  params = region.p.IHEC.SCARB2,
  fill = "#440154", 
  alpha = 0.7, 
  linecolor = NA,
  x = 0.75, 
  y = 8.25, 
  width = 4.0, 
  height = 0.25,
  just = c("left", "top"), 
  default.units = "inches")

annoYaxis(plot = H3K27me3_SCARB2, 
          at = c(0, scale.IHEC.SCARB2.max),
          fontsize = 6)

# Gene track
plotGenes(
  chrom = "chr4",
  chromstart = 76173717,
  chromend = 76253717,
  assembly = assembly(Genome = "hg38refGene", 
                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
                      OrgDb = "org.Hs.eg.db"),
  fontcolor = "black",
  fill = "black",
  x = 0.75,
  y = 8.625,
  width = 4.0,
  height = 0.375,
  just = c("left", "top"),
  default.units = "inches")

# Add the samples name
plotText(label = "H3K4me1", 
         fontsize = 6, 
         fontcolor = "#b5de2b",
         x = 0.75,
         y = 6.75, 
         just = c("left", "top"),
         default.units = "inches")

# Add the samples name
plotText(label = "H3K4me3", 
         fontsize = 6, 
         fontcolor = "#35b779",
         x = 0.75,
         y = 7.125, 
         just = c("left", "top"),
         default.units = "inches")

# Add the samples name
plotText(label = "H3K36me3", 
         fontsize = 6, 
         fontcolor = "#26828e",
         x = 0.75,
         y = 7.5, 
         just = c("left", "top"),
         default.units = "inches")

# Add the samples name
plotText(label = "H3K9me3", 
         fontsize = 6, 
         fontcolor = "#3e4989",
         x = 0.75,
         y = 7.875, 
         just = c("left", "top"),
         default.units = "inches")

# Add the samples name
plotText(label = "H3K27me3", 
         fontsize = 6, 
         fontcolor = "#440154",
         x = 0.75,
         y = 8.25, 
         just = c("left", "top"),
         default.units = "inches")

#### PANEL B - 
# text Supplementary Figure 1
# text B
plotText(label = "B", 
         fontsize = 12,
         x = 0.25, 
         y = 8.5, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

# Load IHEC RNA-seq data (TPM)
IHEC.exp = read_delim("/home/vagrant/Documents/IHEC/RNA_seq/genes_tpm.csv",
                      delim = ",",
                      col_names = TRUE)

# Genes of interest to be plotted
goi_ens.filt = goi_ens %>% 
  as_tibble() %>% 
  dplyr::filter(ENSEMBL != "ENSG00000274577")

IHEC.exp %>% 
  # Remove the dot and number in Ensembl IDS
  mutate(id_col = gsub("\\..*", 
                       "", 
                       id_col)) %>% 
  dplyr:::filter(id_col %in% goi_ens.filt$ENSEMBL) %>% 
  pivot_longer(cols = starts_with("IHEC"),
               names_to = "Sample",
               values_to = "TPM") %>% 
  mutate(Sample = gsub("",
                       "",
                       Sample))

dev.off()
```

### SUPPLEMENTARY FIGURE 2
Plot genes of interest from the TH REP2 mCHERRY cell line RNAseq data to demonstrate that expression is similar
```{r suppFig2, eval = FALSE, echo = TRUE}
############################################
########## SUPPLEMENTARY FIGURE 2 ##########
############################################

# Save as a PDF
pdf("/home/vagrant/Manuscript_1/SUPPLEMENTARY_FIGURE2/SUPPLEMENTARY_FIGURE2.pdf",
    width = 13, 
    height = 15)

# Create a A4 blank page
pageCreate(width = 8.3, 
           height = 11.7, 
           default.units = "inches",
           showGuides = FALSE)

#### PANEL A - 
# text Supplementary Figure 2
plotText(label = "Supplementary Figure 2", 
         fontsize = 14,
         x = 0.25, 
         y = 0.25, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")
# text A
plotText(label = "A", 
         fontsize = 12,
         x = 0.25, 
         y = 0.5, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

# Load data
dat.THREP2.FPKM = read_delim("/home/vagrant/epifunc/RNAseq/TH_REP2_mCHERRY/180604_HT-Rep2_fpkm.tsv",
                      delim = "\t", 
                      col_names = TRUE)

dat.THREP2.FPKM %>% 
  dplyr::filter(gene_name == "SCARB2") %>% 
  summary()

# Filter for genes of interest - BAG3 and LHX1
BAG3.LHX1 = c("BAG3",
              "LHX1")

IDUA.ZBTB14 = c("IDUA",
                "ZBTB14",
                "SLC26A1")

SCARB2.NR2C2 = c("SCARB2",
                 "NR2C2",
                 "FAM47E")

# Reformat the matrix and take only positively sorted neurons
dat.THREP2.FPKM = dat.THREP2.FPKM %>% 
  pivot_longer(starts_with("TH"), 
               names_to = "Samples",
               values_to = "FPKM") %>% 
  dplyr::filter(str_detect(Samples, paste("SmNPC", "pos", sep = "|"))) %>% 
  mutate(Cond = case_when(str_detect(Samples, "D15pos") ~ "Positively sorted neurons D15",
                          str_detect(Samples, "D30pos") ~ "Positively sorted neurons D30",
                          TRUE ~ "smNPCs"),
         Cond = factor(Cond, 
                       levels = c("smNPCs", 
                                  "Positively sorted neurons D15",
                                  "Positively sorted neurons D30")))

# Plot the expression of BAG3 and LHX1
TH.REP2_BAG3.LHX1.exp = ggboxplot(dat.THREP2.FPKM %>% 
                            dplyr::filter(gene_name %in% BAG3.LHX1),
                          x = "Cond", 
                          y = "FPKM", 
                          add = "jitter", 
                          fill = "Cond", 
                          palette = c("#A9A9A9", "#B22222", "#DC143C"),
                          facet.by = "gene_name",
                          xlab = "", 
                          ylab = "Fragments Per Kilobase Million (FPKM)") +
  scale_x_discrete(labels = c("smNPC",
                              expression("mDAN D15"),
                              expression("mDAN D30"))) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))

# Place the plot  
plotGG(plot = TH.REP2_BAG3.LHX1.exp, 
       x = 0.5, 
       y = 0.625, 
       width = 2, 
       height = 3.5,
       just = c("left", "top"), 
       default.units = "inches")

# Plot the expression of IDUA and ZBTB14
TH.REP2_IDUA.ZBTB14.exp = ggboxplot(dat.THREP2.FPKM %>% 
                            dplyr::filter(gene_name %in% IDUA.ZBTB14) %>% 
                              mutate(gene_name = factor(gene_name,
                                                        levels = c("IDUA", "ZBTB14", "SLC26A1"))),
                          x = "Cond", 
                          y = "FPKM", 
                          add = "jitter", 
                          fill = "Cond", 
                          palette = c("#A9A9A9", "#B22222", "#DC143C"),
                          facet.by = "gene_name",
                          xlab = "", 
                          ylab = "Fragments Per Kilobase Million (FPKM)") +
  scale_x_discrete(labels = c("smNPC",
                              expression("mDAN D15"),
                              expression("mDAN D30"))) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))

# Place the plot  
plotGG(plot = TH.REP2_IDUA.ZBTB14.exp, 
       x = 2.75, 
       y = 0.625, 
       width = 2.5, 
       height = 3.5,
       just = c("left", "top"), 
       default.units = "inches")

# Plot the expression of SCARB2 and NR2C2
TH.REP2_SCARB2.NR2C2.exp = ggboxplot(dat.THREP2.FPKM %>% 
                            dplyr::filter(gene_name %in% SCARB2.NR2C2) %>% 
                              mutate(gene_name = factor(gene_name,
                                                        levels = c("SCARB2", "NR2C2", "FAM47E"))),
                          x = "Cond", 
                          y = "FPKM", 
                          add = "jitter", 
                          fill = "Cond", 
                          palette = c("#A9A9A9", "#B22222", "#DC143C"),
                          facet.by = "gene_name",
                          xlab = "", 
                          ylab = "Fragments Per Kilobase Million (FPKM)") +
  scale_x_discrete(labels = c("smNPC",
                              expression("mDAN D15"),
                              expression("mDAN D30"))) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))

# Place the plot  
plotGG(plot = TH.REP2_SCARB2.NR2C2.exp, 
       x = 5.5, 
       y = 0.625, 
       width = 2.5, 
       height = 3.5,
       just = c("left", "top"), 
       default.units = "inches")

#### PANEL B - 
# text B
plotText(label = "B", 
         fontsize = 12,
         x = 0.25, 
         y = 4.5, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

# FOUNDIN-PD data
# Load
FIPD = read_delim("/home/vagrant/epifunc/PPMI_data/FOUNDIN-PD_150.9_RNAB/aggregated_expression/cpmTable.tsv",
                  delim = "\t",
                  col_names = TRUE)

#FIPD = read_delim("/home/vagrant/epifunc/PPMI_data/FOUNDIN-PD_150.9_RNAB/aggregated_expression/countTable.tsv",
#                  delim = "\t",
#                  col_names = TRUE)

# Filter for genes of interest and get the ensembl and gene names
goi_ens = select(org.Hs.eg.db, 
                 keys = c("BAG3",
                          "LHX1",
                          "IDUA",
                          "ZBTB14",
                          "SLC26A1",
                          "SCARB2",
                          "NR2C2",
                          "FAM47E"), 
                 columns = c("SYMBOL",
                             "ENSEMBL"), 
                 keytype = "SYMBOL")

# 2 LHX1 ensembl IDs came back. Check on the Ensembl website which one is correct
goi_ens = goi_ens %>% 
  as_tibble() %>% 
  dplyr::filter(ENSEMBL != "ENSG00000274577") %>% 
  dplyr::rename(ENSEMBL.not.dot = ENSEMBL)

# Load the information abour iPSCs cell lines
info_iPSCs = read_delim("/home/vagrant/epifunc/PPMI_data/Participant_Status_02Jun2023.csv",
                  delim = ",",
                  col_names = TRUE)

info_iPSCs = info_iPSCs %>% 
  mutate(PATNO = as.character(PATNO))

# Filter the matrix of expression for my genes of interest
FIPD.fin = FIPD %>% 
  #mutate(Geneid = str_replace(Geneid, "\\..", "")) %>% 
  dplyr::filter(str_detect(Geneid, paste(goi_ens$ENSEMBL.not.dot, collapse = "|"))) %>% 
  dplyr::rename(ENSEMBL = Geneid) %>% 
  mutate(ENSEMBL.not.dot = gsub("\\..*", "", ENSEMBL)) %>% 
  dplyr::select(ENSEMBL, ENSEMBL.not.dot, everything()) %>% 
  #left_join(goi_ens, by = "ENSEMBL") %>% 
  pivot_longer(cols = starts_with("RNAB"), names_to = "Samples", values_to = "CPM") %>% 
  mutate(PATNO = str_extract(Samples, "[^RNAB_PPMI_]+"),
         Day = str_extract(Samples, "da+\\d+")) %>% 
  left_join(info_iPSCs,
            by = "PATNO") %>% 
  left_join(goi_ens, 
            by = "ENSEMBL.not.dot") %>% 
  dplyr::select(ENSEMBL:Day, COHORT_DEFINITION, SYMBOL) %>% 
  mutate(Condition = case_when(COHORT_DEFINITION == "Healthy Control" ~ "Healthy\ncontrol",
                               COHORT_DEFINITION == "Parkinson's Disease" ~ "Parkinson's\ndisease",
                               TRUE ~ COHORT_DEFINITION)) %>% 
  #group_by(SYMBOL, Day, COHORT_DEFINITION) %>% 
  group_by(ENSEMBL, Day) %>% 
  mutate(AVG_CPM = mean(CPM, na.rm = TRUE))

# Plot expression of all putative target genes and TFs except SCARB2 (will be plot alone)
FIPD.exp.pl = ggboxplot(FIPD.fin %>% 
                          dplyr::filter(SYMBOL != "SCARB2"),
                     x = "Day", 
                     y = "AVG_CPM", 
                     add = "jitter", 
                     fill = "Day", 
                     palette = c("#482677FF", "#2D708EFF", "#29AF7FFF"),
                     facet.by = "SYMBOL",
                     xlab = "", 
                     ylab = "CPM") +
  scale_x_discrete(labels = c("Day 0",
                              "Day 25",
                              "Day 65")) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90),
        strip.text.x = element_text(size = 6))

# Place the plot  
plotGG(plot = FIPD.exp.pl, 
       x = 0.5, 
       y = 4.75 ,
       width = 6, 
       height = 4.5,
       just = c("left", "top"), 
       default.units = "inches")

# Plot expression of SCARB2
FIPD.exp.SCARB2.pl = ggboxplot(FIPD.fin %>% 
                          dplyr::filter(SYMBOL == "SCARB2"),
                     x = "Day", 
                     y = "AVG_CPM", 
                     add = "jitter", 
                     fill = "Day", 
                     palette = c("#482677FF", "#2D708EFF", "#29AF7FFF"),
                     facet.by = "SYMBOL",
                     xlab = "", 
                     ylab = "CPM") +
  scale_x_discrete(labels = c("Day 0",
                              "Day 25",
                              "Day 65")) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90),
        strip.text.x = element_text(size = 6))

# Place the plot  
plotGG(plot = FIPD.exp.SCARB2.pl, 
       x = 0.5, 
       y = 9.75 ,
       width = 6, 
       height = 3.5,
       just = c("left", "top"), 
       default.units = "inches")

dev.off()
```

### SUPPLEMENTARY FIGURE 3
Plot FACS results for experiments where knockdown were performed at day 9 and samples collected 3 and 6 days post-transduction
```{r suupFig3, eval = FALSE, echo = TRUE}
############################################
########## SUPPLEMENTARY FIGURE 3 ##########
############################################

# Save as a PDF
pdf("/home/vagrant/Manuscript_1/SUPPLEMENTARY_FIGURE3/SUPPLEMENTARY_FIGURE3.pdf",
    width = 13, 
    height = 15)

# Create a A4 blank page
pageCreate(width = 8.3, 
           height = 11.7, 
           default.units = "inches",
           showGuides = TRUE)

#### PANEL A - 
# text Supplementary Figure 3
plotText(label = "Supplementary Figure 3", 
         fontsize = 14,
         x = 0.25, 
         y = 0.25, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")
# text A
plotText(label = "A", 
         fontsize = 12,
         x = 0.25, 
         y = 0.5, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

# Read the facs files (.fcs)
#facs.path = "/home/vagrant/Documents/Wetlab/epifunc/"
facs.path = "/Volumes/deborah.gerard/Documents/Wetlab/epifunc/"

facs_6days_PT_N1.fs = read.flowSet(path = paste0(facs.path,
                                              "2022.11_DG_KD_SCARB2_NR2C2_1/FACS/RAW_DATA/NEW_EXPORT_06122022_1624/2022.11_DG_KD_SCARB2_NR2C2_1/"),
                                pattern = ".fcs",
                               alter.names = TRUE,
                               truncate_max_range = FALSE)

# Check what channels are present
colnames(facs_6days_PT_N1.fs)

# Check sample
pData(facs_6days_PT_N1.fs)

# Rename some for clarity
colnames(facs_6days_PT_N1.fs)[colnames(facs_6days_PT_N1.fs) == "FITC.A"] = "GFP"
colnames(facs_6days_PT_N1.fs)[colnames(facs_6days_PT_N1.fs) == "mCherry..A"] = "mCHERRY"
colnames(facs_6days_PT_N1.fs)[colnames(facs_6days_PT_N1.fs) == "SYTOX_BLUE..A"] = "SYTOX BLUE"

# To be able to add gates, the object must be transformed as a GatingSet object
facs_6days_PT_N1.gs = GatingSet(facs_6days_PT_N1.fs)

# Define neurons gate
dead.neur.gate = polygonGate(filterId = "Neurons",
                        "FSC.A" = c(5e4, 2e5, 2e5, 5e4),
                        "SSC.A" = c(0e4, 125e3, 2.e5, 1e5))

# Plot SYTOX BLUE positive CTRL
ggcyto(facs_6days_PT_N1.gs[[1]],
       aes(x = FSC.A, 
           y = SSC.A),
       subset = "root") + 
  geom_hex(bins = 200) +
  geom_gate(dead.neur.gate) +
  ggcyto_par_set(limits = "instrument")

# The gate for dead neurons has been defined -> add the gate to the gateset and recompute
add(facs_6days_PT_N1.gs,
    dead.neur.gate)

recompute(facs_6days_PT_N1.gs)

dev.off()
```

SCARB2 snp (rs1465922) for samples with whole genome sequencing data (75 cases)
```{r, eval= FALSE, echo = TRUE}
# Load data
SCARB2.SNP.WGS.75 = read_excel("/Volumes/deborah.gerard/Documents/epifunc/Final.WGS.SCARB2.OK_from_Sinthu.xlsx")

# Filter for rs1465922
SCARB2.SNP.WGS.75 %>% 
  filter(avsnp150 == "rs1465922") %>% 
  select(samples) %>% 
  separate(samples,
           sep = ", ",
           into = )

```

```{r}
sessionInfo()
```

### 2024-04-03 Manuscript_1.Rmd
Final edit of all main figures

@@
                       fig.height = 3, 
-                      cache = TRUE, 
+                      cache = FALSE, 
                       tidy = TRUE, 
@@
 #library("BSgenome.Hsapiens.UCSC.hg38")
-#library("TxDb.Hsapiens.UCSC.hg38.knownGene")
+library("TxDb.Hsapiens.UCSC.hg38.knownGene")
 library("TxDb.Hsapiens.UCSC.hg38.refGene")
@@
 library("ggcyto")
+library("ggmanh")
 
@@
 packageVersion("dbplyr")  #2.3.4
+packageVersion("ggmanh")  #1.2.0
 
@@
 # FIGURES
+Generating the manhattan plot for the PD GWAS is memory demanding. Go to the HPC
+```{bash, eval = FALSE, echo = TRUE}
+ssh iris-cluster
+salloc --nodes=1 -p interactive --qos debug -C batch -t 02:00:00 --mem 24G
+
+# Load the Singularity module
+module load tools/Singularity/3.8.1
+singularity shell --bind /scratch/users/dgerard:/scratch/users/dgerard $HOME/Singularity_containers/Manuscript_1_singularity.sif
+```
+
 ### FIGURE 1
@@
 
+# Save as TIFF, 300 ppi
+tiff("/home/vagrant/Manuscript_1/FIGURE1/FIGURE1.tiff",
+     width = 8.27,
+     height = 11.67,
+     units = "in",
+     res = 300,
+     compression = "lzw")
+
 # Create a A4 blank page
-pageCreate(width = 8.3, 
-           height = 11.7, 
+pageCreate(width = 8.27, 
+           height = 11.67, 
            default.units = "inches",
@@
          fontsize = 14,
+         fontfamily = "Helvetica",
          x = 0.25, 
@@
          fontface = "bold")
+
 # text A
@@
          fontsize = 12,
+         fontfamily = "Helvetica",
          x = 0.25, 
@@
 
+###################
+#### Figure 1A ####
+###################
+# Figure 1A generated in Biorender
+#fig1A = readPNG("/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/Fig1A.png")
+fig1A = readPNG("/home/vagrant/Manuscript_1/FIGURE1/Fig1A.png")
+
+plotRaster(image = fig1A,
+           x = 0.25, 
+           y = 1, 
+           width = 8.0, 
+           height = 1.0, 
+           just = "left",
+           interpolate = TRUE)
+
 # text B
@@
          fontsize = 12,
-         x = 0.25, 
-         y = 8.25, 
+         fontfamily = "Helvetica",
+         x = 3.25, 
+         y = 4.5, 
          just = "left", 
@@
 
-###################
-#### Figure 1A ####
-###################
-Fig1A = readPNG("/home/vagrant/Manuscript_1/FIGURE1/Fig1A.png")
-
-# Plot Figure 1A
-plotRaster(image = Fig1A,
-           x = 0.375,
-           y = 0.625,
-           width = 7.55,
-           height = 1.0,
-           just = c("left", 
-                    "top"),
-           interpolate = FALSE)
+# text E
+plotText(label = "E", 
+         fontsize = 12,
+         fontfamily = "Helvetica",
+         x = 0.25, 
+         y = 4.5, 
+         just = "left", 
+         default.units = "inches",
+         fontface = "bold")
 
@@
 Fig1C_pip = readPNG("/home/vagrant/Manuscript_1/FIGURE1/Fig1C_pipeline.png")
-
-Fig1C_tab1.1 = readPNG("/home/vagrant/Manuscript_1/FIGURE1/Fig1C_SNPs_tab1.png/Fig1C_SNPs_tab1.png-1.png")
-Fig1C_tab1.2 = readPNG("/home/vagrant/Manuscript_1/FIGURE1/Fig1C_SNPs_tab1.png/Fig1C_SNPs_tab1.png-2.png")
-
-# Plot Figure 1C
+#Fig1C_pip = readPNG("/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/Fig1C_pipeline.png")
+
+# Plot Figure 1C - Pipeline
 plotRaster(image = Fig1C_pip,
            x = 0.375,
-           y = 5.25,
+           y = 4.75,
            width = 3.0,
-           height = 2.5,
+           height = 3.5,
            just = c("left", 
                     "top"),
-           interpolate = FALSE)
-
-plotRaster(image = Fig1C_tab1.1,
-           x = 3.375,
-           y = 5.25,
-           width = 2.3,
-           height = 2.5,
-           just = c("left", 
-                    "top"),
-           interpolate = FALSE)
-
-plotRaster(image = Fig1C_tab1.2,
-           x = 5.8,
-           y = 5.25,
-           width = 2.3,
-           height = 2.5,
-           just = c("left", 
-                    "top"),
-           interpolate = FALSE)
-
-#diag_edge_data = tibble(from = c("~17x10^6\nPD GWAS SNPs",
-#                                 "~3400 significant\nPD GWAS SNPs",
-#                                 "28 significant\nPD rSNPs"),
-#                        to = c("~3400 significant\nPD GWAS SNPs",
-#                               "28 significant\nPD rSNPs",
-#                               "3 significant\nPD rSNPs"))
-#
-#diag_node_data = tibble(name = c("~17x10^6\nPD GWAS SNPs",
-#                                 "~3400 significant\nPD GWAS SNPs",
-#                                 "28 significant\nPD rSNPs",
-#                                "3 significant\nPD rSNPs"),
-#                        label = name)
-
-# Diagramme
-# fig1C = ggflowchart(diag_edge_data,
-#                    diag_node_data,
-#                    text_size = 3.0,
-#                    arrow_size = 0.2)
-
-# Place the diagramme
-#plotGG(plot = fig1C, 
-#       x = 0.5, 
-#       y = 4.5, 
-#      width = 1.5, 
-#       height = 3.0,
-#       just = c("left", "top"), 
-#      default.units = "inches")
+           interpolate = TRUE)
+
+###################
+#### Figure 1C Manhattan plot ####
+###################
+# Load the Nalls et al. GWAS data
+nalls_allSNPs.HG38.GR = readRDS(
+  "/home/vagrant/Manuscript_1/FIGURE1/nalls_allSNPs.HG38.GR.rds")
+
+#nalls_allSNPs.HG38.GR = readRDS(
+#"/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/nalls_allSNPs.HG38.GR.rds")
+
+# Load the rsIDS FOR THE 28 significant SNPs
+rsID.28 = read_delim("/home/vagrant/Manuscript_1/FIGURE1/20210309_28SNPs_rsID.csv",
+                     delim = ",",
+                     col_names = TRUE)
+
+rsID.28 = read_delim("/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/20210309_28SNPs_rsID.csv",
+                     delim = ",",
+                     col_names = TRUE)
+
+rsID.28.filt = rsID.28 %>% 
+  dplyr::select(chrom, chromEnd, name) %>% 
+  unite(col = "pos", chrom, chromEnd, sep = "_")
+
+# Select the SNPs position from nalls et al and associate rsIDs
+nalls.manH = nalls_allSNPs.HG38.GR %>% 
+  as_tibble() %>% 
+  dplyr::select(seqnames, base_pair_position, p) %>% 
+  unite(col = "pos", seqnames, base_pair_position, sep = "_", remove = FALSE) %>%
+  left_join(rsID.28.filt, by = "pos") %>% 
+  separate(pos, into = c("chrom", "pos"), sep = "_", remove = TRUE) %>% 
+  dplyr::select(chrom, pos, p, name)
+
+# Save
+write_rds(nalls.manH,
+          "/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/20240304_28SNPs_rdID_manH.rds")
+
+nalls.manH = read_rds("/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/20240304_28SNPs_rdID_manH.rds")
+nalls.manH = read_rds("/home/vagrant/Manuscript_1/FIGURE1/20240304_28SNPs_rdID_manH.rds")
+
+# Rename columns
+nalls.manH = nalls.manH %>% 
+  dplyr::rename(snp = name) %>% 
+  mutate(pos = as.numeric(pos)) %>% 
+  dplyr::filter(chrom %in% rsID.28$chrom)
+
+# Manhattan plot - highlight  the 28 SNPs with rsID
+snp_2_high = nalls.manH %>% 
+  dplyr::filter(!is.na(snp),
+                p <= 5e-08)
+
+# Random sampling for plotting test
+snp_to_pl = nalls.manH %>% 
+  mutate(snp = NA_character_) %>% 
+  bind_rows(snp_2_high) %>% 
+  #dplyr::filter(p <= 5e-08) %>% 
+  mutate(pbis = -log10(p),
+         chrom = factor(chrom,
+                        levels = c("chr1",
+                                   "chr3",
+                                   "chr4",
+                                   "chr7",
+                                   "chr10",
+                                   "chr12",
+                                   "chr16",
+                                   "chr17")))
+
+# And plot
+snp.pl = manhattan_plot(x = snp_to_pl, 
+               pval.colname = "p", 
+               chr.colname = "chrom", 
+               pos.colname = "pos",
+               label.colname = "snp",
+               signif = 5e-08,
+               max.overlaps = 50)
+
+saveRDS(snp.pl,
+        "/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/Nalls_manh_label.rds")
+snp.pl = readRDS("/home/vagrant/Manuscript_1/FIGURE1/Nalls_manh_label.rds")
+
+# Place the plot
+plotGG(plot = snp.pl, 
+       x = 3.5, 
+       y = 4.75, 
+       width = 4.5, 
+       height = 3.5,
+       just = c("left", "top"), 
+       default.units = "inches")
 
@@
 # Locus plot
-# Load the Nalls et al. GWAS data
-nalls_allSNPs.HG38.GR = readRDS(
-  "/home/vagrant/Manuscript_1/FIGURE1/nalls_allSNPs.HG38.GR.rds")
-
-#nalls_allSNPs.HG38.GR = readRDS(
-#  "/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/nalls_allSNPs.HG38.GR.rds")
-
 # Here our SNPs of interest and their location
@@
 # Get SNPs info from Ensembl
-snp.ensembl = useEnsembl(biomart = "snp", dataset = "hsapiens_snp")
+#snp.ensembl = useEnsembl(biomart = "snp", 
+#                         dataset = "hsapiens_snp")
+
+snp.ensembl = useMart(biomart = "ENSEMBL_MART_SNP",
+                      dataset = "hsapiens_snp")
 
@@
   unite(col = "position", c(chr, end, base_pair_position), sep = ":", remove = FALSE) %>% 
-  filter(GWAS_p_sig != "no") %>%
+  dplyr::filter(GWAS_p_sig != "no") %>%
   dplyr::select(position) %>% 
@@
   left_join(BAG3_R2, by = "Coord") %>% 
-  dplyr::select(seqnames, base_pair_position, p, refsnp_id.x,R2) %>% 
+  dplyr::select(seqnames, base_pair_position, p, refsnp_id.x, R2) %>% 
   dplyr::rename(chrom = seqnames,
@@
   as_tibble() %>% 
-  filter(seqnames == "chr4",
+  dplyr::filter(seqnames == "chr4",
          between(base_pair_position, 987108 - r, 987108 + r)) %>% 
@@
 IDUA_SNPs_LD = IDUA_SNPs_LD %>% 
-  filter(!str_detect(refsnp_id, "^CR"))
+  dplyr::filter(!str_detect(refsnp_id, "^CR"))
 
@@
   as_tibble() %>% 
-  filter(seqnames == "chr4",
+  dplyr::filter(seqnames == "chr4",
          between(base_pair_position, 76213717 - r, 76213717 + r)) %>% 
@@
 
+# Save as TIFF, 300 ppi
+tiff("/home/vagrant/Manuscript_1/FIGURE2/FIGURE2.tiff",
+     width = 8.27,
+     height = 11.67,
+     units = "in",
+     res = 300,
+     compression = "lzw")
+
 # Create a A4 blank page
-pageCreate(width = 8.3, 
-           height = 11.7, 
+pageCreate(width = 8.27, 
+           height = 11.67, 
            default.units = "inches",
@@
 bw.path = "/home/vagrant/epifunc/"
+#bw.path = "/Volumes/deborah.gerard/Documents/epifunc/"
 
@@
          fontcolor = "#A9A9A9",
+         fontfamily = "Helvetica",
          x = 0.75, 
@@
          just = c("left", "top"),
-         default.units = "inches")
+         default.units = "inches",
+         fontface = "bold")
 
@@
          fontsize = 6, 
+         fontfamily = "Helvetica",
          fontcolor = "#B22222",
@@
          fontsize = 6, 
+         fontfamily = "Helvetica",
          fontcolor = "#DC143C",
@@
          fontsize = 6, 
+         fontfamily = "Helvetica",
          fontcolor = "#E9967A",
@@
          fontsize = 12,
+         fontfamily = "Helvetica",
          x = 5.0, 
@@
 dat.RPKM.filt = read_rds("/home/vagrant/Manuscript_1/FIGURE2/mat_RPKM.rds")
+dat.RPKM.filt = read_rds("/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE2/mat_RPKM.rds")
+
+dat.RPKM.filt %>% 
+  #filter(str_detect(gene_id, " ENSG00000272414"))
+  filter(str_detect(gene_name, paste0(c("FAM47E", "STBD1"),
+                                      collapse = "|"))) %>% 
+  View()
 
@@
 LHX1 = as.list(LHX1)
-LHX1_TFBS = ggseqlogo(LHX1)
+
+# Remove the nucleotide position
+LHX1_TFBS = ggseqlogo(LHX1) +
+  annotate("rect", 
+           xmin = 4.5, 
+           xmax = 5.5, 
+           ymin = -0.05, 
+           ymax = 2.5, 
+           alpha = .1, 
+           col = "black", 
+           fill = "#404788FF") +
+  theme(axis.text.x = element_blank())
 
@@
 plotGG(plot = LHX1_TFBS, 
-       x = 1.7125, 
+       x = 1.7425, 
        y = 2.625, 
@@
          fontcolor = "#B22222",
+         fontfamily = "Helvetica",
          x = 0.75, 
@@
          fontcolor = "#DC143C",
+         fontfamily = "Helvetica",
          x = 0.75, 
@@
          fontcolor = "#E9967A",
+         fontfamily = "Helvetica",
          x = 0.75, 
@@
 ZBTB14 = as.list(ZBTB14)
-ZBTB14_TFBS = ggseqlogo(ZBTB14)
+
+# Remove the nucleotide position
+ZBTB14_TFBS = ggseqlogo(ZBTB14) +
+  annotate("rect", 
+           xmin = 8.5, 
+           xmax = 9.5, 
+           ymin = -0.05, 
+           ymax = 2.5, 
+           alpha = .1, 
+           col = "black", 
+           fill = "#404788FF") +
+  theme(axis.text.x = element_blank())
 
@@
 plotGG(plot = ZBTB14_TFBS, 
-       x = 1.7125, 
+       x = 1.6225, 
        y = 6.625, 
@@
 NR2C2 = as.list(NR2C2)
-NR2C2_TFBS = ggseqlogo(NR2C2)
+
+# Remove nucleotide
+NR2C2_TFBS = ggseqlogo(NR2C2) +
+  annotate("rect", 
+           xmin = 3.5, 
+           xmax = 4.5, 
+           ymin = -0.05, 
+           ymax = 2.0, 
+           alpha = .1, 
+           col = "black", 
+           fill = "#404788FF") +
+  theme(axis.text.x = element_blank())
 
@@
 plotGG(plot = NR2C2_TFBS, 
-       x = 1.6875, 
+       x = 1.8475, 
        y = 10.375, 
@@
      units = "in",
-     res = 300)
+     res = 300,
+     compression = "lzw")
 
@@
            default.units = "inches",
-           showGuides = TRUE)
+           showGuides = FALSE)
 
@@
          default.units = "inches")
+
+# Fig3A
+fig3A = readPNG("/home/vagrant/Manuscript_1/FIGURE3/Fig3A_BIORENDER.png")
+#fig3A = readPNG("/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE3/Fig3A_BIORENDER.png")
+
+plotRaster(image = fig3A,
+           x = 0.25, 
+           y = 1, 
+           width = 8.0, 
+           height = 1.0, 
+           just = "left",
+           interpolate = TRUE)
 
@@
                      x = "Gene",
-                     y.position = 0.5,
+                     y.position = c(0.5, 1.2),
                      size = 3.0,
-                     hide.ns = TRUE)
+                     hide.ns = FALSE)
 
@@
   scale_y_continuous(expand = c(0, 0),
-                     limits = c(0, 1.8)) +
+                     limits = c(0, 1.9)) +
   stat_pvalue_manual(stat_ZBTB14.KD,
@@
                      x = "Gene",
-                     y.position = 0.5,
+                     y.position = c(0.5, 1.6),
                      size = 3.0,
-                     hide.ns = TRUE)
+                     hide.ns = FALSE)
 
@@
                      x = "Gene",
-                     y.position = 1.5,
-                     size = 3.0)
+                     y.position = c(0.65, 1.5),
+                     size = 3.0,
+                     hide.ns = FALSE)
 
@@
                      x = "Gene",
-                     y.position = 1.5,
+                     y.position = c(0.85, 1.5),
                      size = 3.0,
-                     hide.ns = TRUE)
+                     hide.ns = FALSE)
 
@@
 ### FIGURE 4
+Allelic imbalance at rs1465922 in ATACseq of differentiated TH REP1 cell line.  
+```{bash, eval = FALSE, echo = TRUE}
+# Copy the ATACseq BAM locally 
+rsync -avzPhu --no-p iris-cluster://work/projects/epifunc/merged_bam/ /Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE4/
+```
+
+Within R
+```{r, eval = FALSE, echo = TRUE}
+# Since TH REP1 cell line is heterozygous for rs1465922 check around that position for chromatin allelic imbalance in ATACseq data
+# hg38
+searchArea = GRanges(seqnames = c("chr4"), 
+                     ranges = IRanges(start = c(76213716), 
+                                      end = c(76213726)))
+
+# Path where the ATACseq BAM files are
+pathToFiles = "/home/vagrant/Manuscript_1/FIGURE4/"
+
+# Import a specific region (10bp around rs1465922) from the BAM files
+reads = impBamGAL(pathToFiles, 
+                  searchArea, 
+                  verbose = TRUE)
+
+# Identify the position of rs1465922 in the BAM files
+heterozygotePositions = scanForHeterozygotes(reads, 
+                                             verbose = TRUE)
+
+# Count the number of reads for the 2 different alleles at that position
+countList = getAlleleCounts(reads, 
+                            heterozygotePositions, 
+                            verbose = FALSE)
+
+# Save as a rds file for loading later if necessary
+saveRDS(countList, 
+        file = "/home/vagrant/Manuscript_1/FIGURE4/SCARB2_het_counts_THREP1_ATACseq.rds")
+```
+
 ```{r fig4, eval = FALSE, echo = TRUE}
@@
 
-#FIG 4A
-AI_RNA = tibble(Samples = 
-                  c("smNPCs", "Neurons positively sorted D15", "Neurons positively sorted D30",
-                    "Neurons positively sorted D50", "Astrocytes"),
-                A = c(5, 23, 77, 56, 30),
-                G = c(8, 4, 62, 34, 47)) %>% 
-  gather(-Samples, key = "Base", value = "Reads")
-
-AI_ATAC = tibble(Samples = 
-                  c("smNPCs", "mDAN D15", "mDAN D30",
-                    "mDAN D50", "Astrocytes"),
-                A = c(31, 195, 202, 118, 155),
-                G = c(39, 263, 264, 196, 179)) %>% 
-  gather(-Samples, key = "Base", value = "Reads")
-
-AI = AI_ATAC %>% 
-  bind_rows(AI_RNA) %>% 
-  mutate(Cond = rep(c("ATAC", "RNA"), each = 10))
-
-# Good looking plot
-chrom_AI = ggbarplot(AI_ATAC, x = "Samples", y = "Reads",
-          fill = "Base",
+# Chromatin imbalance values as calculated by the AllelicImbalance R package
+countList = readRDS("/home/vagrant/Manuscript_1/FIGURE4/SCARB2_het_counts_THREP1_ATACseq.rds")
+
+# Extract and reformat for positively sorted TH population
+AI_ATAC = countList$chr4_76213717 %>% 
+  as_tibble() %>% 
+  mutate(Sample = rownames(countList$chr4_76213717)) %>% 
+  pivot_longer(cols = c(A, C, G, T), names_to = "Base", values_to = "Reads") %>% 
+  mutate(Sample.n = case_when(str_detect(Sample, "astrocytes") ~ "Astrocytes",
+                              str_detect(Sample, "D15_neg") ~ "Negative DAN D15",
+                              str_detect(Sample, "D15_pos") ~ "mDAN D15",
+                              str_detect(Sample, "D30_pos") ~ "mDAN D30",
+                              str_detect(Sample, "D50_neg") ~ "Negative DAN D50",
+                              str_detect(Sample, "D50_pos") ~ "mDAN D50",
+                              TRUE ~ "smNPCs")) %>% 
+  dplyr::filter(!str_detect(Sample, "neg"),
+                Base %in% c("A", "G")) %>% 
+  mutate(Sample.n = factor(Sample.n,
+                           levels = c("smNPCs",
+                                      "mDAN D15",
+                                      "mDAN D30",
+                                      "mDAN D50",
+                                      "Astrocytes")),
+         Allele = case_when(Base == "A" ~ "PD allele",
+                            TRUE ~ "Other allele"))
+
+# Plot
+chrom_AI = ggplot(AI_ATAC,
+                  aes(Sample.n, 
+                      Reads, 
+                      fill = interaction(Sample.n, Base)), 
+                  alpha = Base) +
+  geom_bar(stat = "identity",
+           position = "dodge",
+           width = 0.5,
+           colour = "black") +
+  geom_text(aes(label = format(c(0.3,
+                          "",
+                          0.3,
+                          "",
+                          0.003,
+                          "",
+                          0.0000003,
+                          "",
+                          0.2,
+                          ""),
+                          scientific = TRUE),
+                 y = Reads + 100),
+            vjust = 0) +
+  scale_fill_manual(aesthetics = "fill",
+                    values = c("#D3D3D3",
+                               "#B22222",
+                               "#FF6347",
+                               "#FFA07A",
+                               "#b8627db2",
+                               "#C0C0C0",
+                               "#A52A2A",
+                               "#FF0000",
+                               "#FA8072",
+                               "#cc6a70b2")) +
+  coord_flip() +
+  theme_classic() +
+  scale_y_continuous(expand = c(0, 0),
+                     limits = c(0, 330)) +
+  xlab("") +
+  theme(axis.text = element_text(face = "bold", colour = "black"),
+        axis.title.x = element_text(face = "bold", colour = "black"),
+        legend.position = "none") 
+#######################################################################
+
+ggplot(AI_ATAC,
+       aes(Allele, 
+           Reads,
+           fill = Sample.n,
+           alpha = Base)) +
+  # geom_col(position = position_dodge(),
+  #          width = 1.0,
+  #          colour = "black") +
+  geom_bar(stat = "identity",
+           position = "dodge",
+           width = 0.5,
+           colour = "black") +
+  facet_wrap(~Sample.n,
+             strip.position = "bottom") +
+  theme_classic() +
+  theme(strip.placement = "outside") +
+  scale_fill_manual(values = c("#A9A9A9",
+                               "#B22222",
+                               "#DC143C", 
+                               "#E9967A",
+                               "#CC6A70B2")) +
+  scale_y_continuous(expand = c(0, 0),
+                     limits = c(0, 330)) +
+  theme(legend.position = "none") +
+  xlab("") +
+  #coord_flip()
+  geom_text(aes(label = format(c(0.3,
+                          "",
+                          0.3,
+                          "",
+                          0.003,
+                          "",
+                          0.0000003,
+                          "",
+                          0.2,
+                          ""),
+                          scientific = TRUE),
+                 y = Reads + 100),
+            vjust = 0) +
+  scale_fill_manual(aesthetics = "fill",
+                    values = c("#D3D3D3",
+                               "#B22222",
+                               "#FF6347",
+                               "#FFA07A",
+                               "#b8627db2",
+                               "#C0C0C0",
+                               "#A52A2A",
+                               "#FF0000",
+                               "#FA8072",
+                               "#cc6a70b2")) +
+  coord_flip() +
+  theme_classic() +
+  scale_y_continuous(expand = c(0, 0),
+                     limits = c(0, 330)) +
+  xlab("") +
+  theme(axis.text = element_text(face = "bold", colour = "black"),
+        axis.title.x = element_text(face = "bold", colour = "black"),
+        legend.position = "none")
+
+AI_ATAC = AI_ATAC %>%
+  mutate(term.i = as.factor(paste(Sample.n, Base)))
+
+chrom_AI = ggbarplot(AI_ATAC,
+                     x = "Sample.n",
+                     y = "Reads",
+                     fill = "Allele",
                      position = position_dodge(0.7),
-          xlab = "", ylab = "Reads",
-          #title = "Allelic imbalance at chr4:76213717 - SNP in SCARB2 promoter",
-          label = c(0.3, 0.001, 0.004, 1e-5, 0.2,
-                    rep("", 5)),
+                     xlab = "",
+                     ylab = "Reads",
+                     title = "Read at SCARB2 promoter overlapping rs1465922 (SCARB2)",
+                     label = format(c(0.3,
+                          "",
+                          0.3,
+                          "",
+                          0.003,
+                          "",
+                          0.0000003,
+                          "",
+                          0.2,
+                          ""),
+                          scientific = TRUE),
                      label.pos = "out",
-          lab.size = 3) +
+                     lab.size = 3,
+                     lab.vjust = 0.5,
+                     lab.hjust = -0.5,
+                     orientation = "horiz") +
   theme(legend.position = "right",
@@
         axis.title.y = element_text(face = "bold", size = 10),
+        axis.title.x = element_text(face = "bold", size = 10),
         legend.text = element_text(face = "bold", size = 10),
-        legend.title = element_text(face = "bold", size = 10)) +
-        # title = element_text(hjust = 0.5)) +
-  scale_fill_manual(values = c("#80A44F", "#427F96"))
-
+        legend.title = element_text(face = "bold", size = 10),
+        plot.title = element_text(hjust = 0.5)) +
+  scale_fill_manual(values = c("#80A44F", "#427F96")) +
+  scale_y_continuous(expand = c(0, 0),
+                     limits = c(0, 330))
+
+# Place the plot
 plotGG(plot = chrom_AI, 
@@
        y = 0.75, 
-       width = 6, 
+       width = 7, 
        height = 4,
@@
 
+# GTEX_SNPs_interest = read_delim("/Volumes/deborah.gerard/Documents/epifunc/eQTpLot/20230117_GTEX_data.csv",
+#               delim = ";",
+#              col_names = TRUE)
+
 GTEX_SNPs_interest = read_delim("/home/vagrant/epifunc/eQTpLot/20230117_GTEX_data.csv",
@@
   mutate(GTEX_sig = if_else(P.Value < 0.05, "*", "")) %>% 
-  filter(str_detect(Tissue, "Brain"),
-         Gene.Symbol == "SCARB2")
-
-GTEX_eqtl = ggplot(data = GTEX_SNPs_SCARB2_brain, mapping = aes(x = SNP.Id,
+  dplyr::filter(str_detect(Tissue, "Brain"),
+         Gene.Symbol == "SCARB2") %>% 
+  mutate(SNP.Id = factor(SNP.Id,
+                         levels = c("rs6825004",
+                                    "rs7697073",
+                                    "rs11547135",
+                                    "rs6812193",
+                                    "rs1465922")))
+
+GTEX_eqtl = ggplot(data = GTEX_SNPs_SCARB2_brain, 
+                   mapping = aes(x = SNP.Id,
                                  y = Tissue,
@@
 
+# Save as TIFF, 300 ppi
+tiff("/home/vagrant/Manuscript_1/FIGURE5/FIGURE5.tiff",
+     width = 8.27,
+     height = 11.67,
+     units = "in",
+     res = 300,
+     compression = "lzw")
+
 # Create a A4 blank page
@@
          fontsize = 14,
+
          x = 0.25, 
@@
          fontface = "bold")
+
+GCase_signal = tibble(Sample = c("shSCARB2", "shNR2C2", "shSCRAMBLE"),
+                     n1_rep1 = c(11577, 9485, 9903),
+                     n1_rep2 = c(11329, 9685, 9574),
+                     n2_rep1 = c(8979, 9443, 9489),
+                     n2_rep2 = c(9489, 9440, 11333),
+                     n3_rep1 = c(9209, 10130, 10353),
+                     n3_rep2 = c(10104, 11158, 14640),
+                     n4_rep1 = c(15255, 15551, 15611),
+                     n4_rep2 = c(14964, 16078, 16352)) %>% 
+  pivot_longer(!Sample, names_to = "Meas", values_to = "Abs_val") %>% 
+  mutate(Meas2 = gsub("\\_.*", "\\1", Meas)) %>% 
+  group_by(Sample, Meas2) %>% 
+  mutate(AVG = mean(Abs_val, na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  dplyr::select(-Meas, -Abs_val, -Meas2) %>%
+  distinct(AVG, .keep_all = TRUE)
+
+# Plot 
+GCase.pl = ggbarplot(GCase_signal, 
+                      x = "Sample", 
+                      y = "AVG",
+                      width = 0.25,
+                      add = c("mean_se", 
+                              "jitter"),
+                      fill = "grey",
+                      xlab = "",
+                      ylab = "GCase absolute fluorescence value",
+                      position = position_dodge(0.9)) +
+  theme(legend.position = "none",
+        axis.text.x = element_text(angle = 90, hjust = 1.0, size = 9, face = "bold", family = "Helvetica"),
+        axis.text.y = element_text(size = 9, face = "bold"),
+        axis.title.y = element_text(size = 10, face = "bold")) +
+  scale_y_continuous(expand = c(0, 0),
+                     limits = c(0, 17000.0))
+
+# Place the plot
+plotGG(plot = GCase.pl, 
+       x = 0.50, 
+       y = 0.5, 
+       width = 2, 
+       height = 4.25,
+       just = c("left", "top"), 
+       default.units = "inches")
+
+dev.off()
+
+############ WILL BE SUPP #####
 
@@
 ### SUPPLEMENTARY FIGURE 1
-IHEC consortium has one sample of substantia nigra for H3K27me3, H3K9me3, H3K4me1, H3K4me3 and H3K36me3 from a healthy brain for BAG3, IDUA and SCARB2 loci
-```{r suppFig1, eval = FALSE, echo = TRUE}
+Plot genes of interest from the TH REP2 mCHERRY cell line RNAseq data to demonstrate that expression is similar.  
+In addition, do the same for FOUNDIN-PD.
+```{r suppFig2, eval = FALSE, echo = TRUE}
 ############################################
@@
 pdf("/home/vagrant/Manuscript_1/SUPPLEMENTARY_FIGURE1/SUPPLEMENTARY_FIGURE1.pdf",
-    width = 8.3, 
-    height = 11.7)
+    width = 13, 
+    height = 15)
+
+# Save as TIFF, 300 dpi
+tiff("/home/vagrant/Manuscript_1/SUPPLEMENTARY_FIGURE1/SUPPLEMENTARY_FIGURE1.tiff",
+     width = 8.27,
+     height = 11.67,
+     units = "in",
+     res = 300)
 
 # Create a A4 blank page
-pageCreate(width = 8.3, 
-           height = 11.7, 
+pageCreate(width = 8.27, 
+           height = 11.67, 
            default.units = "inches",
-           showGuides = TRUE)
+           showGuides = FALSE)
 
@@
 
-# ChIP-seq signal BAG3
-# path where bigwig files are
-bw.IHEC.path = "/home/vagrant/Documents/IHEC/ChIP_Seq/BIGWIG/"
-
-# Reads BIGWIG file at BAG3 location - H3K4me1
-bw.BAG3.H3K4me1 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6a1889bf-7312-4e41-b1cc-e2f3be7a8076.fc.signal.bigwig"),
-                               chrom = "chr10",
-                               chromstart = 119611305,
-                               chromend = 119691505)
-
-# Reads BIGWIG file at BAG3 location - H3K4me3
-bw.BAG3.H3K4me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.4cb9300f-9097-4374-8f2a-4afd8ff855fb.fc.signal.bigwig"),
-                               chrom = "chr10",
-                               chromstart = 119611305,
-                               chromend = 119691505)
-
-# Reads BIGWIG file at BAG3 location - H3K36me3
-bw.BAG3.H3K36me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6586e624-852f-4cac-83df-2325cee19699.fc.signal.bigwig"),
-                               chrom = "chr10",
-                               chromstart = 119611305,
-                               chromend = 119691505)
-
-# Reads BIGWIG file at BAG3 location - H3K9me3
-bw.BAG3.H3K9me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.e8fe7664-906e-4d87-8f3a-6ce88dbeadc6.fc.signal.bigwig"),
-                               chrom = "chr10",
-                               chromstart = 119611305,
-                               chromend = 119691505)
-
-# Reads BIGWIG file at BAG3 location - H3K27me3
-bw.BAG3.H3K27me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.5f5024a9-2e3f-4527-82ec-0ed04bf4a848.fc.signal.bigwig"),
-                               chrom = "chr10",
-                               chromstart = 119611305,
-                               chromend = 119691505)
-
-# Add a scale next to the bigwig files - check the maximum to choose
-scale.IHEC.BAG3.max = max(c(bw.BAG3.H3K4me1$score,
-                              bw.BAG3.H3K4me3$score,
-                              bw.BAG3.H3K36me3$score,
-                              bw.BAG3.H3K9me3$score,
-                              bw.BAG3.H3K27me3$score)) %>% 
-  round(.,
-        digits = 1.0)
-
-print(scale.IHEC.BAG3.max)
-
-# Define parameters for the regions
-region.p.IHEC.BAG3 = pgParams(chrom = "chr10",
-                         chromstart = 119611405,
-                         chromend = 119691405,
-                         assembly = "hg38",
-                         range = c(0, scale.IHEC.BAG3.max))
-
-# Add the genomic label
-plotGenomeLabel(
-  chrom = "chr10",
-  chromstart = 119611405,
-  chromend = 119691405,
-  assembly = "hg38",
-  x = 0.75,
-  y = 0.625,
-  length = 4.0,
-  default.units = "inches",
-  scale = "Mb")
-
-# ChIPseq signal H3K4me1
-H3K4me1_BAG3 = plotSignal(
-  data = bw.BAG3.H3K4me1, 
-  params = region.p.IHEC.BAG3,
-  fill = "#b5de2b", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 0.875, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K4me1_BAG3, 
-          at = c(0, scale.IHEC.BAG3.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K4me3
-H3K4me3_BAG3 = plotSignal(
-  data = bw.BAG3.H3K4me3, 
-  params = region.p.IHEC.BAG3,
-  fill = "#35b779", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 1.25, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K4me3_BAG3, 
-          at = c(0, scale.IHEC.BAG3.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K36me3
-H3K36me3_BAG3 = plotSignal(
-  data = bw.BAG3.H3K36me3, 
-  params = region.p.IHEC.BAG3,
-  fill = "#26828e", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 1.625, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K36me3_BAG3, 
-          at = c(0, scale.IHEC.BAG3.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K9me3
-H3K9me3_BAG3 = plotSignal(
-  data = bw.BAG3.H3K9me3, 
-  params = region.p.IHEC.BAG3,
-  fill = "#3e4989", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 2.0, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K9me3_BAG3, 
-          at = c(0, scale.IHEC.BAG3.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K27me3
-H3K27me3_BAG3 = plotSignal(
-  data = bw.BAG3.H3K27me3, 
-  params = region.p.IHEC.BAG3,
-  fill = "#440154", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 2.375, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K27me3_BAG3, 
-          at = c(0, scale.IHEC.BAG3.max),
-          fontsize = 6)
-
-# Gene track
-plotGenes(
-  chrom = "chr10",
-  chromstart = 119611405,
-  chromend = 119691405,
-  assembly = assembly(Genome = "hg38refGene", 
-                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
-                      OrgDb = "org.Hs.eg.db"),
-  fontcolor = "black",
-  fill = "black",
-  x = 0.75,
-  y = 2.75,
-  width = 4.0,
-  height = 0.375,
-  just = c("left", "top"),
-  default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K4me1", 
-         fontsize = 6, 
-         fontcolor = "#b5de2b",
-         x = 0.75,
-         y = 0.875, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K4me3", 
-         fontsize = 6, 
-         fontcolor = "#35b779",
-         x = 0.75,
-         y = 1.25, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K36me3", 
-         fontsize = 6, 
-         fontcolor = "#26828e",
-         x = 0.75,
-         y = 1.625, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K9me3", 
-         fontsize = 6, 
-         fontcolor = "#3e4989",
-         x = 0.75,
-         y = 2.0, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K27me3", 
-         fontsize = 6, 
-         fontcolor = "#440154",
-         x = 0.75,
-         y = 2.375, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Reads BIGWIG file at IDUA location - H3K4me1
-bw.IDUA.H3K4me1 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6a1889bf-7312-4e41-b1cc-e2f3be7a8076.fc.signal.bigwig"),
-                               chrom = "chr4",
-                               chromstart = 947008,
-                               chromend = 1027208)
-
-# Reads BIGWIG file at IDUA location - H3K4me3
-bw.IDUA.H3K4me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.4cb9300f-9097-4374-8f2a-4afd8ff855fb.fc.signal.bigwig"),
-                               chrom = "chr4",
-                               chromstart = 947008,
-                               chromend = 1027208)
-
-# Reads BIGWIG file at IDUA location - H3K36me3
-bw.IDUA.H3K36me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6586e624-852f-4cac-83df-2325cee19699.fc.signal.bigwig"),
-                               chrom = "chr4",
-                               chromstart = 947008,
-                               chromend = 1027208)
-
-# Reads BIGWIG file at IDUA location - H3K9me3
-bw.IDUA.H3K9me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.e8fe7664-906e-4d87-8f3a-6ce88dbeadc6.fc.signal.bigwig"),
-                               chrom = "chr4",
-                               chromstart = 947008,
-                               chromend = 1027208)
-
-# Reads BIGWIG file at IDUA location - H3K27me3
-bw.IDUA.H3K27me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.5f5024a9-2e3f-4527-82ec-0ed04bf4a848.fc.signal.bigwig"),
-                               chrom = "chr4",
-                               chromstart = 947008,
-                               chromend = 1027208)
-
-# Add a scale next to the bigwig files - check the maximum to choose
-scale.IHEC.IDUA.max = max(c(bw.IDUA.H3K4me1$score,
-                              bw.IDUA.H3K4me3$score,
-                              bw.IDUA.H3K36me3$score,
-                              bw.IDUA.H3K9me3$score,
-                              bw.IDUA.H3K27me3$score)) %>% 
-  round(.,
-        digits = 1.0)
-
-print(scale.IHEC.IDUA.max)
-
-# Define parameters for the regions
-region.p.IHEC.IDUA = pgParams(chrom = "chr4",
-                         chromstart = 947108,
-                         chromend = 1027108,
-                         assembly = "hg38",
-                         range = c(0, scale.IHEC.IDUA.max))
-
-# Add the genomic label
-plotGenomeLabel(
-  chrom = "chr4",
-  chromstart = 947108,
-  chromend = 1027108,
-  assembly = "hg38",
-  x = 0.75,
-  y = 3.5,
-  length = 4.0,
-  default.units = "inches",
-  scale = "Mb")
-
-# ChIPseq signal H3K4me1
-H3K4me1_IDUA = plotSignal(
-  data = bw.IDUA.H3K4me1, 
-  params = region.p.IHEC.IDUA,
-  fill = "#b5de2b", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 3.75, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K4me1_IDUA, 
-          at = c(0, scale.IHEC.IDUA.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K4me3
-H3K4me3_IDUA = plotSignal(
-  data = bw.IDUA.H3K4me3, 
-  params = region.p.IHEC.IDUA,
-  fill = "#35b779", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 4.125, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K4me3_IDUA, 
-          at = c(0, scale.IHEC.IDUA.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K36me3
-H3K36me3_IDUA = plotSignal(
-  data = bw.IDUA.H3K36me3, 
-  params = region.p.IHEC.IDUA,
-  fill = "#26828e", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 4.5, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K36me3_IDUA, 
-          at = c(0, scale.IHEC.IDUA.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K9me3
-H3K9me3_IDUA = plotSignal(
-  data = bw.IDUA.H3K9me3, 
-  params = region.p.IHEC.IDUA,
-  fill = "#3e4989", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 4.875, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K9me3_IDUA, 
-          at = c(0, scale.IHEC.IDUA.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K27me3
-H3K27me3_IDUA = plotSignal(
-  data = bw.IDUA.H3K27me3, 
-  params = region.p.IHEC.IDUA,
-  fill = "#440154", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 5.25, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K27me3_IDUA, 
-          at = c(0, scale.IHEC.IDUA.max),
-          fontsize = 6)
-
-# Gene track
-plotGenes(
-  chrom = "chr4",
-  chromstart = 947108,
-  chromend = 1027108,
-  assembly = assembly(Genome = "hg38refGene", 
-                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
-                      OrgDb = "org.Hs.eg.db"),
-  fontcolor = "black",
-  fill = "black",
-  x = 0.75,
-  y = 5.625,
-  width = 4.0,
-  height = 0.375,
-  just = c("left", "top"),
-  default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K4me1", 
-         fontsize = 6, 
-         fontcolor = "#b5de2b",
-         x = 0.75,
-         y = 3.75, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K4me3", 
-         fontsize = 6, 
-         fontcolor = "#35b779",
-         x = 0.75,
-         y = 4.125, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K36me3", 
-         fontsize = 6, 
-         fontcolor = "#26828e",
-         x = 0.75,
-         y = 4.5, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K9me3", 
-         fontsize = 6, 
-         fontcolor = "#3e4989",
-         x = 0.75,
-         y = 4.875, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K27me3", 
-         fontsize = 6, 
-         fontcolor = "#440154",
-         x = 0.75,
-         y = 5.25, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# ChIP-seq signal SCARB2
-# Reads BIGWIG file at SCARB2 location - H3K4me1
-bw.SCARB2.H3K4me1 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6a1889bf-7312-4e41-b1cc-e2f3be7a8076.fc.signal.bigwig"),
-                               chrom = "chr4",
-                               chromstart = 76173617,
-                               chromend = 76253817)
-
-# Reads BIGWIG file at SCARB2 location - H3K4me3
-bw.SCARB2.H3K4me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.4cb9300f-9097-4374-8f2a-4afd8ff855fb.fc.signal.bigwig"),
-                               chrom = "chr4",
-                               chromstart = 76173617,
-                               chromend = 76253817)
-
-# Reads BIGWIG file at SCARB2 location - H3K36me3
-bw.SCARB2.H3K36me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6586e624-852f-4cac-83df-2325cee19699.fc.signal.bigwig"),
-                               chrom = "chr4",
-                               chromstart = 76173617,
-                               chromend = 76253817)
-
-# Reads BIGWIG file at SCARB2 location - H3K9me3
-bw.SCARB2.H3K9me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.e8fe7664-906e-4d87-8f3a-6ce88dbeadc6.fc.signal.bigwig"),
-                               chrom = "chr4",
-                               chromstart = 76173617,
-                               chromend = 76253817)
-
-# Reads BIGWIG file at SCARB2 location - H3K27me3
-bw.SCARB2.H3K27me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.5f5024a9-2e3f-4527-82ec-0ed04bf4a848.fc.signal.bigwig"),
-                               chrom = "chr4",
-                               chromstart = 76173617,
-                               chromend = 76253817)
-
-# Add a scale next to the bigwig files - check the maximum to choose
-scale.IHEC.SCARB2.max = max(c(bw.SCARB2.H3K4me1$score,
-                              bw.SCARB2.H3K4me3$score,
-                              bw.SCARB2.H3K36me3$score,
-                              bw.SCARB2.H3K9me3$score,
-                              bw.SCARB2.H3K27me3$score)) %>% 
-  round(.,
-        digits = 1.0)
-
-print(scale.IHEC.SCARB2.max)
-
-# Define parameters for the regions
-region.p.IHEC.SCARB2 = pgParams(chrom = "chr4",
-                         chromstart = 76173717,
-                         chromend = 76253717,
-                         assembly = "hg38",
-                         range = c(0, scale.IHEC.SCARB2.max))
-
-# Add the genomic label
-plotGenomeLabel(
-  chrom = "chr4",
-  chromstart = 76173717,
-  chromend = 76253717,
-  assembly = "hg38",
-  x = 0.75,
-  y = 6.5,
-  length = 4.0,
-  default.units = "inches",
-  scale = "Mb")
-
-# ChIPseq signal H3K4me1
-H3K4me1_SCARB2 = plotSignal(
-  data = bw.SCARB2.H3K4me1, 
-  params = region.p.IHEC.SCARB2,
-  fill = "#b5de2b", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 6.75, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K4me1_SCARB2, 
-          at = c(0, scale.IHEC.SCARB2.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K4me3
-H3K4me3_SCARB2 = plotSignal(
-  data = bw.SCARB2.H3K4me3, 
-  params = region.p.IHEC.SCARB2,
-  fill = "#35b779", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 7.125, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K4me3_SCARB2, 
-          at = c(0, scale.IHEC.SCARB2.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K36me3
-H3K36me3_SCARB2 = plotSignal(
-  data = bw.SCARB2.H3K36me3, 
-  params = region.p.IHEC.SCARB2,
-  fill = "#26828e", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 7.5, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K36me3_SCARB2, 
-          at = c(0, scale.IHEC.SCARB2.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K9me3
-H3K9me3_SCARB2 = plotSignal(
-  data = bw.SCARB2.H3K9me3, 
-  params = region.p.IHEC.SCARB2,
-  fill = "#3e4989", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 7.875, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K9me3_SCARB2, 
-          at = c(0, scale.IHEC.SCARB2.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K27me3
-H3K27me3_SCARB2 = plotSignal(
-  data = bw.SCARB2.H3K27me3, 
-  params = region.p.IHEC.SCARB2,
-  fill = "#440154", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 8.25, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K27me3_SCARB2, 
-          at = c(0, scale.IHEC.SCARB2.max),
-          fontsize = 6)
-
-# Gene track
-plotGenes(
-  chrom = "chr4",
-  chromstart = 76173717,
-  chromend = 76253717,
-  assembly = assembly(Genome = "hg38refGene", 
-                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
-                      OrgDb = "org.Hs.eg.db"),
-  fontcolor = "black",
-  fill = "black",
-  x = 0.75,
-  y = 8.625,
-  width = 4.0,
-  height = 0.375,
-  just = c("left", "top"),
-  default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K4me1", 
-         fontsize = 6, 
-         fontcolor = "#b5de2b",
-         x = 0.75,
-         y = 6.75, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K4me3", 
-         fontsize = 6, 
-         fontcolor = "#35b779",
-         x = 0.75,
-         y = 7.125, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K36me3", 
-         fontsize = 6, 
-         fontcolor = "#26828e",
-         x = 0.75,
-         y = 7.5, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K9me3", 
-         fontsize = 6, 
-         fontcolor = "#3e4989",
-         x = 0.75,
-         y = 7.875, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K27me3", 
-         fontsize = 6, 
-         fontcolor = "#440154",
-         x = 0.75,
-         y = 8.25, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-#### PANEL B - 
-# text Supplementary Figure 1
-# text B
-plotText(label = "B", 
-         fontsize = 12,
-         x = 0.25, 
-         y = 8.5, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
-
-# Load IHEC RNA-seq data (TPM)
-IHEC.exp = read_delim("/home/vagrant/Documents/IHEC/RNA_seq/genes_tpm.csv",
-                      delim = ",",
-                      col_names = TRUE)
-
-# Genes of interest to be plotted
-goi_ens.filt = goi_ens %>% 
-  as_tibble() %>% 
-  dplyr::filter(ENSEMBL != "ENSG00000274577")
-
-IHEC.exp %>% 
-  # Remove the dot and number in Ensembl IDS
-  mutate(id_col = gsub("\\..*", 
-                       "", 
-                       id_col)) %>% 
-  dplyr:::filter(id_col %in% goi_ens.filt$ENSEMBL) %>% 
-  pivot_longer(cols = starts_with("IHEC"),
-               names_to = "Sample",
-               values_to = "TPM") %>% 
-  mutate(Sample = gsub("",
-                       "",
-                       Sample))
-
-dev.off()
-```
-
-### SUPPLEMENTARY FIGURE 2
-Plot genes of interest from the TH REP2 mCHERRY cell line RNAseq data to demonstrate that expression is similar
-```{r suppFig2, eval = FALSE, echo = TRUE}
-############################################
-########## SUPPLEMENTARY FIGURE 2 ##########
-############################################
-
-# Save as a PDF
-pdf("/home/vagrant/Manuscript_1/SUPPLEMENTARY_FIGURE2/SUPPLEMENTARY_FIGURE2.pdf",
-    width = 13, 
-    height = 15)
-
-# Create a A4 blank page
-pageCreate(width = 8.3, 
-           height = 11.7, 
-           default.units = "inches",
-           showGuides = FALSE)
-
-#### PANEL A - 
-# text Supplementary Figure 2
-plotText(label = "Supplementary Figure 2", 
-         fontsize = 14,
-         x = 0.25, 
-         y = 0.25, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
-# text A
-plotText(label = "A", 
-         fontsize = 12,
-         x = 0.25, 
-         y = 0.5, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
-
 # Load data
@@
 
-dat.THREP2.FPKM %>% 
-  dplyr::filter(gene_name == "SCARB2") %>% 
-  summary()
-
-# Filter for genes of interest - BAG3 and LHX1
+dat.THREP2.FPKM = read_delim("/Volumes/deborah.gerard/Documents/epifunc/RNAseq/TH_REP2_mCHERRY/180604_HT-Rep2_fpkm.tsv",
+                     delim = "\t",
+                     col_names = TRUE)
+
+# Filter for genes of interest - BAG3 and LHX1 - IDUA, ZBTB14, SLC26A1 - SCARB2, NR2C2, FAM47E
 BAG3.LHX1 = c("BAG3",
@@
                values_to = "FPKM") %>% 
-  dplyr::filter(str_detect(Samples, paste("SmNPC", "pos", sep = "|"))) %>% 
+  #dplyr::filter(str_detect(Samples, paste("SmNPC", "pos", sep = "|"))) %>% 
   mutate(Cond = case_when(str_detect(Samples, "D15pos") ~ "Positively sorted neurons D15",
+                          str_detect(Samples, "D15neg") ~ "Negatively sorted neurons D15",
                           str_detect(Samples, "D30pos") ~ "Positively sorted neurons D30",
+                          str_detect(Samples, "D30neg") ~ "Negatively sorted neurons D30",
                           TRUE ~ "smNPCs"),
@@
                        levels = c("smNPCs", 
+                                  "Negatively sorted neurons D15",
                                   "Positively sorted neurons D15",
+                                  "Negatively sorted neurons D30",
                                   "Positively sorted neurons D30")))
+
+# GBA expression in TH REP2 cell line
+ggboxplot(dat.THREP2.FPKM %>% 
+                            dplyr::filter(str_detect(gene_id, "ENSG00000177628")),
+                          x = "Cond", 
+                          y = "FPKM", 
+                          add = "jitter", 
+                          fill = "Cond", 
+                          facet.by = "gene_name",
+                          xlab = "", 
+                          ylab = "Fragments Per Kilobase Million (FPKM)",
+          title = "GBA expression in TH REP2 cell line") +
+  scale_x_discrete(labels = c("smNPCs",
+                              "Negatively sorted neurons D15",
+                              "Positively sorted neurons D15",
+                              "Negatively sorted neurons D30",
+                              "Positively sorted neurons D30")) +
+  theme(legend.position = "none",
+        axis.text.x = element_text(angle = 45, hjust = 1.0))
+
+ggboxplot(dat.RPKM.filt %>% 
+                            dplyr::filter(str_detect(gene_id, "ENSG00000177628")),
+                          x = "Cond", 
+                          y = "RPKM", 
+                          add = "jitter", 
+                          fill = "Cond", 
+                          palette = c("#A9A9A9", "#B22222", "#DC143C", "#E9967A"),
+                          facet.by = "gene_name",
+                          xlab = "", 
+                          ylab = "Reads Per Kilobase Million (RPKM)") +
+  scale_x_discrete(labels = c("smNPC",
+                              expression("mDAN D15"),
+                              expression("mDAN D30"),
+                              expression("mDAN D50"))) +
+  theme(legend.position = "none",
+        axis.text.x = element_text(angle = 90))
 
@@
 
-#FIPD = read_delim("/home/vagrant/epifunc/PPMI_data/FOUNDIN-PD_150.9_RNAB/aggregated_expression/countTable.tsv",
-#                  delim = "\t",
-#                  col_names = TRUE)
+FIPD = read_delim("/Volumes/deborah.gerard/Documents/epifunc/PPMI_data/FOUNDIN-PD_150.9_RNAB/aggregated_expression/cpmTable.tsv",
+                  delim = "\t",
+                  col_names = TRUE)
 
@@
                           "SLC26A1",
+                          "SCARB1",
                           "SCARB2",
+                          "SCARB3",
+                          "CD36",
                           "NR2C2",
-                          "FAM47E"), 
+                          "FAM47E",
+                          "TH",
+                          "GAPDH",
+                          "ACTB",
+                          "GBA1",
+                          "PSAP",
+                          "CTSD"), 
                  columns = c("SYMBOL",
@@
   as_tibble() %>% 
-  dplyr::filter(ENSEMBL != "ENSG00000274577") %>% 
+  dplyr::filter(!ENSEMBL %in% c("ENSG00000274577",
+                                "ENSG00000262446")) %>% 
   dplyr::rename(ENSEMBL.not.dot = ENSEMBL)
-
-# Load the information abour iPSCs cell lines
-info_iPSCs = read_delim("/home/vagrant/epifunc/PPMI_data/Participant_Status_02Jun2023.csv",
-                  delim = ",",
-                  col_names = TRUE)
-
-info_iPSCs = info_iPSCs %>% 
-  mutate(PATNO = as.character(PATNO))
 
@@
 FIPD.fin = FIPD %>% 
-  #mutate(Geneid = str_replace(Geneid, "\\..", "")) %>% 
   dplyr::filter(str_detect(Geneid, paste(goi_ens$ENSEMBL.not.dot, collapse = "|"))) %>% 
@@
   dplyr::select(ENSEMBL, ENSEMBL.not.dot, everything()) %>% 
-  #left_join(goi_ens, by = "ENSEMBL") %>% 
   pivot_longer(cols = starts_with("RNAB"), names_to = "Samples", values_to = "CPM") %>% 
-  mutate(PATNO = str_extract(Samples, "[^RNAB_PPMI_]+"),
-         Day = str_extract(Samples, "da+\\d+")) %>% 
-  left_join(info_iPSCs,
-            by = "PATNO") %>% 
+  mutate(Day = str_extract(Samples, "da+\\d+")) %>% 
   left_join(goi_ens, 
             by = "ENSEMBL.not.dot") %>% 
-  dplyr::select(ENSEMBL:Day, COHORT_DEFINITION, SYMBOL) %>% 
-  mutate(Condition = case_when(COHORT_DEFINITION == "Healthy Control" ~ "Healthy\ncontrol",
-                               COHORT_DEFINITION == "Parkinson's Disease" ~ "Parkinson's\ndisease",
-                               TRUE ~ COHORT_DEFINITION)) %>% 
-  #group_by(SYMBOL, Day, COHORT_DEFINITION) %>% 
-  group_by(ENSEMBL, Day) %>% 
-  mutate(AVG_CPM = mean(CPM, na.rm = TRUE))
-
-# Plot expression of all putative target genes and TFs except SCARB2 (will be plot alone)
-FIPD.exp.pl = ggboxplot(FIPD.fin %>% 
-                          dplyr::filter(SYMBOL != "SCARB2"),
+  dplyr::select(SYMBOL, Day, CPM)
+
+# Anova
+BAG3.aov = FIPD.fin %>% 
+  dplyr::filter(SYMBOL %in% BAG3.LHX1) %>% 
+  group_by(SYMBOL) %>% 
+  anova_test(CPM ~ Day)
+
+# Tukey post-hoc test
+BAG3.ph = FIPD.fin %>% 
+  dplyr::filter(SYMBOL %in% BAG3.LHX1) %>% 
+  group_by(SYMBOL) %>% 
+  tukey_hsd(CPM ~ Day) %>% 
+  add_xy_position(x = "Day")
+
+# Plot expression of BAG3 and LHX1
+FIPD.exp_BAG3.LHX1 = ggboxplot(FIPD.fin %>% 
+                          dplyr::filter(SYMBOL %in% BAG3.LHX1),
                      x = "Day", 
-                     y = "AVG_CPM", 
+                     y = "CPM", 
                      add = "jitter", 
@@
                      xlab = "", 
-                     ylab = "CPM") +
+                     ylab = "Counts per Million (CPM)",
+                     add.params = list(size = 0.1)) +
   scale_x_discrete(labels = c("Day 0",
@@
   theme(legend.position = "none",
-        axis.text.x = element_text(angle = 90),
-        strip.text.x = element_text(size = 6))
+        axis.text.x = element_text(angle = 90))
+  # stat_pvalue_manual(BAG3.ph, 
+  #                    hide.ns = TRUE,
+  #                    label = "p.adj") +
+  # labs(subtitle = get_test_label(BAG3.aov, 
+  #                                detailed = FALSE))
 
 # Place the plot  
-plotGG(plot = FIPD.exp.pl, 
+plotGG(plot = FIPD.exp_BAG3.LHX1, 
        x = 0.5, 
        y = 4.75 ,
-       width = 6, 
-       height = 4.5,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-# Plot expression of SCARB2
-FIPD.exp.SCARB2.pl = ggboxplot(FIPD.fin %>% 
-                          dplyr::filter(SYMBOL == "SCARB2"),
+       width = 2.5, 
+       height = 3.5,
+       just = c("left", "top"), 
+       default.units = "inches")
+
+# Anova
+IDUA.aov = FIPD.fin %>% 
+  dplyr::filter(SYMBOL %in% IDUA.ZBTB14) %>% 
+  group_by(SYMBOL) %>% 
+  anova_test(CPM ~ Day)
+
+# Tukey post-hoc test
+IDUA.ph = FIPD.fin %>% 
+  dplyr::filter(SYMBOL %in% IDUA.ZBTB14) %>% 
+  group_by(SYMBOL) %>% 
+  tukey_hsd(CPM ~ Day) %>% 
+  add_xy_position(x = "Day")
+
+# Plot expression of IDUA and ZBTB14
+FIPD.exp_IDUA.ZBTB14 = ggboxplot(FIPD.fin %>% 
+                                   dplyr::filter(SYMBOL %in% IDUA.ZBTB14) %>% 
+                            mutate(SYMBOL = factor(SYMBOL, levels = c("IDUA", "ZBTB14", "SLC26A1"))),
                      x = "Day", 
-                     y = "AVG_CPM", 
+                     y = "CPM", 
                      add = "jitter", 
@@
   theme(legend.position = "none",
-        axis.text.x = element_text(angle = 90),
-        strip.text.x = element_text(size = 6))
+        axis.text.x = element_text(angle = 90))
+  # stat_pvalue_manual(IDUA.ph, 
+  #                    hide.ns = TRUE,
+  #                    label = "p.adj") +
+  # labs(subtitle = get_test_label(IDUA.aov, 
+  #                                detailed = FALSE))
 
 # Place the plot  
-plotGG(plot = FIPD.exp.SCARB2.pl, 
-       x = 0.5, 
-       y = 9.75 ,
-       width = 6, 
+plotGG(plot = FIPD.exp_IDUA.ZBTB14, 
+       x = 3.125, 
+       y = 4.75 ,
+       width = 2.5, 
        height = 3.5,
@@
        default.units = "inches")
+
+# Anova
+SCARB2.aov = FIPD.fin %>% 
+  dplyr::filter(SYMBOL %in% SCARB2.NR2C2) %>% 
+  group_by(SYMBOL) %>% 
+  anova_test(CPM ~ Day)
+
+# Tukey post-hoc test
+SCARB2.ph = FIPD.fin %>% 
+  dplyr::filter(SYMBOL %in% SCARB2.NR2C2) %>% 
+  group_by(SYMBOL) %>% 
+  tukey_hsd(CPM ~ Day) %>% 
+  add_xy_position(x = "Day")
+
+# Plot expression of SCARB2 and NR2C2
+FIPD.exp_SCARB2.NR2C2 = ggboxplot(FIPD.fin %>% 
+                                   dplyr::filter(SYMBOL %in% SCARB2.NR2C2) %>% 
+                            mutate(SYMBOL = factor(SYMBOL, levels = c("SCARB2", "NR2C2", "FAM47E"))),
+                     x = "Day", 
+                     y = "CPM", 
+                     add = "jitter", 
+                     fill = "Day", 
+                     palette = c("#482677FF", "#2D708EFF", "#29AF7FFF"),
+                     facet.by = "SYMBOL",
+                     xlab = "", 
+                     ylab = "Counts per Million (CPM)",
+                     add.params = list(size = 0.1)) +
+  scale_x_discrete(labels = c("Day 0",
+                              "Day 25",
+                              "Day 65")) +
+  theme(legend.position = "none",
+        axis.text.x = element_text(angle = 90))
+  # stat_pvalue_manual(SCARB2.ph, 
+  #                    hide.ns = TRUE,
+  #                    label = "p.adj") +
+  # labs(subtitle = get_test_label(SCARB2.aov, 
+  #                                detailed = FALSE))
+
+# Place the plot  
+plotGG(plot = FIPD.exp_SCARB2.NR2C2, 
+       x = 5.625, 
+       y = 4.75 ,
+       width = 2.5, 
+       height = 3.5,
+       just = c("left", "top"), 
+       default.units = "inches")
+
+dev.off()
+
+## GBA expression in FOUNDIN-PD
+ggboxplot(FIPD.fin %>% 
+            dplyr::filter(SYMBOL == "GBA1"),
+                     x = "Day", 
+                     y = "CPM", 
+                     add = "jitter", 
+                     fill = "Day", 
+                     palette = c("#482677FF", "#2D708EFF", "#29AF7FFF"),
+                     facet.by = "SYMBOL",
+                     xlab = "", 
+                     ylab = "Counts per Million (CPM)",
+                     add.params = list(size = 0.1),
+          title = "GBA expression in FOUNDIN-PD cell lines") +
+  scale_x_discrete(labels = c("Day 0",
+                              "Day 25",
+                              "Day 65")) +
+  theme(legend.position = "none",
+        axis.text.x = element_text(angle = 90))
+
+FIPD %>% 
+  dplyr::filter(str_detect(Geneid, "ENSG00000177628")) %>% 
+  pivot_longer(cols = starts_with("RNAB"), names_to = "Sample",
+               values_to = "CPM") %>%
+
+```
+
+### SUPPLEMENTARY FIGURE 2
+IHEC consortium has one sample of substantia nigra for H3K27me3, H3K9me3, H3K4me1, H3K4me3 and H3K36me3 from a healthy brain for BAG3, IDUA and SCARB2 loci
+```{r suppFig1, eval = FALSE, echo = TRUE}
+############################################
+########## SUPPLEMENTARY FIGURE 2 ##########
+############################################
+
+# Save as a PDF
+pdf("/home/vagrant/Manuscript_1/SUPPLEMENTARY_FIGURE2/SUPPLEMENTARY_FIGURE2.pdf",
+    width = 8.3, 
+    height = 11.7)
+
+# Save as TIFF, 300 dpi
+tiff("/home/vagrant/Manuscript_1/SUPPLEMENTARY_FIGURE2/SUPPLEMENTARY_FIGURE2.tiff",
+     width = 8.27,
+     height = 11.67,
+     units = "in",
+     res = 300)
+
+# Create a A4 blank page
+pageCreate(width = 8.27, 
+           height = 11.67, 
+           default.units = "inches",
+           showGuides = FALSE)
+
+#### PANEL A - 
+# text Supplementary Figure 2
+plotText(label = "Supplementary Figure 2", 
+         fontsize = 14,
+         x = 0.25, 
+         y = 0.25, 
+         just = "left", 
+         default.units = "inches",
+         fontface = "bold")
+# text A
+plotText(label = "A", 
+         fontsize = 12,
+         x = 0.25, 
+         y = 0.5, 
+         just = "left", 
+         default.units = "inches",
+         fontface = "bold")
+
+# ChIP-seq signal BAG3
+# path where bigwig files are
+bw.IHEC.path = "/home/vagrant/Documents/IHEC/ChIP_Seq/BIGWIG/"
+
+# Reads BIGWIG file at BAG3 location - H3K4me1
+bw.BAG3.H3K4me1 = readBigwig(file = paste0(bw.IHEC.path,
+                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6a1889bf-7312-4e41-b1cc-e2f3be7a8076.fc.signal.bigwig"),
+                               chrom = "chr10",
+                               chromstart = 119611305,
+                               chromend = 119691505)
+
+# Reads BIGWIG file at BAG3 location - H3K4me3
+bw.BAG3.H3K4me3 = readBigwig(file = paste0(bw.IHEC.path,
+                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.4cb9300f-9097-4374-8f2a-4afd8ff855fb.fc.signal.bigwig"),
+                               chrom = "chr10",
+                               chromstart = 119611305,
+                               chromend = 119691505)
+
+# Reads BIGWIG file at BAG3 location - H3K36me3
+bw.BAG3.H3K36me3 = readBigwig(file = paste0(bw.IHEC.path,
+                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6586e624-852f-4cac-83df-2325cee19699.fc.signal.bigwig"),
+                               chrom = "chr10",
+                               chromstart = 119611305,
+                               chromend = 119691505)
+
+# Reads BIGWIG file at BAG3 location - H3K9me3
+bw.BAG3.H3K9me3 = readBigwig(file = paste0(bw.IHEC.path,
+                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.e8fe7664-906e-4d87-8f3a-6ce88dbeadc6.fc.signal.bigwig"),
+                               chrom = "chr10",
+                               chromstart = 119611305,
+                               chromend = 119691505)
+
+# Reads BIGWIG file at BAG3 location - H3K27me3
+bw.BAG3.H3K27me3 = readBigwig(file = paste0(bw.IHEC.path,
+                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.5f5024a9-2e3f-4527-82ec-0ed04bf4a848.fc.signal.bigwig"),
+                               chrom = "chr10",
+                               chromstart = 119611305,
+                               chromend = 119691505)
+
+# Add a scale next to the bigwig files - check the maximum to choose
+scale.IHEC.BAG3.max = max(c(bw.BAG3.H3K4me1$score,
+                              bw.BAG3.H3K4me3$score,
+                              bw.BAG3.H3K36me3$score,
+                              bw.BAG3.H3K9me3$score,
+                              bw.BAG3.H3K27me3$score)) %>% 
+  round(.,
+        digits = 1.0)
+
+print(scale.IHEC.BAG3.max)
+
+# Define parameters for the regions
+region.p.IHEC.BAG3 = pgParams(chrom = "chr10",
+                         chromstart = 119611405,
+                         chromend = 119691405,
+                         assembly = "hg38",
+                         range = c(0, scale.IHEC.BAG3.max))
+
+# Add the genomic label
+plotGenomeLabel(
+  chrom = "chr10",
+  chromstart = 119611405,
+  chromend = 119691405,
+  assembly = "hg38",
+  x = 0.75,
+  y = 0.625,
+  length = 4.0,
+  default.units = "inches",
+  scale = "Mb")
+
+# ChIPseq signal H3K4me1
+H3K4me1_BAG3 = plotSignal(
+  data = bw.BAG3.H3K4me1, 
+  params = region.p.IHEC.BAG3,
+  fill = "#b5de2b", 
+  alpha = 0.7, 
+  linecolor = NA,
+  x = 0.75, 
+  y = 0.875, 
+  width = 4.0, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+annoYaxis(plot = H3K4me1_BAG3, 
+          at = c(0, scale.IHEC.BAG3.max),
+          fontsize = 6)
+
+# ChIPseq signal H3K4me3
+H3K4me3_BAG3 = plotSignal(
+  data = bw.BAG3.H3K4me3, 
+  params = region.p.IHEC.BAG3,
+  fill = "#35b779", 
+  alpha = 0.7, 
+  linecolor = NA,
+  x = 0.75, 
+  y = 1.25, 
+  width = 4.0, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+annoYaxis(plot = H3K4me3_BAG3, 
+          at = c(0, scale.IHEC.BAG3.max),
+          fontsize = 6)
+
+# ChIPseq signal H3K36me3
+H3K36me3_BAG3 = plotSignal(
+  data = bw.BAG3.H3K36me3, 
+  params = region.p.IHEC.BAG3,
+  fill = "#26828e", 
+  alpha = 0.7, 
+  linecolor = NA,
+  x = 0.75, 
+  y = 1.625, 
+  width = 4.0, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+annoYaxis(plot = H3K36me3_BAG3, 
+          at = c(0, scale.IHEC.BAG3.max),
+          fontsize = 6)
+
+# ChIPseq signal H3K9me3
+H3K9me3_BAG3 = plotSignal(
+  data = bw.BAG3.H3K9me3, 
+  params = region.p.IHEC.BAG3,
+  fill = "#3e4989", 
+  alpha = 0.7, 
+  linecolor = NA,
+  x = 0.75, 
+  y = 2.0, 
+  width = 4.0, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+annoYaxis(plot = H3K9me3_BAG3, 
+          at = c(0, scale.IHEC.BAG3.max),
+          fontsize = 6)
+
+# ChIPseq signal H3K27me3
+H3K27me3_BAG3 = plotSignal(
+  data = bw.BAG3.H3K27me3, 
+  params = region.p.IHEC.BAG3,
+  fill = "#440154", 
+  alpha = 0.7, 
+  linecolor = NA,
+  x = 0.75, 
+  y = 2.375, 
+  width = 4.0, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+annoYaxis(plot = H3K27me3_BAG3, 
+          at = c(0, scale.IHEC.BAG3.max),
+          fontsize = 6)
+
+# Gene track
+plotGenes(
+  chrom = "chr10",
+  chromstart = 119611405,
+  chromend = 119691405,
+  assembly = assembly(Genome = "hg38refGene", 
+                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
+                      OrgDb = "org.Hs.eg.db"),
+  fontcolor = "black",
+  fill = "black",
+  x = 0.75,
+  y = 2.75,
+  width = 4.0,
+  height = 0.375,
+  just = c("left", "top"),
+  default.units = "inches")
+
+# Add the samples name
+plotText(label = "H3K4me1", 
+         fontsize = 6, 
+         fontcolor = "#b5de2b",
+         x = 0.75,
+         y = 0.875, 
+         just = c("left", "top"),
+         default.units = "inches")
+
+# Add the samples name
+plotText(label = "H3K4me3", 
+         fontsize = 6, 
+         fontcolor = "#35b779",
+         x = 0.75,
+         y = 1.25, 
+         just = c("left", "top"),
+         default.units = "inches")
+
+# Add the samples name
+plotText(label = "H3K36me3", 
+         fontsize = 6, 
+         fontcolor = "#26828e",
+         x = 0.75,
+         y = 1.625, 
+         just = c("left", "top"),
+         default.units = "inches")
+
+# Add the samples name
+plotText(label = "H3K9me3", 
+         fontsize = 6, 
+         fontcolor = "#3e4989",
+         x = 0.75,
+         y = 2.0, 
+         just = c("left", "top"),
+         default.units = "inches")
+
+# Add the samples name
+plotText(label = "H3K27me3", 
+         fontsize = 6, 
+         fontcolor = "#440154",
+         x = 0.75,
+         y = 2.375, 
+         just = c("left", "top"),
+         default.units = "inches")
+
+# Reads BIGWIG file at IDUA location - H3K4me1
+bw.IDUA.H3K4me1 = readBigwig(file = paste0(bw.IHEC.path,
+                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6a1889bf-7312-4e41-b1cc-e2f3be7a8076.fc.signal.bigwig"),
+                               chrom = "chr4",
+                               chromstart = 947008,
+                               chromend = 1027208)
+
+# Reads BIGWIG file at IDUA location - H3K4me3
+bw.IDUA.H3K4me3 = readBigwig(file = paste0(bw.IHEC.path,
+                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.4cb9300f-9097-4374-8f2a-4afd8ff855fb.fc.signal.bigwig"),
+                               chrom = "chr4",
+                               chromstart = 947008,
+                               chromend = 1027208)
+
+# Reads BIGWIG file at IDUA location - H3K36me3
+bw.IDUA.H3K36me3 = readBigwig(file = paste0(bw.IHEC.path,
+                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6586e624-852f-4cac-83df-2325cee19699.fc.signal.bigwig"),
+                               chrom = "chr4",
+                               chromstart = 947008,
+                               chromend = 1027208)
+
+# Reads BIGWIG file at IDUA location - H3K9me3
+bw.IDUA.H3K9me3 = readBigwig(file = paste0(bw.IHEC.path,
+                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.e8fe7664-906e-4d87-8f3a-6ce88dbeadc6.fc.signal.bigwig"),
+                               chrom = "chr4",
+                               chromstart = 947008,
+                               chromend = 1027208)
+
+# Reads BIGWIG file at IDUA location - H3K27me3
+bw.IDUA.H3K27me3 = readBigwig(file = paste0(bw.IHEC.path,
+                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.5f5024a9-2e3f-4527-82ec-0ed04bf4a848.fc.signal.bigwig"),
+                               chrom = "chr4",
+                               chromstart = 947008,
+                               chromend = 1027208)
+
+# Add a scale next to the bigwig files - check the maximum to choose
+scale.IHEC.IDUA.max = max(c(bw.IDUA.H3K4me1$score,
+                              bw.IDUA.H3K4me3$score,
+                              bw.IDUA.H3K36me3$score,
+                              bw.IDUA.H3K9me3$score,
+                              bw.IDUA.H3K27me3$score)) %>% 
+  round(.,
+        digits = 1.0)
+
+print(scale.IHEC.IDUA.max)
+
+# Define parameters for the regions
+region.p.IHEC.IDUA = pgParams(chrom = "chr4",
+                         chromstart = 947108,
+                         chromend = 1027108,
+                         assembly = "hg38",
+                         range = c(0, scale.IHEC.IDUA.max))
+
+# Add the genomic label
+plotGenomeLabel(
+  chrom = "chr4",
+  chromstart = 947108,
+  chromend = 1027108,
+  assembly = "hg38",
+  x = 0.75,
+  y = 3.5,
+  length = 4.0,
+  default.units = "inches",
+  scale = "Mb")
+
+# ChIPseq signal H3K4me1
+H3K4me1_IDUA = plotSignal(
+  data = bw.IDUA.H3K4me1, 
+  params = region.p.IHEC.IDUA,
+  fill = "#b5de2b", 
+  alpha = 0.7, 
+  linecolor = NA,
+  x = 0.75, 
+  y = 3.75, 
+  width = 4.0, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+annoYaxis(plot = H3K4me1_IDUA, 
+          at = c(0, scale.IHEC.IDUA.max),
+          fontsize = 6)
+
+# ChIPseq signal H3K4me3
+H3K4me3_IDUA = plotSignal(
+  data = bw.IDUA.H3K4me3, 
+  params = region.p.IHEC.IDUA,
+  fill = "#35b779", 
+  alpha = 0.7, 
+  linecolor = NA,
+  x = 0.75, 
+  y = 4.125, 
+  width = 4.0, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+annoYaxis(plot = H3K4me3_IDUA, 
+          at = c(0, scale.IHEC.IDUA.max),
+          fontsize = 6)
+
+# ChIPseq signal H3K36me3
+H3K36me3_IDUA = plotSignal(
+  data = bw.IDUA.H3K36me3, 
+  params = region.p.IHEC.IDUA,
+  fill = "#26828e", 
+  alpha = 0.7, 
+  linecolor = NA,
+  x = 0.75, 
+  y = 4.5, 
+  width = 4.0, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+annoYaxis(plot = H3K36me3_IDUA, 
+          at = c(0, scale.IHEC.IDUA.max),
+          fontsize = 6)
+
+# ChIPseq signal H3K9me3
+H3K9me3_IDUA = plotSignal(
+  data = bw.IDUA.H3K9me3, 
+  params = region.p.IHEC.IDUA,
+  fill = "#3e4989", 
+  alpha = 0.7, 
+  linecolor = NA,
+  x = 0.75, 
+  y = 4.875, 
+  width = 4.0, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+annoYaxis(plot = H3K9me3_IDUA, 
+          at = c(0, scale.IHEC.IDUA.max),
+          fontsize = 6)
+
+# ChIPseq signal H3K27me3
+H3K27me3_IDUA = plotSignal(
+  data = bw.IDUA.H3K27me3, 
+  params = region.p.IHEC.IDUA,
+  fill = "#440154", 
+  alpha = 0.7, 
+  linecolor = NA,
+  x = 0.75, 
+  y = 5.25, 
+  width = 4.0, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+annoYaxis(plot = H3K27me3_IDUA, 
+          at = c(0, scale.IHEC.IDUA.max),
+          fontsize = 6)
+
+# Gene track
+plotGenes(
+  chrom = "chr4",
+  chromstart = 947108,
+  chromend = 1027108,
+  assembly = assembly(Genome = "hg38refGene", 
+                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
+                      OrgDb = "org.Hs.eg.db"),
+  fontcolor = "black",
+  fill = "black",
+  x = 0.75,
+  y = 5.625,
+  width = 4.0,
+  height = 0.375,
+  just = c("left", "top"),
+  default.units = "inches")
+
+# Add the samples name
+plotText(label = "H3K4me1", 
+         fontsize = 6, 
+         fontcolor = "#b5de2b",
+         x = 0.75,
+         y = 3.75, 
+         just = c("left", "top"),
+         default.units = "inches")
+
+# Add the samples name
+plotText(label = "H3K4me3", 
+         fontsize = 6, 
+         fontcolor = "#35b779",
+         x = 0.75,
+         y = 4.125, 
+         just = c("left", "top"),
+         default.units = "inches")
+
+# Add the samples name
+plotText(label = "H3K36me3", 
+         fontsize = 6, 
+         fontcolor = "#26828e",
+         x = 0.75,
+         y = 4.5, 
+         just = c("left", "top"),
+         default.units = "inches")
+
+# Add the samples name
+plotText(label = "H3K9me3", 
+         fontsize = 6, 
+         fontcolor = "#3e4989",
+         x = 0.75,
+         y = 4.875, 
+         just = c("left", "top"),
+         default.units = "inches")
+
+# Add the samples name
+plotText(label = "H3K27me3", 
+         fontsize = 6, 
+         fontcolor = "#440154",
+         x = 0.75,
+         y = 5.25, 
+         just = c("left", "top"),
+         default.units = "inches")
+
+# ChIP-seq signal SCARB2
+# Reads BIGWIG file at SCARB2 location - H3K4me1
+bw.SCARB2.H3K4me1 = readBigwig(file = paste0(bw.IHEC.path,
+                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6a1889bf-7312-4e41-b1cc-e2f3be7a8076.fc.signal.bigwig"),
+                               chrom = "chr4",
+                               chromstart = 76173617,
+                               chromend = 76253817)
+
+# Reads BIGWIG file at SCARB2 location - H3K4me3
+bw.SCARB2.H3K4me3 = readBigwig(file = paste0(bw.IHEC.path,
+                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.4cb9300f-9097-4374-8f2a-4afd8ff855fb.fc.signal.bigwig"),
+                               chrom = "chr4",
+                               chromstart = 76173617,
+                               chromend = 76253817)
+
+# Reads BIGWIG file at SCARB2 location - H3K36me3
+bw.SCARB2.H3K36me3 = readBigwig(file = paste0(bw.IHEC.path,
+                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6586e624-852f-4cac-83df-2325cee19699.fc.signal.bigwig"),
+                               chrom = "chr4",
+                               chromstart = 76173617,
+                               chromend = 76253817)
+
+# Reads BIGWIG file at SCARB2 location - H3K9me3
+bw.SCARB2.H3K9me3 = readBigwig(file = paste0(bw.IHEC.path,
+                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.e8fe7664-906e-4d87-8f3a-6ce88dbeadc6.fc.signal.bigwig"),
+                               chrom = "chr4",
+                               chromstart = 76173617,
+                               chromend = 76253817)
+
+# Reads BIGWIG file at SCARB2 location - H3K27me3
+bw.SCARB2.H3K27me3 = readBigwig(file = paste0(bw.IHEC.path,
+                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.5f5024a9-2e3f-4527-82ec-0ed04bf4a848.fc.signal.bigwig"),
+                               chrom = "chr4",
+                               chromstart = 76173617,
+                               chromend = 76253817)
+
+# Add a scale next to the bigwig files - check the maximum to choose
+scale.IHEC.SCARB2.max = max(c(bw.SCARB2.H3K4me1$score,
+                              bw.SCARB2.H3K4me3$score,
+                              bw.SCARB2.H3K36me3$score,
+                              bw.SCARB2.H3K9me3$score,
+                              bw.SCARB2.H3K27me3$score)) %>% 
+  round(.,
+        digits = 1.0)
+
+print(scale.IHEC.SCARB2.max)
+
+# Define parameters for the regions
+region.p.IHEC.SCARB2 = pgParams(chrom = "chr4",
+                         chromstart = 76173717,
+                         chromend = 76253717,
+                         assembly = "hg38",
+                         range = c(0, scale.IHEC.SCARB2.max))
+
+# Add the genomic label
+plotGenomeLabel(
+  chrom = "chr4",
+  chromstart = 76173717,
+  chromend = 76253717,
+  assembly = "hg38",
+  x = 0.75,
+  y = 6.5,
+  length = 4.0,
+  default.units = "inches",
+  scale = "Mb")
+
+# ChIPseq signal H3K4me1
+H3K4me1_SCARB2 = plotSignal(
+  data = bw.SCARB2.H3K4me1, 
+  params = region.p.IHEC.SCARB2,
+  fill = "#b5de2b", 
+  alpha = 0.7, 
+  linecolor = NA,
+  x = 0.75, 
+  y = 6.75, 
+  width = 4.0, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+annoYaxis(plot = H3K4me1_SCARB2, 
+          at = c(0, scale.IHEC.SCARB2.max),
+          fontsize = 6)
+
+# ChIPseq signal H3K4me3
+H3K4me3_SCARB2 = plotSignal(
+  data = bw.SCARB2.H3K4me3, 
+  params = region.p.IHEC.SCARB2,
+  fill = "#35b779", 
+  alpha = 0.7, 
+  linecolor = NA,
+  x = 0.75, 
+  y = 7.125, 
+  width = 4.0, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+annoYaxis(plot = H3K4me3_SCARB2, 
+          at = c(0, scale.IHEC.SCARB2.max),
+          fontsize = 6)
+
+# ChIPseq signal H3K36me3
+H3K36me3_SCARB2 = plotSignal(
+  data = bw.SCARB2.H3K36me3, 
+  params = region.p.IHEC.SCARB2,
+  fill = "#26828e", 
+  alpha = 0.7, 
+  linecolor = NA,
+  x = 0.75, 
+  y = 7.5, 
+  width = 4.0, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+annoYaxis(plot = H3K36me3_SCARB2, 
+          at = c(0, scale.IHEC.SCARB2.max),
+          fontsize = 6)
+
+# ChIPseq signal H3K9me3
+H3K9me3_SCARB2 = plotSignal(
+  data = bw.SCARB2.H3K9me3, 
+  params = region.p.IHEC.SCARB2,
+  fill = "#3e4989", 
+  alpha = 0.7, 
+  linecolor = NA,
+  x = 0.75, 
+  y = 7.875, 
+  width = 4.0, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+annoYaxis(plot = H3K9me3_SCARB2, 
+          at = c(0, scale.IHEC.SCARB2.max),
+          fontsize = 6)
+
+# ChIPseq signal H3K27me3
+H3K27me3_SCARB2 = plotSignal(
+  data = bw.SCARB2.H3K27me3, 
+  params = region.p.IHEC.SCARB2,
+  fill = "#440154", 
+  alpha = 0.7, 
+  linecolor = NA,
+  x = 0.75, 
+  y = 8.25, 
+  width = 4.0, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+annoYaxis(plot = H3K27me3_SCARB2, 
+          at = c(0, scale.IHEC.SCARB2.max),
+          fontsize = 6)
+
+# Gene track
+plotGenes(
+  chrom = "chr4",
+  chromstart = 76173717,
+  chromend = 76253717,
+  assembly = assembly(Genome = "hg38refGene", 
+                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
+                      OrgDb = "org.Hs.eg.db"),
+  fontcolor = "black",
+  fill = "black",
+  x = 0.75,
+  y = 8.625,
+  width = 4.0,
+  height = 0.375,
+  just = c("left", "top"),
+  default.units = "inches")
+
+# Add the samples name
+plotText(label = "H3K4me1", 
+         fontsize = 6, 
+         fontcolor = "#b5de2b",
+         x = 0.75,
+         y = 6.75, 
+         just = c("left", "top"),
+         default.units = "inches")
+
+# Add the samples name
+plotText(label = "H3K4me3", 
+         fontsize = 6, 
+         fontcolor = "#35b779",
+         x = 0.75,
+         y = 7.125, 
+         just = c("left", "top"),
+         default.units = "inches")
+
+# Add the samples name
+plotText(label = "H3K36me3", 
+         fontsize = 6, 
+         fontcolor = "#26828e",
+         x = 0.75,
+         y = 7.5, 
+         just = c("left", "top"),
+         default.units = "inches")
+
+# Add the samples name
+plotText(label = "H3K9me3", 
+         fontsize = 6, 
+         fontcolor = "#3e4989",
+         x = 0.75,
+         y = 7.875, 
+         just = c("left", "top"),
+         default.units = "inches")
+
+# Add the samples name
+plotText(label = "H3K27me3", 
+         fontsize = 6, 
+         fontcolor = "#440154",
+         x = 0.75,
+         y = 8.25, 
+         just = c("left", "top"),
+         default.units = "inches")
+
+#### PANEL B - 
+# text Supplementary Figure 1
+# text B
+plotText(label = "B", 
+         fontsize = 12,
+         x = 0.25, 
+         y = 8.5, 
+         just = "left", 
+         default.units = "inches",
+         fontface = "bold")
+
+# Load IHEC RNA-seq data (TPM)
+IHEC.exp = read_delim("/home/vagrant/Documents/IHEC/RNA_seq/genes_tpm.csv",
+                      delim = ",",
+                      col_names = TRUE)
+
+# Genes of interest to be plotted
+goi_ens.filt = goi_ens %>% 
+  as_tibble() %>% 
+  dplyr::filter(ENSEMBL != "ENSG00000274577")
+
+IHEC.exp %>% 
+  # Remove the dot and number in Ensembl IDS
+  mutate(id_col = gsub("\\..*", 
+                       "", 
+                       id_col)) %>% 
+  dplyr:::filter(id_col %in% goi_ens.filt$ENSEMBL) %>% 
+  pivot_longer(cols = starts_with("IHEC"),
+               names_to = "Sample",
+               values_to = "TPM") %>% 
+  mutate(Sample = gsub("",
+                       "",
+                       Sample))
 
@@
 
+# Save as TIFF, 300 ppi
+tiff("/home/vagrant/Manuscript_1/SUPPLEMENTARY_FIGURE3/SUPPLEMENTARY_FIGURE3.tiff",
+     width = 8.27,
+     height = 11.67,
+     units = "in",
+     res = 300)
+
 # Create a A4 blank page
-pageCreate(width = 8.3, 
-           height = 11.7, 
+pageCreate(width = 8.27, 
+           height = 11.67, 
            default.units = "inches",
@@
   filter(avsnp150 == "rs1465922") %>% 
-  select(samples) %>% 
+  dplyr::select(samples) %>% 
   separate(samples,
@@
 
-```{r}
+```{r, eval = FALSE, echo = TRUE}
 sessionInfo()
 ```
+
+```{r, eval = FALSE, echo = TRUE}
+library("tidyverse")
+library("readxl")
+library("AnnotationDbi")
+library("EnsDb.Hsapiens.v86")
+
+# Load data
+TFlist = read_excel("/Volumes/deborah.gerard/Documents/Elena/Human_TF_list.xls",
+                    skip = 1,
+                    col_names = TRUE)
+
+# Add gene symbol
+TFlist.GN = select(EnsDb.Hsapiens.v86, 
+       keys = as.character(TFlist$EntrezID), 
+       columns = c("ENTREZID", "GENENAME"), 
+       keytype = "ENTREZID")
+
+TFlist.GN %>% 
+  as_tibble() %>% 
+  distinct(GENENAME)
+  write_delim(.,
+              "/Volumes/deborah.gerard/Documents/Elena/Human_TF_list_geneName.txt",
+              col_names = TRUE,
+              delim = "\t")
+
+```
+
+### TEST GBA and SNPs
+```{r, eval = FALSE, echo = TRUE}
+# Load the genotype of rs1465922 from the PPMI data
+GT_PPMI = read_delim("/Volumes/deborah.gerard/Documents/epifunc/PPMI_data/VCF/ppmi.july2018.chr4.vqsr_with_my_snps.vcf",
+                     delim = "\t",
+                     comment = "##",
+                     col_names = TRUE)
+
+# Filter for rs1465922 only and assign genotype for that snp
+GT_PPMI.filt = GT_PPMI %>% 
+  filter(ID == "rs1465922") %>% 
+  dplyr::select(-QUAL:-FORMAT) %>% 
+  pivot_longer(cols = starts_with("PPMI"),
+               names_to = "Sample",
+               values_to = "Genotype.plus") %>% 
+  mutate(Genotype = gsub("\\:.*", "", Genotype.plus),
+         Genotype.l = case_when(Genotype == "1/1" ~ "A/A",
+                                Genotype == "0/1" ~ "G/A",
+                                Genotype == "0/0" ~ "G/G"),
+         Sample = gsub("SI", "", Sample)) %>%
+  dplyr::select(ID, Sample, Genotype.l)
+
+# Expression for SCARB2, NR2C2, TH, GAPDH and ACTIN
+FIPD.fin2 = FIPD %>% 
+  #dplyr::filter(str_detect(Geneid, paste(goi_ens$ENSEMBL.not.dot, collapse = "|"))) %>% 
+  dplyr::filter(str_detect(Geneid, paste(goi_ens$ENSEMBL.not.dot, 
+                                         collapse = "|"))) %>% 
+  dplyr::rename(ENSEMBL = Geneid) %>% 
+  mutate(ENSEMBL.not.dot = gsub("\\..*", "", ENSEMBL)) %>% 
+  dplyr::select(ENSEMBL, ENSEMBL.not.dot, everything()) %>% 
+  pivot_longer(cols = starts_with("RNAB"), names_to = "Samples", values_to = "CPM") %>% 
+  mutate(Day = str_extract(Samples, "da+\\d+")) %>% 
+  left_join(goi_ens, 
+            by = "ENSEMBL.not.dot") %>% 
+  dplyr::select(SYMBOL, Samples, Day, CPM) %>% 
+  #dplyr::filter(SYMBOL %in% c("SCARB2", "NR2C2", "TH", "ACTB", "GAPDH", "FAM47E", "GBA1")) %>% 
+  mutate(Sample = str_extract(Samples, "PPMI+\\d+")) %>% 
+  left_join(GT_PPMI.filt,
+            by = "Sample")
+
+# How many samples are heterozygous for rs1465922
+FIPD.fin2 %>% 
+  dplyr::select(Sample:Genotype.l) %>% 
+  filter(Genotype.l == "G/A") %>% 
+  dplyr::select(Sample) %>% 
+  distinct(Sample) %>% 
+  summarise(count = n())
+
+# Number of samples
+FIPD.fin2 %>% 
+  dplyr::select(Sample) %>% 
+  distinct(Sample) %>% 
+  summarise(count = n())
+
+# Plot for SCARB2
+ggboxplot(FIPD.fin2 %>% 
+            dplyr::filter(SYMBOL == "SCARB2"),
+          x = "Genotype.l",
+          y = "CPM",
+          facet.by = "Day",
+          title = "SCARB2 expression associated to rs1465922 genotype") + 
+  stat_compare_means(method = "anova",
+                     label.y = 1500) +
+  stat_compare_means(comparisons = list(c("A/A", "G/A"),
+                                        c("A/A", "G/G"),
+                                        c("G/A", "G/G")))
+
+# Plot for NR2C2
+ggboxplot(FIPD.fin2 %>% 
+            dplyr::filter(SYMBOL == "NR2C2"),
+          x = "Genotype.l",
+          y = "CPM",
+          facet.by = "Day",
+          title = "NR2C2 expression associated to rs1465922 genotype") + 
+  stat_compare_means(method = "anova",
+                     label.y = 100) +
+  stat_compare_means(comparisons = list(c("A/A", "G/A"),
+                                        c("A/A", "G/G"),
+                                        c("G/A", "G/G")))
+
+# Plot for TH
+ggboxplot(FIPD.fin2 %>% 
+            dplyr::filter(SYMBOL == "TH"),
+          x = "Genotype.l",
+          y = "CPM",
+          facet.by = "Day",
+          title = "TH expression associated to rs1465922 genotype") + 
+  stat_compare_means(method = "anova",
+                     label.y = 100) +
+  stat_compare_means(comparisons = list(c("A/A", "G/A"),
+                                        c("A/A", "G/G"),
+                                        c("G/A", "G/G")))
+
+# Plot for FAM47E
+ggboxplot(FIPD.fin2 %>% 
+            dplyr::filter(SYMBOL == "FAM47E"),
+          x = "Genotype.l",
+          y = "CPM",
+          facet.by = "Day",
+          title = "FAM47E expression associated to rs1465922 genotype") + 
+  stat_compare_means(method = "anova",
+                     label.y = 30) +
+  stat_compare_means(comparisons = list(c("A/A", "G/A"),
+                                        c("A/A", "G/G"),
+                                        c("G/A", "G/G")))
+
+# Plot for GAPDH
+ggboxplot(FIPD.fin2 %>% 
+            dplyr::filter(SYMBOL == "GAPDH"),
+          x = "Genotype.l",
+          y = "CPM",
+          facet.by = "Day",
+          title = "GAPDH expression associated to rs1465922 genotype") + 
+  stat_compare_means(method = "anova",
+                     label.y = 4500) +
+  stat_compare_means(comparisons = list(c("A/A", "G/A"),
+                                        c("A/A", "G/G"),
+                                        c("G/A", "G/G")))
+
+# Plot for ACTB
+ggboxplot(FIPD.fin2 %>% 
+            dplyr::filter(SYMBOL == "ACTB"),
+          x = "Genotype.l",
+          y = "CPM",
+          facet.by = "Day",
+          title = "ACTB expression associated to rs1465922 genotype") + 
+  stat_compare_means(method = "anova",
+                     label.y = 10000) +
+  stat_compare_means(comparisons = list(c("A/A", "G/A"),
+                                        c("A/A", "G/G"),
+                                        c("G/A", "G/G")))
+
+# Plot for GBA1
+ggboxplot(FIPD.fin2 %>% 
+            dplyr::filter(SYMBOL == "GBA1"),
+          x = "Genotype.l",
+          y = "CPM",
+          facet.by = "Day",
+          title = "GBA1 expression associated to rs1465922 genotype") + 
+  stat_compare_means(method = "anova",
+                     label.y = 100) +
+  stat_compare_means(comparisons = list(c("A/A", "G/A"),
+                                        c("A/A", "G/G"),
+                                        c("G/A", "G/G")))
+
+# Plot for PSAP
+ggboxplot(FIPD.fin2 %>% 
+            dplyr::filter(SYMBOL == "PSAP"),
+          x = "Genotype.l",
+          y = "CPM",
+          facet.by = "Day",
+          title = "PSAP expression associated to rs1465922 genotype") + 
+  stat_compare_means(method = "anova",
+                     label.y = 100) +
+  stat_compare_means(comparisons = list(c("A/A", "G/A"),
+                                        c("A/A", "G/G"),
+                                        c("G/A", "G/G")))
+
+# Scatterplot of GBA1 and SCARB2 independtly of the genotype
+FIPD.fin2 %>% 
+  dplyr::filter(SYMBOL %in% c("GBA1", "SCARB2")) %>% 
+  pivot_wider(names_from = SYMBOL, values_from = CPM) %>% 
+  ggscatter(x = "SCARB2",
+            y = "GBA1",
+            color = "Genotype.l",
+            facet.by = c("Day", "Genotype.l"),
+            add = "reg.line",
+            cor.coef = TRUE,
+            cor.coeff.args = list(method = "pearson", label.x = 3, label.sep = "\n"),
+            xlab = "SCARB2 expression (CPM)",
+            ylab = "GBA1 expression (CPM)") +
+  theme(legend.position = "right")
+
+# Scatterplot of NR2C2 and SCARB2 independtly of the genotype
+FIPD.fin2 %>% 
+  dplyr::filter(SYMBOL %in% c("NR2C2", "SCARB2")) %>% 
+  pivot_wider(names_from = SYMBOL, values_from = CPM) %>% 
+  ggscatter(x = "SCARB2",
+            y = "NR2C2",
+            color = "Genotype.l",
+            facet.by = c("Day", "Genotype.l"),
+            add = "reg.line",
+            cor.coef = TRUE,
+            cor.coeff.args = list(method = "pearson", label.x = 3, label.sep = "\n"),
+            xlab = "SCARB2 expression (CPM)",
+            ylab = "NR2C2 expression (CPM)") +
+  theme(legend.position = "right")
+
+dat.RPKM = read_delim("/Volumes/deborah.gerard/Documents/epifunc/RNAseq/RPKM_genename",
+                      delim = "\t",
+                      col_names = TRUE)
+
+dat.RPKM %>% 
+  #mutate(gene_id = gsub("\\..*", "", gene_id)) %>% 
+  dplyr::filter(str_detect(gene_id, "ENSG00000177628")) %>% 
+  pivot_longer(cols = contains("reads"), names_to = "Sample", values_to = "RPKM") %>% 
+  mutate(Cond = case_when(str_detect(Sample, "D15_possort") ~ "Positively sorted neurons D15",
+                         str_detect(Sample, "D30_possort") ~ "Positively sorted neurons D30",
+                         str_detect(Sample, "D50_possort") ~ "Positively sorted neurons D50",
+                         str_detect(Sample, "D15_negsort") ~ "Negatively sorted neurons D15",
+                         str_detect(Sample, "D50_negsort") ~ "Negatively sorted neurons D50",
+                         str_detect(Sample, "ASTRO") ~ "Astrocytes D65",
+                         TRUE ~ "smNPCs"),
+         Cond = factor(Cond, levels = c("smNPCs", 
+                                        "Negatively sorted neurons D15",
+                                        "Positively sorted neurons D15",
+                                        "Positively sorted neurons D30",
+                                        "Negatively sorted neurons D50",
+                                        "Positively sorted neurons D50",
+                                        "Astrocytes D65"))) %>% 
+  ggboxplot(.,
+            x = "Cond",
+            y = "RPKM",
+            fill = "Cond",
+            facet.by = "gene_name",
+            title = "GBA expression in TH REP1 cell line") +
+  theme(legend.position = "none",
+        axis.text.x = element_text(angle = 45, hjust = 1))
+
+## TH REP1 RNA feature counts
+THREP1.rawCount = read_rds("/Volumes/deborah.gerard/Documents/epifunc/RNAseq/fc_hs_q30RNA.rds")
+
+# TH REP1 reads assigned
+THREP1.seqDepth = THREP1.rawCount$stat %>% 
+  dplyr::slice(1) %>% 
+  as_tibble() %>% 
+  pivot_longer(cols = contains("bam"), names_to = "Sample", values_to = "seqDepthInSple") %>% 
+  #dplyr::filter(!str_detect(Sample, "ASTRO")) %>% 
+  dplyr::select(-Status)
+
+# TH REP1 raw read counts
+THREP1.rawCount$counts %>% 
+ as.data.frame() %>% 
+  rownames_to_column(var = "gene_id") %>% 
+  as_tibble() %>% 
+  filter(str_detect(gene_id, "ENSG00000177628")) %>% 
+  pivot_longer(cols = contains("bam"), names_to = "Sample", values_to = "rawCounts") %>% 
+  #dplyr::filter(!str_detect(Sample, "ASTRO")) %>% 
+  left_join(THREP1.seqDepth, by = "Sample") %>% 
+  mutate(CPM = (rawCounts/seqDepthInSple)*10^6) %>% 
+  mutate(Cond = case_when(str_detect(Sample, "D15_pos") ~ "Positively sorted neurons D15",
+                          str_detect(Sample, "D15_neg") ~ "Negatively sorted neurons D15",
+                          str_detect(Sample, "D30_pos") ~ "Positively sorted neurons D30",
+                          str_detect(Sample, "D50_neg") ~ "Negatively sorted neurons D50",
+                          str_detect(Sample, "D50_pos") ~ "Positively sorted neurons D50",
+                          str_detect(Sample, "ASTRO") ~ "Astrocytes D65",
+                          TRUE ~ "smNPCs"),
+         Cond = factor(Cond, 
+                       levels = c("smNPCs", 
+                                  "Negatively sorted neurons D15",
+                                  "Positively sorted neurons D15",
+                                  "Negatively sorted neurons D30",
+                                  "Positively sorted neurons D30",
+                                  "Negatively sorted neurons D50",
+                                  "Positively sorted neurons D50",
+                                  "Astrocytes D65"))) %>% 
+  ggboxplot(.,
+            x = "Cond",
+            y = "CPM",
+            facet.by = "gene_id",
+            fill = "Cond",
+            title = "GBA expression (as CPM) in TH REP1 cell line") +
+  theme(legend.position = "none",
+        axis.text.x = element_text(angle = 45, hjust = 1))
+
+# TEST IF GBA is mutated in TH REP1 from WGS
+THREP1.wgs = read_rds("/Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/E19D017a78.merge.qc.SNP_INDEL.hg19.annotated.rds")
+
+THREP1.wgs %>% 
+  dplyr::filter(str_detect(Gene.refGene, "GBA"),
+                CHR == 1) %>% 
+  View()
+```
+
+##TEST 28 SNPs
+```{bash, eval = FALSE, echo = TRUE}
+# Concatenate all output files from Nina
+# smNPC
+awk 'BEGIN{ FS = OFS = "\t" } { print $0, (NR==1?
+"Sample" : "smNPC") }' /Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/PD_smNPC_0.01_0.5.txt > /Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/REPRO/PD_smNPC_0.01_0.5_SAMPLE_NAME.txt
+
+# mDAN D15
+awk 'BEGIN{ FS = OFS = "\t" } { print $0, (NR==1?
+"Sample" : "mDAN_D15") }' /Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/PD_D15_pos_0.01_0.5.txt > /Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/REPRO/PD_D15_pos_0.01_0.5_SAMPLE_NAME.txt
+
+# mDAN D30
+awk 'BEGIN{ FS = OFS = "\t" } { print $0, (NR==1?
+"Sample" : "mDAN_D30") }' /Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/PD_D30_pos_0.01_0.5_new_20210308.txt > /Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/REPRO/PD_D30_pos_0.01_0.5_new_20210308_SAMPLE_NAME.txt
+
+# mDAN D50
+awk 'BEGIN{ FS = OFS = "\t" } { print $0, (NR==1?
+"Sample" : "mDAN_D50") }' /Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/PD_D50_pos_0.01_0.5.txt > /Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/REPRO/PD_D50_pos_0.01_0.5_SAMPLE_NAME.txt
+
+# Astro
+awk 'BEGIN{ FS = OFS = "\t" } { print $0, (NR==1?
+"Sample" : "astro") }' /Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/PD_astro_0.01_0.5.txt > /Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/REPRO/PD_astro_0.01_0.5_SAMPLE_NAME.txt
+
+# Concatenate them all together
+cat /Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/REPRO/PD_smNPC_0.01_0.5_SAMPLE_NAME.txt \
+/Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/REPRO/PD_D15_pos_0.01_0.5_SAMPLE_NAME.txt \
+/Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/REPRO/PD_D30_pos_0.01_0.5_new_20210308_SAMPLE_NAME.txt \
+/Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/REPRO/PD_D50_pos_0.01_0.5_SAMPLE_NAME.txt \
+/Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/REPRO/PD_astro_0.01_0.5_SAMPLE_NAME.txt > /Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/REPRO/SNEEP_PD.txt
+```
+
+Load the PD GWAS data (hg38)
+```{r, eval = FALSE, echo = TRUE}
+nalls_allSNPs.HG38.GR = readRDS(
+"/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/nalls_allSNPs.HG38.GR.rds")
+
+nalls_allSNPs.HG38.GR.pvalFilt = nalls_allSNPs.HG38.GR %>% 
+  as_tibble() %>% 
+  dplyr::select(seqnames:end, p, effect_allele:other_allele) %>% 
+  unite(col = "tmp", c(seqnames, start), sep = ":", remove = FALSE) %>% 
+  unite(col = "SNP_position", c(tmp, end), sep = "-", remove = TRUE) %>% 
+  dplyr::filter(p < 5e-08)
+
+nalls_allSNPs.HG38.GR.pvalFilt106 = nalls_allSNPs.HG38.GR %>% 
+  as_tibble() %>% 
+  dplyr::select(seqnames:end, p, effect_allele:other_allele) %>% 
+  unite(col = "tmp", c(seqnames, start), sep = ":", remove = FALSE) %>% 
+  unite(col = "SNP_position", c(tmp, end), sep = "-", remove = TRUE) %>% 
+  dplyr::filter(p < 5e-06)
+
+SNEEP_out_all = read_delim("/Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/REPRO/SNEEP_PD.txt",
+                           delim = "\t",
+                           col_names = TRUE)
+
+SNEEP_out_all %>% 
+  dplyr::filter(SNP_position %in% nalls_allSNPs.HG38.GR.pvalFilt$SNP_position) %>% 
+  distinct(SNP_position, .keep_all = TRUE) %>% 
+  View()
+
+SNEEP_out_all %>% 
+  dplyr::filter(SNP_position %in% nalls_allSNPs.HG38.GR.pvalFilt106$SNP_position) %>% 
+  distinct(SNP_position, .keep_all = TRUE) %>% 
+  View()
+
+strawr::readHicChroms("/Volumes/deborah.gerard/Documents/Wetlab/epifunc/LOW_C/LowCO/LowCO/FANC_output_mixedNeur/hic/binned/FANC_opti_mixed_neur_100kb.hic")
+```

### 2024-04-03 Manuscript_1.Rmd
Edit Figure 4A

@@
            colour = "black") +
-  geom_text(aes(label = format(c(0.3,
+  geom_text(aes(label = format(c(paste0("p = ",
+                                        0.3),
                           "",
-                          0.3,
+                          paste0("p = ",
+                                 0.3),
                           "",
-                          0.003,
+                          paste0("p = ",
+                                 0.003),
                           "",
-                          0.0000003,
+                          paste0("p = ",
+                                 0.0000003),
                           "",
-                          0.2,
+                          paste0("p = ",
+                                 0.2),
                           ""),
@@
                      title = "Read at SCARB2 promoter overlapping rs1465922 (SCARB2)",
-                     label = format(c(0.3,
+                     label = format(c(paste0("p = ",
+                                        0.3),
                           "",
-                          0.3,
+                          paste0("p = ",
+                                 0.3),
                           "",
-                          0.003,
+                          paste0("p = ",
+                                 0.003),
                           "",
-                          0.0000003,
+                          paste0("p = ",
+                                 0.0000003),
                           "",
-                          0.2,
+                          paste0("p = ",
+                                 0.2),
                           ""),

### 2025-01-30 Manuscript_1.Rmd
Code for figures update

--- 2024-02-13 Manuscript_1.Rmd
@@
 
+##
+#rsync -avzPhu iris-cluster:/home/users/dgerard/Singularity_containers/Manuscript_1_singularity.sif ~/Downloads/
+
+#scp -r -P 2222 -i /Users/deborah.gerard/singularity-vm/.vagrant/machines/default/virtualbox/private_key \
+#~/Downloads/Manuscript_1_singularity.sif vagrant@127.0.0.1:/home/vagrant/Manuscript_1_singularity/
+
+##
 # Check singularity version
@@
 sudo singularity shell --writable Manuscript_1_singularity_tmp
+
+# TEST
+sudo singularity build --sandbox Manuscript_1_singularity_tmp Manuscript_1_singularity.sif
 
@@
 devtools::install_version("dbplyr", version = "2.3.4")
+
+# ggmanh
+BiocManager::install("ggmanh")
 ```
@@
 library("ggcyto")
+library("ggmanh")
+library("rtracklayer")
+library("plyranges")
+library("RColorBrewer")
 
@@
 packageVersion("extrafont") #0.19
-packageVersion("showtext")  #0.9.6
+packageVersion("showtext")  #0.9.7
 packageVersion("JASPAR2020")  #0.99.10
 packageVersion("TFBSTools") #1.36.0
-packageVersion("ggseqlogo") #0.1
+packageVersion("ggseqlogo") #0.2
 packageVersion("biomaRt") #2.54.1
-packageVersion("LDlinkR") #1.3.0
+packageVersion("LDlinkR") #1.4.0
 packageVersion("AllelicImbalance")  #1.36.0
@@
 packageVersion("AnnotationDbi") #1.60.2
-packageVersion("dbplyr")  #2.3.4
+#packageVersion("dbplyr")  #2.5.0
+packageVersion("scales")  #1.3.0
+packageVersion("flowCore")  #2.10.0
+packageVersion("ggcyto")  #1.26.4
+packageVersion("ggmanh")  #1.2.0
+packageVersion("rtracklayer") #1.58.0
+packageVersion("plyranges") #1.18.0
+packageVersion("RColorBrewer")  #1.1.3
 
@@
 # FIGURES
+Generating the manhattan plot for the PD GWAS is memory demanding. Go to the HPC
+```{bash, eval = FALSE, echo = TRUE}
+#ssh iris-cluster
+#salloc --nodes=1 -p interactive --qos debug -C batch -t 02:00:00 --mem 24G
+
+# Load the Singularity module
+#module load tools/Singularity/3.8.1
+#singularity shell --bind /scratch/users/dgerard:/scratch/users/dgerard $HOME/Singularity_containers/Manuscript_1_singularity.sif
+```
+
 ### FIGURE 1
@@
 ##############################
-# Save as a PDF
-pdf("/home/vagrant/Manuscript_1/FIGURE1/FIGURE1.pdf",
-    width = 8.3, 
-    height = 11.7)
+# Save as TIFF, 300 ppi
+tiff("/home/vagrant/Manuscript_1/FIGURE1/FIGURE1.tiff",
+     width = 8.27,
+     height = 9.5,
+     units = "in",
+     res = 300,
+     compression = "lzw")
 
 # Create a A4 blank page
-pageCreate(width = 8.3, 
-           height = 11.7, 
+pageCreate(width = 8.27, 
+           height = 9.5, 
            default.units = "inches",
-           showGuides = FALSE)
+           showGuides = TRUE)
 
@@
 
+##########################################
+#### Figure 1A Data generation scheme ####
+##########################################
+# Figure 1A generated in Biorender
+fig1A = readPNG("/home/vagrant/Manuscript_1/FIGURE1/Fig1A_Biorender_vertical.png")
+
+plotRaster(image = fig1A,
+           x = 0.5, 
+           y = 2.5, 
+           default.units = "inches",
+           width = 2.5, 
+           height = 3.75, 
+           just = "left",
+           interpolate = TRUE)
+
+##########################################
+#### Figure 1B Odd ratio #################
+##########################################
 # text B
@@
          fontsize = 12,
-         x = 0.25, 
-         y = 1.5, 
+         fontfamily = "Helvetica",
+         x = 3.0, 
+         y = 0.5, 
          just = "left", 
@@
 
-# text C
-plotText(label = "C", 
-         fontsize = 12,
-         x = 0.25, 
-         y = 4.5, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
-
-# text D
-plotText(label = "D", 
-         fontsize = 12,
-         x = 0.25, 
-         y = 8.25, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
-
-###################
-#### Figure 1A ####
-###################
-Fig1A = readPNG("/home/vagrant/Manuscript_1/FIGURE1/Fig1A.png")
-
-# Plot Figure 1A
-plotRaster(image = Fig1A,
-           x = 0.375,
-           y = 0.625,
-           width = 7.55,
-           height = 1.0,
-           just = c("left", 
-                    "top"),
-           interpolate = FALSE)
-
-###################
-#### Figure 1B ####
-###################
 # Load data obtained from Jochen
@@
                         col_names = TRUE)
-
-#RNAseq_odd = read_delim("/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/REFORMAT_tpm_gene_sets.gsa.txt",
-#                        delim = "\t",
-#                        col_names = TRUE)
 
@@
             nudge_y = 0.40) +
-  xlab("Odds ratio (95% Confidence Interval)") +
+  xlab("Odds ratio \n(95% Confidence Interval)") +
   ylab("")
 
-# Place
+# Place the plot
 plotGG(plot = fig1B, 
+       x = 3.25, 
+       y = 0.5, 
+       width = 4.5, 
+       height = 4.5,
+       just = c("left", "top"), 
+       default.units = "inches")
+
+####################################
+#### Figure 1C LowC - Chr4 #########
+####################################
+# text C
+plotText(label = "C", 
+         fontsize = 12,
+         fontfamily = "Helvetica",
+         x = 0.25, 
+         y = 5.25, 
+         just = "left", 
+         default.units = "inches",
+         fontface = "bold")
+
+# Load TH REP1 mCHERRY mDAN neurons D30 (N1) at 50kb resolution
+mDAN.D30.50kb = readHic(file = "/home/vagrant/epifunc/LowC_smNPC_THpos_neur/FANC_output_N1_mDAN_D30/hic/juicer_like/N1_mDAN_D30.juicer.50kb.hic",
+                     chrom = "chr4",
+                     assembly = "hg38",
+                     resolution = 50000,
+                     res_scale = "BP",
+                     norm = "NONE",
+                     matrix = "observed")
+
+# Load TH REP1 mCHERRY mDAN neurons D30 (N1) at 25kb resolution
+mDAN.D30.25kb = readHic(file = "/home/vagrant/epifunc/LowC_smNPC_THpos_neur/FANC_output_N1_mDAN_D30/hic/juicer_like/N1_mDAN_D30.juicer.25kb.hic",
+                     chrom = "chr4",
+                     assembly = "hg38",
+                     resolution = 25000,
+                     res_scale = "BP",
+                     norm = "NONE",
+                     matrix = "observed")
+
+# Load TH REP1 mCHERRY smNPCs (N1) at 50kb resolution
+smNPC.50kb = readHic(file = "/home/vagrant/epifunc/LowC_smNPC_THpos_neur/FANC_output_N1_smNPC/hic/juicer_like/N1_smNPC.juicer.50kb.hic",
+                     chrom = "chr4",
+                     assembly = "hg38",
+                     resolution = 50000,
+                     res_scale = "BP",
+                     norm = "NONE",
+                     matrix = "observed")
+
+# Full chr4 to display
+region.p.chr4 = pgParams(chrom = "chr4",
+                         assembly = assembly(Genome = "hg38refGene",
+                                             TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene",
+                                             OrgDb = "org.Hs.eg.db"),
+                         just = c("left", "top"),
+                         width = 3.5,
+                         fontcolor = "black",
+                         fill = "black")
+
+# Plot full chr4 - smNPC on top of the diagonale and mDAN D30 at the bottom of the diagonale
+LowC_smNPC.top = plotHicSquare(data = smNPC.50kb, 
+                               params = region.p.chr4,
+                               zrange = c(0, 5), 
+                               resolution = "auto",
+                               half = "top",
+                               x = 0.5,
+                               y = 5.5, 
+                               height = 3.5)
+
+annoHeatmapLegend(plot = LowC_smNPC.top, 
+                  fontsize = 7,
                   x = 0.375, 
-       y = 1.75, 
-       width = 3.0, 
-       height = 2.5,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-###################
-#### Figure 1C ####
-###################
-Fig1C_pip = readPNG("/home/vagrant/Manuscript_1/FIGURE1/Fig1C_pipeline.png")
-
-Fig1C_tab1.1 = readPNG("/home/vagrant/Manuscript_1/FIGURE1/Fig1C_SNPs_tab1.png/Fig1C_SNPs_tab1.png-1.png")
-Fig1C_tab1.2 = readPNG("/home/vagrant/Manuscript_1/FIGURE1/Fig1C_SNPs_tab1.png/Fig1C_SNPs_tab1.png-2.png")
-
-# Plot Figure 1C
-plotRaster(image = Fig1C_pip,
-           x = 0.375,
+                  y = 6.0,
+                  width = 0.07, 
+                  height = 0.5, 
+                  just = c("left", "top"),
+                  default.units = "inches")
+
+# smNPC
+plotText(label = "smNPC", 
+         fontsize = 12,
+         fontfamily = "Helvetica",
+         x = 0.5625, 
+         y = 5.625, 
+         just = "left", 
+         default.units = "inches",
+         fontface = "bold")
+
+LowC_mDAND30.bottom = plotHicSquare(data = mDAN.D30.50kb, 
+                               params = region.p.chr4,
+                               zrange = c(0, 5), 
+                               resolution = "auto",
+                               half = "bottom",
+                               x = 0.5,
+                               y = 5.5, 
+                               height = 3.5)
+
+annoHeatmapLegend(plot = LowC_mDAND30.bottom, fontsize = 7,
+                  x = 4.0625, 
+                  y = 6.0,
+                  width = 0.07, 
+                  height = 0.5,
+                  just = c("left", "top"),
+                  default.units = "inches")
+
+# mDAN D30
+plotText(label = "mDAN D30", 
+         fontsize = 12,
+         fontfamily = "Helvetica",
+         x = 3.0, 
+         y = 8.9375, 
+         just = "left", 
+         default.units = "inches",
+         fontface = "bold")
+
+# Add genome label of chr4
+annoGenomeLabel(plot = LowC_mDAND30.bottom, 
+                scale = "Mb", 
+                axis = "x",
+                x = 0.5, 
+                y = 9.0625, 
+                just = c("left", "top"))
+
+# Annotate SNCA domain that will be zoomed in fid1D
+SNCA.TAD = GRanges("chr4",
+                   ranges = IRanges(start = 89000000,
+                                    end = 91000000))
+
+domainAnno = annoDomains(plot = LowC_mDAND30.bottom, 
+                         data = SNCA.TAD,
+                         half = "bottom", 
+                         linecolor = "red")
+
+###################################
+#### Figure 1D SNCA locus #########
+###################################
+# Zoom on SNCA an add ATACseq dataof the locus
+# Define parameters for a small part of chr4 where SNCA is
+# Add ATACseq track of smNPC, mDAN D15, mDAN D30, mDAN D50
+# text D
+plotText(label = "D", 
+         fontsize = 12,
+         fontfamily = "Helvetica",
+         x = 4.125, 
          y = 5.25, 
-           width = 3.0,
-           height = 2.5,
-           just = c("left", 
-                    "top"),
-           interpolate = FALSE)
-
-plotRaster(image = Fig1C_tab1.1,
-           x = 3.375,
-           y = 5.25,
-           width = 2.3,
-           height = 2.5,
-           just = c("left", 
-                    "top"),
-           interpolate = FALSE)
-
-plotRaster(image = Fig1C_tab1.2,
-           x = 5.8,
-           y = 5.25,
-           width = 2.3,
-           height = 2.5,
-           just = c("left", 
-                    "top"),
-           interpolate = FALSE)
-
-#diag_edge_data = tibble(from = c("~17x10^6\nPD GWAS SNPs",
-#                                 "~3400 significant\nPD GWAS SNPs",
-#                                 "28 significant\nPD rSNPs"),
-#                        to = c("~3400 significant\nPD GWAS SNPs",
-#                               "28 significant\nPD rSNPs",
-#                               "3 significant\nPD rSNPs"))
-#
-#diag_node_data = tibble(name = c("~17x10^6\nPD GWAS SNPs",
-#                                 "~3400 significant\nPD GWAS SNPs",
-#                                 "28 significant\nPD rSNPs",
-#                                "3 significant\nPD rSNPs"),
-#                        label = name)
-
-# Diagramme
-# fig1C = ggflowchart(diag_edge_data,
-#                    diag_node_data,
-#                    text_size = 3.0,
-#                    arrow_size = 0.2)
-
-# Place the diagramme
-#plotGG(plot = fig1C, 
-#       x = 0.5, 
-#       y = 4.5, 
-#      width = 1.5, 
-#       height = 3.0,
-#       just = c("left", "top"), 
-#      default.units = "inches")
+         just = "left", 
+         default.units = "inches",
+         fontface = "bold")
+
+bw.path = "/home/vagrant/epifunc/"
+
+# smNPC N1
+bw.SNCA.smNPC.1 = readBigwig(file = paste0(bw.path, "BIGWIG/smNPC_I.bw"),
+    chrom = "chr4", chromstart = 89000000, chromend = 91000000)
+
+# smNPC N2
+bw.SNCA.smNPC.2 = readBigwig(file = paste0(bw.path, "BIGWIG/smNPC_II.bw"),
+    chrom = "chr4", chromstart = 89000000, chromend = 91000000)
+
+# smNPC N3
+bw.SNCA.smNPC.3 = readBigwig(file = paste0(bw.path, "BIGWIG/smNPC_III.bw"),
+    chrom = "chr4", chromstart = 89000000, chromend = 91000000)
+
+# mDAN D15 N1
+bw.SNCA.mDAN.D15.1 = readBigwig(file = paste0(bw.path, "BIGWIG/D15_POS_I.bw"),
+    chrom = "chr4", chromstart = 89000000, chromend = 91000000)
+
+# mDAN D15 N2
+bw.SNCA.mDAN.D15.2 = readBigwig(file = paste0(bw.path, "BIGWIG/D15_POS_II.bw"),
+    chrom = "chr4", chromstart = 89000000, chromend = 91000000)
+
+# mDAN D15 N3
+bw.SNCA.mDAN.D15.3 = readBigwig(file = paste0(bw.path, "BIGWIG/D15_POS_III.bw"),
+    chrom = "chr4", chromstart = 89000000, chromend = 91000000)
+
+# mDAN D30 N1
+bw.SNCA.mDAN.D30.1 = readBigwig(file = paste0(bw.path, "BIGWIG/D30_POS_I.bw"),
+    chrom = "chr4", chromstart = 89000000, chromend = 91000000)
+
+# mDAN D30 N2
+bw.SNCA.mDAN.D30.2 = readBigwig(file = paste0(bw.path, "BIGWIG/D30_POS_II.bw"),
+    chrom = "chr4", chromstart = 89000000, chromend = 91000000)
+
+# mDAN D30 N3
+bw.SNCA.mDAN.D30.3 = readBigwig(file = paste0(bw.path, "BIGWIG/D30_POS_III.bw"),
+    chrom = "chr4", chromstart = 89000000, chromend = 91000000)
+
+# mDAN D50 N1
+bw.SNCA.mDAN.D50.1 = readBigwig(file = paste0(bw.path, "BIGWIG/HFFTHmCherry_D50_possort_S1.bw"),
+    chrom = "chr4", chromstart = 89000000, chromend = 91000000)
+
+# mDAN D50 N2
+bw.SNCA.mDAN.D50.2 = readBigwig(file = paste0(bw.path, "BIGWIG/HFFTHmCherry_D50_possort_S3.bw"),
+    chrom = "chr4", chromstart = 89000000, chromend = 91000000)
+
+# mDAN D50 N3
+bw.SNCA.mDAN.D50.3 = readBigwig(file = paste0(bw.path, "BIGWIG/HFFTHmCherry_D50_possort_S4.bw"),
+    chrom = "chr4", chromstart = 89000000, chromend = 91000000)
+
+# Add a scale next to the bigwig files - check the maximum to choose
+scale.SNCA.max = max(c(bw.SNCA.smNPC.1$score,
+                       bw.SNCA.smNPC.2$score,
+                       bw.SNCA.smNPC.3$score,
+                       bw.SNCA.mDAN.D15.1$score,
+                       bw.SNCA.mDAN.D15.2$score,
+                       bw.SNCA.mDAN.D15.3$score,
+                       bw.SNCA.mDAN.D30.1$score,
+                       bw.SNCA.mDAN.D30.2$score,
+                       bw.SNCA.mDAN.D30.3$score,
+                       bw.SNCA.mDAN.D50.1$score,
+                       bw.SNCA.mDAN.D50.2$score,
+                       bw.SNCA.mDAN.D50.3$score))
+
+print(scale.SNCA.max)
+
+# Define a small region of chr4
+region.p.chr4.small = pgParams(chrom = "chr4",
+                         chromstart = 89000000,
+                         chromend = 91000000,
+                         assembly = assembly(Genome = "hg38refGene",
+                                               TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene",
+                                               OrgDb = "org.Hs.eg.db"),
+                         just = c("left", "top"),
+                         width = 3.5,
+                         fontcolor = "black",
+                         fill = "black",
+                         range = c(0, scale.SNCA.max))
+
+# Plot Low-C data SNCA in mDAN D30 (10kb resolution)
+chr4.SNCA.sq = plotHicTriangle(
+    data = mDAN.D30.25kb,
+    params = region.p.chr4.small,
+    height = 1.75,
+    resolution = 25000,
+    x = 4.5,
+    y = 5.5,
+    zrange = c(0, 5),
+    just = c("left", "top"), 
+    default.units = "inches",
+    palette = colorRampPalette(brewer.pal(n = 9, "YlGnBu")))
+
+# ATACseq signal smNPC_I and scale
+ATAC_smNPC_I = plotSignal(
+  data = bw.SNCA.smNPC.1, 
+  params = region.p.chr4.small,
+  fill = "#313695", 
+  alpha = 0.7, 
+  linecolor = NA,
+  x = 4.5, 
+  y = 7.25, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+# ATACseq signal smNPC_II and scale
+ATAC_smNPC_II = plotSignal(
+  data = bw.SNCA.smNPC.2, 
+  params = region.p.chr4.small,
+  fill = "#313695", 
+  alpha = 0.6, 
+  linecolor = NA,
+  x = 4.5, 
+  y = 7.25, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+# ATACseq signal smNPC_III and scale
+ATAC_smNPC_III = plotSignal(
+  data = bw.SNCA.smNPC.3, 
+  params = region.p.chr4.small,
+  fill = "#313695", 
+  alpha = 0.5, 
+  linecolor = NA,
+  x = 4.5, 
+  y = 7.25, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+annoYaxis(plot = ATAC_smNPC_III, 
+          at = c(0, scale.SNCA.max),
+          fontsize = 6)
+
+plotText(label = "smNPC", 
+         fontsize = 6, 
+         fontcolor = "#313695",
+         fontfamily = "Helvetica",
+         x = 4.125, 
+         y = 7.3125, 
+         just = c("left", "top"),
+         default.units = "inches",
+         fontface = "bold")
+
+# ATACseq signal mDAN D15 I and scale
+ATAC_mDAN.D15_I = plotSignal(
+  data = bw.SNCA.mDAN.D15.1, 
+  params = region.p.chr4.small,
+  fill = "#053061", 
+  alpha = 0.7, 
+  linecolor = NA,
+  x = 4.5, 
+  y = 7.625, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+# ATACseq signal mDAN D15 II and scale
+ATAC_mDAN.D15_II = plotSignal(
+  data = bw.SNCA.mDAN.D15.2, 
+  params = region.p.chr4.small,
+  fill = "#053061", 
+  alpha = 0.6, 
+  linecolor = NA,
+  x = 4.5, 
+  y = 7.625, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+# ATACseq signal mDAN D15 III and scale
+ATAC_mDAN.D15_III = plotSignal(
+  data = bw.SNCA.mDAN.D15.3, 
+  params = region.p.chr4.small,
+  fill = "#053061", 
+  alpha = 0.5, 
+  linecolor = NA,
+  x = 4.5, 
+  y = 7.625, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+annoYaxis(plot = ATAC_mDAN.D15_III, 
+          at = c(0, scale.SNCA.max),
+          fontsize = 6)
+
+plotText(label = "mDAN D15", 
+         fontsize = 6, 
+         fontcolor = "#053061",
+         fontfamily = "Helvetica",
+         x = 4.125, 
+         y = 7.6875, 
+         just = c("left", "top"),
+         default.units = "inches",
+         fontface = "bold")
+
+# ATACseq signal mDAN D30 I and scale
+ATAC_mDAN.D30_I = plotSignal(
+  data = bw.SNCA.mDAN.D30.1, 
+  params = region.p.chr4.small,
+  fill = "#2D004B", 
+  alpha = 0.7, 
+  linecolor = NA,
+  x = 4.5, 
+  y = 8.0, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+# ATACseq signal mDAN D30 II and scale
+ATAC_mDAN.D30_II = plotSignal(
+  data = bw.SNCA.mDAN.D30.2, 
+  params = region.p.chr4.small,
+  fill = "#2D004B", 
+  alpha = 0.6, 
+  linecolor = NA,
+  x = 4.5, 
+  y = 8.0, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+# ATACseq signal mDAN D30 III and scale
+ATAC_mDAN.D30_III = plotSignal(
+  data = bw.SNCA.mDAN.D30.3, 
+  params = region.p.chr4.small,
+  fill = "#2D004B", 
+  alpha = 0.5, 
+  linecolor = NA,
+  x = 4.5, 
+  y = 8.0, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+annoYaxis(plot = ATAC_mDAN.D30_III, 
+          at = c(0, scale.SNCA.max),
+          fontsize = 6)
+
+plotText(label = "mDAN D30", 
+         fontsize = 6, 
+         fontcolor = "#2D004B",
+         fontfamily = "Helvetica",
+         x = 4.125, 
+         y = 8.125, 
+         just = c("left", "top"),
+         default.units = "inches",
+         fontface = "bold")
+
+# ATACseq signal mDAN D50 I and scale
+ATAC_mDAN.D50_I = plotSignal(
+  data = bw.SNCA.mDAN.D50.1, 
+  params = region.p.chr4.small,
+  fill = "#003C30", 
+  alpha = 0.7, 
+  linecolor = NA,
+  x = 4.5, 
+  y =87.375, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+# ATACseq signal mDAN D50 II and scale
+ATAC_mDAN.D50_II = plotSignal(
+  data = bw.SNCA.mDAN.D50.2, 
+  params = region.p.chr4.small,
+  fill = "#003C30", 
+  alpha = 0.6, 
+  linecolor = NA,
+  x = 4.5, 
+  y = 8.375, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+# ATACseq signal mDAN D50 III and scale
+ATAC_mDAN.D50_III = plotSignal(
+  data = bw.SNCA.mDAN.D50.3, 
+  params = region.p.chr4.small,
+  fill = "#003C30", 
+  alpha = 0.5, 
+  linecolor = NA,
+  x = 4.5, 
+  y = 8.375, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+annoYaxis(plot = ATAC_mDAN.D50_III, 
+          at = c(0, scale.SNCA.max),
+          fontsize = 6)
+
+plotText(label = "mDAN D50", 
+         fontsize = 6, 
+         fontcolor = "#003C30",
+         fontfamily = "Helvetica",
+         x = 4.125, 
+         y = 8.5, 
+         just = c("left", "top"),
+         default.units = "inches",
+         fontface = "bold")
+
+# Add gene name and genome labels for the chr4
+# Add gene name
+SNCA_g = plotGenes(params = region.p.chr4.small,
+          x = 4.5,
+          y = 8.8125, 
+          height = 0.5,
+          geneHighlights = data.frame(gene = c("SNCA"),
+                        color = "red"),
+          assembly = assembly(Genome = "hg38refGene", 
+                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
+                      OrgDb = "org.Hs.eg.db"),
+          geneBackground = "black")
+
+# Add genome label
+annoGenomeLabel(plot = SNCA_g, 
+                scale = "Mb", 
+                axis = "x",
+                x = 4.5, 
+                y = 8.6875, 
+                just = c("left", "top"))
+
+pageGuideHide()
+dev.off()
+```
+
+Process the results of the SNEEP pipeline
+```{r, eval = FALSE, echo = TRUE}
+## Take the smNPCs, TH+ neurons at day 15 - day 30 - day 50
+## Load the data
+# smNPC
+SNEEP.smNPC = read_delim("/home/vagrant/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/parkinsonDisease_project_Deborah_Lasse/sneep_witATAC_mergedlowC_2409/result_PD_smNPV_lowC_ATAC_merged_2409.txt",
+                         delim = "\t",
+                         col_names = TRUE)
+
+# Add a column specifying the sample name
+SNEEP.smNPC = SNEEP.smNPC %>% 
+  mutate(Sample = "smNPC")
+
+# Unique rSNPs 
+SNEEP.smNPC %>% 
+  distinct(SNP_position) %>% 
+  write_delim("/home/vagrant/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/output/uniq_rSNPs_smNPC.txt",
+              delim = "\t",
+              col_names = FALSE)
+
+# How many unique target genes associated to those 91 PD-rSNPs found in smNPC
+TG_smNPC = SNEEP.smNPC %>% 
+  dplyr::select(SNP_position, geneNames) %>% 
+  dplyr::filter(geneNames != ".") %>% 
+  group_by(SNP_position, geneNames) %>% 
+  distinct(SNP_position, .keep_all = TRUE) %>% 
+  separate_rows(geneNames, sep = ",") %>% 
+  ungroup() %>% 
+  distinct(geneNames)
+
+write_delim(TG_smNPC,
+            "/home/vagrant/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/output/enrichR/distinct_target_genes_smNPC.txt",
+              delim = "\t",
+              col_names = FALSE)
+
+# 293 target genes are associated to 91 PD-rSNPs in smNPC
+
+# TH+ neurons day 15
+SNEEP.THposD15 = read_delim("/home/vagrant/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/parkinsonDisease_project_Deborah_Lasse/sneep_witATAC_mergedlowC_2409/result_PD_mDAN_day15_lowC_ATAC_N1_2409.txt",
+                         delim = "\t",
+                         col_names = TRUE)
+
+SNEEP.THposD15 = SNEEP.THposD15 %>% 
+  mutate(Sample = "THpos_neurons_D15")
+
+# Unique rSNPs 
+SNEEP.THposD15 %>% 
+  distinct(SNP_position) %>% 
+  write_delim("/home/vagrant/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/output/uniq_rSNPs_mDAND15.txt",
+              delim = "\t",
+              col_names = FALSE)
+
+# How many unique target genes associated to those 180 PD-rSNPs found in mDAN D15
+TG_mDAN.D15 = SNEEP.THposD15 %>% 
+  dplyr::select(SNP_position, geneNames) %>% 
+  dplyr::filter(geneNames != ".") %>% 
+  group_by(SNP_position, geneNames) %>% 
+  distinct(SNP_position, .keep_all = TRUE) %>% 
+  separate_rows(geneNames, sep = ",") %>% 
+  ungroup() %>% 
+  distinct(geneNames)
+
+write_delim(TG_mDAN.D15,
+            "/home/vagrant/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/output/enrichR/distinct_target_genes_mDAN_D15.txt",
+              delim = "\t",
+              col_names = FALSE)
+
+# 308 target genes are associated to 180 PD-rSNPs in mDAN D15
+
+# TH+ neurons day 30
+SNEEP.THposD30 = read_delim("/home/vagrant/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/parkinsonDisease_project_Deborah_Lasse/sneep_witATAC_mergedlowC_2409/result_PD_mDAN_day30_lowC_ATAC_N1_2409.txt",
+                         delim = "\t",
+                         col_names = TRUE)
+
+SNEEP.THposD30 = SNEEP.THposD30 %>% 
+  mutate(Sample = "THpos_neurons_D30")
+
+# Unique rSNPs 
+SNEEP.THposD30 %>% 
+  distinct(SNP_position) %>% 
+  write_delim("/home/vagrant/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/output/uniq_rSNPs_mDAND30.txt",
+              delim = "\t",
+              col_names = FALSE)
+
+# How many unique target genes associated to those 181 PD-rSNPs found in mDAN D30
+TG_mDAN.D30 = SNEEP.THposD30 %>% 
+  dplyr::select(SNP_position, geneNames) %>% 
+  dplyr::filter(geneNames != ".") %>% 
+  group_by(SNP_position, geneNames) %>% 
+  distinct(SNP_position, .keep_all = TRUE) %>% 
+  separate_rows(geneNames, sep = ",") %>% 
+  ungroup() %>% 
+  distinct(geneNames)
+
+write_delim(TG_mDAN.D30,
+            "/home/vagrant/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/output/enrichR/distinct_target_genes_mDAN_D30.txt",
+              delim = "\t",
+              col_names = FALSE)
+
+# 301 target genes are associated to 181 PD-rSNPs in mDAN D30
+
+# TH+ neurons day 50
+SNEEP.THposD50 = read_delim("/home/vagrant/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/parkinsonDisease_project_Deborah_Lasse/sneep_witATAC_mergedlowC_2409/result_PD_mDAN_day50_lowC_ATAC_N1_2409.txt",
+                         delim = "\t",
+                         col_names = TRUE)
+
+SNEEP.THposD50 = SNEEP.THposD50 %>% 
+  mutate(Sample = "THpos_neurons_D50")
+
+# Unique rSNPs 
+SNEEP.THposD50 %>% 
+  distinct(SNP_position) %>% 
+  write_delim("/home/vagrant/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/output/uniq_rSNPs_mDAND50.txt",
+              delim = "\t",
+              col_names = FALSE)
+
+# How many unique target genes associated to those 160 PD-rSNPs found in mDAN D50
+TG_mDAN.D50 = SNEEP.THposD50 %>% 
+  dplyr::select(SNP_position, geneNames) %>% 
+  dplyr::filter(geneNames != ".") %>% 
+  group_by(SNP_position, geneNames) %>% 
+  distinct(SNP_position, .keep_all = TRUE) %>% 
+  separate_rows(geneNames, sep = ",") %>% 
+  ungroup() %>% 
+  distinct(geneNames)
+
+write_delim(TG_mDAN.D50,
+            "/home/vagrant/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/output/enrichR/distinct_target_genes_mDAN_D50.txt",
+              delim = "\t",
+              col_names = FALSE)
+
+# 300 target genes are associated to 160 PD-rSNPs in mDAN D50
+
+# Combine target genes from mDAN D15, D30 and D50 together
+TG_distinct_mDAN = TG_mDAN.D15 %>% 
+  bind_rows(TG_mDAN.D30) %>% 
+  bind_rows(TG_mDAN.D50) %>% 
+  distinct(geneNames)
+
+write_delim(TG_distinct_mDAN,
+            "/home/vagrant/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/output/enrichR/distinct_target_genes_mDAN_all_together.txt",
+              delim = "\t",
+              col_names = FALSE)
+
+# Combine them all
+SNEEP_all = SNEEP.smNPC %>% 
+  bind_rows(SNEEP.THposD15) %>% 
+  bind_rows(SNEEP.THposD30) %>% 
+  bind_rows(SNEEP.THposD50)
+
+# And save them
+write_delim(SNEEP_all,
+            "/home/vagrant/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/output/SNEEP_all_res_comb.txt",
+            delim = "\t",
+            col_names = TRUE)
+
+# Load when needed
+SNEEP_all = read_delim("/home/vagrant/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/output/SNEEP_all_res_comb.txt",
+            delim = "\t",
+            col_names = TRUE)
+
+SNEEP_all = read_delim("/Volumes/deborah.gerard/Documents/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/output/SNEEP_all_res_comb.txt",
+            delim = "\t",
+            col_names = TRUE)
+
+# How many unique rSNPs per samples
+SNEEP_all %>%
+  group_by(Sample) %>%
+  summarise(dplyr::n())
+
+SNEEP_all %>%
+  group_by(Sample) %>%
+  distinct(SNP_position) %>% 
+  summarise(dplyr::n())
+
+# How many unique rSNPs?
+SNEEP_all %>% 
+  distinct(SNP_position) %>% 
+  write_delim(.,
+              "/home/vagrant/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/output/SNEEP_uniq_rSNPs.txt",
+              delim = "\t",
+              col_names = TRUE)
+
+# How many SNPs among the 254 PD-rSNPs are creating or disturbing TFBS
+SNEEP_all %>% 
+  distinct(SNP_position, .keep_all = TRUE) %>% 
+  dplyr::select(SNP_position, log_pvalueBindAffVar1_pvalueBindAffVar2) %>% 
+  mutate(pos = sum(log_pvalueBindAffVar1_pvalueBindAffVar2 > 0),
+         neg = sum(log_pvalueBindAffVar1_pvalueBindAffVar2 < 0))
+
+# How many SNPs among the 254 PD-rSNPs are associated to MAPT or SNCA
+# MAPT
+SNEEP_all %>% 
+  #group_by(SNP_position, geneNames) %>% 
+  dplyr::select(SNP_position, TF, geneNames) %>% 
+  #distinct(SNP_position, .keep_all = TRUE) %>% 
+  dplyr::filter(str_detect(geneNames, "MAPT")) %>% 
+  distinct(SNP_position, .keep_all = TRUE)
+
+# 34 out 254 PD-rSNPs are associated to MAPT
+# SNCA
+SNEEP_all %>% 
+  #group_by(SNP_position, geneNames) %>% 
+  dplyr::select(SNP_position, TF, geneNames) %>% 
+  #distinct(SNP_position, .keep_all = TRUE) %>% 
+  dplyr::filter(str_detect(geneNames, "SNCA")) %>% 
+  distinct(SNP_position, .keep_all = TRUE)
+
+# 7 out 254 PD-rSNPs are associated to SNCA
+
+# How many chromosomes have at least one of the 254 PD-rSNPs 
+SNEEP_all %>% 
+  distinct(SNP_position) %>% 
+  separate(SNP_position, into = c("chr", "tmp"), sep = ":") %>% 
+  group_by(chr) %>% 
+  summarise(chr_nb = n())
+```
+
+Now that unique set of rSNPs is available, filter this number by computing correlation between the expression of the TFs and their predicted target genes
+```{r, eval = FALSE, echo = TRUE}
+# Load RNAse data
+dat.RPKM.filt = read_rds("/home/vagrant/Manuscript_1/FIGURE2/mat_RPKM.rds")
+#dat.RPKM.filt = read_rds("/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE2/mat_RPKM.rds")
+
+# Extract the TFBS predicted to be altered by the 254 rSNPs and plot their expression as well a and s the expression of their putative target genes
+## As some TFs act as dimers, extract the expression of each and the lowest one (of each pair) will be the rate limiting TF
+TF_dimer_exp = SNEEP_all %>% 
+  dplyr::select(SNP_position:var2, TF, geneNames, Sample) %>% 
+  group_by(SNP_position, Sample) %>% 
+  dplyr::filter(geneNames != ".") %>% # Filter out rSNPs where there are no putative target genes
+  mutate(TF = gsub("\\(.*", "\\1", TF)) %>% # remove the JASPAR ID next to some TFs
+  dplyr::filter(str_detect(TF, "::")) %>%  # Filter out the TF dimers and check if one of the TFs is low expressed
+  dplyr::select(SNP_position, TF) %>% 
+  mutate(TF_dimer = TF) %>% 
+  separate_rows(TF, sep = "::") %>% 
+  ungroup() %>% 
+  dplyr::select(-Sample)
+
+## Plot
+dat_2_plot = dat.RPKM.filt %>% 
+  dplyr::filter(gene_name %in% TF_dimer_exp$TF) %>% 
+  dplyr::rename(TF = gene_name) %>% 
+  left_join(TF_dimer_exp,
+            by = "TF") %>% 
+  mutate(TF = as.factor(TF))
+
+pdf("/home/vagrant/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/output/TF_dimer_Ind_exp.pdf",
+    width = 15,
+    height = 20)
+ggboxplot(dat_2_plot,
+          x = "Cond", 
+          y = "RPKM", 
+          add = "jitter", 
+          color = "TF", 
+          #palette = c("#A9A9A9", "#B22222", "#DC143C", "#E9967A"),
+          facet.by = "TF_dimer",
+          xlab = "", 
+          ylab = "Reads Per Kilobase Million (RPKM)") +
+  geom_hline(yintercept = 5,
+             linetype = "dashed") +  # 5 RPKM expression threshold
+  scale_x_discrete(labels = c("smNPC",
+                              expression("mDAN D15"),
+                              expression("mDAN D30"),
+                              expression("mDAN D50"))) +
+  theme(legend.position = "right",
+        axis.text.x = element_text(angle = 90))
+
+dev.off()
+
+## Compute Pearson correlation to filter rSNPs
+# Tibble for TF expression
+TF_exp = SNEEP_all %>%
+  dplyr::select(SNP_position, TF, geneNames) %>%
+  dplyr::filter(geneNames != ".") %>% # no target genes idenditifed
+  mutate(TF = gsub("\\(.*", "\\1", TF)) %>%
+  separate_rows(TF, sep = "::") %>% # Separate TF dimers into single TF
+  separate_rows(geneNames, sep = ",") %>% # Separate target genes into single target genes
+  unite(col = "Item", c("SNP_position", "TF", "geneNames"), remove = FALSE) %>%
+  dplyr::select(Item, TF) %>%
+  dplyr::rename(gene_name = TF) %>%
+  dplyr::filter(gene_name %in% dat.RPKM.filt$gene_name) %>%
+  left_join(dat.RPKM.filt,
+            by = "gene_name") %>%
+  group_by(gene_name) %>% 
+  dplyr::filter(any(RPKM > 1)) %>% # Keep only TF that have RPKM > 1 in all samples
+  dplyr::select(-gene_id, -Cond) %>%
+  dplyr::rename(TF = gene_name,
+                RPKM.TF = RPKM)
+
+# Tibble for TG expression  
+TG_exp = SNEEP_all %>%
+  dplyr::select(SNP_position, TF, geneNames) %>%
+  dplyr::filter(geneNames != ".") %>% # no target genes idenditifed
+  mutate(TF = gsub("\\(.*", "\\1", TF)) %>%
+  separate_rows(TF, sep = "::") %>% # Separate TF dimers into single TF
+  separate_rows(geneNames, sep = ",") %>% # Separate target genes into single target genes
+  unite(col = "Item", c("SNP_position", "TF", "geneNames"), remove = FALSE) %>%
+  dplyr::select(Item, geneNames) %>%
+  separate_rows(geneNames, sep = ",") %>%
+  dplyr::rename(gene_name = geneNames) %>%
+  dplyr::filter(gene_name %in% dat.RPKM.filt$gene_name) %>%
+  left_join(dat.RPKM.filt,
+            by = "gene_name") %>%
+  group_by(gene_name) %>% 
+  dplyr::filter(any(RPKM > 1)) %>% # Keep only target genes that have RPKM > 1 in all samples
+  dplyr::select(-gene_id, -Cond) %>%
+  dplyr::rename(target_gene = gene_name,
+                RPKM.TG = RPKM)
+
+# Join both target gene and TF tables. Filter out TF or target genes with expression below 1 RPKM
+TF_TG_mat = merge(TF_exp, TG_exp) %>% 
+  as_tibble() %>% 
+  group_by(TF, target_gene) %>% 
+  distinct(Sample, .keep_all = TRUE)
+
+# Pearson correlation
+TF_TG_mat_Pearson_cor = cor_test(TF_TG_mat %>% 
+                                   group_by(TF, target_gene),
+                                 vars = c("RPKM.TF","RPKM.TG"),
+                                 use = "everything")
+
+write_delim(TF_TG_mat_Pearson_cor,
+            "/Volumes/deborah.gerard/Documents/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/output/TF_TG_exp_pearsonCor.txt",
+            delim = "\t",
+            col_names = TRUE)
+
+# Filter the correlation matrix to only keep TF-target gene pairs with a strong correlation/anti-correlation
+TF_TG_mat_Pearson_cor.filt = TF_TG_mat_Pearson_cor %>% 
+  dplyr::filter(cor > 0.5 | cor < -0.5)
+
+unique(TF_TG_mat_Pearson_cor.filt$target_gene)
+unique(TF_TG_mat_Pearson_cor.filt$TF)
+
+write_delim(TF_TG_mat_Pearson_cor.filt,
+            "/Volumes/deborah.gerard/Documents/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/output/TF_TG_exp_pearsonCor_abs0.5.txt",
+            delim = "\t",
+            col_names = TRUE)
+
+# Reassociate the rSNPs to which the TF-target genes pairs belongs and make a table
+tbl.TF.TG = TF_TG_mat_Pearson_cor.filt %>% 
+  unite(col = "TF_TG_pair", TF, target_gene, sep = "_", remove = FALSE)
+
+tbl.TF.TG.FINAL = TF_TG_mat %>% 
+  ungroup() %>% 
+  dplyr::filter(str_detect(Item, paste0(tbl.TF.TG$TF_TG_pair, collapse = "|"))) %>% 
+  distinct(Item, .keep_all = TRUE) %>% 
+  dplyr::select(Item, TF, target_gene) %>% 
+  mutate(rSNPs = gsub("\\_.*", "\\1", Item)) %>% 
+  dplyr::select(rSNPs, TF, target_gene)
+
+# Select the coordinates of the rSNPs ans associate back rsID from UCSC using all snps from db155
+tbl.TF.TG.FINAL %>% 
+  dplyr::select(rSNPs) %>% 
+  distinct(rSNPs) %>% 
+  write_delim(.,
+              "/Volumes/deborah.gerard/Documents/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/output/UCSC_coordinates_rSNPs.txt",
+              delim = "\t",
+              col_names = FALSE)
+
+# Load the newly created file
+# rsID_PD_rSNP = read_delim("/Volumes/deborah.gerard/Documents/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/output/UCSC_coordinates_rSNPs_rsID.txt",
+#               delim = ",",
+#               col_names = TRUE)
+
+rsID_PD_rSNP = read_delim("/home/vagrant/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/output/UCSC_coordinates_rSNPs_rsID.txt",
+              delim = ",",
+              col_names = TRUE)
+
+# Load the newly created file
+rsID_PD_rSNP.filt = rsID_PD_rSNP %>% 
+  dplyr::filter(class == "snv") %>% 
+  unite(col = "tmp", c(`#"chrom"`, chromStart), sep = ":", remove = TRUE) %>% 
+  unite(col = "rSNPs", c("tmp", "chromEnd"), sep = "-", remove = FALSE) %>% 
+  dplyr::select(rSNPs, name, ref, alts) %>% 
+  distinct(name, .keep_all = TRUE) # Remove doublets
+
+# Filter the final table
+tbl.TF.TG.FINAL.rsID = tbl.TF.TG.FINAL %>% 
+  #dplyr::select(rSNPs) %>% 
+  #distinct(rSNPs) %>% 
+  dplyr::filter(rSNPs %in% rsID_PD_rSNP.filt$rSNPs) %>% 
+  left_join(rsID_PD_rSNP.filt,
+            by = "rSNPs") %>% 
+  dplyr::select(rSNPs, name:alts, TF, target_gene) %>% 
+  separate(rSNPs, into = c("chr", "tmp"), sep = ":", remove = TRUE) %>% 
+  separate(tmp, into = c("start", "end"), sep = "-", remove = TRUE) %>% 
+  dplyr::rename(rsID = name)
+
+# Extract the unique rsIDs and get the MAF (minor allele frequencies)
+snp2MAF = tbl.TF.TG.FINAL.rsID %>% 
+  dplyr::select(rsID) %>% 
+  distinct(rsID) %>% 
+  pull()
+
+# Get allele frequencies
+LDproxy_batch(snp = snp2MAF,
+              pop = "EUR",
+              r2d = "r2",
+              token = "5bba40af90d7",
+              append = TRUE,
+              genome_build = "grch38_high_coverage")
+
+# The data has been automaticcaly saved -> load it
+MAF.snp = read_delim("/home/vagrant/Manuscript_1/TABLES/combined_query_snp_list_grch38_high_coverage.txt",
+                     delim = "\t",
+                     col_names = TRUE)
+
+# MAF.snp = read_delim("/Volumes/deborah.gerard/Documents/Manuscript_1/TABLES/combined_query_snp_list_grch38_high_coverage.txt",
+#                      delim = "\t",
+#                      col_names = TRUE)
+
+# The linkage desiquilibrium linkage value has been also calculated. Filter only the snp that are in linkage desiquilibrium with themselves
+MAF.snp %>% 
+  dplyr::select(RS_Number:Distance) %>% 
+  dplyr::rename(query_snp = RS_Number,
+                rsID = Coord,
+                Coord = Alleles,
+                Allele = MAF,
+                MAF = Distance) %>% 
+  mutate(same.snp = if_else(query_snp == rsID, 1, 0)) %>% 
+  # dplyr::filter(same.snp == 1,
+  #               rsID %in% snp2MAF) %>% 
+  dplyr::filter(same.snp == 1) %>% 
+  #left_join(tbl.TF.TG.FINAL.rsID, by = "rsID") %>% 
+  full_join(tbl.TF.TG.FINAL.rsID, by = "rsID") %>% 
+  #distinct(rsID, .keep_all = TRUE) %>% 
+  View()
+  write_delim(.,
+            "/home/vagrant/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/output/final_tbl_PD_rSNPs_with_MAF.txt",
+            delim = "\t",
+            col_names = TRUE)
+
+# Expression distribution of the 77 target genes
+#unique(TF_TG_mat_Pearson_cor.filt$target_gene)
+pdf("/Volumes/deborah.gerard/Documents/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/output/ExpDistri77TG.pdf",
+    width = 10,
+    height = 13)
+
+TF_TG_mat %>% 
+  ungroup() %>% 
+  dplyr::select(Sample, target_gene, RPKM.TG) %>% 
+  group_by(Sample) %>% 
+  distinct(target_gene, .keep_all = TRUE) %>% 
+  dplyr::filter(target_gene %in% TF_TG_mat_Pearson_cor.filt$target_gene) %>% 
+  mutate(target_gene = as.factor(target_gene),
+         Cond = gsub("\\_.*", "\\1", Sample),
+         log2RPKM.TG = log2(RPKM.TG + 0.001)) %>% # add a pseudocount to avoid -Inf if RPKM is 0
+  ggdensity(.,
+            x = "log2RPKM.TG",
+            facet.by = "target_gene",
+            fill = "target_gene",
+            title = "Distribution of the log2 expression of the 77 target genes") +
+  theme(legend.position = "none") +
+  geom_vline(xintercept = 0,
+             linetype = "dashed")
+
+dev.off()
+
+# Plot of the Pearson correlation coefficient vs the pvalue of the diffbinf affinity
+# Take the necessary columns from SNEEP_all
+SNEEP_all_2 = SNEEP_all %>% 
+  mutate(TF = gsub("\\(.*", "\\1", TF)) %>% 
+  dplyr::select(SNP_position, TF, geneNames, pvalue_DiffBindAff) %>% 
+  dplyr::filter(geneNames != ".") %>% 
+  separate_rows(., geneNames, sep = ",") %>% 
+  unite(col = "Item", SNP_position, TF, geneNames, sep = "_", remove = FALSE)
+
+# And merge with the table with the Pearson correlation
+TF_TG_mat_Pearson_cor2 = TF_TG_mat_Pearson_cor %>% 
+  unite(col = "TF_TG_pair", TF, target_gene, sep = "_", remove = TRUE)
+
+lbl.pl = c("LHX1_BAG3",
+           "ZBTB14_IDUA",
+           "NR2C2_SCARB2")
+
+pvalDiffBind_cor = TF_TG_mat %>% 
+  ungroup() %>% 
+  dplyr::select(Item) %>% 
+  mutate(SNP_position = gsub("\\_.*", "\\1", Item)) %>% 
+  distinct(Item, .keep_all = TRUE) %>% 
+  left_join(SNEEP_all_2,
+            by = "Item") %>% 
+  unite(col = "TF_TG_pair", TF, geneNames, sep = "_", remove = TRUE) %>%
+  left_join(TF_TG_mat_Pearson_cor2, 
+            by = "TF_TG_pair") %>% 
+  #drop_na() %>% 
+  dplyr::select(Item, TF_TG_pair, pvalue_DiffBindAff, cor) %>% 
+  distinct(Item, .keep_all = TRUE) %>% 
+  mutate(pvalue_DiffBindAff_log = log2(pvalue_DiffBindAff),
+         lbl = if_else(TF_TG_pair %in% lbl.pl, TF_TG_pair, NA_character_))
+
+# And plot
+ggscatter(pvalDiffBind_cor,
+          x = "cor",
+          y = "pvalue_DiffBindAff_log",
+          color = "lbl", 
+          #palette = c("#00AFBB", "black"),
+          label = "lbl",
+          repel = TRUE)
+
+```
+
+```{r, eval = FALSE, echo = TRUE}
 
@@
 ### FIGURE 2
+The SNEEP analysis will be run again by Nina with the PD GWAS SNPs that been filtered only for the GWAS p-value of 5e-08
+```{r, eval = FALSE, echo = TRUE}
+# This is the file obtained by Jochen
+nalls_allSNPs = vroom(
+  "/Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/nallsEtAl2019_hg38_full.tsv")
+
+# Select the coordinates, the alleles and the p-value columns. Filter for the GWAS p-value
+nalls_allSNPs %>% 
+  dplyr::select(CHR_hg38:END_hg38, A1:A2, p) %>% 
+  dplyr::filter(p < 5e-08) %>% # GWAS p-value threshold
+  write_delim("/Volumes/deborah.gerard/Documents/epifunc/SNEEP2024/input/Nalls_PD_SNPs_GWASpval_filtered.txt",
+              delim = "\t",
+              col_names = TRUE)
+
+# Provide the RPKM data from the RNAseq to Nina
+dat.RPKM = read_delim("/Volumes/deborah.gerard/Documents/epifunc/RNAseq/RPKM_genename",
+                      delim = "\t", 
+                      col_names = TRUE)
+
+# Provide the file as a text file
+dat.RPKM %>% 
+  write_delim(.,
+              "/Volumes/deborah.gerard/Documents/epifunc/SNEEP2024/input/RNAseq/All_samples_RPKM.txt",
+              delim = "\t",
+              col_names = TRUE)
+
+# Check the hg38 coordinates 
+nalls_allSNPs %>% 
+  dplyr::filter(CHR_hg38 == "chr4",
+                END_hg38 == "76213717")
+```
+
+For the SNEEP analysis, retrieve also the `narrowPeak` files and send them to Nina
+```{bash, eval = FALSE, echo = TRUE}
+# narrowPeak files for smNPC, mDAN neurons day 15 - day 30 - day 50
+rsync -avzPhu --no-p iris-cluster:/work/projects/epifunc/manuscript_sample_submission/ATAC/peaks/*narrowPeak /Volumes/deborah.gerard/Documents/epifunc/SNEEP2024/input/ATAC/narrowPeaks/
+
+# narrowPeak files for astrocytes and non-mDAN neurons at day 15 and day 50 (day 30 data does not exist)
+# According to the epifunc gitlab (https://git-r3lab.uni.lu/jochen.ohnmacht/epifunc) they are in /work/projects/epifunc/genrich_replicates_opt.
+According the epifunc gitlab, the filtered.narrowPeak files were used for HINT-ATAC and EPIC-DREM
+rsync -avzPhu --no-p iris-cluster:/work/projects/epifunc/genrich_replicates_opt/*neg.filtered.narrowPeak /Volumes/deborah.gerard/Documents/epifunc/SNEEP2024/input/ATAC/narrowPeaks/
+
+rsync -avzPhu --no-p iris-cluster:/work/projects/epifunc/genrich_replicates_opt/astrocytes.filtered.narrowPeak /Volumes/deborah.gerard/Documents/epifunc/SNEEP2024/input/ATAC/narrowPeaks/
+```
+
 Create the page layout that will contain all the necessary plots
@@
 ```{r fig2, eval = FALSE, echo = TRUE}
-########## FIGURE 2 ##########
-##############################
-
-# Save as a PDF
-pdf("/home/vagrant/Manuscript_1/FIGURE2/FIGURE2.pdf",
-    width = 8.3, 
-    height = 11.7)
+####################
+#### Figure 2  ####
+###################
+# Save as TIFF, 300 ppi
+tiff("/home/vagrant/Manuscript_1/FIGURE2/FIGURE2.tiff",
+     width = 8.27,
+     height = 11.67,
+     units = "in",
+     res = 300,
+     compression = "lzw")
 
 # Create a A4 blank page
-pageCreate(width = 8.3, 
-           height = 11.7, 
+pageCreate(width = 8.27, 
+           height = 11.67, 
            default.units = "inches",
-           showGuides = FALSE)
-
-#### PANEL A - BAG3 locus
+           showGuides = TRUE)
+
 # text Figure 2
@@
          fontface = "bold")
+
+#### PANEL A - SNEEP PIPELINE ####
 # text A
@@
 
+# Load the picture prepared in Biorender
+Fig2A_pip = readPNG("/home/vagrant/Manuscript_1/FIGURE2/Fig2A_FlowChart.png")
+
+# Plot Figure 2A - Pipeline
+plotRaster(image = Fig2A_pip,
+           x = 0.5,
+           y = 0.625,
+           width = 3.5,
+           height = 3.0,
+           just = c("left", 
+                    "top"),
+           interpolate = TRUE)
+
+#### PANEL B - Pizza plot of 50 PD-rSNPs (among 54) that shows allelic imbalance #### 
+# text B
+plotText(label = "B", 
+         fontsize = 12,
+         fontfamily = "Helvetica",
+         x = 4.125, 
+         y = 0.5, 
+         just = "left", 
+         default.units = "inches",
+         fontface = "bold")
+
+# Since there are 254 unique rSNPs but we do not have about them being heterozygous or not, check if there is also chromatin allelic imbalance
+# hg38
+# Load the 254 PD rSNPs coordinates
+PD_rSNPs_254 = read_delim("/Volumes/deborah.gerard/Documents/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/output/SNEEP_uniq_rSNPs.txt",
+                          delim = "\t",
+                          col_names = TRUE)
+
+PD_rSNPs_254_fmt = PD_rSNPs_254 %>% 
+  separate(SNP_position, into = c("chr", "tmp"), sep = ":", remove = FALSE) %>% 
+  separate(tmp, into = c("start", "end"), sep = "-", remove = TRUE) %>% 
+  mutate(start = as.numeric(start),
+         end = as.numeric(end))
+
+# Make a Granges object of the 254 PD rSNPs (width has to be one)
+searchArea = GRanges(seqnames = PD_rSNPs_254_fmt$chr, 
+                     ranges = IRanges(start = PD_rSNPs_254_fmt$end, 
+                                      end = PD_rSNPs_254_fmt$end),
+                     name = PD_rSNPs_254_fmt$SNP_position)
+
+# Path where the ATACseq BAM files are
+pathToFiles = "/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE4/"
+
+# Import a specific region from the BAM files (based on the search area above)
+reads = impBamGAL(pathToFiles, 
+                  searchArea, 
+                  verbose = TRUE)
+
+# Count the number of reads for the 2 different alleles at that position
+countList = getAlleleCounts(reads, 
+                           searchArea, 
+                            verbose = TRUE)
+
+# Save as a rds file for loading later if necessary
+saveRDS(countList, 
+        file = "/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE4/PD_rSNPs_254_het_counts_THREP1_ATACseq.rds")
+
+# Load the new results of the 254 rSNPs
+countList = read_rds("/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE4/PD_rSNPs_254_het_counts_THREP1_ATACseq.rds")
+
+# Make an ASEset object to be able to plot
+countList.ASE = ASEsetFromCountList(searchArea, countList)
+
+# And plot one graph per pdf file
+for (i in 1:length(countList.ASE)){
+  pdf(paste0("/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE4/20241111_AlellicImbalance_254rSNPs_", 
+             rownames(countList.ASE[i]),
+             ".pdf"))
+  barplot(countList.ASE[i])
+  dev.off()
+}
+
+# Now check how many are truly heterozygous thanks to the whole genome sequencing data (WGS)
+# Use table browser to retrieve according to this link http://genome.ucsc.edu/FAQ/FAQreleases.html#snpConversion
+searchArea %>% 
+  as_tibble() %>% 
+  dplyr::select(-start) %>% # Not the real start when converting a GRanges to a tibble 
+  mutate(start = end - 1) %>% 
+  dplyr::select(seqnames, start, end, name) %>% 
+  dplyr::rename(rSNPs = name) %>% 
+  inner_join(PD_rSNPs_254_rsID.filt,
+             by = "rSNPs") %>% 
+  dplyr::select(name) %>% 
+  write_delim(.,
+              "/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE4/rsIDs_254PDrSNPs.txt",
+              delim = "\t",
+              col_names = FALSE)
+
+# Load now the coordinates that are in hg19
+PD_rSNPs_254_hg19 = read_delim("/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE4/rsIDs_254PDrSNPs_hg19_coord.txt",
+                               delim = "\t",
+                               col_names = TRUE)
+
+# Only keep SNPs that are on canonical chromosomes
+PD_rSNPs_254_hg19.GR = PD_rSNPs_254_hg19 %>% 
+  dplyr::filter(!str_detect(`#chrom`, "_")) %>% 
+  dplyr::select(`#chrom`:name) %>% 
+  dplyr::rename(chr = `#chrom`) %>% 
+  makeGRangesFromDataFrame(.,
+                           keep.extra.columns = TRUE,
+                           seqnames.field = "chr",
+                           start.field = "chromStart",
+                           end.field = "chromEnd",
+                           starts.in.df.are.0based = TRUE)
+
+# Load WGS data of TH REP1 mCHERRY cell line (hg19 genome version)
+dat.SNPs.only.GR = read_rds("/Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/E19D017a78.merge.qc.SNP_INDEL.hg19.annotated.rds")
+
+dat.SNPs.only.GR = dat.SNPs.only.GR %>% 
+  dplyr::select(CHR:POS, REF:FILTER, E19D017a78) %>% 
+  mutate(START = POS - 1) %>% 
+  makeGRangesFromDataFrame(.,
+                           keep.extra.columns = TRUE,
+                           seqnames.field = "CHR",
+                           start.field = "START",
+                           end.field = "POS",
+                           starts.in.df.are.0based = TRUE)
+
+seqlevelsStyle(dat.SNPs.only.GR) = "UCSC"
+seqlevelsStyle(dat.SNPs.only.GR)
+
+# Overlap
+hits = findOverlaps(PD_rSNPs_254_hg19.GR, dat.SNPs.only.GR)
+rSNP.254_in_E19D017a78 = PD_rSNPs_254_hg19.GR[queryHits(hits)]
+E19D017a78_w_rSNP.254 = dat.SNPs.only.GR[subjectHits(hits)]
+
+mcols(rSNP.254_in_E19D017a78) = cbind(mcols(rSNP.254_in_E19D017a78),
+                                 mcols(E19D017a78_w_rSNP.254))
+
+rSNP.254_in_E19D017a78 = as.data.frame(rSNP.254_in_E19D017a78) %>% 
+  as_tibble()
+
+# Out of 254 PD-rSNPs, we have information about 242
+
+# Save
+write_delim(rSNP.254_in_E19D017a78,
+            "/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE4/Genotype_of_254PDrSNPs_in_THREP1mCHERRY.txt",
+            delim = "\t",
+            col_names = TRUE)
+
+# Load later
+rSNP.254_in_E19D017a78 = read_delim("/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE4/Genotype_of_254PDrSNPs_in_THREP1mCHERRY.txt",
+                                    delim = "\t",
+                                    col_names = TRUE)
+
+# Check how many are "unknown" (./.:.)
+rSNP.254_in_E19D017a78 %>% 
+  mutate(Genotype = gsub("\\:.*", "\\1", E19D017a78)) %>% 
+  group_by(Genotype) %>% 
+  summarise(GT.num = n()) # 54 PD-rSNPs are heterozygous in TH REP1 mCHERRY cell line, 24 are homozygous for the alternative allele and 164 are                                  unknown
+
+# Check if the 54 PD-rSNPs that are heterozygous in TH REP1 mCHERRY cell line also lead to chromatin allelic imbalance
+# rsIDs of the 54 heterozygous PD-rSNPs 
+rSNP.254_in_E19D017a78_0.1 = rSNP.254_in_E19D017a78 %>% 
+  mutate(Genotype = gsub("\\:.*", "\\1", E19D017a78),
+         Genotype2 = gsub("\\|", "\\/", Genotype)) %>% 
+  dplyr::filter(str_detect(Genotype2, "0/1")) %>% 
+  #unite(col = "toInves", seqnames, end, sep = "_") %>% 
+  dplyr::select(name)
+
+# Get their coordinates
+hetero_54_rSNP_in_E19D017a78.hg38 = searchArea %>% 
+  as_tibble() %>% 
+  dplyr::select(-start) %>% # Not the real start when converting a GRanges to a tibble 
+  mutate(start = end - 1) %>% 
+  dplyr::select(seqnames, start, end, name) %>% 
+  dplyr::rename(rSNPs = name) %>% 
+  inner_join(PD_rSNPs_254_rsID.filt,
+             by = "rSNPs") %>% 
+  dplyr::filter(name %in% rSNP.254_in_E19D017a78_0.1$name) %>% 
+  unite(col = "coordToInves", seqnames, end, sep = "_")
+
+# Extract the 54 heterozygous PD-rSNPs from thre ASet object
+PDrSNPs_54_het = countList[intersect(names(countList), hetero_54_rSNP_in_E19D017a78.hg38$coordToInves)]
+
+searchArea.0.1 = searchArea %>% 
+  as_tibble() %>% 
+  dplyr::filter(name %in% hetero_54_rSNP_in_E19D017a78.hg38$rSNPs)
+
+searchArea.0.1 = searchArea.0.1 %>% 
+  makeGRangesFromDataFrame(.,
+                           keep.extra.columns = TRUE,
+                           seqnames.field = "seqnames",
+                           start.field = "start",
+                           end.field = "end",
+                           starts.in.df.are.0based = FALSE)
+
+# And make it a ASet object back and proceed with a chi-squared test
+PDrSNPs_54_het.ASE = ASEsetFromCountList(searchArea.0.1, PDrSNPs_54_het)
+ref(PDrSNPs_54_het.ASE) = c("G", "T", "C")
+PDrSNPs_54_het.ASE.chisq = as_tibble(chisq.test(PDrSNPs_54_het.ASE[,1:7], "+")) %>% 
+  mutate(Sample = colnames(PDrSNPs_54_het.ASE)) %>% 
+  dplyr::select(Sample, everything())
+
+# Consider that a PD-rSNP lead to allelic imbalance if at least one sample (smNPC, mDAN-D15, mDAN-D30, mDAN-D50) shows allelic imbalance
+PDrSNPs_54_het.ASE.chisq %>% 
+  dplyr::filter(!str_detect(Sample, paste0(c("astrocyte", "neg"), collapse = "|"))) %>% 
+  #pivot_longer(!Sample, names_to = "PDrSNPs", values_to = "pvalue") %>% 
+  #group_by(Sample) %>% 
+  #dplyr::filter(if_any(where(is.numeric), ~ . < 0.05))
+  select_if(~any(. < 0.05)) %>% 
+  mutate(AI_yes = ncol(.)) %>% 
+  View()
+# 46 among 54 PD-rSNPs show allelic imbalance
+
+test = tibble(AI = c("yes", "no"),
+       value = c(46, 8),
+       percent = round((value/sum(value))*100, digits = 1))
+
+pizza.AI = ggplot(test,
+       aes(x = "", y = value, fill = AI)) +
+  geom_bar(width = 1, stat = "identity", alpha = 0.5) +
+    #theme_void() +
+    scale_fill_manual(values = c("#4682BD", "#64A7D1")) +
+    coord_polar(theta = "y", start = 2.125, clip = "off") +
+    geom_text(aes(
+        x = c(1.0, 1.2),
+        y = c(21.5, 50),
+        label = paste0(percent, "%")),
+        size = 5.0, 
+        color = "black",
+        fontface = "bold") +
+  theme_void() +
+  theme(legend.position = "none")
+
+plotGG(plot = pizza.AI, 
+       x = 3.0, 
+       y = 0.5, 
+       width = 6.0, 
+       height = 1.75,
+       just = c("left", "top"), 
+       default.units = "inches")
+
+# And plot one graph per pdf file
+for (i in 1:length(PDrSNPs_54_het.ASE)){
+  pdf(paste0("/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE4/20241115_AlellicImbalance_54HeterorSNPs_",
+             rownames(PDrSNPs_54_het.ASE[i]),
+             ".pdf"))
+  barplot(PDrSNPs_54_het.ASE[i])
+  dev.off()
+}
+
+#### PANEL C - Manhattan plot #### 
+# text C
+plotText(label = "C", 
+         fontsize = 12,
+         fontfamily = "Helvetica",
+         x = 4.125, 
+         y = 2.125, 
+         just = "left", 
+         default.units = "inches",
+         fontface = "bold")
+
+# Load the Nalls et al. GWAS data
+nalls_allSNPs.HG38.GR = readRDS("/home/vagrant/Manuscript_1/FIGURE1/nalls_allSNPs.HG38.GR.rds")
+#nalls_allSNPs.HG38.GR = readRDS("/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/nalls_allSNPs.HG3#8.GR.rds")
+
+# Load the rsIDS FOR THE 254 significant SNPs
+rsID.254 = read_delim("/Volumes/deborah.gerard/Documents/epifunc/SNEEP2024/RESULTS_SEPTEMBER_2024/output/SNEEP_uniq_rSNPs.txt",
+                     delim = "\t",
+                     col_names = TRUE)
+
+# Extract the chr and the position
+rsID.254_2 = rsID.254 %>% 
+  separate(col = "SNP_position", 
+           into = c("chr", "pos"), 
+           sep = ":",
+           remove = FALSE) %>% 
+  separate(col = "pos",
+           into = c("start", "end"),
+           sep = "-",
+           remove = TRUE) %>% 
+  unite(col = pos, 
+        c("chr", "end"), 
+        sep = "_", 
+        remove = TRUE) %>% 
+  dplyr::select(-start)
+
+# Select the SNPs position from nalls et al and associate rsIDs
+nalls.manH = nalls_allSNPs.HG38.GR %>% 
+  as_tibble() %>% 
+  dplyr::select(seqnames, base_pair_position, p) %>% 
+  unite(col = "pos", seqnames, base_pair_position, sep = "_", remove = FALSE) %>%
+  left_join(rsID.254_2, by = "pos") %>% 
+  separate(pos, into = c("chrom", "pos"), sep = "_", remove = TRUE) %>% 
+  dplyr::select(chrom, pos, p, SNP_position)
+
+# Save
+write_rds(nalls.manH,
+          "/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/20241107_254_manH.rds")
+
+# Load for later 
+nalls.manH = read_rds("/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/20241107_254_manH.rds")
+
+# Rename columns
+nalls.manH = nalls.manH %>% 
+  dplyr::rename(snp = SNP_position) %>% 
+  mutate(pos = as.numeric(pos))
+
+# Manhattan plot - highlight the 254 SNPs with rsID
+# Get the rsID of the 254 rSNPs first
+nalls.manH %>% 
+  dplyr::filter(!is.na(snp),
+                p <= 5e-08) %>% 
+  dplyr::select(snp) %>% 
+  write_delim(.,
+              "/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/20241107_254PDrSNPs_coord.txt",
+              col_names = FALSE,
+              delim = "\t")
+
+# Load the files with the associated rsIDs
+PD_rSNPs_254_rsID = read_delim("/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/20241107_254PDrSNPs_rsID.txt",
+                               delim = "\t",
+                               col_names = TRUE)
+
+# Only keep snv
+PD_rSNPs_254_rsID.filt = PD_rSNPs_254_rsID %>% 
+  filter(class == "snv") %>% 
+  dplyr::select(`#chrom`:name) %>% 
+  distinct(name, .keep_all = TRUE) %>% 
+  unite(col = "tmp", `#chrom`, chromStart, sep = ":", remove = FALSE) %>% 
+  unite(col = "rSNPs", tmp, chromEnd, sep = "-", remove = TRUE)
+
+# Associated then the significant GWAS pvalue
+snp_2_high = nalls.manH %>% 
+  dplyr::filter(!is.na(snp),
+                p <= 5e-08) %>% 
+  dplyr::rename(rSNPs = snp) %>% 
+  left_join(PD_rSNPs_254_rsID.filt,
+            by = "rSNPs") %>% 
+  dplyr::select(-rSNPs, -`#chrom`, -chromStart) %>% 
+  dplyr::rename(snp = name)
+
+# Get the full set of SNPs and associate rsID to the one I want to highlight
+# snp_to_pl = nalls.manH %>% 
+#   mutate(snp = NA_character_) %>% 
+#   bind_rows(snp_2_high)
+
+snp_to_pl = nalls.manH %>%
+  mutate(snp = NA_character_) %>%
+  bind_rows(snp_2_high) %>%
+  mutate(pbis = -log10(p),
+         chrom = factor(chrom,
+                        levels = paste0("chr",
+                                        1:22)),
+         color = if_else(is.na(snp), "no_high", "high"),
+
+         label = if_else(snp %in% c("rs1465922", "rs144814361"), snp, NA_character_))
+
+highlight_colormap = c("no_high" = adjustcolor( "grey", 
+                                                alpha.f = 0.2), 
+                       "high" = "#6600FF")
+
+no_high = manhattan_data_preprocess(snp_to_pl,
+                                    pval.colname = "p",
+                                    chr.colname = "chrom",
+                                    pos.colname = "pos",
+                                    highlight.colname = "color",
+                                    highlight.col = highlight_colormap,
+                                    signif = c(5e-08))
+# Plot
+snp.pl = manhattan_plot(x = no_high,
+                        color.by.highlight = TRUE,
+                        rescale = TRUE,
+                        label.colname = "label") +
+  theme(axis.text.x = element_text(size = 9,
+                                 face = "bold",
+                                 angle = 90),
+        axis.text.y = element_text(size = 9,
+                                   face = "bold"),
+        axis.title.x = element_blank(),
+        axis.title.y = element_text(size = 11,
+                                    face = "bold"))
+
+# saveRDS(snp.pl,
+#        "/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE2/Fig2C_ManhattanPlot.rds")
+snp.pl = readRDS("/home/vagrant/Manuscript_1/FIGURE2/Fig2C_ManhattanPlot.rds")
+
+# Place the plot
+plotGG(plot = snp.pl, 
+       x = 4.5, 
+       y = 2.25, 
+       width = 3.75, 
+       height = 1.5,
+       just = c("left", "top"), 
+       default.units = "inches")
+
+#### PANEL D - BAG3 locus #### 
+# text D
+plotText(label = "D", 
+         fontsize = 12,
+         fontfamily = "Helvetica",
+         x = 0.25, 
+         y = 4.0, 
+         just = "left", 
+         default.units = "inches",
+         fontface = "bold")
+
 # ATACseq signal BAG3
@@
   assembly = "hg38",
-  x = 0.75,
-  y = 0.625,
+  x = 0.5,
+  y = 4.125,
   length = 4.0,
@@
   linecolor = NA,
-  x = 0.75, 
-  y = 0.875, 
+  x = 0.5, 
+  y = 4.375, 
   width = 4.0, 
@@
   default.units = "inches")
-
-annoYaxis(plot = ATAC_smNPC_I, 
-          at = c(0, scale.BAG3.max),
-          fontsize = 6)
 
@@
   default.units = "inches")
-
-annoYaxis(plot = ATAC_smNPC_II, 
-          at = c(0, scale.BAG3.max),
-          fontsize = 6)
 
@@
           fontsize = 6)
+
+# Add the samples name
+plotText(label = "smNPC", 
+         fontsize = 6, 
+         fontcolor = "#A9A9A9",
+         fontfamily = "Helvetica",
+         x = 0.25, 
+         y = 4.5, 
+         just = c("left", "top"),
+         default.units = "inches",
+         fontface = "bold")
 
@@
   linecolor = NA,
-  x = 0.75, 
-  y = 1.25, 
+  x = 0.5, 
+  y = 4.675, 
   width = 4.0, 
@@
   default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D15_I, 
-          at = c(0, scale.BAG3.max),
-          fontsize = 6)
 
@@
   default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D15_II, 
-          at = c(0, scale.BAG3.max),
-          fontsize = 6)
 
@@
           fontsize = 6)
+
+# Annotate sample name
+plotText(label = "mDAN D15", 
+         fontsize = 6, 
+         fontfamily = "Helvetica",
+         fontcolor = "#B22222",
+         x = 0.25, 
+         y = 4.75, 
+         just = c("left", "top"),
+         default.units = "inches",
+         fontface = "bold")
 
@@
   linecolor = NA,
-  x = 0.75, 
-  y = 1.625, 
+  x = 0.5, 
+  y = 4.975, 
   width = 4.0, 
@@
   default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D30_I, 
-          at = c(0, scale.BAG3.max),
-          fontsize = 6)
 
@@
   default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D30_II, 
-          at = c(0, scale.BAG3.max),
-          fontsize = 6)
 
@@
   linecolor = NA,
-  x = 0.75, 
-  y = 1.625, 
+  x = 0.5, 
+  y = 4.975,
   width = 4.0, 
@@
           fontsize = 6)
+
+# Annotate sample name
+plotText(label = "mDAN D30", 
+         fontsize = 6, 
+         fontfamily = "Helvetica",
+         fontcolor = "#DC143C",
+         x = 0.25, 
+         y = 5.0625, 
+         just = c("left", "top"),
+         default.units = "inches",
+         fontface = "bold")
 
@@
   linecolor = NA,
-  x = 0.75, 
-  y = 2.0, 
+  x = 0.5, 
+  y = 5.275, 
   width = 4.0, 
@@
   default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D50_I, 
-          at = c(0, scale.BAG3.max),
-          fontsize = 6)
 
@@
   default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D50_II, 
-          at = c(0, scale.BAG3.max),
-          fontsize = 6)
 
@@
   linecolor = NA,
-  x = 0.75, 
-  y = 2.0, 
+  x = 0.5, 
+  y = 5.275,
   width = 4.0, 
@@
           fontsize = 6)
+
+# Annotate sample name
+plotText(label = "mDAN D50", 
+         fontsize = 6, 
+         fontfamily = "Helvetica",
+         fontcolor = "#E9967A",
+         x = 0.25, 
+         y = 5.375, 
+         just = c("left", "top"),
+         default.units = "inches",
+         fontface = "bold")
 
@@
   fill = "black",
-  x = 0.75,
-  y = 2.375,
+  x = 0.5,
+  y = 5.625,
   width = 4.0,
@@
 
-# Add the samples name
-plotText(label = "smNPC", 
-         fontsize = 6, 
-         fontcolor = "#A9A9A9",
-         x = 0.75, 
-         y = 0.875, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-plotText(label = "mDAN D15", 
-         fontsize = 6, 
-         fontcolor = "#B22222",
-         x = 0.75, 
-         y = 1.25, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-plotText(label = "mDAN D30", 
-         fontsize = 6, 
-         fontcolor = "#DC143C",
-         x = 0.75, 
-         y = 1.625, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-plotText(label = "mDAN D50", 
-         fontsize = 6, 
-         fontcolor = "#E9967A",
-         x = 0.75, 
-         y = 2.0, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-#### PANEL B - BAG3 and LHX1 expression (RNAseq)
-# text B
-plotText(label = "B", 
+#### PANEL E - BAG3 and LHX1 expression (RNAseq)
+# text E
+plotText(label = "E", 
          fontsize = 12,
-         x = 5.0, 
-         y = 0.5, 
+         fontfamily = "Helvetica",
+         x = 4.75, 
+         y = 4.0, 
          just = "left", 
@@
 dat.RPKM.filt = read_rds("/home/vagrant/Manuscript_1/FIGURE2/mat_RPKM.rds")
+#dat.RPKM.filt = read_rds("/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE2/mat_RPKM.rds")
 
@@
 plotGG(plot = BAG3.LHX1.exp, 
-       x = 5.25, 
-       y = 0.625, 
-       width = 2, 
+       x = 5.0, 
+       y = 4.125, 
+       width = 3, 
        height = 3.5,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-# Add the transcription factor binding motif (TFBS) for LHX1
-pfm.LHX1 = getMatrixByID(JASPAR2020, 
-                         ID = "MA1518.1")
-LHX1 = new.env()
-
-LHX1$LHX1 = pfm.LHX1@profileMatrix
-
-LHX1 = as.list(LHX1)
-LHX1_TFBS = ggseqlogo(LHX1)
-
-# Place the plot
-plotGG(plot = LHX1_TFBS, 
-       x = 1.7125, 
-       y = 2.625, 
-       width = 1.5, 
-       height = 1.5,
        just = c("left", "top"), 
@@
               fill = "#404788FF",
-              y = 0.875, 
-              height = 1.75, 
+              y = 4.5, 
+              height = 1.5, 
               just = c("left", "top"), 
@@
               params = SNP_param,
-              y0 = 2.625, 
-              x1 = c(2.25, 3.25), 
-              y1 = 2.75, 
-              default.units = "inches")
-
-# text C
-plotText(label = "C", 
+              y0 = 6.0, 
+              x1 = c(2.25, 2.75), 
+              y1 = 6.125, 
+              default.units = "inches")
+
+# Add the transcription factor binding motif (TFBS) for LHX1
+pfm.LHX1 = getMatrixByID(JASPAR2020, 
+                         ID = "MA1518.1")
+LHX1 = new.env()
+
+LHX1$LHX1 = pfm.LHX1@profileMatrix
+
+LHX1 = as.list(LHX1)
+
+# Remove the nucleotide position
+LHX1_TFBS = ggseqlogo(LHX1) +
+  annotate("rect", 
+           xmin = 4.5, 
+           xmax = 5.5, 
+           ymin = -0.05, 
+           ymax = 2.5, 
+           alpha = .1, 
+           col = "black", 
+           fill = "#404788FF") +
+  theme(axis.text.x = element_blank())
+
+# Place the plot
+plotGG(plot = LHX1_TFBS, 
+       x = 1.4925, 
+       y = 5.9375, 
+       width = 1.5, 
+       height = 1.5,
+       just = c("left", "top"), 
+       default.units = "inches")
+
+# text F
+plotText(label = "F", 
          fontsize = 12,
+         fontfamily = "Helvetica",
          x = 0.25, 
-         y = 4.25, 
+         y = 7.75, 
          just = "left", 
@@
 
-# ATACseq signal IDUA
-# 1st bio replicate smNPC
-bw.IDUA.smNPC_1 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/smNPC_I.bw"),
-                        chrom = "chr4",
-                        chromstart = 947008,
-                        chromend = 1027208)
-
-# 2nd bio replicate smNPC
-bw.IDUA.smNPC_2 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/smNPC_II.bw"),
-                        chrom = "chr4",
-                        chromstart = 947008,
-                        chromend = 1027208)
-
-# 3rd bio replicate smNPC
-bw.IDUA.smNPC_3 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/smNPC_III.bw"),
-                        chrom = "chr4",
-                        chromstart = 947008,
-                        chromend = 1027208)
-
-# 1st bio replicate TH positive neurons D15
-bw.IDUA.TH.pos_D15_1 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/D15_POS_I.bw"),
-                        chrom = "chr4",
-                        chromstart = 947008,
-                        chromend = 1027208)
-
-# 2nd bio replicate TH positive neurons D15
-bw.IDUA.TH.pos_D15_2 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/D15_POS_II.bw"),
-                        chrom = "chr4",
-                        chromstart = 947008,
-                        chromend = 1027208)
-
-# 3rd bio replicate TH positive neurons D15
-bw.IDUA.TH.pos_D15_3 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/D15_POS_III.bw"),
-                        chrom = "chr4",
-                        chromstart = 947008,
-                        chromend = 1027208)
-
-# 1st bio replicate TH positive neurons D30
-bw.IDUA.TH.pos_D30_1 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/D30_POS_I.bw"),
-                        chrom = "chr4",
-                        chromstart = 947008,
-                        chromend = 1027208)
-
-# 2nd bio replicate TH positive neurons D30
-bw.IDUA.TH.pos_D30_2 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/D30_POS_II.bw"),
-                        chrom = "chr4",
-                        chromstart = 947008,
-                        chromend = 1027208)
-
-# 3rd bio replicate TH positive neurons D30
-bw.IDUA.TH.pos_D30_3 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/D30_POS_III.bw"),
-                        chrom = "chr4",
-                        chromstart = 947008,
-                        chromend = 1027208)
-
-# 1st bio replicate TH positive neurons D50
-bw.IDUA.TH.pos_D50_1 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/HFFTHmCherry_D50_possort_S1.bw"),
-                        chrom = "chr4",
-                        chromstart = 947008,
-                        chromend = 1027208)
-
-# 2nd bio replicate TH positive neurons D50
-bw.IDUA.TH.pos_D50_2 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/HFFTHmCherry_D50_possort_S3.bw"),
-                        chrom = "chr4",
-                        chromstart = 947008,
-                        chromend = 1027208)
-
-# 3rd bio replicate TH positive neurons D50
-bw.IDUA.TH.pos_D50_3 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/HFFTHmCherry_D50_possort_S4.bw"),
-                        chrom = "chr4",
-                        chromstart = 947008,
-                        chromend = 1027208)
-
-# Add a scale next to the bigwig files - check the maximum to choose
-scale.IDUA.max = max(c(bw.IDUA.smNPC_1$score,
-                       bw.IDUA.smNPC_2$score,
-                       bw.IDUA.smNPC_3$score,
-                       bw.IDUA.TH.pos_D15_1$score,
-                       bw.IDUA.TH.pos_D15_2$score,
-                       bw.IDUA.TH.pos_D15_3$score,
-                       bw.IDUA.TH.pos_D30_1$score,
-                       bw.IDUA.TH.pos_D30_2$score,
-                       bw.IDUA.TH.pos_D30_3$score,
-                       bw.IDUA.TH.pos_D50_1$score,
-                       bw.IDUA.TH.pos_D50_2$score,
-                       bw.IDUA.TH.pos_D50_3$score))
-
-print(scale.IDUA.max)
-
-# Define parameters for the regions
-region.p.IDUA = pgParams(chrom = "chr4",
-                         chromstart = 947108,
-                         chromend = 1027108,
-                         assembly = "hg38",
-                         range = c(0, scale.IDUA.max))
-
-# Add the genomic label
-plotGenomeLabel(
-  chrom = "chr4",
-  chromstart = 947108,
-  chromend = 1027108,
-  assembly = "hg38",
-  x = 0.75,
-  y = 4.375,
-  length = 4.0,
-  default.units = "inches",
-  scale = "Mb")
-
-# ATACseq signal smNPC_I
-ATAC_smNPC_I_IDUA = plotSignal(
-  data = bw.IDUA.smNPC_1, 
-  params = region.p.IDUA,
-  fill = "#D3D3D3", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 4.625, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_smNPC_I_IDUA, 
-          at = c(0, scale.IDUA.max),
-          fontsize = 6)
-
-# ATACseq signal smNPC_II
-ATAC_smNPC_II_IDUA = plotSignal(
-  data = bw.IDUA.smNPC_2, 
-  params = region.p.IDUA,
-  fill = "#C0C0C0", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 4.625, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_smNPC_II_IDUA, 
-          at = c(0, scale.IDUA.max),
-          fontsize = 6)
-
-# Add the SNP position that zoom in the TFBS
-SNP_param_IDUA = pgParams(chrom = "chr4",
-                     chromstart = 987108,
-                     chromend = 987108,
-                     assembly = "hg38")
-
-annoHighlight(plot = ATAC_smNPC_I_IDUA, 
-              params = SNP_param_IDUA,
-              fill = "#404788FF",
-              y = 4.75, 
-              height = 1.875, 
-              just = c("left", "top"), 
-              default.units = "inches")
-
-annoZoomLines(plot = ATAC_smNPC_I_IDUA, 
-              params = SNP_param_IDUA,
-              y0 = 6.625, 
-              x1 = c(2.25, 3.25), 
-              y1 = 6.75, 
-              default.units = "inches")
-
-# ATACseq signal smNPC_III
-ATAC_smNPC_III_IDUA = plotSignal(
-  data = bw.IDUA.smNPC_3, 
-  params = region.p.IDUA,
-  fill = "#A9A9A9", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 4.625, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_smNPC_III_IDUA, 
-          at = c(0, scale.IDUA.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D15 I
-ATAC_TH.pos_D15_I_IDUA = plotSignal(
-  data = bw.IDUA.TH.pos_D15_1, 
-  params = region.p.IDUA,
-  fill = "#B22222", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 5.0, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D15_I_IDUA, 
-          at = c(0, scale.IDUA.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D15 II
-ATAC_TH.pos_D15_II_IDUA = plotSignal(
-  data = bw.IDUA.TH.pos_D15_2, 
-  params = region.p.IDUA,
-  fill = "#A52A2A", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 5.0, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D15_II_IDUA, 
-          at = c(0, scale.IDUA.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D15 III
-ATAC_TH.pos_D15_III_IDUA = plotSignal(
-  data = bw.IDUA.TH.pos_D15_3, 
-  params = region.p.IDUA,
-  fill = "#8B0000", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 5.0, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D15_III_IDUA, 
-          at = c(0, scale.IDUA.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D30 I
-ATAC_TH.pos_D30_I_IDUA = plotSignal(
-  data = bw.IDUA.TH.pos_D30_1, 
-  params = region.p.IDUA,
-  fill = "#FF6347", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 5.375, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D30_I_IDUA, 
-          at = c(0, scale.IDUA.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D30 II
-ATAC_TH.pos_D30_II_IDUA = plotSignal(
-  data = bw.IDUA.TH.pos_D30_2, 
-  params = region.p.IDUA,
-  fill = "#FF0000", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 5.375, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D30_II_IDUA, 
-          at = c(0, scale.IDUA.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D30 III
-ATAC_TH.pos_D30_III_IDUA = plotSignal(
-  data = bw.IDUA.TH.pos_D30_3, 
-  params = region.p.IDUA,
-  fill = "#DC143C", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 5.375, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D30_III_IDUA, 
-          at = c(0, scale.IDUA.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D50 I
-ATAC_TH.pos_D50_I_IDUA = plotSignal(
-  data = bw.IDUA.TH.pos_D50_1, 
-  params = region.p.IDUA,
-  fill = "#FFA07A", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 5.75, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D50_I_IDUA, 
-          at = c(0, scale.IDUA.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D50 II
-ATAC_TH.pos_D50_II_IDUA = plotSignal(
-  data = bw.IDUA.TH.pos_D50_2, 
-  params = region.p.IDUA,
-  fill = "#FA8072", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 5.75, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D50_II_IDUA, 
-          at = c(0, scale.IDUA.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D50 III
-ATAC_TH.pos_D50_III_IDUA = plotSignal(
-  data = bw.IDUA.TH.pos_D50_3, 
-  params = region.p.IDUA,
-  fill = "#E9967A", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 5.75, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D50_III_IDUA, 
-          at = c(0, scale.IDUA.max),
-          fontsize = 6)
-
-# Gene track
-plotGenes(chrom = "chr4",
-  chromstart = 947108,
-  chromend = 1027108,
-  assembly = assembly(Genome = "hg38refGene", 
-                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
-                      OrgDb = "org.Hs.eg.db"),
-  fontcolor = "black",
-  fill = "black",
-  x = 0.75,
-  y = 6.125,
-  width = 4.0,
-  height = 0.375,
-  just = c("left", "top"),
-  default.units = "inches")
-
-# Add the samples name
-plotText(label = "smNPC", 
-         fontsize = 6, 
-         fontcolor = "#A9A9A9",
-         x = 0.75, 
-         y = 4.625, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-plotText(label = "mDAN D15", 
-         fontsize = 6, 
-         fontcolor = "#B22222",
-         x = 0.75, 
-         y = 5.0, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-plotText(label = "mDAN D30", 
-         fontsize = 6, 
-         fontcolor = "#DC143C",
-         x = 0.75, 
-         y = 5.375, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-plotText(label = "mDAN D50", 
-         fontsize = 6, 
-         fontcolor = "#E9967A",
-         x = 0.75, 
-         y = 5.75, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-#### PANEL D - IDUA and ZBTB14 expression (RNAseq)
-# text D
-plotText(label = "D", 
-         fontsize = 12,
-         x = 5.0, 
-         y = 4.25, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
-
-IDUA.ZBTB14.exp = ggboxplot(dat.RPKM.filt %>% 
-                            dplyr::filter(gene_name %in% c("IDUA", "ZBTB14", "SLC26A1")) %>% 
-                              mutate(gene_name = factor(gene_name,
-                                                        levels = c("IDUA", "ZBTB14", "SLC26A1"))),
-                          x = "Cond", 
-                          y = "RPKM", 
-                          add = "jitter", 
-                          fill = "Cond", 
-                          palette = c("#A9A9A9", "#B22222", "#DC143C", "#E9967A"),
-                          facet.by = "gene_name",
-                          xlab = "", 
-                          ylab = "Reads Per Kilobase Million (RPKM)") +
-  scale_x_discrete(labels = c("smNPC",
-                              "mDAN D15",
-                              "mDAN D30",
-                              "mDAN D50")) +
-  theme(legend.position = "none",
-        axis.text.x = element_text(angle = 90))
-
-# Place the plot
-plotGG(plot = IDUA.ZBTB14.exp, 
-       x = 5.25, 
-       y = 4.25, 
-       width = 3, 
-       height = 3.5,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-# Add the transcription factor binding motif (TFBS) for ZBTB14
-pfm.ZBTB14 = getMatrixByID(JASPAR2020, 
-                         ID = "MA1650.1")
-ZBTB14 = new.env()
-
-ZBTB14$ZBTB14 = pfm.ZBTB14@profileMatrix
-
-ZBTB14 = as.list(ZBTB14)
-ZBTB14_TFBS = ggseqlogo(ZBTB14)
-
-# Place the plot
-plotGG(plot = ZBTB14_TFBS, 
-       x = 1.7125, 
-       y = 6.625, 
-       width = 1.5, 
-       height = 1.5,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-# text E
-plotText(label = "E", 
-         fontsize = 12,
-         x = 0.25, 
-         y = 8.0, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
+# # ATACseq signal IDUA
+# # 1st bio replicate smNPC
+# bw.IDUA.smNPC_1 = readBigwig(file = paste0(bw.path, 
+#                                       "BIGWIG/smNPC_I.bw"),
+#                         chrom = "chr4",
+#                         chromstart = 947008,
+#                         chromend = 1027208)
+# 
+# # 2nd bio replicate smNPC
+# bw.IDUA.smNPC_2 = readBigwig(file = paste0(bw.path, 
+#                                       "BIGWIG/smNPC_II.bw"),
+#                         chrom = "chr4",
+#                         chromstart = 947008,
+#                         chromend = 1027208)
+# 
+# # 3rd bio replicate smNPC
+# bw.IDUA.smNPC_3 = readBigwig(file = paste0(bw.path, 
+#                                       "BIGWIG/smNPC_III.bw"),
+#                         chrom = "chr4",
+#                         chromstart = 947008,
+#                         chromend = 1027208)
+# 
+# # 1st bio replicate TH positive neurons D15
+# bw.IDUA.TH.pos_D15_1 = readBigwig(file = paste0(bw.path, 
+#                                       "BIGWIG/D15_POS_I.bw"),
+#                         chrom = "chr4",
+#                         chromstart = 947008,
+#                         chromend = 1027208)
+# 
+# # 2nd bio replicate TH positive neurons D15
+# bw.IDUA.TH.pos_D15_2 = readBigwig(file = paste0(bw.path, 
+#                                       "BIGWIG/D15_POS_II.bw"),
+#                         chrom = "chr4",
+#                         chromstart = 947008,
+#                         chromend = 1027208)
+# 
+# # 3rd bio replicate TH positive neurons D15
+# bw.IDUA.TH.pos_D15_3 = readBigwig(file = paste0(bw.path, 
+#                                       "BIGWIG/D15_POS_III.bw"),
+#                         chrom = "chr4",
+#                         chromstart = 947008,
+#                         chromend = 1027208)
+# 
+# # 1st bio replicate TH positive neurons D30
+# bw.IDUA.TH.pos_D30_1 = readBigwig(file = paste0(bw.path, 
+#                                       "BIGWIG/D30_POS_I.bw"),
+#                         chrom = "chr4",
+#                         chromstart = 947008,
+#                         chromend = 1027208)
+# 
+# # 2nd bio replicate TH positive neurons D30
+# bw.IDUA.TH.pos_D30_2 = readBigwig(file = paste0(bw.path, 
+#                                       "BIGWIG/D30_POS_II.bw"),
+#                         chrom = "chr4",
+#                         chromstart = 947008,
+#                         chromend = 1027208)
+# 
+# # 3rd bio replicate TH positive neurons D30
+# bw.IDUA.TH.pos_D30_3 = readBigwig(file = paste0(bw.path, 
+#                                       "BIGWIG/D30_POS_III.bw"),
+#                         chrom = "chr4",
+#                         chromstart = 947008,
+#                         chromend = 1027208)
+# 
+# # 1st bio replicate TH positive neurons D50
+# bw.IDUA.TH.pos_D50_1 = readBigwig(file = paste0(bw.path, 
+#                                       "BIGWIG/HFFTHmCherry_D50_possort_S1.bw"),
+#                         chrom = "chr4",
+#                         chromstart = 947008,
+#                         chromend = 1027208)
+# 
+# # 2nd bio replicate TH positive neurons D50
+# bw.IDUA.TH.pos_D50_2 = readBigwig(file = paste0(bw.path, 
+#                                       "BIGWIG/HFFTHmCherry_D50_possort_S3.bw"),
+#                         chrom = "chr4",
+#                         chromstart = 947008,
+#                         chromend = 1027208)
+# 
+# # 3rd bio replicate TH positive neurons D50
+# bw.IDUA.TH.pos_D50_3 = readBigwig(file = paste0(bw.path, 
+#                                       "BIGWIG/HFFTHmCherry_D50_possort_S4.bw"),
+#                         chrom = "chr4",
+#                         chromstart = 947008,
+#                         chromend = 1027208)
+# 
+# # Add a scale next to the bigwig files - check the maximum to choose
+# scale.IDUA.max = max(c(bw.IDUA.smNPC_1$score,
+#                        bw.IDUA.smNPC_2$score,
+#                        bw.IDUA.smNPC_3$score,
+#                        bw.IDUA.TH.pos_D15_1$score,
+#                        bw.IDUA.TH.pos_D15_2$score,
+#                        bw.IDUA.TH.pos_D15_3$score,
+#                        bw.IDUA.TH.pos_D30_1$score,
+#                        bw.IDUA.TH.pos_D30_2$score,
+#                        bw.IDUA.TH.pos_D30_3$score,
+#                        bw.IDUA.TH.pos_D50_1$score,
+#                        bw.IDUA.TH.pos_D50_2$score,
+#                        bw.IDUA.TH.pos_D50_3$score))
+# 
+# print(scale.IDUA.max)
+# 
+# # Define parameters for the regions
+# region.p.IDUA = pgParams(chrom = "chr4",
+#                          chromstart = 947108,
+#                          chromend = 1027108,
+#                          assembly = "hg38",
+#                          range = c(0, scale.IDUA.max))
+# 
+# # Add the genomic label
+# plotGenomeLabel(
+#   chrom = "chr4",
+#   chromstart = 947108,
+#   chromend = 1027108,
+#   assembly = "hg38",
+#   x = 0.75,
+#   y = 4.375,
+#   length = 4.0,
+#   default.units = "inches",
+#   scale = "Mb")
+# 
+# # ATACseq signal smNPC_I
+# ATAC_smNPC_I_IDUA = plotSignal(
+#   data = bw.IDUA.smNPC_1, 
+#   params = region.p.IDUA,
+#   fill = "#D3D3D3", 
+#   alpha = 0.7, 
+#   linecolor = NA,
+#   x = 0.75, 
+#   y = 4.625, 
+#   width = 4.0, 
+#   height = 0.25,
+#   just = c("left", "top"), 
+#   default.units = "inches")
+# 
+# annoYaxis(plot = ATAC_smNPC_I_IDUA, 
+#           at = c(0, scale.IDUA.max),
+#           fontsize = 6)
+# 
+# # ATACseq signal smNPC_II
+# ATAC_smNPC_II_IDUA = plotSignal(
+#   data = bw.IDUA.smNPC_2, 
+#   params = region.p.IDUA,
+#   fill = "#C0C0C0", 
+#   alpha = 0.7, 
+#   linecolor = NA,
+#   x = 0.75, 
+#   y = 4.625, 
+#   width = 4.0, 
+#   height = 0.25,
+#   just = c("left", "top"), 
+#   default.units = "inches")
+# 
+# annoYaxis(plot = ATAC_smNPC_II_IDUA, 
+#           at = c(0, scale.IDUA.max),
+#           fontsize = 6)
+# 
+# # Add the SNP position that zoom in the TFBS
+# SNP_param_IDUA = pgParams(chrom = "chr4",
+#                      chromstart = 987108,
+#                      chromend = 987108,
+#                      assembly = "hg38")
+# 
+# annoHighlight(plot = ATAC_smNPC_I_IDUA, 
+#               params = SNP_param_IDUA,
+#               fill = "#404788FF",
+#               y = 4.75, 
+#               height = 1.875, 
+#               just = c("left", "top"), 
+#               default.units = "inches")
+# 
+# annoZoomLines(plot = ATAC_smNPC_I_IDUA, 
+#               params = SNP_param_IDUA,
+#               y0 = 6.625, 
+#               x1 = c(2.25, 3.25), 
+#               y1 = 6.75, 
+#               default.units = "inches")
+# 
+# # ATACseq signal smNPC_III
+# ATAC_smNPC_III_IDUA = plotSignal(
+#   data = bw.IDUA.smNPC_3, 
+#   params = region.p.IDUA,
+#   fill = "#A9A9A9", 
+#   alpha = 0.7, 
+#   linecolor = NA,
+#   x = 0.75, 
+#   y = 4.625, 
+#   width = 4.0, 
+#   height = 0.25,
+#   just = c("left", "top"), 
+#   default.units = "inches")
+# 
+# annoYaxis(plot = ATAC_smNPC_III_IDUA, 
+#           at = c(0, scale.IDUA.max),
+#           fontsize = 6)
+# 
+# # ATACseq signal TH positive neurons D15 I
+# ATAC_TH.pos_D15_I_IDUA = plotSignal(
+#   data = bw.IDUA.TH.pos_D15_1, 
+#   params = region.p.IDUA,
+#   fill = "#B22222", 
+#   alpha = 0.7, 
+#   linecolor = NA,
+#   x = 0.75, 
+#   y = 5.0, 
+#   width = 4.0, 
+#   height = 0.25,
+#   just = c("left", "top"), 
+#   default.units = "inches")
+# 
+# annoYaxis(plot = ATAC_TH.pos_D15_I_IDUA, 
+#           at = c(0, scale.IDUA.max),
+#           fontsize = 6)
+# 
+# # ATACseq signal TH positive neurons D15 II
+# ATAC_TH.pos_D15_II_IDUA = plotSignal(
+#   data = bw.IDUA.TH.pos_D15_2, 
+#   params = region.p.IDUA,
+#   fill = "#A52A2A", 
+#   alpha = 0.7, 
+#   linecolor = NA,
+#   x = 0.75, 
+#   y = 5.0, 
+#   width = 4.0, 
+#   height = 0.25,
+#   just = c("left", "top"), 
+#   default.units = "inches")
+# 
+# annoYaxis(plot = ATAC_TH.pos_D15_II_IDUA, 
+#           at = c(0, scale.IDUA.max),
+#           fontsize = 6)
+# 
+# # ATACseq signal TH positive neurons D15 III
+# ATAC_TH.pos_D15_III_IDUA = plotSignal(
+#   data = bw.IDUA.TH.pos_D15_3, 
+#   params = region.p.IDUA,
+#   fill = "#8B0000", 
+#   alpha = 0.7, 
+#   linecolor = NA,
+#   x = 0.75, 
+#   y = 5.0, 
+#   width = 4.0, 
+#   height = 0.25,
+#   just = c("left", "top"), 
+#   default.units = "inches")
+# 
+# annoYaxis(plot = ATAC_TH.pos_D15_III_IDUA, 
+#           at = c(0, scale.IDUA.max),
+#           fontsize = 6)
+# 
+# # ATACseq signal TH positive neurons D30 I
+# ATAC_TH.pos_D30_I_IDUA = plotSignal(
+#   data = bw.IDUA.TH.pos_D30_1, 
+#   params = region.p.IDUA,
+#   fill = "#FF6347", 
+#   alpha = 0.7, 
+#   linecolor = NA,
+#   x = 0.75, 
+#   y = 5.375, 
+#   width = 4.0, 
+#   height = 0.25,
+#   just = c("left", "top"), 
+#   default.units = "inches")
+# 
+# annoYaxis(plot = ATAC_TH.pos_D30_I_IDUA, 
+#           at = c(0, scale.IDUA.max),
+#           fontsize = 6)
+# 
+# # ATACseq signal TH positive neurons D30 II
+# ATAC_TH.pos_D30_II_IDUA = plotSignal(
+#   data = bw.IDUA.TH.pos_D30_2, 
+#   params = region.p.IDUA,
+#   fill = "#FF0000", 
+#   alpha = 0.7, 
+#   linecolor = NA,
+#   x = 0.75, 
+#   y = 5.375, 
+#   width = 4.0, 
+#   height = 0.25,
+#   just = c("left", "top"), 
+#   default.units = "inches")
+# 
+# annoYaxis(plot = ATAC_TH.pos_D30_II_IDUA, 
+#           at = c(0, scale.IDUA.max),
+#           fontsize = 6)
+# 
+# # ATACseq signal TH positive neurons D30 III
+# ATAC_TH.pos_D30_III_IDUA = plotSignal(
+#   data = bw.IDUA.TH.pos_D30_3, 
+#   params = region.p.IDUA,
+#   fill = "#DC143C", 
+#   alpha = 0.7, 
+#   linecolor = NA,
+#   x = 0.75, 
+#   y = 5.375, 
+#   width = 4.0, 
+#   height = 0.25,
+#   just = c("left", "top"), 
+#   default.units = "inches")
+# 
+# annoYaxis(plot = ATAC_TH.pos_D30_III_IDUA, 
+#           at = c(0, scale.IDUA.max),
+#           fontsize = 6)
+# 
+# # ATACseq signal TH positive neurons D50 I
+# ATAC_TH.pos_D50_I_IDUA = plotSignal(
+#   data = bw.IDUA.TH.pos_D50_1, 
+#   params = region.p.IDUA,
+#   fill = "#FFA07A", 
+#   alpha = 0.7, 
+#   linecolor = NA,
+#   x = 0.75, 
+#   y = 5.75, 
+#   width = 4.0, 
+#   height = 0.25,
+#   just = c("left", "top"), 
+#   default.units = "inches")
+# 
+# annoYaxis(plot = ATAC_TH.pos_D50_I_IDUA, 
+#           at = c(0, scale.IDUA.max),
+#           fontsize = 6)
+# 
+# # ATACseq signal TH positive neurons D50 II
+# ATAC_TH.pos_D50_II_IDUA = plotSignal(
+#   data = bw.IDUA.TH.pos_D50_2, 
+#   params = region.p.IDUA,
+#   fill = "#FA8072", 
+#   alpha = 0.7, 
+#   linecolor = NA,
+#   x = 0.75, 
+#   y = 5.75, 
+#   width = 4.0, 
+#   height = 0.25,
+#   just = c("left", "top"), 
+#   default.units = "inches")
+# 
+# annoYaxis(plot = ATAC_TH.pos_D50_II_IDUA, 
+#           at = c(0, scale.IDUA.max),
+#           fontsize = 6)
+# 
+# # ATACseq signal TH positive neurons D50 III
+# ATAC_TH.pos_D50_III_IDUA = plotSignal(
+#   data = bw.IDUA.TH.pos_D50_3, 
+#   params = region.p.IDUA,
+#   fill = "#E9967A", 
+#   alpha = 0.7, 
+#   linecolor = NA,
+#   x = 0.75, 
+#   y = 5.75, 
+#   width = 4.0, 
+#   height = 0.25,
+#   just = c("left", "top"), 
+#   default.units = "inches")
+# 
+# annoYaxis(plot = ATAC_TH.pos_D50_III_IDUA, 
+#           at = c(0, scale.IDUA.max),
+#           fontsize = 6)
+# 
+# # Gene track
+# plotGenes(chrom = "chr4",
+#   chromstart = 947108,
+#   chromend = 1027108,
+#   assembly = assembly(Genome = "hg38refGene", 
+#                       TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
+#                       OrgDb = "org.Hs.eg.db"),
+#   fontcolor = "black",
+#   fill = "black",
+#   x = 0.75,
+#   y = 6.125,
+#   width = 4.0,
+#   height = 0.375,
+#   just = c("left", "top"),
+#   default.units = "inches")
+# 
+# # Add the samples name
+# plotText(label = "smNPC", 
+#          fontsize = 6, 
+#          fontcolor = "#A9A9A9",
+#          fontfamily = "Helvetica",
+#          x = 0.75, 
+#          y = 4.625, 
+#          just = c("left", "top"),
+#          default.units = "inches",
+#          fontface = "bold")
+# 
+# plotText(label = "mDAN D15", 
+#          fontsize = 6, 
+#          fontcolor = "#B22222",
+#          fontfamily = "Helvetica",
+#          x = 0.75, 
+#          y = 5.0, 
+#          just = c("left", "top"),
+#          default.units = "inches",
+#          fontface = "bold")
+# 
+# plotText(label = "mDAN D30", 
+#          fontsize = 6, 
+#          fontcolor = "#DC143C",
+#          fontfamily = "Helvetica",
+#          x = 0.75, 
+#          y = 5.375, 
+#          just = c("left", "top"),
+#          default.units = "inches",
+#          fontface = "bold")
+# 
+# plotText(label = "mDAN D50", 
+#          fontsize = 6, 
+#          fontcolor = "#E9967A",
+#          fontfamily = "Helvetica",
+#          x = 0.75, 
+#          y = 5.75, 
+#          just = c("left", "top"),
+#          default.units = "inches",
+#          fontface = "bold")
+# 
+# #### PANEL D - IDUA and ZBTB14 expression (RNAseq)
+# # text D
+# plotText(label = "D", 
+#          fontsize = 12,
+#          fontfamily = "Helvetica",
+#          x = 5.0, 
+#          y = 4.25, 
+#          just = "left", 
+#          default.units = "inches",
+#          fontface = "bold")
+# 
+# IDUA.ZBTB14.exp = ggboxplot(dat.RPKM.filt %>% 
+#                             dplyr::filter(gene_name %in% c("IDUA", "ZBTB14", "SLC26A1")) %>% 
+#                               mutate(gene_name = factor(gene_name,
+#                                                         levels = c("IDUA", "ZBTB14", "SLC26A1"))),
+#                           x = "Cond", 
+#                           y = "RPKM", 
+#                           add = "jitter", 
+#                           fill = "Cond", 
+#                           palette = c("#A9A9A9", "#B22222", "#DC143C", "#E9967A"),
+#                           facet.by = "gene_name",
+#                           xlab = "", 
+#                           ylab = "Reads Per Kilobase Million (RPKM)") +
+#   scale_x_discrete(labels = c("smNPC",
+#                               "mDAN D15",
+#                               "mDAN D30",
+#                               "mDAN D50")) +
+#   theme(legend.position = "none",
+#         axis.text.x = element_text(angle = 90))
+#   
+# 
+# # Place the plot
+# plotGG(plot = IDUA.ZBTB14.exp, 
+#        x = 5.25, 
+#        y = 4.25, 
+#        width = 3, 
+#        height = 3.5,
+#        just = c("left", "top"), 
+#        default.units = "inches")
+# 
+# # Add the transcription factor binding motif (TFBS) for ZBTB14
+# pfm.ZBTB14 = getMatrixByID(JASPAR2020, 
+#                          ID = "MA1650.1")
+# ZBTB14 = new.env()
+# 
+# ZBTB14$ZBTB14 = pfm.ZBTB14@profileMatrix
+# 
+# ZBTB14 = as.list(ZBTB14)
+# 
+# # Remove the nucleotide position
+# ZBTB14_TFBS = ggseqlogo(ZBTB14) +
+#   annotate("rect", 
+#            xmin = 8.5, 
+#            xmax = 9.5, 
+#            ymin = -0.05, 
+#            ymax = 2.5, 
+#            alpha = .1, 
+#            col = "black", 
+#            fill = "#404788FF") +
+#   theme(axis.text.x = element_blank())
+# 
+# # Place the plot
+# plotGG(plot = ZBTB14_TFBS, 
+#        x = 1.6225, 
+#        y = 6.625, 
+#        width = 1.5, 
+#        height = 1.5,
+#        just = c("left", "top"), 
+#        default.units = "inches")
+# 
+# # text E
+# plotText(label = "E", 
+#          fontsize = 12,
+#          fontfamily = "Helvetica",
+#          x = 0.25, 
+#          y = 8.0, 
+#          just = "left", 
+#          default.units = "inches",
+#          fontface = "bold")
 
@@
   assembly = "hg38",
-  x = 0.75,
-  y = 8.125,
+  x = 0.5,
+  y = 7.875,
   length = 4.0,
@@
   linecolor = NA,
-  x = 0.75, 
-  y = 8.375, 
+  x = 0.5, 
+  y = 8.125, 
   width = 4.0, 
@@
   default.units = "inches")
-
-annoYaxis(plot = ATAC_smNPC_I_SCARB2, 
-          at = c(0, scale.SCARB2.max),
-          fontsize = 6)
 
@@
   default.units = "inches")
-
-annoYaxis(plot = ATAC_smNPC_II_SCARB2, 
-          at = c(0, scale.SCARB2.max),
-          fontsize = 6)
 
@@
 
-# Add the SNP position that zoom in the TFBS
-SNP_param_SCARB2 = pgParams(chrom = "chr4",
-                     chromstart = 76213717,
-                     chromend = 76213717,
-                     assembly = "hg38")
-
-annoHighlight(plot = ATAC_smNPC_I_SCARB2, 
-              params = SNP_param_SCARB2,
-              fill = "#404788FF",
-              y = 8.375, 
-              height = 1.875, 
-              just = c("left", "top"), 
-              default.units = "inches")
-
-annoZoomLines(plot = ATAC_smNPC_I_SCARB2, 
-              params = SNP_param_SCARB2,
-              y0 = 10.25, 
-              x1 = c(2.25, 3.25), 
-              y1 = 10.5, 
-              default.units = "inches")
+# Add the samples name
+plotText(label = "smNPC", 
+         fontsize = 6, 
+         fontcolor = "#A9A9A9",
+         fontfamily = "Helvetica",
+         x = 0.25, 
+         y = 8.250, 
+         just = c("left", "top"),
+         default.units = "inches",
+         fontface = "bold")
 
@@
   linecolor = NA,
-  x = 0.75, 
-  y = 8.75, 
+  x = 0.5, 
+  y = 8.4375, 
   width = 4.0, 
@@
   default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D15_I_SCARB2, 
-          at = c(0, scale.SCARB2.max),
-          fontsize = 6)
 
@@
   default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D15_II_SCARB2, 
-          at = c(0, scale.SCARB2.max),
-          fontsize = 6)
 
@@
   linecolor = NA,
-  x = 0.75, 
-  y = 8.75, 
+  x = 0.5, 
+  y = 8.4375,  
   width = 4.0, 
@@
           fontsize = 6)
+
+plotText(label = "mDAN D15", 
+         fontsize = 6, 
+         fontcolor = "#B22222",
+         fontfamily = "Helvetica",
+         x = 0.25, 
+         y = 8.5625, 
+         just = c("left", "top"),
+         default.units = "inches",
+         fontface = "bold")
 
@@
   linecolor = NA,
-  x = 0.75, 
-  y = 9.125, 
+  x = 0.5, 
+  y = 8.75, 
   width = 4.0, 
@@
   default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D30_I_SCARB2, 
-          at = c(0, scale.SCARB2.max),
-          fontsize = 6)
 
@@
   default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D30_II_SCARB2, 
-          at = c(0, scale.SCARB2.max),
-          fontsize = 6)
 
@@
           fontsize = 6)
+
+plotText(label = "mDAN D30", 
+         fontsize = 6, 
+         fontcolor = "#DC143C",
+         fontfamily = "Helvetica",
+         x = 0.25, 
+         y = 8.875, 
+         just = c("left", "top"),
+         default.units = "inches",
+         fontface = "bold")
 
@@
   linecolor = NA,
-  x = 0.75, 
-  y = 9.5, 
+  x = 0.5, 
+  y = 9.0625, 
   width = 4.0, 
@@
   default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D50_I_SCARB2, 
-          at = c(0, scale.SCARB2.max),
-          fontsize = 6)
 
@@
   default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D50_II_SCARB2, 
-          at = c(0, scale.SCARB2.max),
-          fontsize = 6)
 
@@
           fontsize = 6)
+
+plotText(label = "mDAN D50", 
+         fontsize = 6, 
+         fontcolor = "#E9967A",
+         fontfamily = "Helvetica",
+         x = 0.25, 
+         y = 9.125, 
+         just = c("left", "top"),
+         default.units = "inches",
+         fontface = "bold")
 
@@
   fill = "black",
-  x = 0.75,
-  y = 9.875,
+  x = 0.5,
+  y = 9.5,
   width = 4.0,
@@
 
-# Add the samples name
-plotText(label = "smNPC", 
-         fontsize = 6, 
-         fontcolor = "#A9A9A9",
-         x = 0.75, 
-         y = 8.375, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-plotText(label = "mDAN D15", 
-         fontsize = 6, 
-         fontcolor = "#B22222",
-         x = 0.75, 
-         y = 8.75, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-plotText(label = "mDAN D30", 
-         fontsize = 6, 
-         fontcolor = "#DC143C",
-         x = 0.75, 
-         y = 9.125, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-plotText(label = "mDAN D50", 
-         fontsize = 6, 
-         fontcolor = "#E9967A",
-         x = 0.75, 
-         y = 9.5, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# text F
-plotText(label = "F", 
+# Add the SNP position that zoom in the TFBS
+SNP_param_SCARB2 = pgParams(chrom = "chr4",
+                     chromstart = 76213717,
+                     chromend = 76213717,
+                     assembly = "hg38")
+
+annoHighlight(plot = ATAC_smNPC_I_SCARB2, 
+              params = SNP_param_SCARB2,
+              fill = "#404788FF",
+              y = 8.25, 
+              height = 1.75, 
+              just = c("left", "top"), 
+              default.units = "inches")
+
+annoZoomLines(plot = ATAC_smNPC_I_SCARB2, 
+              params = SNP_param_SCARB2,
+              y0 = 10.0, 
+              x1 = c(2.25, 2.75), 
+              y1 = 10.125, 
+              default.units = "inches")
+
+# text G
+plotText(label = "G", 
          fontsize = 12,
-         x = 5.0, 
-         y = 8.0, 
+         fontfamily = "Helvetica",
+         x = 4.75, 
+         y = 7.75, 
          just = "left", 
@@
 plotGG(plot = SCARB2.NR2C2.exp, 
-       x = 5.25, 
-       y = 7.875, 
+       x = 5.0, 
+       y = 8.0, 
        width = 3, 
@@
 plotGG(plot = NR2C2_TFBS, 
-       x = 1.6875, 
-       y = 10.375, 
+       x = 1.5975, 
+       y = 10.0, 
        width = 1.5, 
@@
 
+pageGuideHide()
 dev.off()
@@
 ##############################
-# Save as a PDF and as TIF
-pdf("/home/vagrant/Manuscript_1/FIGURE3/FIGURE3.pdf",
-    paper = "a4",
-    family = "Helvetica")
-
-# Save as TIFF, 300 dpi
 tiff("/home/vagrant/Manuscript_1/FIGURE3/FIGURE3.tiff",
@@
        y = 2.25, 
-       width = 2, 
+       width = 3.5, 
        height = 4.25,
@@
 # Plot for IDUA
-GLUC_IDUA = ggbarplot(Gluc_signal_ratio %>% 
-                        dplyr::filter(Sample %in% c("IDUA-WT",
-                                                    "IDUA-MUT",
-                                                    "miniCMV",
-                                                    "Neg_CTRL")), 
-                      x = "Sample", 
-                      y = "value",
-          width = 0.25,
-          add = c("mean_se", 
-                  "jitter"),
-          fill = "grey",
-          xlab = "",
-          ylab = "Ratio Gluc/SEAP",
-          position = position_dodge(0.9)) +
-  theme(legend.position = "none",
-        axis.text.x = element_text(angle = 90, hjust = 1.0, size = 9, face = "bold"),
-        axis.text.y = element_text(size = 9, face = "bold"),
-        axis.title.y = element_text(size = 10, face = "bold")) +
-  scale_x_discrete(labels = c("IDUA other allele",
-                              "IDUA effect allele",
-                              "Positive control",
-                              "Negative control")) +
-  scale_y_continuous(expand = c(0, 0),
-                     limits = c(0, 6.0)) +
-  stat_pvalue_manual(GLUC_stat %>% 
-                       dplyr::filter(group1 == "IDUA-WT",
-                              group2 == "IDUA-MUT"),
-                     label = "p = {p.format}",
-                     y.position = 4.0,
-                     size = 3.0)
-
-# Place the plot
-plotGG(plot = GLUC_IDUA, 
-       x = 3.0, 
-       y = 2.25, 
-       width = 2, 
-       height = 4.25,
-       just = c("left", "top"), 
-       default.units = "inches")
+# GLUC_IDUA = ggbarplot(Gluc_signal_ratio %>% 
+#                         dplyr::filter(Sample %in% c("IDUA-WT",
+#                                                     "IDUA-MUT",
+#                                                     "miniCMV",
+#                                                     "Neg_CTRL")), 
+#                       x = "Sample", 
+#                       y = "value",
+#           width = 0.25,
+#           add = c("mean_se", 
+#                   "jitter"),
+#           fill = "grey",
+#           xlab = "",
+#           ylab = "Ratio Gluc/SEAP",
+#           position = position_dodge(0.9)) +
+#   theme(legend.position = "none",
+#         axis.text.x = element_text(angle = 90, hjust = 1.0, size = 9, face = "bold"),
+#         axis.text.y = element_text(size = 9, face = "bold"),
+#         axis.title.y = element_text(size = 10, face = "bold")) +
+#   scale_x_discrete(labels = c("IDUA other allele",
+#                               "IDUA effect allele",
+#                               "Positive control",
+#                               "Negative control")) +
+#   scale_y_continuous(expand = c(0, 0),
+#                      limits = c(0, 6.0)) +
+#   stat_pvalue_manual(GLUC_stat %>% 
+#                        dplyr::filter(group1 == "IDUA-WT",
+#                               group2 == "IDUA-MUT"),
+#                      label = "p = {p.format}",
+#                      y.position = 4.0,
+#                      size = 3.0)
+# 
+# # Place the plot
+# plotGG(plot = GLUC_IDUA, 
+#        x = 3.0, 
+#        y = 2.25, 
+#        width = 2, 
+#        height = 4.25,
+#        just = c("left", "top"), 
+#        default.units = "inches")
 
@@
 plotGG(plot = GLUC_SCARB2, 
-       x = 5.5, 
+       x = 4.5, 
        y = 2.25, 
-       width = 2, 
+       width = 3.5, 
        height = 4.25,
@@
        y = 7.0, 
-       width = 1.75, 
+       width = 2.0, 
        height = 4.25,
@@
 # Knockdown of ZBTB14 and quantification of ZBTB14 and IDUA expression 3 days post transduction
-KD.IDUA.ZBTB14.3days = tibble(Sple = rep("shZBTB14", 6),
-                            Gene = c(rep("ZBTB14", 3),
-                                     rep("IDUA", 3)),
-                            Exp = c(0.334134302,
-                                    0.316834205,
-                                    0.294206291,
-                                    0.663813558,
-                                    1.259979272,
-                                    1.774054093))
-
-# Stats
-KD.IDUA.ZBTB14.3days.stats = tibble(Sple = c(rep("shZBTB14", 6),
-                                           rep("shCTRL", 6)),
-                                  Gene = rep(c(rep("ZBTB14", 3),
-                                           rep("IDUA", 3)), 2),
-                                  Exp = c(11.39125,
-                                          10.4813,
-                                          10.5062,
-                                          11.56275,
-                                          10.1455,
-                                          9.76485,
-                                          9.80975,
-                                          8.8231,
-                                          8.7411,
-                                          10.9716,
-                                          10.4789,
-                                          10.5919))
-
-stat_ZBTB14.KD = compare_means(Exp ~ Sple,
-                          data = KD.IDUA.ZBTB14.3days.stats,
-                          group.by = "Gene",
-                          method = "t.test",
-                          paired = TRUE)
-
-# Plot
-pl.KD_IDUA_ZBTB14 = KD.IDUA.ZBTB14.3days %>% 
-  mutate(Gene = factor(Gene, levels = c("ZBTB14", "IDUA"))) %>% 
-  ggbarplot(.,
-            x = "Gene",
-            y = "Exp",
-            fill = c("Gene"),
-            position = position_dodge(0.9),
-            palette = c("#440154FF", "#287C8EFF"),
-            add = c("mean_se", "jitter"),
-            xlab = "",
-            ylab = "Relative expression to shSCRAMBLE",
-            title = "shZBTB14 - 3 days") +
-  geom_hline(yintercept = 1.0, lty = "dashed", color = "black") +
-  theme(axis.title.y = element_text(face = "bold", size = 10),
-        axis.text.x = element_text(face = "bold.italic", size = 10, angle = 90, family = "Helvetica"),
-        axis.text.y = element_text(face = "bold", size = 10),
-        legend.position = "none",
-        plot.title = element_text(face = "bold", size = 10, hjust = 0.5)) +
-  scale_y_continuous(expand = c(0, 0),
-                     limits = c(0, 1.8)) +
-  stat_pvalue_manual(stat_ZBTB14.KD,
-                     label = "p = {p.format}",
-                     x = "Gene",
-                     y.position = 0.5,
-                     size = 3.0,
-                     hide.ns = TRUE)
-
-plotGG(plot = pl.KD_IDUA_ZBTB14, 
-       x = 2.375, 
-       y = 7.0, 
-       width = 1.75, 
-       height = 4.25,
-       just = c("left", "top"), 
-       default.units = "inches")
+# KD.IDUA.ZBTB14.3days = tibble(Sple = rep("shZBTB14", 6),
+#                             Gene = c(rep("ZBTB14", 3),
+#                                      rep("IDUA", 3)),
+#                             Exp = c(0.334134302,
+#                                     0.316834205,
+#                                     0.294206291,
+#                                     0.663813558,
+#                                     1.259979272,
+#                                     1.774054093))
+# 
+# # Stats
+# KD.IDUA.ZBTB14.3days.stats = tibble(Sple = c(rep("shZBTB14", 6),
+#                                            rep("shCTRL", 6)),
+#                                   Gene = rep(c(rep("ZBTB14", 3),
+#                                            rep("IDUA", 3)), 2),
+#                                   Exp = c(11.39125,
+#                                           10.4813,
+#                                           10.5062,
+#                                           11.56275,
+#                                           10.1455,
+#                                           9.76485,
+#                                           9.80975,
+#                                           8.8231,
+#                                           8.7411,
+#                                           10.9716,
+#                                           10.4789,
+#                                           10.5919))
+# 
+# stat_ZBTB14.KD = compare_means(Exp ~ Sple,
+#                           data = KD.IDUA.ZBTB14.3days.stats,
+#                           group.by = "Gene",
+#                           method = "t.test",
+#                           paired = TRUE)
+# 
+# # Plot
+# pl.KD_IDUA_ZBTB14 = KD.IDUA.ZBTB14.3days %>% 
+#   mutate(Gene = factor(Gene, levels = c("ZBTB14", "IDUA"))) %>% 
+#   ggbarplot(.,
+#             x = "Gene",
+#             y = "Exp",
+#             fill = c("Gene"),
+#             position = position_dodge(0.9),
+#             palette = c("#440154FF", "#287C8EFF"),
+#             add = c("mean_se", "jitter"),
+#             xlab = "",
+#             ylab = "Relative expression to shSCRAMBLE",
+#             title = "shZBTB14 - 3 days") +
+#   geom_hline(yintercept = 1.0, lty = "dashed", color = "black") +
+#   theme(axis.title.y = element_text(face = "bold", size = 10),
+#         axis.text.x = element_text(face = "bold.italic", size = 10, angle = 90, family = "Helvetica"),
+#         axis.text.y = element_text(face = "bold", size = 10),
+#         legend.position = "none",
+#         plot.title = element_text(face = "bold", size = 10, hjust = 0.5)) +
+#   scale_y_continuous(expand = c(0, 0),
+#                      limits = c(0, 1.9)) +
+#   stat_pvalue_manual(stat_ZBTB14.KD,
+#                      label = "p = {p.format}",
+#                      x = "Gene",
+#                      y.position = c(0.5, 1.6),
+#                      size = 3.0,
+#                      hide.ns = FALSE)
+# 
+# plotGG(plot = pl.KD_IDUA_ZBTB14, 
+#        x = 2.375, 
+#        y = 7.0, 
+#        width = 1.75, 
+#        height = 4.25,
+#        just = c("left", "top"), 
+#        default.units = "inches")
 
@@
                      x = "Gene",
-                     y.position = 1.5,
-                     size = 3.0)
+                     y.position = c(0.65, 1.5),
+                     size = 3.0,
+                     hide.ns = FALSE)
 
 plotGG(plot = pl.KD_SCARB2_NR2C2, 
-       x = 4.25, 
+       x = 3.0, 
        y = 7.0, 
-       width = 1.75, 
+       width = 2.0, 
        height = 4.25,
@@
                      x = "Gene",
-                     y.position = 1.5,
+                     y.position = c(0.85, 1.5),
                      size = 3.0,
-                     hide.ns = TRUE)
+                     hide.ns = FALSE)
 
 plotGG(plot = pl.KD_SCARB2_NR2C2_6days, 
-       x = 6.125, 
+       x = 5.5, 
        y = 7.0, 
-       width = 1.75, 
+       width = 2.0, 
        height = 4.25,
@@
 ### FIGURE 4
+Allelic imbalance at rs1465922 in ATACseq of differentiated TH REP1 cell line.  
+```{bash, eval = FALSE, echo = TRUE}
+# Copy the ATACseq BAM locally 
+rsync -avzPhu --no-p iris-cluster://work/projects/epifunc/merged_bam/ /Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE4/
+```
+
 ```{r fig4, eval = FALSE, echo = TRUE}
@@
 ##############################
-# Save as a PDF
-pdf("/home/vagrant/Manuscript_1/FIGURE4/FIGURE4.pdf",
-    width = 8.3, 
-    height = 11.7)
-
 # Save as TIFF, 300 dpi
@@
 
-#FIG 4A
-AI_RNA = tibble(Samples = 
-                  c("smNPCs", "Neurons positively sorted D15", "Neurons positively sorted D30",
-                    "Neurons positively sorted D50", "Astrocytes"),
-                A = c(5, 23, 77, 56, 30),
-                G = c(8, 4, 62, 34, 47)) %>% 
-  gather(-Samples, key = "Base", value = "Reads")
-
-AI_ATAC = tibble(Samples = 
-                  c("smNPCs", "mDAN D15", "mDAN D30",
-                    "mDAN D50", "Astrocytes"),
-                A = c(31, 195, 202, 118, 155),
-                G = c(39, 263, 264, 196, 179)) %>% 
-  gather(-Samples, key = "Base", value = "Reads")
-
-AI = AI_ATAC %>% 
-  bind_rows(AI_RNA) %>% 
-  mutate(Cond = rep(c("ATAC", "RNA"), each = 10))
-
-# Good looking plot
-chrom_AI = ggbarplot(AI_ATAC, x = "Samples", y = "Reads",
-          fill = "Base",
+# Chromatin imbalance values as calculated by the AllelicImbalance R package
+countList = readRDS("/home/vagrant/Manuscript_1/FIGURE4/SCARB2_het_counts_THREP1_ATACseq.rds")
+
+# Extract and reformat for positively sorted TH population
+AI_ATAC = countList$chr4_76213717 %>% 
+  as_tibble() %>% 
+  mutate(Sample = rownames(countList$chr4_76213717)) %>% 
+  pivot_longer(cols = c(A, C, G, T), names_to = "Base", values_to = "Reads") %>% 
+  mutate(Sample.n = case_when(str_detect(Sample, "astrocytes") ~ "Astrocytes",
+                              str_detect(Sample, "D15_neg") ~ "Negative DAN D15",
+                              str_detect(Sample, "D15_pos") ~ "mDAN D15",
+                              str_detect(Sample, "D30_pos") ~ "mDAN D30",
+                              str_detect(Sample, "D50_neg") ~ "Negative DAN D50",
+                              str_detect(Sample, "D50_pos") ~ "mDAN D50",
+                              TRUE ~ "smNPCs")) %>% 
+  dplyr::filter(!str_detect(Sample, "neg"),
+                Base %in% c("A", "G")) %>% 
+  mutate(Sample.n = factor(Sample.n,
+                           levels = c("smNPCs",
+                                      "mDAN D15",
+                                      "mDAN D30",
+                                      "mDAN D50",
+                                      "Astrocytes")),
+         Allele = case_when(Base == "A" ~ "PD allele",
+                            TRUE ~ "Other allele"))
+# Plot
+chrom_AI = ggbarplot(AI_ATAC,
+                     x = "Sample.n",
+                     y = "Reads",
+                     fill = "Allele",
                      position = position_dodge(0.7),
-          xlab = "", ylab = "Reads",
-          #title = "Allelic imbalance at chr4:76213717 - SNP in SCARB2 promoter",
-          label = c(0.3, 0.001, 0.004, 1e-5, 0.2,
-                    rep("", 5)),
+                     xlab = "",
+                     ylab = "Reads",
+                     label = format(c(paste0("p = ",
+                                        0.3),
+                          "",
+                          paste0("p = ",
+                                 0.3),
+                          "",
+                          paste0("p = ",
+                                 0.003),
+                          "",
+                          paste0("p = ",
+                                 0.0000003),
+                          "",
+                          paste0("p = ",
+                                 0.2),
+                          ""),
+                          scientific = TRUE),
                      label.pos = "out",
-          lab.size = 3) +
+                     lab.size = 3,
+                     lab.vjust = 0.5,
+                     lab.hjust = -0.5,
+                     orientation = "horiz") +
   theme(legend.position = "right",
@@
 ### SUPPLEMENTARY FIGURE 1
-IHEC consortium has one sample of substantia nigra for H3K27me3, H3K9me3, H3K4me1, H3K4me3 and H3K36me3 from a healthy brain for BAG3, IDUA and SCARB2 loci
+Plot genes of interest from the TH REP2 mCHERRY cell line RNAseq data to demonstrate that expression is similar.  
+In addition, do the same for FOUNDIN-PD.
 ```{r suppFig1, eval = FALSE, echo = TRUE}
@@
 ############################################
-
-# Save as a PDF
-pdf("/home/vagrant/Manuscript_1/SUPPLEMENTARY_FIGURE1/SUPPLEMENTARY_FIGURE1.pdf",
-    width = 8.3, 
-    height = 11.7)
+# Save as TIFF, 300 dpi
+tiff("/home/vagrant/Manuscript_1/SUPPLEMENTARY_FIGURE1/SUPPLEMENTARY_FIGURE1.tiff",
+     width = 8.27,
+     height = 9.0,
+     units = "in",
+     res = 300,
+     compression = "lzw")
 
 # Create a A4 blank page
-pageCreate(width = 8.3, 
-           height = 11.7, 
+pageCreate(width = 8.27, 
+           height = 9.0, 
            default.units = "inches",
@@
 
-# ChIP-seq signal BAG3
-# path where bigwig files are
-bw.IHEC.path = "/home/vagrant/Documents/IHEC/ChIP_Seq/BIGWIG/"
-
-# Reads BIGWIG file at BAG3 location - H3K4me1
-bw.BAG3.H3K4me1 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6a1889bf-7312-4e41-b1cc-e2f3be7a8076.fc.signal.bigwig"),
-                               chrom = "chr10",
-                               chromstart = 119611305,
-                               chromend = 119691505)
-
-# Reads BIGWIG file at BAG3 location - H3K4me3
-bw.BAG3.H3K4me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.4cb9300f-9097-4374-8f2a-4afd8ff855fb.fc.signal.bigwig"),
-                               chrom = "chr10",
-                               chromstart = 119611305,
-                               chromend = 119691505)
-
-# Reads BIGWIG file at BAG3 location - H3K36me3
-bw.BAG3.H3K36me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6586e624-852f-4cac-83df-2325cee19699.fc.signal.bigwig"),
-                               chrom = "chr10",
-                               chromstart = 119611305,
-                               chromend = 119691505)
-
-# Reads BIGWIG file at BAG3 location - H3K9me3
-bw.BAG3.H3K9me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.e8fe7664-906e-4d87-8f3a-6ce88dbeadc6.fc.signal.bigwig"),
-                               chrom = "chr10",
-                               chromstart = 119611305,
-                               chromend = 119691505)
-
-# Reads BIGWIG file at BAG3 location - H3K27me3
-bw.BAG3.H3K27me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.5f5024a9-2e3f-4527-82ec-0ed04bf4a848.fc.signal.bigwig"),
-                               chrom = "chr10",
-                               chromstart = 119611305,
-                               chromend = 119691505)
-
-# Add a scale next to the bigwig files - check the maximum to choose
-scale.IHEC.BAG3.max = max(c(bw.BAG3.H3K4me1$score,
-                              bw.BAG3.H3K4me3$score,
-                              bw.BAG3.H3K36me3$score,
-                              bw.BAG3.H3K9me3$score,
-                              bw.BAG3.H3K27me3$score)) %>% 
-  round(.,
-        digits = 1.0)
-
-print(scale.IHEC.BAG3.max)
-
-# Define parameters for the regions
-region.p.IHEC.BAG3 = pgParams(chrom = "chr10",
-                         chromstart = 119611405,
-                         chromend = 119691405,
-                         assembly = "hg38",
-                         range = c(0, scale.IHEC.BAG3.max))
-
-# Add the genomic label
-plotGenomeLabel(
-  chrom = "chr10",
-  chromstart = 119611405,
-  chromend = 119691405,
-  assembly = "hg38",
-  x = 0.75,
+# Load data
+dat.THREP2.FPKM = read_delim("/home/vagrant/epifunc/RNAseq/TH_REP2_mCHERRY/180604_HT-Rep2_fpkm.tsv",
+                      delim = "\t", 
+                      col_names = TRUE)
+
+# Filter for genes of interest - BAG3 and LHX1 - IDUA, ZBTB14, SLC26A1 - SCARB2, NR2C2, FAM47E
+BAG3.LHX1 = c("BAG3",
+              "LHX1")
+
+IDUA.ZBTB14 = c("IDUA",
+                "ZBTB14",
+                "SLC26A1")
+
+SCARB2.NR2C2 = c("SCARB2",
+                 "NR2C2",
+                 "FAM47E")
+
+# Reformat the matrix and take only positively sorted neurons
+dat.THREP2.FPKM = dat.THREP2.FPKM %>% 
+  pivot_longer(starts_with("TH"), 
+               names_to = "Samples",
+               values_to = "FPKM") %>% 
+  #dplyr::filter(str_detect(Samples, paste("SmNPC", "pos", sep = "|"))) %>% 
+  mutate(Cond = case_when(str_detect(Samples, "D15pos") ~ "Positively sorted neurons D15",
+                          str_detect(Samples, "D15neg") ~ "Negatively sorted neurons D15",
+                          str_detect(Samples, "D30pos") ~ "Positively sorted neurons D30",
+                          str_detect(Samples, "D30neg") ~ "Negatively sorted neurons D30",
+                          TRUE ~ "smNPCs"),
+         Cond = factor(Cond, 
+                       levels = c("smNPCs", 
+                                  "Negatively sorted neurons D15",
+                                  "Positively sorted neurons D15",
+                                  "Negatively sorted neurons D30",
+                                  "Positively sorted neurons D30")))
+
+# Plot the expression of BAG3 and LHX1 in smNPC and mDAN
+cdt = c("smNPCs",
+        "Positively")
+
+TH.REP2_BAG3.LHX1.exp = ggboxplot(dat.THREP2.FPKM %>% 
+                            dplyr::filter(gene_name %in% BAG3.LHX1,
+                                          str_detect(Cond, paste0(cdt, collapse = "|"))),
+                          x = "Cond", 
+                          y = "FPKM", 
+                          add = "jitter", 
+                          fill = "Cond", 
+                          palette = c("#A9A9A9", "#B22222", "#DC143C"),
+                          facet.by = "gene_name",
+                          xlab = "", 
+                          ylab = "Fragments Per Kilobase Million (FPKM)") +
+  scale_x_discrete(labels = c("smNPC",
+                              expression("mDAN D15"),
+                              expression("mDAN D30"))) +
+  theme(legend.position = "none",
+        axis.text.x = element_text(angle = 90))
+
+# Place the plot  
+plotGG(plot = TH.REP2_BAG3.LHX1.exp, 
+       x = 0.5, 
        y = 0.625, 
-  length = 4.0,
-  default.units = "inches",
-  scale = "Mb")
-
-# ChIPseq signal H3K4me1
-H3K4me1_BAG3 = plotSignal(
-  data = bw.BAG3.H3K4me1, 
-  params = region.p.IHEC.BAG3,
-  fill = "#b5de2b", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 0.875, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K4me1_BAG3, 
-          at = c(0, scale.IHEC.BAG3.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K4me3
-H3K4me3_BAG3 = plotSignal(
-  data = bw.BAG3.H3K4me3, 
-  params = region.p.IHEC.BAG3,
-  fill = "#35b779", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 1.25, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K4me3_BAG3, 
-          at = c(0, scale.IHEC.BAG3.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K36me3
-H3K36me3_BAG3 = plotSignal(
-  data = bw.BAG3.H3K36me3, 
-  params = region.p.IHEC.BAG3,
-  fill = "#26828e", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 1.625, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K36me3_BAG3, 
-          at = c(0, scale.IHEC.BAG3.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K9me3
-H3K9me3_BAG3 = plotSignal(
-  data = bw.BAG3.H3K9me3, 
-  params = region.p.IHEC.BAG3,
-  fill = "#3e4989", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 2.0, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K9me3_BAG3, 
-          at = c(0, scale.IHEC.BAG3.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K27me3
-H3K27me3_BAG3 = plotSignal(
-  data = bw.BAG3.H3K27me3, 
-  params = region.p.IHEC.BAG3,
-  fill = "#440154", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 2.375, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K27me3_BAG3, 
-          at = c(0, scale.IHEC.BAG3.max),
-          fontsize = 6)
-
-# Gene track
-plotGenes(
-  chrom = "chr10",
-  chromstart = 119611405,
-  chromend = 119691405,
-  assembly = assembly(Genome = "hg38refGene", 
-                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
-                      OrgDb = "org.Hs.eg.db"),
-  fontcolor = "black",
-  fill = "black",
-  x = 0.75,
-  y = 2.75,
-  width = 4.0,
-  height = 0.375,
-  just = c("left", "top"),
-  default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K4me1", 
-         fontsize = 6, 
-         fontcolor = "#b5de2b",
-         x = 0.75,
-         y = 0.875, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K4me3", 
-         fontsize = 6, 
-         fontcolor = "#35b779",
-         x = 0.75,
-         y = 1.25, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K36me3", 
-         fontsize = 6, 
-         fontcolor = "#26828e",
-         x = 0.75,
-         y = 1.625, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K9me3", 
-         fontsize = 6, 
-         fontcolor = "#3e4989",
-         x = 0.75,
-         y = 2.0, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K27me3", 
-         fontsize = 6, 
-         fontcolor = "#440154",
-         x = 0.75,
-         y = 2.375, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Reads BIGWIG file at IDUA location - H3K4me1
-bw.IDUA.H3K4me1 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6a1889bf-7312-4e41-b1cc-e2f3be7a8076.fc.signal.bigwig"),
-                               chrom = "chr4",
-                               chromstart = 947008,
-                               chromend = 1027208)
-
-# Reads BIGWIG file at IDUA location - H3K4me3
-bw.IDUA.H3K4me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.4cb9300f-9097-4374-8f2a-4afd8ff855fb.fc.signal.bigwig"),
-                               chrom = "chr4",
-                               chromstart = 947008,
-                               chromend = 1027208)
-
-# Reads BIGWIG file at IDUA location - H3K36me3
-bw.IDUA.H3K36me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6586e624-852f-4cac-83df-2325cee19699.fc.signal.bigwig"),
-                               chrom = "chr4",
-                               chromstart = 947008,
-                               chromend = 1027208)
-
-# Reads BIGWIG file at IDUA location - H3K9me3
-bw.IDUA.H3K9me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.e8fe7664-906e-4d87-8f3a-6ce88dbeadc6.fc.signal.bigwig"),
-                               chrom = "chr4",
-                               chromstart = 947008,
-                               chromend = 1027208)
-
-# Reads BIGWIG file at IDUA location - H3K27me3
-bw.IDUA.H3K27me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.5f5024a9-2e3f-4527-82ec-0ed04bf4a848.fc.signal.bigwig"),
-                               chrom = "chr4",
-                               chromstart = 947008,
-                               chromend = 1027208)
-
-# Add a scale next to the bigwig files - check the maximum to choose
-scale.IHEC.IDUA.max = max(c(bw.IDUA.H3K4me1$score,
-                              bw.IDUA.H3K4me3$score,
-                              bw.IDUA.H3K36me3$score,
-                              bw.IDUA.H3K9me3$score,
-                              bw.IDUA.H3K27me3$score)) %>% 
-  round(.,
-        digits = 1.0)
-
-print(scale.IHEC.IDUA.max)
-
-# Define parameters for the regions
-region.p.IHEC.IDUA = pgParams(chrom = "chr4",
-                         chromstart = 947108,
-                         chromend = 1027108,
-                         assembly = "hg38",
-                         range = c(0, scale.IHEC.IDUA.max))
-
-# Add the genomic label
-plotGenomeLabel(
-  chrom = "chr4",
-  chromstart = 947108,
-  chromend = 1027108,
-  assembly = "hg38",
-  x = 0.75,
-  y = 3.5,
-  length = 4.0,
-  default.units = "inches",
-  scale = "Mb")
-
-# ChIPseq signal H3K4me1
-H3K4me1_IDUA = plotSignal(
-  data = bw.IDUA.H3K4me1, 
-  params = region.p.IHEC.IDUA,
-  fill = "#b5de2b", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 3.75, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K4me1_IDUA, 
-          at = c(0, scale.IHEC.IDUA.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K4me3
-H3K4me3_IDUA = plotSignal(
-  data = bw.IDUA.H3K4me3, 
-  params = region.p.IHEC.IDUA,
-  fill = "#35b779", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 4.125, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K4me3_IDUA, 
-          at = c(0, scale.IHEC.IDUA.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K36me3
-H3K36me3_IDUA = plotSignal(
-  data = bw.IDUA.H3K36me3, 
-  params = region.p.IHEC.IDUA,
-  fill = "#26828e", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 4.5, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K36me3_IDUA, 
-          at = c(0, scale.IHEC.IDUA.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K9me3
-H3K9me3_IDUA = plotSignal(
-  data = bw.IDUA.H3K9me3, 
-  params = region.p.IHEC.IDUA,
-  fill = "#3e4989", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 4.875, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K9me3_IDUA, 
-          at = c(0, scale.IHEC.IDUA.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K27me3
-H3K27me3_IDUA = plotSignal(
-  data = bw.IDUA.H3K27me3, 
-  params = region.p.IHEC.IDUA,
-  fill = "#440154", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 5.25, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K27me3_IDUA, 
-          at = c(0, scale.IHEC.IDUA.max),
-          fontsize = 6)
-
-# Gene track
-plotGenes(
-  chrom = "chr4",
-  chromstart = 947108,
-  chromend = 1027108,
-  assembly = assembly(Genome = "hg38refGene", 
-                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
-                      OrgDb = "org.Hs.eg.db"),
-  fontcolor = "black",
-  fill = "black",
-  x = 0.75,
-  y = 5.625,
-  width = 4.0,
-  height = 0.375,
-  just = c("left", "top"),
-  default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K4me1", 
-         fontsize = 6, 
-         fontcolor = "#b5de2b",
-         x = 0.75,
-         y = 3.75, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K4me3", 
-         fontsize = 6, 
-         fontcolor = "#35b779",
-         x = 0.75,
-         y = 4.125, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K36me3", 
-         fontsize = 6, 
-         fontcolor = "#26828e",
-         x = 0.75,
-         y = 4.5, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K9me3", 
-         fontsize = 6, 
-         fontcolor = "#3e4989",
-         x = 0.75,
-         y = 4.875, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K27me3", 
-         fontsize = 6, 
-         fontcolor = "#440154",
-         x = 0.75,
-         y = 5.25, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# ChIP-seq signal SCARB2
-# Reads BIGWIG file at SCARB2 location - H3K4me1
-bw.SCARB2.H3K4me1 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6a1889bf-7312-4e41-b1cc-e2f3be7a8076.fc.signal.bigwig"),
-                               chrom = "chr4",
-                               chromstart = 76173617,
-                               chromend = 76253817)
-
-# Reads BIGWIG file at SCARB2 location - H3K4me3
-bw.SCARB2.H3K4me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.4cb9300f-9097-4374-8f2a-4afd8ff855fb.fc.signal.bigwig"),
-                               chrom = "chr4",
-                               chromstart = 76173617,
-                               chromend = 76253817)
-
-# Reads BIGWIG file at SCARB2 location - H3K36me3
-bw.SCARB2.H3K36me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6586e624-852f-4cac-83df-2325cee19699.fc.signal.bigwig"),
-                               chrom = "chr4",
-                               chromstart = 76173617,
-                               chromend = 76253817)
-
-# Reads BIGWIG file at SCARB2 location - H3K9me3
-bw.SCARB2.H3K9me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.e8fe7664-906e-4d87-8f3a-6ce88dbeadc6.fc.signal.bigwig"),
-                               chrom = "chr4",
-                               chromstart = 76173617,
-                               chromend = 76253817)
-
-# Reads BIGWIG file at SCARB2 location - H3K27me3
-bw.SCARB2.H3K27me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.5f5024a9-2e3f-4527-82ec-0ed04bf4a848.fc.signal.bigwig"),
-                               chrom = "chr4",
-                               chromstart = 76173617,
-                               chromend = 76253817)
-
-# Add a scale next to the bigwig files - check the maximum to choose
-scale.IHEC.SCARB2.max = max(c(bw.SCARB2.H3K4me1$score,
-                              bw.SCARB2.H3K4me3$score,
-                              bw.SCARB2.H3K36me3$score,
-                              bw.SCARB2.H3K9me3$score,
-                              bw.SCARB2.H3K27me3$score)) %>% 
-  round(.,
-        digits = 1.0)
-
-print(scale.IHEC.SCARB2.max)
-
-# Define parameters for the regions
-region.p.IHEC.SCARB2 = pgParams(chrom = "chr4",
-                         chromstart = 76173717,
-                         chromend = 76253717,
-                         assembly = "hg38",
-                         range = c(0, scale.IHEC.SCARB2.max))
-
-# Add the genomic label
-plotGenomeLabel(
-  chrom = "chr4",
-  chromstart = 76173717,
-  chromend = 76253717,
-  assembly = "hg38",
-  x = 0.75,
-  y = 6.5,
-  length = 4.0,
-  default.units = "inches",
-  scale = "Mb")
-
-# ChIPseq signal H3K4me1
-H3K4me1_SCARB2 = plotSignal(
-  data = bw.SCARB2.H3K4me1, 
-  params = region.p.IHEC.SCARB2,
-  fill = "#b5de2b", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 6.75, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K4me1_SCARB2, 
-          at = c(0, scale.IHEC.SCARB2.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K4me3
-H3K4me3_SCARB2 = plotSignal(
-  data = bw.SCARB2.H3K4me3, 
-  params = region.p.IHEC.SCARB2,
-  fill = "#35b779", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 7.125, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K4me3_SCARB2, 
-          at = c(0, scale.IHEC.SCARB2.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K36me3
-H3K36me3_SCARB2 = plotSignal(
-  data = bw.SCARB2.H3K36me3, 
-  params = region.p.IHEC.SCARB2,
-  fill = "#26828e", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 7.5, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K36me3_SCARB2, 
-          at = c(0, scale.IHEC.SCARB2.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K9me3
-H3K9me3_SCARB2 = plotSignal(
-  data = bw.SCARB2.H3K9me3, 
-  params = region.p.IHEC.SCARB2,
-  fill = "#3e4989", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 7.875, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K9me3_SCARB2, 
-          at = c(0, scale.IHEC.SCARB2.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K27me3
-H3K27me3_SCARB2 = plotSignal(
-  data = bw.SCARB2.H3K27me3, 
-  params = region.p.IHEC.SCARB2,
-  fill = "#440154", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 8.25, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K27me3_SCARB2, 
-          at = c(0, scale.IHEC.SCARB2.max),
-          fontsize = 6)
-
-# Gene track
-plotGenes(
-  chrom = "chr4",
-  chromstart = 76173717,
-  chromend = 76253717,
-  assembly = assembly(Genome = "hg38refGene", 
-                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
-                      OrgDb = "org.Hs.eg.db"),
-  fontcolor = "black",
-  fill = "black",
-  x = 0.75,
-  y = 8.625,
-  width = 4.0,
-  height = 0.375,
-  just = c("left", "top"),
-  default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K4me1", 
-         fontsize = 6, 
-         fontcolor = "#b5de2b",
-         x = 0.75,
-         y = 6.75, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K4me3", 
-         fontsize = 6, 
-         fontcolor = "#35b779",
-         x = 0.75,
-         y = 7.125, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K36me3", 
-         fontsize = 6, 
-         fontcolor = "#26828e",
-         x = 0.75,
-         y = 7.5, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K9me3", 
-         fontsize = 6, 
-         fontcolor = "#3e4989",
-         x = 0.75,
-         y = 7.875, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K27me3", 
-         fontsize = 6, 
-         fontcolor = "#440154",
-         x = 0.75,
-         y = 8.25, 
+       width = 3.5, 
+       height = 3.5,
+       just = c("left", "top"), 
+       default.units = "inches")
+
+# Plot the expression of IDUA and ZBTB14
+# TH.REP2_IDUA.ZBTB14.exp = ggboxplot(dat.THREP2.FPKM %>% 
+#                             dplyr::filter(gene_name %in% IDUA.ZBTB14) %>% 
+#                               mutate(gene_name = factor(gene_name,
+#                                                         levels = c("IDUA", "ZBTB14", "SLC26A1"))),
+#                           x = "Cond", 
+#                           y = "FPKM", 
+#                           add = "jitter", 
+#                           fill = "Cond", 
+#                           palette = c("#A9A9A9", "#B22222", "#DC143C"),
+#                           facet.by = "gene_name",
+#                           xlab = "", 
+#                           ylab = "Fragments Per Kilobase Million (FPKM)") +
+#   scale_x_discrete(labels = c("smNPC",
+#                               expression("mDAN D15"),
+#                               expression("mDAN D30"))) +
+#   theme(legend.position = "none",
+#         axis.text.x = element_text(angle = 90))
+# 
+# # Place the plot  
+# plotGG(plot = TH.REP2_IDUA.ZBTB14.exp, 
+#        x = 2.75, 
+#        y = 0.625, 
+#        width = 2.5, 
+#        height = 3.5,
+#        just = c("left", "top"), 
+#        default.units = "inches")
+
+# Plot the expression of SCARB2 and NR2C2
+TH.REP2_SCARB2.NR2C2.exp = ggboxplot(dat.THREP2.FPKM %>% 
+                            dplyr::filter(gene_name %in% SCARB2.NR2C2,
+                                          str_detect(Cond, paste0(cdt, collapse = "|"))) %>% 
+                              mutate(gene_name = factor(gene_name,
+                                                        levels = c("SCARB2", "NR2C2", "FAM47E"))),
+                          x = "Cond", 
+                          y = "FPKM", 
+                          add = "jitter", 
+                          fill = "Cond", 
+                          palette = c("#A9A9A9", "#B22222", "#DC143C"),
+                          facet.by = "gene_name",
+                          xlab = "", 
+                          ylab = "Fragments Per Kilobase Million (FPKM)") +
+  scale_x_discrete(labels = c("smNPC",
+                              expression("mDAN D15"),
+                              expression("mDAN D30"))) +
+  theme(legend.position = "none",
+        axis.text.x = element_text(angle = 90))
+
+# Place the plot  
+plotGG(plot = TH.REP2_SCARB2.NR2C2.exp, 
+       x = 4.5, 
+       y = 0.625, 
+       width = 3.5, 
+       height = 3.5,
        just = c("left", "top"), 
@@
 #### PANEL B - 
-# text Supplementary Figure 1
 # text B
@@
          x = 0.25, 
-         y = 8.5, 
+         y = 4.5, 
          just = "left", 
@@
 
-# Load IHEC RNA-seq data (TPM)
-IHEC.exp = read_delim("/home/vagrant/Documents/IHEC/RNA_seq/genes_tpm.csv",
-                      delim = ",",
+# FOUNDIN-PD data
+# Load
+FIPD = read_delim("/home/vagrant/epifunc/PPMI_data/FOUNDIN-PD_150.9_RNAB/aggregated_expression/cpmTable.tsv",
+                  delim = "\t",
                   col_names = TRUE)
 
-# Genes of interest to be plotted
-goi_ens.filt = goi_ens %>% 
+# Filter for genes of interest and get the ensembl and gene names
+goi_ens = AnnotationDbi::select(org.Hs.eg.db, 
+                 keys = c("BAG3",
+                          "LHX1",
+                          #"IDUA",
+                          #"ZBTB14",
+                          #"SLC26A1"
+                          "SCARB2",
+                          "NR2C2",
+                          "FAM47E"), 
+                 columns = c("SYMBOL",
+                             "ENSEMBL"), 
+                 keytype = "SYMBOL")
+
+# 2 LHX1 ensembl IDs came back. Check on the Ensembl website which one is correct
+goi_ens = goi_ens %>% 
   as_tibble() %>% 
-  dplyr::filter(ENSEMBL != "ENSG00000274577")
-
-IHEC.exp %>% 
-  # Remove the dot and number in Ensembl IDS
-  mutate(id_col = gsub("\\..*", 
-                       "", 
-                       id_col)) %>% 
-  dplyr:::filter(id_col %in% goi_ens.filt$ENSEMBL) %>% 
-  pivot_longer(cols = starts_with("IHEC"),
-               names_to = "Sample",
-               values_to = "TPM") %>% 
-  mutate(Sample = gsub("",
-                       "",
-                       Sample))
-
+  dplyr::filter(!ENSEMBL %in% c("ENSG00000274577",
+                                "ENSG00000262446")) %>% 
+  dplyr::rename(ENSEMBL.not.dot = ENSEMBL)
+
+# Filter the matrix of expression for my genes of interest
+FIPD.fin = FIPD %>% 
+  dplyr::filter(str_detect(Geneid, paste(goi_ens$ENSEMBL.not.dot, collapse = "|"))) %>% 
+  dplyr::rename(ENSEMBL = Geneid) %>% 
+  mutate(ENSEMBL.not.dot = gsub("\\..*", "", ENSEMBL)) %>% 
+  dplyr::select(ENSEMBL, ENSEMBL.not.dot, everything()) %>% 
+  pivot_longer(cols = starts_with("RNAB"), names_to = "Samples", values_to = "CPM") %>% 
+  mutate(Day = str_extract(Samples, "da+\\d+")) %>% 
+  left_join(goi_ens, 
+            by = "ENSEMBL.not.dot") %>% 
+  dplyr::select(SYMBOL, Day, CPM)
+
+# Anova
+# BAG3.aov = FIPD.fin %>% 
+#   dplyr::filter(SYMBOL %in% BAG3.LHX1) %>% 
+#   group_by(SYMBOL) %>% 
+#   anova_test(CPM ~ Day)
+
+# Tukey post-hoc test
+# BAG3.ph = FIPD.fin %>% 
+#   dplyr::filter(SYMBOL %in% BAG3.LHX1) %>% 
+#   group_by(SYMBOL) %>% 
+#   tukey_hsd(CPM ~ Day) %>% 
+#   add_xy_position(x = "Day")
+
+# Plot expression of BAG3 and LHX1
+FIPD.exp_BAG3.LHX1 = ggboxplot(FIPD.fin %>% 
+                          dplyr::filter(SYMBOL %in% BAG3.LHX1),
+                     x = "Day", 
+                     y = "CPM", 
+                     add = "jitter", 
+                     fill = "Day", 
+                     palette = c("#482677FF", "#2D708EFF", "#29AF7FFF"),
+                     facet.by = "SYMBOL",
+                     xlab = "", 
+                     ylab = "Counts per Million (CPM)",
+                     add.params = list(size = 0.1)) +
+  scale_x_discrete(labels = c("Day 0",
+                              "Day 25",
+                              "Day 65")) +
+  theme(legend.position = "none",
+        axis.text.x = element_text(angle = 90))
+  # stat_pvalue_manual(BAG3.ph, 
+  #                    hide.ns = TRUE,
+  #                    label = "p.adj") +
+  # labs(subtitle = get_test_label(BAG3.aov, 
+  #                                detailed = FALSE))
+
+# Place the plot  
+plotGG(plot = FIPD.exp_BAG3.LHX1, 
+       x = 0.5, 
+       y = 4.75 ,
+       width = 3.5, 
+       height = 3.5,
+       just = c("left", "top"), 
+       default.units = "inches")
+
+# Plot expression of IDUA and ZBTB14
+# FIPD.exp_IDUA.ZBTB14 = ggboxplot(FIPD.fin %>% 
+#                                    dplyr::filter(SYMBOL %in% IDUA.ZBTB14) %>% 
+#                             mutate(SYMBOL = factor(SYMBOL, levels = c("IDUA", "ZBTB14", "SLC26A1"))),
+#                      x = "Day", 
+#                      y = "CPM", 
+#                      add = "jitter", 
+#                      fill = "Day", 
+#                      palette = c("#482677FF", "#2D708EFF", "#29AF7FFF"),
+#                      facet.by = "SYMBOL",
+#                      xlab = "", 
+#                      ylab = "Counts per Million (CPM)",
+#                      add.params = list(size = 0.1)) +
+#   scale_x_discrete(labels = c("Day 0",
+#                               "Day 25",
+#                               "Day 65")) +
+#   theme(legend.position = "none",
+#         axis.text.x = element_text(angle = 90))
+  # stat_pvalue_manual(IDUA.ph, 
+  #                    hide.ns = TRUE,
+  #                    label = "p.adj") +
+  # labs(subtitle = get_test_label(IDUA.aov, 
+  #                                detailed = FALSE))
+
+# Place the plot  
+# plotGG(plot = FIPD.exp_IDUA.ZBTB14, 
+#        x = 3.125, 
+#        y = 4.75 ,
+#        width = 2.5, 
+#        height = 3.5,
+#        just = c("left", "top"), 
+#        default.units = "inches")
+
+# Plot expression of SCARB2 alone
+FIPD.exp_SCARB2 = ggboxplot(FIPD.fin %>% 
+                                   dplyr::filter(SYMBOL %in% "SCARB2"),
+                     x = "Day", 
+                     y = "CPM", 
+                     add = "jitter", 
+                     fill = "Day", 
+                     palette = c("#482677FF", "#2D708EFF", "#29AF7FFF"),
+                     facet.by = "SYMBOL",
+                     xlab = "", 
+                     ylab = "Counts per Million (CPM)",
+                     add.params = list(size = 0.1)) +
+  scale_x_discrete(labels = c("Day 0",
+                              "Day 25",
+                              "Day 65")) +
+  theme(legend.position = "none",
+        axis.text.x = element_text(angle = 90))
+  # stat_pvalue_manual(SCARB2.ph, 
+  #                    hide.ns = TRUE,
+  #                    label = "p.adj") +
+  # labs(subtitle = get_test_label(SCARB2.aov, 
+  #                                detailed = FALSE))
+
+# Place the plot  
+plotGG(plot = FIPD.exp_SCARB2, 
+       x = 4.25, 
+       y = 4.75 ,
+       width = 1.5, 
+       height = 3.5,
+       just = c("left", "top"), 
+       default.units = "inches")
+
+# Plot expression of NR2C2 and FAM47E
+FIPD.exp_NR2C2.FAM47E = ggboxplot(FIPD.fin %>% 
+                                   dplyr::filter(SYMBOL %in% c("NR2C2", "FAM47E")) %>% 
+                            mutate(SYMBOL = factor(SYMBOL, levels = c("NR2C2", "FAM47E"))),
+                     x = "Day", 
+                     y = "CPM", 
+                     add = "jitter", 
+                     fill = "Day", 
+                     palette = c("#482677FF", "#2D708EFF", "#29AF7FFF"),
+                     facet.by = "SYMBOL",
+                     xlab = "", 
+                     ylab = "Counts per Million (CPM)",
+                     add.params = list(size = 0.1)) +
+  scale_x_discrete(labels = c("Day 0",
+                              "Day 25",
+                              "Day 65")) +
+  theme(legend.position = "none",
+        axis.text.x = element_text(angle = 90))
+
+# Place the plot  
+plotGG(plot = FIPD.exp_NR2C2.FAM47E, 
+       x = 6.0, 
+       y = 4.75 ,
+       width = 2.0, 
+       height = 3.5,
+       just = c("left", "top"), 
+       default.units = "inches")
+
+pageGuideHide()
 dev.off()
@@
 ### SUPPLEMENTARY FIGURE 2
-Plot genes of interest from the TH REP2 mCHERRY cell line RNAseq data to demonstrate that expression is similar
+IHEC consortium has one sample of substantia nigra for H3K27me3, H3K9me3, H3K4me1, H3K4me3 and H3K36me3 from a healthy brain for BAG3, IDUA and SCARB2 loci
 ```{r suppFig2, eval = FALSE, echo = TRUE}
@@
 ############################################
-
-# Save as a PDF
-pdf("/home/vagrant/Manuscript_1/SUPPLEMENTARY_FIGURE2/SUPPLEMENTARY_FIGURE2.pdf",
-    width = 13, 
-    height = 15)
+# Save as TIFF, 300 dpi
+tiff("/home/vagrant/Manuscript_1/SUPPLEMENTARY_FIGURE2/SUPPLEMENTARY_FIGURE2.tiff",
+     width = 8.27,
+     height = 6.5,
+     units = "in",
+     res = 300,
+     compression = "lzw")
 
 # Create a A4 blank page
-pageCreate(width = 8.3, 
-           height = 11.7, 
+pageCreate(width = 8.27, 
+           height = 6.5, 
            default.units = "inches",
-           showGuides = FALSE)
+           showGuides = TRUE)
 
@@
 
-# Load data
-dat.THREP2.FPKM = read_delim("/home/vagrant/epifunc/RNAseq/TH_REP2_mCHERRY/180604_HT-Rep2_fpkm.tsv",
-                      delim = "\t", 
-                      col_names = TRUE)
-
-dat.THREP2.FPKM %>% 
-  dplyr::filter(gene_name == "SCARB2") %>% 
-  summary()
-
-# Filter for genes of interest - BAG3 and LHX1
-BAG3.LHX1 = c("BAG3",
-              "LHX1")
-
-IDUA.ZBTB14 = c("IDUA",
-                "ZBTB14",
-                "SLC26A1")
-
-SCARB2.NR2C2 = c("SCARB2",
-                 "NR2C2",
-                 "FAM47E")
-
-# Reformat the matrix and take only positively sorted neurons
-dat.THREP2.FPKM = dat.THREP2.FPKM %>% 
-  pivot_longer(starts_with("TH"), 
-               names_to = "Samples",
-               values_to = "FPKM") %>% 
-  dplyr::filter(str_detect(Samples, paste("SmNPC", "pos", sep = "|"))) %>% 
-  mutate(Cond = case_when(str_detect(Samples, "D15pos") ~ "Positively sorted neurons D15",
-                          str_detect(Samples, "D30pos") ~ "Positively sorted neurons D30",
-                          TRUE ~ "smNPCs"),
-         Cond = factor(Cond, 
-                       levels = c("smNPCs", 
-                                  "Positively sorted neurons D15",
-                                  "Positively sorted neurons D30")))
-
-# Plot the expression of BAG3 and LHX1
-TH.REP2_BAG3.LHX1.exp = ggboxplot(dat.THREP2.FPKM %>% 
-                            dplyr::filter(gene_name %in% BAG3.LHX1),
-                          x = "Cond", 
-                          y = "FPKM", 
-                          add = "jitter", 
-                          fill = "Cond", 
-                          palette = c("#A9A9A9", "#B22222", "#DC143C"),
-                          facet.by = "gene_name",
-                          xlab = "", 
-                          ylab = "Fragments Per Kilobase Million (FPKM)") +
-  scale_x_discrete(labels = c("smNPC",
-                              expression("mDAN D15"),
-                              expression("mDAN D30"))) +
-  theme(legend.position = "none",
-        axis.text.x = element_text(angle = 90))
-
-# Place the plot  
-plotGG(plot = TH.REP2_BAG3.LHX1.exp, 
-       x = 0.5, 
+# ChIP-seq signal BAG3
+# path where bigwig files are
+bw.IHEC.path = "/home/vagrant/Documents/IHEC/ChIP_Seq/BIGWIG/"
+
+# Reads BIGWIG file at BAG3 location - H3K4me1
+bw.BAG3.H3K4me1 = readBigwig(file = paste0(bw.IHEC.path,
+                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6a1889bf-7312-4e41-b1cc-e2f3be7a8076.fc.signal.bigwig"),
+                               chrom = "chr10",
+                               chromstart = 119611305,
+                               chromend = 119691505)
+
+# Reads BIGWIG file at BAG3 location - H3K4me3
+bw.BAG3.H3K4me3 = readBigwig(file = paste0(bw.IHEC.path,
+                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.4cb9300f-9097-4374-8f2a-4afd8ff855fb.fc.signal.bigwig"),
+                               chrom = "chr10",
+                               chromstart = 119611305,
+                               chromend = 119691505)
+
+# Reads BIGWIG file at BAG3 location - H3K36me3
+bw.BAG3.H3K36me3 = readBigwig(file = paste0(bw.IHEC.path,
+                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6586e624-852f-4cac-83df-2325cee19699.fc.signal.bigwig"),
+                               chrom = "chr10",
+                               chromstart = 119611305,
+                               chromend = 119691505)
+
+# Reads BIGWIG file at BAG3 location - H3K9me3
+bw.BAG3.H3K9me3 = readBigwig(file = paste0(bw.IHEC.path,
+                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.e8fe7664-906e-4d87-8f3a-6ce88dbeadc6.fc.signal.bigwig"),
+                               chrom = "chr10",
+                               chromstart = 119611305,
+                               chromend = 119691505)
+
+# Reads BIGWIG file at BAG3 location - H3K27me3
+bw.BAG3.H3K27me3 = readBigwig(file = paste0(bw.IHEC.path,
+                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.5f5024a9-2e3f-4527-82ec-0ed04bf4a848.fc.signal.bigwig"),
+                               chrom = "chr10",
+                               chromstart = 119611305,
+                               chromend = 119691505)
+
+# Add a scale next to the bigwig files - check the maximum to choose
+scale.IHEC.BAG3.max = max(c(bw.BAG3.H3K4me1$score,
+                              bw.BAG3.H3K4me3$score,
+                              bw.BAG3.H3K36me3$score,
+                              bw.BAG3.H3K9me3$score,
+                              bw.BAG3.H3K27me3$score)) %>% 
+  round(.,
+        digits = 1.0)
+
+print(scale.IHEC.BAG3.max)
+
+# Define parameters for the regions
+region.p.IHEC.BAG3 = pgParams(chrom = "chr10",
+                         chromstart = 119611405,
+                         chromend = 119691405,
+                         assembly = "hg38",
+                         range = c(0, scale.IHEC.BAG3.max))
+
+# Add the genomic label
+plotGenomeLabel(
+  chrom = "chr10",
+  chromstart = 119611405,
+  chromend = 119691405,
+  assembly = "hg38",
+  x = 0.75,
   y = 0.625,
-       width = 2, 
-       height = 3.5,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-# Plot the expression of IDUA and ZBTB14
-TH.REP2_IDUA.ZBTB14.exp = ggboxplot(dat.THREP2.FPKM %>% 
-                            dplyr::filter(gene_name %in% IDUA.ZBTB14) %>% 
-                              mutate(gene_name = factor(gene_name,
-                                                        levels = c("IDUA", "ZBTB14", "SLC26A1"))),
-                          x = "Cond", 
-                          y = "FPKM", 
-                          add = "jitter", 
-                          fill = "Cond", 
-                          palette = c("#A9A9A9", "#B22222", "#DC143C"),
-                          facet.by = "gene_name",
-                          xlab = "", 
-                          ylab = "Fragments Per Kilobase Million (FPKM)") +
-  scale_x_discrete(labels = c("smNPC",
-                              expression("mDAN D15"),
-                              expression("mDAN D30"))) +
-  theme(legend.position = "none",
-        axis.text.x = element_text(angle = 90))
-
-# Place the plot  
-plotGG(plot = TH.REP2_IDUA.ZBTB14.exp, 
-       x = 2.75, 
-       y = 0.625, 
-       width = 2.5, 
-       height = 3.5,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-# Plot the expression of SCARB2 and NR2C2
-TH.REP2_SCARB2.NR2C2.exp = ggboxplot(dat.THREP2.FPKM %>% 
-                            dplyr::filter(gene_name %in% SCARB2.NR2C2) %>% 
-                              mutate(gene_name = factor(gene_name,
-                                                        levels = c("SCARB2", "NR2C2", "FAM47E"))),
-                          x = "Cond", 
-                          y = "FPKM", 
-                          add = "jitter", 
-                          fill = "Cond", 
-                          palette = c("#A9A9A9", "#B22222", "#DC143C"),
-                          facet.by = "gene_name",
-                          xlab = "", 
-                          ylab = "Fragments Per Kilobase Million (FPKM)") +
-  scale_x_discrete(labels = c("smNPC",
-                              expression("mDAN D15"),
-                              expression("mDAN D30"))) +
-  theme(legend.position = "none",
-        axis.text.x = element_text(angle = 90))
-
-# Place the plot  
-plotGG(plot = TH.REP2_SCARB2.NR2C2.exp, 
-       x = 5.5, 
-       y = 0.625, 
-       width = 2.5, 
-       height = 3.5,
+  length = 4.0,
+  default.units = "inches",
+  scale = "Mb")
+
+# ChIPseq signal H3K4me1
+H3K4me1_BAG3 = plotSignal(
+  data = bw.BAG3.H3K4me1, 
+  params = region.p.IHEC.BAG3,
+  fill = "#b5de2b", 
+  alpha = 0.7, 
+  linecolor = NA,
+  x = 0.75, 
+  y = 0.875, 
+  width = 4.0, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+annoYaxis(plot = H3K4me1_BAG3, 
+          at = c(0, scale.IHEC.BAG3.max),
+          fontsize = 6)
+
+# ChIPseq signal H3K4me3
+H3K4me3_BAG3 = plotSignal(
+  data = bw.BAG3.H3K4me3, 
+  params = region.p.IHEC.BAG3,
+  fill = "#35b779", 
+  alpha = 0.7, 
+  linecolor = NA,
+  x = 0.75, 
+  y = 1.25, 
+  width = 4.0, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+annoYaxis(plot = H3K4me3_BAG3, 
+          at = c(0, scale.IHEC.BAG3.max),
+          fontsize = 6)
+
+# ChIPseq signal H3K36me3
+H3K36me3_BAG3 = plotSignal(
+  data = bw.BAG3.H3K36me3, 
+  params = region.p.IHEC.BAG3,
+  fill = "#26828e", 
+  alpha = 0.7, 
+  linecolor = NA,
+  x = 0.75, 
+  y = 1.625, 
+  width = 4.0, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+annoYaxis(plot = H3K36me3_BAG3, 
+          at = c(0, scale.IHEC.BAG3.max),
+          fontsize = 6)
+
+# ChIPseq signal H3K9me3
+H3K9me3_BAG3 = plotSignal(
+  data = bw.BAG3.H3K9me3, 
+  params = region.p.IHEC.BAG3,
+  fill = "#3e4989", 
+  alpha = 0.7, 
+  linecolor = NA,
+  x = 0.75, 
+  y = 2.0, 
+  width = 4.0, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+annoYaxis(plot = H3K9me3_BAG3, 
+          at = c(0, scale.IHEC.BAG3.max),
+          fontsize = 6)
+
+# ChIPseq signal H3K27me3
+H3K27me3_BAG3 = plotSignal(
+  data = bw.BAG3.H3K27me3, 
+  params = region.p.IHEC.BAG3,
+  fill = "#440154", 
+  alpha = 0.7, 
+  linecolor = NA,
+  x = 0.75, 
+  y = 2.375, 
+  width = 4.0, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+annoYaxis(plot = H3K27me3_BAG3, 
+          at = c(0, scale.IHEC.BAG3.max),
+          fontsize = 6)
+
+# Gene track
+plotGenes(
+  chrom = "chr10",
+  chromstart = 119611405,
+  chromend = 119691405,
+  assembly = assembly(Genome = "hg38refGene", 
+                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
+                      OrgDb = "org.Hs.eg.db"),
+  fontcolor = "black",
+  fill = "black",
+  x = 0.75,
+  y = 2.75,
+  width = 4.0,
+  height = 0.375,
+  just = c("left", "top"),
+  default.units = "inches")
+
+# Add the samples name
+plotText(label = "H3K4me1", 
+         fontsize = 6, 
+         fontcolor = "#b5de2b",
+         x = 0.75,
+         y = 0.875, 
+         just = c("left", "top"),
+         default.units = "inches")
+
+# Add the samples name
+plotText(label = "H3K4me3", 
+         fontsize = 6, 
+         fontcolor = "#35b779",
+         x = 0.75,
+         y = 1.25, 
+         just = c("left", "top"),
+         default.units = "inches")
+
+# Add the samples name
+plotText(label = "H3K36me3", 
+         fontsize = 6, 
+         fontcolor = "#26828e",
+         x = 0.75,
+         y = 1.625, 
+         just = c("left", "top"),
+         default.units = "inches")
+
+# Add the samples name
+plotText(label = "H3K9me3", 
+         fontsize = 6, 
+         fontcolor = "#3e4989",
+         x = 0.75,
+         y = 2.0, 
+         just = c("left", "top"),
+         default.units = "inches")
+
+# Add the samples name
+plotText(label = "H3K27me3", 
+         fontsize = 6, 
+         fontcolor = "#440154",
+         x = 0.75,
+         y = 2.375, 
          just = c("left", "top"),
@@
          x = 0.25, 
-         y = 4.5, 
+         y = 3.25, 
          just = "left", 
@@
 
-# FOUNDIN-PD data
-# Load
-FIPD = read_delim("/home/vagrant/epifunc/PPMI_data/FOUNDIN-PD_150.9_RNAB/aggregated_expression/cpmTable.tsv",
-                  delim = "\t",
-                  col_names = TRUE)
-
-#FIPD = read_delim("/home/vagrant/epifunc/PPMI_data/FOUNDIN-PD_150.9_RNAB/aggregated_expression/countTable.tsv",
-#                  delim = "\t",
-#                  col_names = TRUE)
-
-# Filter for genes of interest and get the ensembl and gene names
-goi_ens = select(org.Hs.eg.db, 
-                 keys = c("BAG3",
-                          "LHX1",
-                          "IDUA",
-                          "ZBTB14",
-                          "SLC26A1",
-                          "SCARB2",
-                          "NR2C2",
-                          "FAM47E"), 
-                 columns = c("SYMBOL",
-                             "ENSEMBL"), 
-                 keytype = "SYMBOL")
-
-# 2 LHX1 ensembl IDs came back. Check on the Ensembl website which one is correct
-goi_ens = goi_ens %>% 
-  as_tibble() %>% 
-  dplyr::filter(ENSEMBL != "ENSG00000274577") %>% 
-  dplyr::rename(ENSEMBL.not.dot = ENSEMBL)
-
-# Load the information abour iPSCs cell lines
-info_iPSCs = read_delim("/home/vagrant/epifunc/PPMI_data/Participant_Status_02Jun2023.csv",
-                  delim = ",",
-                  col_names = TRUE)
-
-info_iPSCs = info_iPSCs %>% 
-  mutate(PATNO = as.character(PATNO))
-
-# Filter the matrix of expression for my genes of interest
-FIPD.fin = FIPD %>% 
-  #mutate(Geneid = str_replace(Geneid, "\\..", "")) %>% 
-  dplyr::filter(str_detect(Geneid, paste(goi_ens$ENSEMBL.not.dot, collapse = "|"))) %>% 
-  dplyr::rename(ENSEMBL = Geneid) %>% 
-  mutate(ENSEMBL.not.dot = gsub("\\..*", "", ENSEMBL)) %>% 
-  dplyr::select(ENSEMBL, ENSEMBL.not.dot, everything()) %>% 
-  #left_join(goi_ens, by = "ENSEMBL") %>% 
-  pivot_longer(cols = starts_with("RNAB"), names_to = "Samples", values_to = "CPM") %>% 
-  mutate(PATNO = str_extract(Samples, "[^RNAB_PPMI_]+"),
-         Day = str_extract(Samples, "da+\\d+")) %>% 
-  left_join(info_iPSCs,
-            by = "PATNO") %>% 
-  left_join(goi_ens, 
-            by = "ENSEMBL.not.dot") %>% 
-  dplyr::select(ENSEMBL:Day, COHORT_DEFINITION, SYMBOL) %>% 
-  mutate(Condition = case_when(COHORT_DEFINITION == "Healthy Control" ~ "Healthy\ncontrol",
-                               COHORT_DEFINITION == "Parkinson's Disease" ~ "Parkinson's\ndisease",
-                               TRUE ~ COHORT_DEFINITION)) %>% 
-  #group_by(SYMBOL, Day, COHORT_DEFINITION) %>% 
-  group_by(ENSEMBL, Day) %>% 
-  mutate(AVG_CPM = mean(CPM, na.rm = TRUE))
-
-# Plot expression of all putative target genes and TFs except SCARB2 (will be plot alone)
-FIPD.exp.pl = ggboxplot(FIPD.fin %>% 
-                          dplyr::filter(SYMBOL != "SCARB2"),
-                     x = "Day", 
-                     y = "AVG_CPM", 
-                     add = "jitter", 
-                     fill = "Day", 
-                     palette = c("#482677FF", "#2D708EFF", "#29AF7FFF"),
-                     facet.by = "SYMBOL",
-                     xlab = "", 
-                     ylab = "CPM") +
-  scale_x_discrete(labels = c("Day 0",
-                              "Day 25",
-                              "Day 65")) +
-  theme(legend.position = "none",
-        axis.text.x = element_text(angle = 90),
-        strip.text.x = element_text(size = 6))
-
-# Place the plot  
-plotGG(plot = FIPD.exp.pl, 
-       x = 0.5, 
-       y = 4.75 ,
-       width = 6, 
-       height = 4.5,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-# Plot expression of SCARB2
-FIPD.exp.SCARB2.pl = ggboxplot(FIPD.fin %>% 
-                          dplyr::filter(SYMBOL == "SCARB2"),
-                     x = "Day", 
-                     y = "AVG_CPM", 
-                     add = "jitter", 
-                     fill = "Day", 
-                     palette = c("#482677FF", "#2D708EFF", "#29AF7FFF"),
-                     facet.by = "SYMBOL",
-                     xlab = "", 
-                     ylab = "CPM") +
-  scale_x_discrete(labels = c("Day 0",
-                              "Day 25",
-                              "Day 65")) +
-  theme(legend.position = "none",
-        axis.text.x = element_text(angle = 90),
-        strip.text.x = element_text(size = 6))
-
-# Place the plot  
-plotGG(plot = FIPD.exp.SCARB2.pl, 
-       x = 0.5, 
-       y = 9.75 ,
-       width = 6, 
-       height = 3.5,
-       just = c("left", "top"), 
-       default.units = "inches")
-
+# Reads BIGWIG file at SCARB2 location - H3K4me1
+bw.SCARB2.H3K4me1 = readBigwig(file = paste0(bw.IHEC.path,
+                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6a1889bf-7312-4e41-b1cc-e2f3be7a8076.fc.signal.bigwig"),
+                               chrom = "chr4",
+                               chromstart = 76173617,
+                               chromend = 76253817)
+
+# Reads BIGWIG file at SCARB2 location - H3K4me3
+bw.SCARB2.H3K4me3 = readBigwig(file = paste0(bw.IHEC.path,
+                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.4cb9300f-9097-4374-8f2a-4afd8ff855fb.fc.signal.bigwig"),
+                               chrom = "chr4",
+                               chromstart = 76173617,
+                               chromend = 76253817)
+
+# Reads BIGWIG file at SCARB2 location - H3K36me3
+bw.SCARB2.H3K36me3 = readBigwig(file = paste0(bw.IHEC.path,
+                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6586e624-852f-4cac-83df-2325cee19699.fc.signal.bigwig"),
+                               chrom = "chr4",
+                               chromstart = 76173617,
+                               chromend = 76253817)
+
+# Reads BIGWIG file at SCARB2 location - H3K9me3
+bw.SCARB2.H3K9me3 = readBigwig(file = paste0(bw.IHEC.path,
+                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.e8fe7664-906e-4d87-8f3a-6ce88dbeadc6.fc.signal.bigwig"),
+                               chrom = "chr4",
+                               chromstart = 76173617,
+                               chromend = 76253817)
+
+# Reads BIGWIG file at SCARB2 location - H3K27me3
+bw.SCARB2.H3K27me3 = readBigwig(file = paste0(bw.IHEC.path,
+                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.5f5024a9-2e3f-4527-82ec-0ed04bf4a848.fc.signal.bigwig"),
+                               chrom = "chr4",
+                               chromstart = 76173617,
+                               chromend = 76253817)
+
+# Add a scale next to the bigwig files - check the maximum to choose
+scale.IHEC.SCARB2.max = max(c(bw.SCARB2.H3K4me1$score,
+                              bw.SCARB2.H3K4me3$score,
+                              bw.SCARB2.H3K36me3$score,
+                              bw.SCARB2.H3K9me3$score,
+                              bw.SCARB2.H3K27me3$score)) %>% 
+  round(.,
+        digits = 1.0)
+
+print(scale.IHEC.SCARB2.max)
+
+# Define parameters for the regions
+region.p.IHEC.SCARB2 = pgParams(chrom = "chr4",
+                         chromstart = 76173717,
+                         chromend = 76253717,
+                         assembly = "hg38",
+                         range = c(0, scale.IHEC.SCARB2.max))
+
+# Add the genomic label
+plotGenomeLabel(
+  chrom = "chr4",
+  chromstart = 76173717,
+  chromend = 76253717,
+  assembly = "hg38",
+  x = 0.75,
+  y = 3.5,
+  length = 4.0,
+  default.units = "inches",
+  scale = "Mb")
+
+# ChIPseq signal H3K4me1
+H3K4me1_SCARB2 = plotSignal(
+  data = bw.SCARB2.H3K4me1, 
+  params = region.p.IHEC.SCARB2,
+  fill = "#b5de2b", 
+  alpha = 0.7, 
+  linecolor = NA,
+  x = 0.75, 
+  y = 3.75, 
+  width = 4.0, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+annoYaxis(plot = H3K4me1_SCARB2, 
+          at = c(0, scale.IHEC.SCARB2.max),
+          fontsize = 6)
+
+# ChIPseq signal H3K4me3
+H3K4me3_SCARB2 = plotSignal(
+  data = bw.SCARB2.H3K4me3, 
+  params = region.p.IHEC.SCARB2,
+  fill = "#35b779", 
+  alpha = 0.7, 
+  linecolor = NA,
+  x = 0.75, 
+  y = 4.125, 
+  width = 4.0, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+annoYaxis(plot = H3K4me3_SCARB2, 
+          at = c(0, scale.IHEC.SCARB2.max),
+          fontsize = 6)
+
+# ChIPseq signal H3K36me3
+H3K36me3_SCARB2 = plotSignal(
+  data = bw.SCARB2.H3K36me3, 
+  params = region.p.IHEC.SCARB2,
+  fill = "#26828e", 
+  alpha = 0.7, 
+  linecolor = NA,
+  x = 0.75, 
+  y = 4.5, 
+  width = 4.0, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+annoYaxis(plot = H3K36me3_SCARB2, 
+          at = c(0, scale.IHEC.SCARB2.max),
+          fontsize = 6)
+
+# ChIPseq signal H3K9me3
+H3K9me3_SCARB2 = plotSignal(
+  data = bw.SCARB2.H3K9me3, 
+  params = region.p.IHEC.SCARB2,
+  fill = "#3e4989", 
+  alpha = 0.7, 
+  linecolor = NA,
+  x = 0.75, 
+  y = 4.875, 
+  width = 4.0, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+annoYaxis(plot = H3K9me3_SCARB2, 
+          at = c(0, scale.IHEC.SCARB2.max),
+          fontsize = 6)
+
+# ChIPseq signal H3K27me3
+H3K27me3_SCARB2 = plotSignal(
+  data = bw.SCARB2.H3K27me3, 
+  params = region.p.IHEC.SCARB2,
+  fill = "#440154", 
+  alpha = 0.7, 
+  linecolor = NA,
+  x = 0.75, 
+  y = 5.25, 
+  width = 4.0, 
+  height = 0.25,
+  just = c("left", "top"), 
+  default.units = "inches")
+
+annoYaxis(plot = H3K27me3_SCARB2, 
+          at = c(0, scale.IHEC.SCARB2.max),
+          fontsize = 6)
+
+# Gene track
+plotGenes(
+  chrom = "chr4",
+  chromstart = 76173717,
+  chromend = 76253717,
+  assembly = assembly(Genome = "hg38refGene", 
+                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
+                      OrgDb = "org.Hs.eg.db"),
+  fontcolor = "black",
+  fill = "black",
+  x = 0.75,
+  y = 5.625,
+  width = 4.0,
+  height = 0.375,
+  just = c("left", "top"),
+  default.units = "inches")
+
+# Add the samples name
+plotText(label = "H3K4me1", 
+         fontsize = 6, 
+         fontcolor = "#b5de2b",
+         x = 0.75,
+         y = 3.75, 
+         just = c("left", "top"),
+         default.units = "inches")
+
+# Add the samples name
+plotText(label = "H3K4me3", 
+         fontsize = 6, 
+         fontcolor = "#35b779",
+         x = 0.75,
+         y = 4.125, 
+         just = c("left", "top"),
+         default.units = "inches")
+
+# Add the samples name
+plotText(label = "H3K36me3", 
+         fontsize = 6, 
+         fontcolor = "#26828e",
+         x = 0.75,
+         y = 4.5, 
+         just = c("left", "top"),
+         default.units = "inches")
+
+# Add the samples name
+plotText(label = "H3K9me3", 
+         fontsize = 6, 
+         fontcolor = "#3e4989",
+         x = 0.75,
+         y = 4.875, 
+         just = c("left", "top"),
+         default.units = "inches")
+
+# Add the samples name
+plotText(label = "H3K27me3", 
+         fontsize = 6, 
+         fontcolor = "#440154",
+         x = 0.75,
+         y = 5.25, 
+         just = c("left", "top"),
+         default.units = "inches")
+
+pageGuideHide()  
 dev.off()
+```
+
+Synchronise the files between my personal ATLAS and the FSTC.SYSBIO ATLAS
+```{bash, eval = FALSE, echo = TRUE}
+cd /Volumes/FSTC_SYSBIO/13-\ PAPERS/2025_Gerard_et_al_SCARB2
+rsync -avzPhu --no-p --chmod=ugo=rwx --delete /Volumes/deborah.gerard/Documents/Manuscript_1/ .
 ```
@@
 ############################################
-
 # Save as a PDF
@@
 
+# Save as TIFF, 300 ppi
+tiff("/home/vagrant/Manuscript_1/SUPPLEMENTARY_FIGURE3/SUPPLEMENTARY_FIGURE3.tiff",
+     width = 8.27,
+     height = 11.67,
+     units = "in",
+     res = 300,
+     compression = "lzw")
+
 # Create a A4 blank page
-pageCreate(width = 8.3, 
-           height = 11.7, 
+pageCreate(width = 8.27, 
+           height = 11.67, 
            default.units = "inches",
@@
 
-```{r}
+```{r, eval = FALSE, echo = TRUE}
 sessionInfo()
 ```
+
+```{r, eval = FALSE, echo = TRUE}
+library("tidyverse")
+library("readxl")
+library("AnnotationDbi")
+library("EnsDb.Hsapiens.v86")
+
+# Load data
+TFlist = read_excel("/Volumes/deborah.gerard/Documents/Elena/Human_TF_list.xls",
+                    skip = 1,
+                    col_names = TRUE)
+
+# Add gene symbol
+TFlist.GN = select(EnsDb.Hsapiens.v86, 
+       keys = as.character(TFlist$EntrezID), 
+       columns = c("ENTREZID", "GENENAME"), 
+       keytype = "ENTREZID")
+
+TFlist.GN %>% 
+  as_tibble() %>% 
+  distinct(GENENAME)
+  write_delim(.,
+              "/Volumes/deborah.gerard/Documents/Elena/Human_TF_list_geneName.txt",
+              col_names = TRUE,
+              delim = "\t")
+
+```

### 2025-01-30 Manuscript_1.Rmd
Update README file and fix a typo in script

@@
 ###################################
-# Zoom on SNCA an add ATACseq dataof the locus
+# Zoom on SNCA an add ATACseq data of the locus
 # Define parameters for a small part of chr4 where SNCA is

### 2025-01-30 SingularityContainer.Rmd
Add the steps showing how the Singularity container was created and set up. Update README file

--- 2024-04-03 Manuscript_1.Rmd
@@
 ---
-title: "Manuscript_1"
+title: "SingularityContainer"
 author: Deborah Gérard^[University of Luxembourg - FSTM - DLSM - Systems Biology group - Epigenetics team]
@@
 devtools::install_version("dbplyr", version = "2.3.4")
+
+# ggmanh
+BiocManager::install("ggmanh")
 ```
-
-Load libraries and check their versions
-
-```{r load_lib, eval = FALSE, echo = TRUE}
-# Load
-library("tidyverse")
-library("rstatix")
-library("ggpubr")
-library("plotgardener")
-#library("BSgenome.Hsapiens.UCSC.hg38")
-library("TxDb.Hsapiens.UCSC.hg38.knownGene")
-library("TxDb.Hsapiens.UCSC.hg38.refGene")
-library("org.Hs.eg.db")
-library("extrafont")
-library("showtext")
-library("JASPAR2020")
-library("TFBSTools")
-library("ggseqlogo")
-library("biomaRt")
-library("LDlinkR")
-library("AllelicImbalance")
-library("png")
-library("AnnotationDbi")
-library("scales")
-library("flowCore")
-library("ggcyto")
-library("ggmanh")
-
-# Check
-packageVersion("tidyverse") #2.0.0
-packageVersion("rstatix") #0.7.2
-packageVersion("ggpubr")  #0.6.0
-packageVersion("plotgardener")  #1.4.2
-#packageVersion("BSgenome.Hsapiens.UCSC.hg38") #1.4.5
-#packageVersion("TxDb.Hsapiens.UCSC.hg38.knownGene") #3.16.0
-packageVersion("TxDb.Hsapiens.UCSC.hg38.refGene") #3.15.0
-packageVersion("org.Hs.eg.db")  #3.16.0
-packageVersion("extrafont") #0.19
-packageVersion("showtext")  #0.9.6
-packageVersion("JASPAR2020")  #0.99.10
-packageVersion("TFBSTools") #1.36.0
-packageVersion("ggseqlogo") #0.1
-packageVersion("biomaRt") #2.54.1
-packageVersion("LDlinkR") #1.3.0
-packageVersion("AllelicImbalance")  #1.36.0
-packageVersion("png") #0.1.8
-packageVersion("AnnotationDbi") #1.60.2
-packageVersion("dbplyr")  #2.3.4
-packageVersion("ggmanh")  #1.2.0
-
-# Import all available fonts
-font_import()
-```
-
-# FIGURES
-Generating the manhattan plot for the PD GWAS is memory demanding. Go to the HPC
-```{bash, eval = FALSE, echo = TRUE}
-ssh iris-cluster
-salloc --nodes=1 -p interactive --qos debug -C batch -t 02:00:00 --mem 24G
-
-# Load the Singularity module
-module load tools/Singularity/3.8.1
-singularity shell --bind /scratch/users/dgerard:/scratch/users/dgerard $HOME/Singularity_containers/Manuscript_1_singularity.sif
-```
-
-### FIGURE 1
-```{r fig1, eval = FALSE, echo = TRUE}
-########## FIGURE 1 ##########
-##############################
-# Save as a PDF
-pdf("/home/vagrant/Manuscript_1/FIGURE1/FIGURE1.pdf",
-    width = 8.3, 
-    height = 11.7)
-
-# Save as TIFF, 300 ppi
-tiff("/home/vagrant/Manuscript_1/FIGURE1/FIGURE1.tiff",
-     width = 8.27,
-     height = 11.67,
-     units = "in",
-     res = 300,
-     compression = "lzw")
-
-# Create a A4 blank page
-pageCreate(width = 8.27, 
-           height = 11.67, 
-           default.units = "inches",
-           showGuides = FALSE)
-
-#### PANEL A - 
-# text Figure 1
-plotText(label = "Figure 1", 
-         fontsize = 14,
-         fontfamily = "Helvetica",
-         x = 0.25, 
-         y = 0.25, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
-
-# text A
-plotText(label = "A", 
-         fontsize = 12,
-         fontfamily = "Helvetica",
-         x = 0.25, 
-         y = 0.5, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
-
-###################
-#### Figure 1A ####
-###################
-# Figure 1A generated in Biorender
-#fig1A = readPNG("/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/Fig1A.png")
-fig1A = readPNG("/home/vagrant/Manuscript_1/FIGURE1/Fig1A.png")
-
-plotRaster(image = fig1A,
-           x = 0.25, 
-           y = 1, 
-           width = 8.0, 
-           height = 1.0, 
-           just = "left",
-           interpolate = TRUE)
-
-# text B
-plotText(label = "B", 
-         fontsize = 12,
-         fontfamily = "Helvetica",
-         x = 0.25, 
-         y = 1.5, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
-
-# text C
-plotText(label = "C", 
-         fontsize = 12,
-         fontfamily = "Helvetica",
-         x = 0.25, 
-         y = 4.5, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
-
-# text D
-plotText(label = "D", 
-         fontsize = 12,
-         fontfamily = "Helvetica",
-         x = 3.25, 
-         y = 4.5, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
-
-# text E
-plotText(label = "E", 
-         fontsize = 12,
-         fontfamily = "Helvetica",
-         x = 0.25, 
-         y = 4.5, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
-
-###################
-#### Figure 1B ####
-###################
-# Load data obtained from Jochen
-RNAseq_odd = read_delim("/home/vagrant/Manuscript_1/FIGURE1/REFORMAT_tpm_gene_sets.gsa.txt",
-                        delim = "\t",
-                        col_names = TRUE)
-
-#RNAseq_odd = read_delim("/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/REFORMAT_tpm_gene_sets.gsa.txt",
-#                      delim = "\t",
-#                      col_names = TRUE)
-
-# Calculate odd ratio
-RNAseq_odd = RNAseq_odd %>% 
-  dplyr::filter(!VARIABLE %in% c("microglia")) %>% 
-  mutate(odd_R = exp(BETA)) %>% 
-  mutate(VARIABLE = factor(VARIABLE, 
-                           levels = c("smNPC",
-                                      "D15negsort",
-                                      "D15possort",
-                                      "D30postsort",
-                                      "D50negsort",
-                                      "D50possort",
-                                      "astrocytes")))
-
-# Plot
-fig1B = ggplot(RNAseq_odd,
-       aes(x = odd_R,
-           y = VARIABLE)) +
-  geom_point(shape = 16, size = 3) +
-  geom_errorbarh(aes(xmin = odd_R - SE, 
-                     xmax = odd_R + SE), 
-                 height = 0.25) +
-  geom_vline(xintercept = 1.0, linetype = "dashed", color = "grey") +
-  theme_classic() +
-  theme(axis.title = element_text(face = "bold"),
-        axis.text = element_text(face = "bold")) +
-  scale_y_discrete(labels = c("smNPC" = "smNPC", 
-                              "D15negsort" = "non-mDAN D15", 
-                              "D15possort" = "mDAN D15", 
-                              "D30postsort" = "mDAN D30", 
-                              "D50negsort" = "non-mDAN D50",
-                              "D50possort" = "mDAN D50",
-                              "astrocytes" = "Astrocytes")) +
-  geom_text(label = round(RNAseq_odd$P, 
-                          digits = 3),
-            nudge_y = 0.40) +
-  xlab("Odds ratio (95% Confidence Interval)") +
-  ylab("")
-
-# Place
-plotGG(plot = fig1B, 
-       x = 0.375, 
-       y = 1.75, 
-       width = 3.0, 
-       height = 2.5,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-###################
-#### Figure 1C ####
-###################
-Fig1C_pip = readPNG("/home/vagrant/Manuscript_1/FIGURE1/Fig1C_pipeline.png")
-#Fig1C_pip = readPNG("/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/Fig1C_pipeline.png")
-
-# Plot Figure 1C - Pipeline
-plotRaster(image = Fig1C_pip,
-           x = 0.375,
-           y = 4.75,
-           width = 3.0,
-           height = 3.5,
-           just = c("left", 
-                    "top"),
-           interpolate = TRUE)
-
-###################
-#### Figure 1C Manhattan plot ####
-###################
-# Load the Nalls et al. GWAS data
-nalls_allSNPs.HG38.GR = readRDS(
-  "/home/vagrant/Manuscript_1/FIGURE1/nalls_allSNPs.HG38.GR.rds")
-
-#nalls_allSNPs.HG38.GR = readRDS(
-#"/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/nalls_allSNPs.HG38.GR.rds")
-
-# Load the rsIDS FOR THE 28 significant SNPs
-rsID.28 = read_delim("/home/vagrant/Manuscript_1/FIGURE1/20210309_28SNPs_rsID.csv",
-                     delim = ",",
-                     col_names = TRUE)
-
-rsID.28 = read_delim("/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/20210309_28SNPs_rsID.csv",
-                     delim = ",",
-                     col_names = TRUE)
-
-rsID.28.filt = rsID.28 %>% 
-  dplyr::select(chrom, chromEnd, name) %>% 
-  unite(col = "pos", chrom, chromEnd, sep = "_")
-
-# Select the SNPs position from nalls et al and associate rsIDs
-nalls.manH = nalls_allSNPs.HG38.GR %>% 
-  as_tibble() %>% 
-  dplyr::select(seqnames, base_pair_position, p) %>% 
-  unite(col = "pos", seqnames, base_pair_position, sep = "_", remove = FALSE) %>%
-  left_join(rsID.28.filt, by = "pos") %>% 
-  separate(pos, into = c("chrom", "pos"), sep = "_", remove = TRUE) %>% 
-  dplyr::select(chrom, pos, p, name)
-
-# Save
-write_rds(nalls.manH,
-          "/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/20240304_28SNPs_rdID_manH.rds")
-
-nalls.manH = read_rds("/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/20240304_28SNPs_rdID_manH.rds")
-nalls.manH = read_rds("/home/vagrant/Manuscript_1/FIGURE1/20240304_28SNPs_rdID_manH.rds")
-
-# Rename columns
-nalls.manH = nalls.manH %>% 
-  dplyr::rename(snp = name) %>% 
-  mutate(pos = as.numeric(pos)) %>% 
-  dplyr::filter(chrom %in% rsID.28$chrom)
-
-# Manhattan plot - highlight  the 28 SNPs with rsID
-snp_2_high = nalls.manH %>% 
-  dplyr::filter(!is.na(snp),
-                p <= 5e-08)
-
-# Random sampling for plotting test
-snp_to_pl = nalls.manH %>% 
-  mutate(snp = NA_character_) %>% 
-  bind_rows(snp_2_high) %>% 
-  #dplyr::filter(p <= 5e-08) %>% 
-  mutate(pbis = -log10(p),
-         chrom = factor(chrom,
-                        levels = c("chr1",
-                                   "chr3",
-                                   "chr4",
-                                   "chr7",
-                                   "chr10",
-                                   "chr12",
-                                   "chr16",
-                                   "chr17")))
-
-# And plot
-snp.pl = manhattan_plot(x = snp_to_pl, 
-               pval.colname = "p", 
-               chr.colname = "chrom", 
-               pos.colname = "pos",
-               label.colname = "snp",
-               signif = 5e-08,
-               max.overlaps = 50)
-
-saveRDS(snp.pl,
-        "/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/Nalls_manh_label.rds")
-snp.pl = readRDS("/home/vagrant/Manuscript_1/FIGURE1/Nalls_manh_label.rds")
-
-# Place the plot
-plotGG(plot = snp.pl, 
-       x = 3.5, 
-       y = 4.75, 
-       width = 4.5, 
-       height = 3.5,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-###################
-#### Figure 1D ####
-###################
-
-# Locus plot
-# Here our SNPs of interest and their location
-snp = GRanges(seqnames = c("chr10", "chr4", "chr4"),
-              ranges = IRanges(start = c(119651404, 987107, 76213716),
-                               end = c(119651405, 987108, 76213717)))
-
-# Retrieve them from Nalls et al data
-snp_Nalls = subsetByOverlaps(nalls_allSNPs.HG38.GR, snp) %>% 
-  as_tibble() %>% 
-  dplyr::select(-width, -strand) %>% 
-  mutate(rsID = c("rs144814361", "rs1465922", "rs11248061"))
-
-# Visualise the genomic region per SNP (+- 400100 bp)
-# rs144814361
-r = 40100
-
-# Filter for the SNP in BAG3 regulatory region
-Nalls_sel_reg.BAG3 = nalls_allSNPs.HG38.GR %>% 
-  as_tibble() %>% 
-  dplyr::filter(seqnames == "chr10",
-         between(base_pair_position, 119651405 - r, 119651405 + r)) %>% 
-  mutate(minus_log_10_p = -log10(p),
-         GWAS_p_sig = if_else(minus_log_10_p > -log10(5e-8), "yes", "no"),
-         rsID = if_else(seqnames == "chr10" & base_pair_position == 119651405, "rs144814361", ""))
-
-# Get SNPs info from Ensembl
-#snp.ensembl = useEnsembl(biomart = "snp", 
-#                         dataset = "hsapiens_snp")
-
-snp.ensembl = useMart(biomart = "ENSEMBL_MART_SNP",
-                      dataset = "hsapiens_snp")
-
-# SNP info
-query.snp = getBM(c("ensembl_gene_stable_id", 
-                            "refsnp_id", 
-                            "chr_name", 
-                            "chrom_start", 
-                            "chrom_end", 
-                            "minor_allele", 
-                            "minor_allele_freq"),
-                          filters = "snp_filter",
-                          values = c("rs144814361", "rs1465922", "rs11248061"),
-                  mart = snp.ensembl)
-
-# Get rsID of SNPs that are significant and append 
-position_chr10 = Nalls_sel_reg.BAG3 %>% 
-  mutate(chr = gsub("chr", "", seqnames)) %>% 
-  unite(col = "position", c(chr, end, base_pair_position), sep = ":", remove = FALSE) %>% 
-  dplyr::filter(GWAS_p_sig != "no") %>%
-  dplyr::select(position) %>% 
-  pull()
-
-rsID_sig_SNPs.chr10 = getBM(c("refsnp_id", "chr_name", "chrom_start", "chrom_end", "allele", "minor_allele"),
-                      filters = "chromosomal_region",
-                      values = position_chr10,
-                      mart = snp.ensembl)
-
-rsID_sig_SNPs.chr10 = rsID_sig_SNPs.chr10 %>% 
-  unite(col = "position", chr_name:chrom_end, sep = ":", remove = FALSE)
-
-Nalls_sel_reg.BAG3 = Nalls_sel_reg.BAG3 %>% 
-  mutate(chr = gsub("chr", "", seqnames)) %>% 
-  unite(col = "position", c(chr, end, base_pair_position),
-        sep = ":", remove = FALSE) %>% 
-  left_join(rsID_sig_SNPs.chr10, by = "position")
-
-# Calculate R2 to check if SNPs are in LD
-BAG3_SNPs_LD = Nalls_sel_reg.BAG3 %>% 
-  dplyr::select(refsnp_id) %>% 
-  drop_na()
-
-BAG3_R2 = LDproxy(snp = "rs144814361",
-                   pop = "EUR",
-                   r2d = "r2",
-                   token = "5bba40af90d7",
-                   genome_build = "grch38_high_coverage")
-
-BAG3_R2 = BAG3_R2 %>% 
-  as_tibble() %>% 
-  dplyr::select(RS_Number, Coord, R2) %>% 
-  dplyr::rename(refsnp_id = RS_Number)
-
-# Plot
-BAG3.pl = Nalls_sel_reg.BAG3 %>% 
-  unite("Coord", seqnames, base_pair_position, sep = ":", remove = FALSE) %>% 
-  left_join(BAG3_R2, by = "Coord") %>% 
-  dplyr::select(seqnames, base_pair_position, p, refsnp_id.x, R2) %>% 
-  dplyr::rename(chrom = seqnames,
-               pos = base_pair_position,
-               snp = refsnp_id.x, 
-               LD = R2) %>% 
-  mutate(chrom = as.character(chrom)) %>% 
-  group_by(LD) %>% 
-  mutate(LD_grp = cut(LD, seq(0, 1.0, 0.2)))
-
-BAG3.pl$LD_grp = addNA(BAG3.pl$LD_grp)
-
-BAG3_leadSNP = "rs144814361"
-
-BAG3_MP = plotManhattan(data = BAG3.pl,
-              chrom = "chr10",
-              chromstart = 119611405,
-              chromend = 119691405,
-              assembly = "hg38",
-              fill = colorby("LD_grp",
-                             palette = colorRampPalette(c("#35b779",
-                                                          "#21918c", 
-                                                          "#31688e",
-                                                          "#443983", 
-                                                          "#440154", 
-                                                          "#CCCCCC"))),
-        trans = "-log10", 
-        sigLine = TRUE, col = "grey",
-        lty = 2, range = c(0, 16),
-        leadSNP = list(
-        snp = BAG3_leadSNP,
-        pch = 18,
-        cex = 0.75,
-        fill = "#990066",
-        fontsize = 8),
-              x = 0.5, 
-              y = 8.5, 
-              width = 1.5, 
-              height = 2.5,
-              just = c("left", "top"), 
-              default.units = "inches")
-
-## Annotate genome label
-annoGenomeLabel(
-    plot = BAG3_MP, x = 0.5, y = 11,
-    fontsize = 8, scale = "Mb",
-    just = c("left", "top"), default.units = "inches"
-)
-
-## Annotate y-axis
-annoYaxis(
-    plot = BAG3_MP,
-    at = c(0, 2, 4, 6, 8, 10, 12),
-    axisLine = TRUE, fontsize = 8
-)
-
-## Plot y-axis label
-plotText(
-    label = "-log10(p-value)", x = 0.125, y = 10.125, rot = 90,
-    fontsize = 8, fontface = "bold", just = "center",
-    default.units = "inches"
-)
-
-# Plot gene BAG3
-plotGenes(
-    chrom = "chr10", chromstart = 119611405, chromend = 119691405,
-    x = 0.5, y = 8.5, width = 1.5, height = 0.5,
-    just = c("left", "top"), default.units = "inches",
-    fontcolor = "black",
-    fill = "black",
-    assembly = assembly(Genome = "hg38refGene", 
-                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
-                      OrgDb = "org.Hs.eg.db")
-)
-
-# Filter for the SNP in IDUA regulatory region
-Nalls_sel_reg.IDUA = nalls_allSNPs.HG38.GR %>% 
-  as_tibble() %>% 
-  dplyr::filter(seqnames == "chr4",
-         between(base_pair_position, 987108 - r, 987108 + r)) %>% 
-  mutate(minus_log_10_p = -log10(p),
-         GWAS_p_sig = if_else(minus_log_10_p > -log10(5e-8), "yes", "no"),
-         rsID = if_else(seqnames == "chr4" & base_pair_position == 987108, "rs11248061", ""))
-
-# Get rsID of SNPs that significant and append 
-position_chr4.IDUA = Nalls_sel_reg.IDUA %>% 
-  mutate(chr = gsub("chr", "", seqnames)) %>% 
-  unite(col = "position", c(chr, end, base_pair_position), sep = ":", remove = FALSE) %>% 
-  dplyr::filter(GWAS_p_sig != "no") %>%
-  dplyr::select(position) %>% 
-  pull()
-
-rsID_sig_SNPs.chr4.IDUA = getBM(c("refsnp_id", "chr_name", "chrom_start", "chrom_end", "allele", "minor_allele",
-                        "minor_allele_freq"),
-                      filters = "chromosomal_region",
-                      values = position_chr4.IDUA,
-                      mart = snp.ensembl)
-
-rsID_sig_SNPs.chr4.IDUA = rsID_sig_SNPs.chr4.IDUA %>% 
-  unite(col = "position", chr_name:chrom_end, sep = ":", remove = FALSE)
-
-Nalls_sel_reg.IDUA = Nalls_sel_reg.IDUA %>% 
-  mutate(chr = gsub("chr", "", seqnames)) %>% 
-  unite(col = "position", c(chr, end, base_pair_position),
-        sep = ":", remove = FALSE) %>% 
-  left_join(rsID_sig_SNPs.chr4.IDUA, by = "position")
-
-# Calculate R2 to check if SNPs are in LD
-IDUA_SNPs_LD = Nalls_sel_reg.IDUA %>% 
-  dplyr::select(refsnp_id) %>% 
-  drop_na()
-
-IDUA_SNPs_LD = IDUA_SNPs_LD %>% 
-  dplyr::filter(!str_detect(refsnp_id, "^CR"))
-
-IDUA_R2 = LDproxy(snp = "rs11248061",
-                   pop = "EUR",
-                   r2d = "r2",
-                   token = "5bba40af90d7",
-                   genome_build = "grch38_high_coverage")
-
-IDUA_R2 = IDUA_R2 %>% 
-  as_tibble() %>% 
-  dplyr::select(RS_Number, Coord, R2) %>% 
-  dplyr::rename(refsnp_id = RS_Number)
-
-# Plot
-IDUA.pl = Nalls_sel_reg.IDUA %>% 
-  unite("Coord", seqnames, base_pair_position, sep = ":", remove = FALSE) %>% 
-  distinct(Coord, .keep_all = TRUE) %>% 
-  left_join(IDUA_R2, by = "Coord") %>% 
-  dplyr::select(seqnames, base_pair_position, p, refsnp_id.x, R2) %>% 
-  dplyr::rename(chrom = seqnames,
-               pos = base_pair_position,
-               snp = refsnp_id.x, 
-               LD = R2) %>% 
-  mutate(chrom = as.character(chrom)) %>% 
-  group_by(LD) %>% 
-  mutate(LD_grp = cut(LD, seq(0, 1.0, 0.2)))
-
-IDUA.pl$LD_grp = addNA(IDUA.pl$LD_grp)
-
-IDUA_leadSNP = "rs11248061"
-
-IDUA_MP = plotManhattan(data = IDUA.pl,
-              chrom = "chr4",
-              chromstart = 947108,
-              chromend = 1027108,
-              assembly = "hg38",
-              fill = colorby("LD_grp",
-                             palette = colorRampPalette(c("#35b779",
-                                                          "#21918c", 
-                                                          "#31688e",
-                                                          "#443983", 
-                                                          "#440154", 
-                                                          "#CCCCCC"))),
-        trans = "-log10", 
-        sigLine = TRUE, col = "grey",
-        lty = 2, range = c(0, 16),
-        leadSNP = list(
-        snp = IDUA_leadSNP,
-        pch = 18,
-        cex = 0.75,
-        fill = "#990066",
-        fontsize = 8),
-              x = 2.5, 
-              y = 8.5, 
-              width = 1.5, 
-              height = 2.5,
-              just = c("left", "top"), 
-              default.units = "inches")
-
-## Annotate genome label
-annoGenomeLabel(
-    plot = IDUA_MP, x = 2.5, y = 11,
-    fontsize = 8, scale = "Mb",
-    just = c("left", "top"), default.units = "inches"
-)
-
-## Annotate y-axis
-annoYaxis(
-    plot = IDUA_MP,
-    at = c(0, 2, 4, 6, 8, 10, 12),
-    axisLine = TRUE, fontsize = 8
-)
-
-## Plot y-axis label
-plotText(
-    label = "-log10(p-value)", x = 2.125, y = 10.125, rot = 90,
-    fontsize = 8, fontface = "bold", just = "center",
-    default.units = "inches"
-)
-
-# Plot gene IDUA
-plotGenes(
-    chrom = "chr4", chromstart = 947108, chromend = 1027108,
-    x = 2.5, y = 8.5, width = 1.5, height = 0.5,
-    just = c("left", "top"), default.units = "inches",
-    fontcolor = "black",
-    fill = "black",
-    assembly = assembly(Genome = "hg38refGene", 
-                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
-                      OrgDb = "org.Hs.eg.db")
-)
-
-# Filter for the SNP in SCARB2 regulatory region
-Nalls_sel_reg.SCARB2 = nalls_allSNPs.HG38.GR %>% 
-  as_tibble() %>% 
-  dplyr::filter(seqnames == "chr4",
-         between(base_pair_position, 76213717 - r, 76213717 + r)) %>% 
-  mutate(minus_log_10_p = -log10(p),
-         GWAS_p_sig = if_else(minus_log_10_p > -log10(5e-8), "yes", "no"),
-         rsID = if_else(seqnames == "chr4" & base_pair_position == 76213717, "rs1465922", ""))
-
-# Get rsID of SNPs that significant and append 
-position_chr4.SCARB2 = Nalls_sel_reg.SCARB2 %>% 
-  mutate(chr = gsub("chr", "", seqnames)) %>% 
-  unite(col = "position", c(chr, end, base_pair_position), sep = ":", remove = FALSE) %>% 
-  dplyr::filter(GWAS_p_sig != "no") %>%
-  dplyr::select(position) %>% 
-  pull()
-
-rsID_sig_SNPs.chr4.SCARB2 = getBM(c("refsnp_id", "chr_name", "chrom_start", "chrom_end", "allele", "minor_allele",
-                        "minor_allele_freq"),
-                      filters = "chromosomal_region",
-                      values = position_chr4.SCARB2,
-                      mart = snp.ensembl)
-
-rsID_sig_SNPs.chr4.SCARB2 = rsID_sig_SNPs.chr4.SCARB2 %>% 
-  unite(col = "position", chr_name:chrom_end, sep = ":", remove = FALSE)
-
-Nalls_sel_reg.SCARB2 = Nalls_sel_reg.SCARB2 %>% 
-  mutate(chr = gsub("chr", "", seqnames)) %>% 
-  unite(col = "position", c(chr, end, base_pair_position),
-        sep = ":", remove = FALSE) %>% 
-  left_join(rsID_sig_SNPs.chr4.SCARB2, by = "position")
-
-# Calculate R2 to check if SNPs are in LD
-SCARB2_SNPs_LD = Nalls_sel_reg.SCARB2 %>% 
-  dplyr::select(refsnp_id) %>% 
-  drop_na()
-
-SCARB2_R2 = LDproxy(snp = "rs1465922",
-                   pop = "EUR",
-                   r2d = "r2",
-                   token = "5bba40af90d7",
-                   genome_build = "grch38_high_coverage")
-
-SCARB2_R2 = SCARB2_R2 %>% 
-  as_tibble() %>% 
-  dplyr::select(RS_Number, Coord, R2) %>% 
-  dplyr::rename(refsnp_id = RS_Number)
-
-# Plot
-SCARB2.pl = Nalls_sel_reg.SCARB2 %>% 
-  unite("Coord", seqnames, base_pair_position, sep = ":", remove = FALSE) %>% 
-  left_join(SCARB2_R2, by = "Coord") %>% 
-  dplyr::select(seqnames, base_pair_position, p, refsnp_id.x, R2) %>% 
-  dplyr::rename(chrom = seqnames,
-               pos = base_pair_position,
-               snp = refsnp_id.x, 
-               LD = R2) %>% 
-  mutate(chrom = as.character(chrom)) %>% 
-  group_by(LD) %>% 
-  mutate(LD_grp = cut(LD, seq(0, 1.0, 0.2)))
-
-SCARB2.pl$LD_grp = addNA(SCARB2.pl$LD_grp)
-
-SCARB2_leadSNP = "rs1465922"
-
-SCARB2_MP = plotManhattan(data = SCARB2.pl,
-              chrom = "chr4",
-              chromstart = 76173717,
-              chromend = 76253717,
-              assembly = "hg38",
-              fill = colorby("LD_grp",
-                             palette = colorRampPalette(c("#35b779",
-                                                          "#21918c", 
-                                                          "#31688e",
-                                                          "#443983", 
-                                                          "#440154", 
-                                                          "#CCCCCC"))),
-        trans = "-log10", 
-        sigLine = TRUE, col = "grey",
-        lty = 2, range = c(0, 16),
-        leadSNP = list(
-        snp = SCARB2_leadSNP,
-        pch = 18,
-        cex = 0.75,
-        fill = "#990066",
-        fontsize = 8),
-              x = 4.5, 
-              y = 8.5, 
-              width = 1.5, 
-              height = 2.5,
-              just = c("left", "top"), 
-              default.units = "inches")
-
-## Annotate genome label
-annoGenomeLabel(
-    plot = SCARB2_MP, x = 4.5, y = 11,
-    fontsize = 8, scale = "Mb",
-    just = c("left", "top"), default.units = "inches"
-)
-
-## Annotate y-axis
-annoYaxis(
-    plot = SCARB2_MP,
-    at = c(0, 2, 4, 6, 8, 10, 12),
-    axisLine = TRUE, fontsize = 8
-)
-
-## Plot y-axis label
-plotText(
-    label = "-log10(p-value)", x = 4.125, y = 10.125, rot = 90,
-    fontsize = 8, fontface = "bold", just = "center",
-    default.units = "inches"
-)
-
-# Plot gene SCARB2
-plotGenes(
-    chrom = "chr4", chromstart = 76173717, chromend = 76253717,
-    x = 4.5, y = 8.5, width = 1.5, height = 0.5,
-    just = c("left", "top"), default.units = "inches",
-    fontcolor = "black",
-    fill = "black",
-    assembly = assembly(Genome = "hg38refGene", 
-                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
-                      OrgDb = "org.Hs.eg.db")
-)
-
-# Legend LD score
-plotLegend(
-  legend = c("LD reference SNP",
-             paste("0", "<", "r^2", "<= 0.2"),
-             paste("0.2", "<", "r^2", "<= 0.4"),
-             paste("0.4", "<", "r^2", "<= 0.6"),
-             paste("0.6", "<", "r^2", "<= 0.8"),
-             paste("0.8", "<", "r^2", "<= 1.0"),
-             "no LD data"),
-    fill = c("#990066", "#35b779", "#21918c", "#31688e", "#443983", "#440154", "#CCCCCC"), 
-  cex = 0.75,
-    pch = c(18, 19, 19, 19, 19, 19, 19), border = FALSE, x = 6.5, y = 9.25,
-    width = 1.0, height = 1.0, just = c("left", "top"),
-    default.units = "inches"
-)
-
-dev.off()
-```
-
-### FIGURE 2
-Create the page layout that will contain all the necessary plots
-
-```{r fig2, eval = FALSE, echo = TRUE}
-########## FIGURE 2 ##########
-##############################
-
-# Save as a PDF
-pdf("/home/vagrant/Manuscript_1/FIGURE2/FIGURE2.pdf",
-    width = 8.3, 
-    height = 11.7)
-
-# Save as TIFF, 300 ppi
-tiff("/home/vagrant/Manuscript_1/FIGURE2/FIGURE2.tiff",
-     width = 8.27,
-     height = 11.67,
-     units = "in",
-     res = 300,
-     compression = "lzw")
-
-# Create a A4 blank page
-pageCreate(width = 8.27, 
-           height = 11.67, 
-           default.units = "inches",
-           showGuides = FALSE)
-
-#### PANEL A - BAG3 locus
-# text Figure 2
-plotText(label = "Figure 2", 
-         fontsize = 14,
-         fontfamily = "Helvetica",
-         x = 0.25, 
-         y = 0.25, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
-
-# text A
-plotText(label = "A", 
-         fontsize = 12,
-         fontfamily = "Helvetica",
-         x = 0.25, 
-         y = 0.5, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
-
-# ATACseq signal BAG3
-# path where bigwig files are
-bw.path = "/home/vagrant/epifunc/"
-#bw.path = "/Volumes/deborah.gerard/Documents/epifunc/"
-
-# 1st bio replicate smNPC
-bw.smNPC_1 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/smNPC_I.bw"),
-                        chrom = "chr10",
-                        chromstart = 119611305,
-                        chromend = 119691505)
-
-# 2nd bio replicate smNPC
-bw.smNPC_2 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/smNPC_II.bw"),
-                        chrom = "chr10",
-                        chromstart = 119611305,
-                        chromend = 119691505)
-
-# 3rd bio replicate smNPC
-bw.smNPC_3 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/smNPC_III.bw"),
-                        chrom = "chr10",
-                        chromstart = 119611305,
-                        chromend = 119691505)
-
-# 1st bio replicate TH positive neurons D15
-bw.TH.pos_D15_1 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/D15_POS_I.bw"),
-                        chrom = "chr10",
-                        chromstart = 119611305,
-                        chromend = 119691505)
-
-# 2nd bio replicate TH positive neurons D15
-bw.TH.pos_D15_2 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/D15_POS_II.bw"),
-                        chrom = "chr10",
-                        chromstart = 119611305,
-                        chromend = 119691505)
-
-# 3rd bio replicate TH positive neurons D15
-bw.TH.pos_D15_3 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/D15_POS_III.bw"),
-                        chrom = "chr10",
-                        chromstart = 119611305,
-                        chromend = 119691505)
-
-# 1st bio replicate TH positive neurons D30
-bw.TH.pos_D30_1 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/D30_POS_I.bw"),
-                        chrom = "chr10",
-                        chromstart = 119611305,
-                        chromend = 119691505)
-
-# 2nd bio replicate TH positive neurons D30
-bw.TH.pos_D30_2 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/D30_POS_II.bw"),
-                        chrom = "chr10",
-                        chromstart = 119611305,
-                        chromend = 119691505)
-
-# 3rd bio replicate TH positive neurons D30
-bw.TH.pos_D30_3 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/D30_POS_III.bw"),
-                        chrom = "chr10",
-                        chromstart = 119611305,
-                        chromend = 119691505)
-
-# 1st bio replicate TH positive neurons D50
-bw.TH.pos_D50_1 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/HFFTHmCherry_D50_possort_S1.bw"),
-                        chrom = "chr10",
-                        chromstart = 119611305,
-                        chromend = 119691505)
-
-# 2nd bio replicate TH positive neurons D50
-bw.TH.pos_D50_2 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/HFFTHmCherry_D50_possort_S3.bw"),
-                        chrom = "chr10",
-                        chromstart = 119611305,
-                        chromend = 119691505)
-
-# 3rd bio replicate TH positive neurons D50
-bw.TH.pos_D50_3 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/HFFTHmCherry_D50_possort_S4.bw"),
-                        chrom = "chr10",
-                        chromstart = 119611305,
-                        chromend = 119691505)
-
-# Add a scale next to the bigwig files - check the maximum to choose
-scale.BAG3.max = max(c(bw.smNPC_1$score,
-                       bw.smNPC_2$score,
-                       bw.smNPC_3$score,
-                       bw.TH.pos_D15_1$score,
-                       bw.TH.pos_D15_2$score,
-                       bw.TH.pos_D15_3$score,
-                       bw.TH.pos_D30_1$score,
-                       bw.TH.pos_D30_2$score,
-                       bw.TH.pos_D30_3$score,
-                       bw.TH.pos_D50_1$score,
-                       bw.TH.pos_D50_2$score,
-                       bw.TH.pos_D50_3$score))
-
-print(scale.BAG3.max)
-
-# Define parameters for the regions
-region.p.BAG3 = pgParams(chrom = "chr10",
-                         chromstart = 119611405,
-                         chromend = 119691405,
-                         assembly = "hg38",
-                         range = c(0, scale.BAG3.max))
-
-# Add the genomic label
-plotGenomeLabel(
-  chrom = "chr10",
-  chromstart = 119611405,
-  chromend = 119691405,
-  assembly = "hg38",
-  x = 0.75,
-  y = 0.625,
-  length = 4.0,
-  default.units = "inches",
-  scale = "Mb")
-
-# ATACseq signal smNPC_I and scale
-ATAC_smNPC_I = plotSignal(
-  data = bw.smNPC_1, 
-  params = region.p.BAG3,
-  fill = "#D3D3D3", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 0.875, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_smNPC_I, 
-          at = c(0, scale.BAG3.max),
-          fontsize = 6)
-
-# ATACseq signal smNPC_II
-ATAC_smNPC_II = plotSignal(
-  data = bw.smNPC_2, 
-  params = region.p.BAG3,
-  fill = "#C0C0C0", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 0.875, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_smNPC_II, 
-          at = c(0, scale.BAG3.max),
-          fontsize = 6)
-
-# ATACseq signal smNPC_III
-ATAC_smNPC_III = plotSignal(
-  data = bw.smNPC_3, 
-  params = region.p.BAG3,
-  fill = "#A9A9A9", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 0.875, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_smNPC_III, 
-          at = c(0, scale.BAG3.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D15 I
-ATAC_TH.pos_D15_I = plotSignal(
-  data = bw.TH.pos_D15_1, 
-  params = region.p.BAG3,
-  fill = "#B22222", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 1.25, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D15_I, 
-          at = c(0, scale.BAG3.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D15 II
-ATAC_TH.pos_D15_II = plotSignal(
-  data = bw.TH.pos_D15_2, 
-  params = region.p.BAG3,
-  fill = "#A52A2A", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 1.25, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D15_II, 
-          at = c(0, scale.BAG3.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D15 III
-ATAC_TH.pos_D15_III = plotSignal(
-  data = bw.TH.pos_D15_3, 
-  params = region.p.BAG3,
-  fill = "#8B0000", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 1.25, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D15_III, 
-          at = c(0, scale.BAG3.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D30 I
-ATAC_TH.pos_D30_I = plotSignal(
-  data = bw.TH.pos_D30_1, 
-  params = region.p.BAG3,
-  fill = "#FF6347", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 1.625, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D30_I, 
-          at = c(0, scale.BAG3.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D30 II
-ATAC_TH.pos_D30_II = plotSignal(
-  data = bw.TH.pos_D30_2, 
-  params = region.p.BAG3,
-  fill = "#FF0000", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 1.625, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D30_II, 
-          at = c(0, scale.BAG3.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D30 III
-ATAC_TH.pos_D30_III = plotSignal(
-  data = bw.TH.pos_D30_3, 
-  params = region.p.BAG3,
-  fill = "#DC143C", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 1.625, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D30_III, 
-          at = c(0, scale.BAG3.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D50 I
-ATAC_TH.pos_D50_I = plotSignal(
-  data = bw.TH.pos_D50_1, 
-  params = region.p.BAG3,
-  fill = "#FFA07A", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 2.0, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D50_I, 
-          at = c(0, scale.BAG3.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D50 II
-ATAC_TH.pos_D50_II = plotSignal(
-  data = bw.TH.pos_D50_2, 
-  params = region.p.BAG3,
-  fill = "#FA8072", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 2.0, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D50_II, 
-          at = c(0, scale.BAG3.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D50 III
-ATAC_TH.pos_D50_III = plotSignal(
-  data = bw.TH.pos_D50_3, 
-  params = region.p.BAG3,
-  fill = "#E9967A", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 2.0, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D50_III, 
-          at = c(0, scale.BAG3.max),
-          fontsize = 6)
-
-# Gene track
-plotGenes(chrom = "chr10",
-  chromstart = 119611405,
-  chromend = 119691405,
-  assembly = assembly(Genome = "hg38refGene", 
-                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
-                      OrgDb = "org.Hs.eg.db"),
-  fontcolor = "black",
-  fill = "black",
-  x = 0.75,
-  y = 2.375,
-  width = 4.0,
-  height = 0.375,
-  just = c("left", "top"),
-  default.units = "inches")
-
-# Add the samples name
-plotText(label = "smNPC", 
-         fontsize = 6, 
-         fontcolor = "#A9A9A9",
-         fontfamily = "Helvetica",
-         x = 0.75, 
-         y = 0.875, 
-         just = c("left", "top"),
-         default.units = "inches",
-         fontface = "bold")
-
-plotText(label = "mDAN D15", 
-         fontsize = 6, 
-         fontfamily = "Helvetica",
-         fontcolor = "#B22222",
-         x = 0.75, 
-         y = 1.25, 
-         just = c("left", "top"),
-         default.units = "inches",
-         fontface = "bold")
-
-plotText(label = "mDAN D30", 
-         fontsize = 6, 
-         fontfamily = "Helvetica",
-         fontcolor = "#DC143C",
-         x = 0.75, 
-         y = 1.625, 
-         just = c("left", "top"),
-         default.units = "inches",
-         fontface = "bold")
-
-plotText(label = "mDAN D50", 
-         fontsize = 6, 
-         fontfamily = "Helvetica",
-         fontcolor = "#E9967A",
-         x = 0.75, 
-         y = 2.0, 
-         just = c("left", "top"),
-         default.units = "inches",
-         fontface = "bold")
-
-#### PANEL B - BAG3 and LHX1 expression (RNAseq)
-# text B
-plotText(label = "B", 
-         fontsize = 12,
-         fontfamily = "Helvetica",
-         x = 5.0, 
-         y = 0.5, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
-
-# Load RPKM matrix obtained from Borja and rename columns
-# dat.RPKM = read_delim("/home/vagrant/epifunc/RNAseq/RPKM_genename",
-#                       delim = "\t", 
-#                       col_names = TRUE)
-# 
-# dat.RPKM = dat.RPKM %>% 
-#   dplyr::select(gene_id, gene_name, everything())
-
-# RPKM data - Remove the negative sorted neurons and astrocytes
-# dat.RPKM.filt = dat.RPKM %>% 
-#   dplyr::select(!contains("negsort"), -starts_with("ASTRO")) %>% 
-#   pivot_longer(cols = ends_with("bam"), names_to = "Sample", values_to = "RPKM") %>% 
-#   mutate(Cond = case_when(str_detect(Sample, "D15_possort") ~ "Positively sorted neurons D15",
-#                          str_detect(Sample, "D30_possort") ~ "Positively sorted neurons D30",
-#                          str_detect(Sample, "D50_possort") ~ "Positively sorted neurons D50",
-#                          TRUE ~ "smNPCs"),
-#          Cond = factor(Cond, levels = c("smNPCs", "Positively sorted neurons D15",
-#                                   "Positively sorted neurons D30", 
-#                                   "Positively sorted neurons D50")),
-#          gene_id = gsub("\\..*", "", gene_id))
-
-# Save the matrix of expression
-# write_rds(dat.RPKM.filt,
-#           "/home/vagrant/Manuscript_1/FIGURE2/mat_RPKM.rds")
-
-# Load it for making the plots
-dat.RPKM.filt = read_rds("/home/vagrant/Manuscript_1/FIGURE2/mat_RPKM.rds")
-dat.RPKM.filt = read_rds("/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE2/mat_RPKM.rds")
-
-dat.RPKM.filt %>% 
-  #filter(str_detect(gene_id, " ENSG00000272414"))
-  filter(str_detect(gene_name, paste0(c("FAM47E", "STBD1"),
-                                      collapse = "|"))) %>% 
-  View()
-
-# Expression for BAG3 and LHX1
-BAG3.LHX1.exp = ggboxplot(dat.RPKM.filt %>% 
-                            dplyr::filter(gene_name %in% c("BAG3", "LHX1")),
-                          x = "Cond", 
-                          y = "RPKM", 
-                          add = "jitter", 
-                          fill = "Cond", 
-                          palette = c("#A9A9A9", "#B22222", "#DC143C", "#E9967A"),
-                          facet.by = "gene_name",
-                          xlab = "", 
-                          ylab = "Reads Per Kilobase Million (RPKM)") +
-  scale_x_discrete(labels = c("smNPC",
-                              expression("mDAN D15"),
-                              expression("mDAN D30"),
-                              expression("mDAN D50"))) +
-  theme(legend.position = "none",
-        axis.text.x = element_text(angle = 90))
-
-# Place the plot
-plotGG(plot = BAG3.LHX1.exp, 
-       x = 5.25, 
-       y = 0.625, 
-       width = 2, 
-       height = 3.5,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-# Add the transcription factor binding motif (TFBS) for LHX1
-pfm.LHX1 = getMatrixByID(JASPAR2020, 
-                         ID = "MA1518.1")
-LHX1 = new.env()
-
-LHX1$LHX1 = pfm.LHX1@profileMatrix
-
-LHX1 = as.list(LHX1)
-
-# Remove the nucleotide position
-LHX1_TFBS = ggseqlogo(LHX1) +
-  annotate("rect", 
-           xmin = 4.5, 
-           xmax = 5.5, 
-           ymin = -0.05, 
-           ymax = 2.5, 
-           alpha = .1, 
-           col = "black", 
-           fill = "#404788FF") +
-  theme(axis.text.x = element_blank())
-
-# Place the plot
-plotGG(plot = LHX1_TFBS, 
-       x = 1.7425, 
-       y = 2.625, 
-       width = 1.5, 
-       height = 1.5,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-# Add the SNP position that zoom in the TFBS
-SNP_param = pgParams(chrom = "chr10",
-                     chromstart = 119651405,
-                     chromend = 119651405,
-                     assembly = "hg38")
-
-annoHighlight(plot = ATAC_smNPC_I, 
-              params = SNP_param,
-              fill = "#404788FF",
-              y = 0.875, 
-              height = 1.75, 
-              just = c("left", "top"), 
-              default.units = "inches")
-
-annoZoomLines(plot = ATAC_smNPC_I, 
-              params = SNP_param,
-              y0 = 2.625, 
-              x1 = c(2.25, 3.25), 
-              y1 = 2.75, 
-              default.units = "inches")
-
-# text C
-plotText(label = "C", 
-         fontsize = 12,
-         fontfamily = "Helvetica",
-         x = 0.25, 
-         y = 4.25, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
-
-# ATACseq signal IDUA
-# 1st bio replicate smNPC
-bw.IDUA.smNPC_1 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/smNPC_I.bw"),
-                        chrom = "chr4",
-                        chromstart = 947008,
-                        chromend = 1027208)
-
-# 2nd bio replicate smNPC
-bw.IDUA.smNPC_2 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/smNPC_II.bw"),
-                        chrom = "chr4",
-                        chromstart = 947008,
-                        chromend = 1027208)
-
-# 3rd bio replicate smNPC
-bw.IDUA.smNPC_3 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/smNPC_III.bw"),
-                        chrom = "chr4",
-                        chromstart = 947008,
-                        chromend = 1027208)
-
-# 1st bio replicate TH positive neurons D15
-bw.IDUA.TH.pos_D15_1 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/D15_POS_I.bw"),
-                        chrom = "chr4",
-                        chromstart = 947008,
-                        chromend = 1027208)
-
-# 2nd bio replicate TH positive neurons D15
-bw.IDUA.TH.pos_D15_2 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/D15_POS_II.bw"),
-                        chrom = "chr4",
-                        chromstart = 947008,
-                        chromend = 1027208)
-
-# 3rd bio replicate TH positive neurons D15
-bw.IDUA.TH.pos_D15_3 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/D15_POS_III.bw"),
-                        chrom = "chr4",
-                        chromstart = 947008,
-                        chromend = 1027208)
-
-# 1st bio replicate TH positive neurons D30
-bw.IDUA.TH.pos_D30_1 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/D30_POS_I.bw"),
-                        chrom = "chr4",
-                        chromstart = 947008,
-                        chromend = 1027208)
-
-# 2nd bio replicate TH positive neurons D30
-bw.IDUA.TH.pos_D30_2 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/D30_POS_II.bw"),
-                        chrom = "chr4",
-                        chromstart = 947008,
-                        chromend = 1027208)
-
-# 3rd bio replicate TH positive neurons D30
-bw.IDUA.TH.pos_D30_3 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/D30_POS_III.bw"),
-                        chrom = "chr4",
-                        chromstart = 947008,
-                        chromend = 1027208)
-
-# 1st bio replicate TH positive neurons D50
-bw.IDUA.TH.pos_D50_1 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/HFFTHmCherry_D50_possort_S1.bw"),
-                        chrom = "chr4",
-                        chromstart = 947008,
-                        chromend = 1027208)
-
-# 2nd bio replicate TH positive neurons D50
-bw.IDUA.TH.pos_D50_2 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/HFFTHmCherry_D50_possort_S3.bw"),
-                        chrom = "chr4",
-                        chromstart = 947008,
-                        chromend = 1027208)
-
-# 3rd bio replicate TH positive neurons D50
-bw.IDUA.TH.pos_D50_3 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/HFFTHmCherry_D50_possort_S4.bw"),
-                        chrom = "chr4",
-                        chromstart = 947008,
-                        chromend = 1027208)
-
-# Add a scale next to the bigwig files - check the maximum to choose
-scale.IDUA.max = max(c(bw.IDUA.smNPC_1$score,
-                       bw.IDUA.smNPC_2$score,
-                       bw.IDUA.smNPC_3$score,
-                       bw.IDUA.TH.pos_D15_1$score,
-                       bw.IDUA.TH.pos_D15_2$score,
-                       bw.IDUA.TH.pos_D15_3$score,
-                       bw.IDUA.TH.pos_D30_1$score,
-                       bw.IDUA.TH.pos_D30_2$score,
-                       bw.IDUA.TH.pos_D30_3$score,
-                       bw.IDUA.TH.pos_D50_1$score,
-                       bw.IDUA.TH.pos_D50_2$score,
-                       bw.IDUA.TH.pos_D50_3$score))
-
-print(scale.IDUA.max)
-
-# Define parameters for the regions
-region.p.IDUA = pgParams(chrom = "chr4",
-                         chromstart = 947108,
-                         chromend = 1027108,
-                         assembly = "hg38",
-                         range = c(0, scale.IDUA.max))
-
-# Add the genomic label
-plotGenomeLabel(
-  chrom = "chr4",
-  chromstart = 947108,
-  chromend = 1027108,
-  assembly = "hg38",
-  x = 0.75,
-  y = 4.375,
-  length = 4.0,
-  default.units = "inches",
-  scale = "Mb")
-
-# ATACseq signal smNPC_I
-ATAC_smNPC_I_IDUA = plotSignal(
-  data = bw.IDUA.smNPC_1, 
-  params = region.p.IDUA,
-  fill = "#D3D3D3", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 4.625, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_smNPC_I_IDUA, 
-          at = c(0, scale.IDUA.max),
-          fontsize = 6)
-
-# ATACseq signal smNPC_II
-ATAC_smNPC_II_IDUA = plotSignal(
-  data = bw.IDUA.smNPC_2, 
-  params = region.p.IDUA,
-  fill = "#C0C0C0", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 4.625, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_smNPC_II_IDUA, 
-          at = c(0, scale.IDUA.max),
-          fontsize = 6)
-
-# Add the SNP position that zoom in the TFBS
-SNP_param_IDUA = pgParams(chrom = "chr4",
-                     chromstart = 987108,
-                     chromend = 987108,
-                     assembly = "hg38")
-
-annoHighlight(plot = ATAC_smNPC_I_IDUA, 
-              params = SNP_param_IDUA,
-              fill = "#404788FF",
-              y = 4.75, 
-              height = 1.875, 
-              just = c("left", "top"), 
-              default.units = "inches")
-
-annoZoomLines(plot = ATAC_smNPC_I_IDUA, 
-              params = SNP_param_IDUA,
-              y0 = 6.625, 
-              x1 = c(2.25, 3.25), 
-              y1 = 6.75, 
-              default.units = "inches")
-
-# ATACseq signal smNPC_III
-ATAC_smNPC_III_IDUA = plotSignal(
-  data = bw.IDUA.smNPC_3, 
-  params = region.p.IDUA,
-  fill = "#A9A9A9", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 4.625, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_smNPC_III_IDUA, 
-          at = c(0, scale.IDUA.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D15 I
-ATAC_TH.pos_D15_I_IDUA = plotSignal(
-  data = bw.IDUA.TH.pos_D15_1, 
-  params = region.p.IDUA,
-  fill = "#B22222", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 5.0, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D15_I_IDUA, 
-          at = c(0, scale.IDUA.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D15 II
-ATAC_TH.pos_D15_II_IDUA = plotSignal(
-  data = bw.IDUA.TH.pos_D15_2, 
-  params = region.p.IDUA,
-  fill = "#A52A2A", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 5.0, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D15_II_IDUA, 
-          at = c(0, scale.IDUA.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D15 III
-ATAC_TH.pos_D15_III_IDUA = plotSignal(
-  data = bw.IDUA.TH.pos_D15_3, 
-  params = region.p.IDUA,
-  fill = "#8B0000", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 5.0, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D15_III_IDUA, 
-          at = c(0, scale.IDUA.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D30 I
-ATAC_TH.pos_D30_I_IDUA = plotSignal(
-  data = bw.IDUA.TH.pos_D30_1, 
-  params = region.p.IDUA,
-  fill = "#FF6347", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 5.375, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D30_I_IDUA, 
-          at = c(0, scale.IDUA.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D30 II
-ATAC_TH.pos_D30_II_IDUA = plotSignal(
-  data = bw.IDUA.TH.pos_D30_2, 
-  params = region.p.IDUA,
-  fill = "#FF0000", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 5.375, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D30_II_IDUA, 
-          at = c(0, scale.IDUA.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D30 III
-ATAC_TH.pos_D30_III_IDUA = plotSignal(
-  data = bw.IDUA.TH.pos_D30_3, 
-  params = region.p.IDUA,
-  fill = "#DC143C", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 5.375, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D30_III_IDUA, 
-          at = c(0, scale.IDUA.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D50 I
-ATAC_TH.pos_D50_I_IDUA = plotSignal(
-  data = bw.IDUA.TH.pos_D50_1, 
-  params = region.p.IDUA,
-  fill = "#FFA07A", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 5.75, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D50_I_IDUA, 
-          at = c(0, scale.IDUA.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D50 II
-ATAC_TH.pos_D50_II_IDUA = plotSignal(
-  data = bw.IDUA.TH.pos_D50_2, 
-  params = region.p.IDUA,
-  fill = "#FA8072", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 5.75, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D50_II_IDUA, 
-          at = c(0, scale.IDUA.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D50 III
-ATAC_TH.pos_D50_III_IDUA = plotSignal(
-  data = bw.IDUA.TH.pos_D50_3, 
-  params = region.p.IDUA,
-  fill = "#E9967A", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 5.75, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D50_III_IDUA, 
-          at = c(0, scale.IDUA.max),
-          fontsize = 6)
-
-# Gene track
-plotGenes(chrom = "chr4",
-  chromstart = 947108,
-  chromend = 1027108,
-  assembly = assembly(Genome = "hg38refGene", 
-                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
-                      OrgDb = "org.Hs.eg.db"),
-  fontcolor = "black",
-  fill = "black",
-  x = 0.75,
-  y = 6.125,
-  width = 4.0,
-  height = 0.375,
-  just = c("left", "top"),
-  default.units = "inches")
-
-# Add the samples name
-plotText(label = "smNPC", 
-         fontsize = 6, 
-         fontcolor = "#A9A9A9",
-         fontfamily = "Helvetica",
-         x = 0.75, 
-         y = 4.625, 
-         just = c("left", "top"),
-         default.units = "inches",
-         fontface = "bold")
-
-plotText(label = "mDAN D15", 
-         fontsize = 6, 
-         fontcolor = "#B22222",
-         fontfamily = "Helvetica",
-         x = 0.75, 
-         y = 5.0, 
-         just = c("left", "top"),
-         default.units = "inches",
-         fontface = "bold")
-
-plotText(label = "mDAN D30", 
-         fontsize = 6, 
-         fontcolor = "#DC143C",
-         fontfamily = "Helvetica",
-         x = 0.75, 
-         y = 5.375, 
-         just = c("left", "top"),
-         default.units = "inches",
-         fontface = "bold")
-
-plotText(label = "mDAN D50", 
-         fontsize = 6, 
-         fontcolor = "#E9967A",
-         fontfamily = "Helvetica",
-         x = 0.75, 
-         y = 5.75, 
-         just = c("left", "top"),
-         default.units = "inches",
-         fontface = "bold")
-
-#### PANEL D - IDUA and ZBTB14 expression (RNAseq)
-# text D
-plotText(label = "D", 
-         fontsize = 12,
-         fontfamily = "Helvetica",
-         x = 5.0, 
-         y = 4.25, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
-
-IDUA.ZBTB14.exp = ggboxplot(dat.RPKM.filt %>% 
-                            dplyr::filter(gene_name %in% c("IDUA", "ZBTB14", "SLC26A1")) %>% 
-                              mutate(gene_name = factor(gene_name,
-                                                        levels = c("IDUA", "ZBTB14", "SLC26A1"))),
-                          x = "Cond", 
-                          y = "RPKM", 
-                          add = "jitter", 
-                          fill = "Cond", 
-                          palette = c("#A9A9A9", "#B22222", "#DC143C", "#E9967A"),
-                          facet.by = "gene_name",
-                          xlab = "", 
-                          ylab = "Reads Per Kilobase Million (RPKM)") +
-  scale_x_discrete(labels = c("smNPC",
-                              "mDAN D15",
-                              "mDAN D30",
-                              "mDAN D50")) +
-  theme(legend.position = "none",
-        axis.text.x = element_text(angle = 90))
-
-# Place the plot
-plotGG(plot = IDUA.ZBTB14.exp, 
-       x = 5.25, 
-       y = 4.25, 
-       width = 3, 
-       height = 3.5,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-# Add the transcription factor binding motif (TFBS) for ZBTB14
-pfm.ZBTB14 = getMatrixByID(JASPAR2020, 
-                         ID = "MA1650.1")
-ZBTB14 = new.env()
-
-ZBTB14$ZBTB14 = pfm.ZBTB14@profileMatrix
-
-ZBTB14 = as.list(ZBTB14)
-
-# Remove the nucleotide position
-ZBTB14_TFBS = ggseqlogo(ZBTB14) +
-  annotate("rect", 
-           xmin = 8.5, 
-           xmax = 9.5, 
-           ymin = -0.05, 
-           ymax = 2.5, 
-           alpha = .1, 
-           col = "black", 
-           fill = "#404788FF") +
-  theme(axis.text.x = element_blank())
-
-# Place the plot
-plotGG(plot = ZBTB14_TFBS, 
-       x = 1.6225, 
-       y = 6.625, 
-       width = 1.5, 
-       height = 1.5,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-# text E
-plotText(label = "E", 
-         fontsize = 12,
-         fontfamily = "Helvetica",
-         x = 0.25, 
-         y = 8.0, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
-
-# ATACseq signal SCARB2
-# 1st bio replicate smNPC
-bw.SCARB2.smNPC_1 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/smNPC_I.bw"),
-                        chrom = "chr4",
-                        chromstart = 76173617,
-                        chromend = 76253817)
-
-# 2nd bio replicate smNPC
-bw.SCARB2.smNPC_2 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/smNPC_II.bw"),
-                        chrom = "chr4",
-                        chromstart = 76173617,
-                        chromend = 76253817)
-
-# 3rd bio replicate smNPC
-bw.SCARB2.smNPC_3 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/smNPC_III.bw"),
-                        chrom = "chr4",
-                        chromstart = 76173617,
-                        chromend = 76253817)
-
-# 1st bio replicate TH positive neurons D15
-bw.SCARB2.TH.pos_D15_1 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/D15_POS_I.bw"),
-                        chrom = "chr4",
-                        chromstart = 76173617,
-                        chromend = 76253817)
-
-# 2nd bio replicate TH positive neurons D15
-bw.SCARB2.TH.pos_D15_2 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/D15_POS_II.bw"),
-                        chrom = "chr4",
-                        chromstart = 76173617,
-                        chromend = 76253817)
-
-# 3rd bio replicate TH positive neurons D15
-bw.SCARB2.TH.pos_D15_3 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/D15_POS_III.bw"),
-                        chrom = "chr4",
-                        chromstart = 76173617,
-                        chromend = 76253817)
-
-# 1st bio replicate TH positive neurons D30
-bw.SCARB2.TH.pos_D30_1 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/D30_POS_I.bw"),
-                        chrom = "chr4",
-                        chromstart = 76173617,
-                        chromend = 76253817)
-
-# 2nd bio replicate TH positive neurons D30
-bw.SCARB2.TH.pos_D30_2 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/D30_POS_II.bw"),
-                        chrom = "chr4",
-                        chromstart = 76173617,
-                        chromend = 76253817)
-
-# 3rd bio replicate TH positive neurons D30
-bw.SCARB2.TH.pos_D30_3 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/D30_POS_III.bw"),
-                        chrom = "chr4",
-                        chromstart = 76173617,
-                        chromend = 76253817)
-
-# 1st bio replicate TH positive neurons D50
-bw.SCARB2.TH.pos_D50_1 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/HFFTHmCherry_D50_possort_S1.bw"),
-                        chrom = "chr4",
-                        chromstart = 76173617,
-                        chromend = 76253817)
-
-# 2nd bio replicate TH positive neurons D50
-bw.SCARB2.TH.pos_D50_2 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/HFFTHmCherry_D50_possort_S3.bw"),
-                        chrom = "chr4",
-                        chromstart = 76173617,
-                        chromend = 76253817)
-
-# 3rd bio replicate TH positive neurons D50
-bw.SCARB2.TH.pos_D50_3 = readBigwig(file = paste0(bw.path, 
-                                      "BIGWIG/HFFTHmCherry_D50_possort_S4.bw"),
-                        chrom = "chr4",
-                        chromstart = 76173617,
-                        chromend = 76253817)
-
-# Add a scale next to the bigwig files - check the maximum to choose
-scale.SCARB2.max = max(c(bw.SCARB2.smNPC_1$score,
-                       bw.SCARB2.smNPC_2$score,
-                       bw.SCARB2.smNPC_3$score,
-                       bw.SCARB2.TH.pos_D15_1$score,
-                       bw.SCARB2.TH.pos_D15_2$score,
-                       bw.SCARB2.TH.pos_D15_3$score,
-                       bw.SCARB2.TH.pos_D30_1$score,
-                       bw.SCARB2.TH.pos_D30_2$score,
-                       bw.SCARB2.TH.pos_D30_3$score,
-                       bw.SCARB2.TH.pos_D50_1$score,
-                       bw.SCARB2.TH.pos_D50_2$score,
-                       bw.SCARB2.TH.pos_D50_3$score))
-
-print(scale.SCARB2.max)
-
-# Define parameters for the regions
-region.p.SCARB2 = pgParams(chrom = "chr4",
-                         chromstart = 76173717,
-                         chromend = 76253717,
-                         assembly = "hg38",
-                         range = c(0, scale.SCARB2.max))
-
-# Add the genomic label
-plotGenomeLabel(
-  chrom = "chr4",
-  chromstart = 76173717,
-  chromend = 76253717,
-  assembly = "hg38",
-  x = 0.75,
-  y = 8.125,
-  length = 4.0,
-  default.units = "inches",
-  scale = "Mb")
-
-# ATACseq signal smNPC_I
-ATAC_smNPC_I_SCARB2 = plotSignal(
-  data = bw.SCARB2.smNPC_1, 
-  params = region.p.SCARB2,
-  fill = "#D3D3D3", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 8.375, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_smNPC_I_SCARB2, 
-          at = c(0, scale.SCARB2.max),
-          fontsize = 6)
-
-# ATACseq signal smNPC_II
-ATAC_smNPC_II_SCARB2 = plotSignal(
-  data = bw.SCARB2.smNPC_2, 
-  params = region.p.SCARB2,
-  fill = "#C0C0C0", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 8.375, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_smNPC_II_SCARB2, 
-          at = c(0, scale.SCARB2.max),
-          fontsize = 6)
-
-# ATACseq signal smNPC_III
-ATAC_smNPC_III_SCARB2 = plotSignal(
-  data = bw.SCARB2.smNPC_3, 
-  params = region.p.SCARB2,
-  fill = "#A9A9A9", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 8.375, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_smNPC_III_SCARB2, 
-          at = c(0, scale.SCARB2.max),
-          fontsize = 6)
-
-# Add the SNP position that zoom in the TFBS
-SNP_param_SCARB2 = pgParams(chrom = "chr4",
-                     chromstart = 76213717,
-                     chromend = 76213717,
-                     assembly = "hg38")
-
-annoHighlight(plot = ATAC_smNPC_I_SCARB2, 
-              params = SNP_param_SCARB2,
-              fill = "#404788FF",
-              y = 8.375, 
-              height = 1.875, 
-              just = c("left", "top"), 
-              default.units = "inches")
-
-annoZoomLines(plot = ATAC_smNPC_I_SCARB2, 
-              params = SNP_param_SCARB2,
-              y0 = 10.25, 
-              x1 = c(2.25, 3.25), 
-              y1 = 10.5, 
-              default.units = "inches")
-
-# ATACseq signal TH positive neurons D15 I
-ATAC_TH.pos_D15_I_SCARB2 = plotSignal(
-  data = bw.SCARB2.TH.pos_D15_1, 
-  params = region.p.SCARB2,
-  fill = "#B22222", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 8.75, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D15_I_SCARB2, 
-          at = c(0, scale.SCARB2.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D15 II
-ATAC_TH.pos_D15_II_SCARB2 = plotSignal(
-  data = bw.SCARB2.TH.pos_D15_2, 
-  params = region.p.SCARB2,
-  fill = "#A52A2A", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 8.75, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D15_II_SCARB2, 
-          at = c(0, scale.SCARB2.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D15 III
-ATAC_TH.pos_D15_III_SCARB2 = plotSignal(
-  data = bw.SCARB2.TH.pos_D15_3, 
-  params = region.p.SCARB2,
-  fill = "#8B0000", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 8.75, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D15_III_SCARB2, 
-          at = c(0, scale.SCARB2.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D30 I
-ATAC_TH.pos_D30_I_SCARB2 = plotSignal(
-  data = bw.SCARB2.TH.pos_D30_1, 
-  params = region.p.SCARB2,
-  fill = "#FF6347", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 9.125, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D30_I_SCARB2, 
-          at = c(0, scale.SCARB2.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D30 II
-ATAC_TH.pos_D30_II_SCARB2 = plotSignal(
-  data = bw.SCARB2.TH.pos_D30_2, 
-  params = region.p.SCARB2,
-  fill = "#FF0000", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 9.125, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D30_II_SCARB2, 
-          at = c(0, scale.SCARB2.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D30 III
-ATAC_TH.pos_D30_III_SCARB2 = plotSignal(
-  data = bw.SCARB2.TH.pos_D30_3, 
-  params = region.p.SCARB2,
-  fill = "#DC143C", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 9.125, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D30_III_SCARB2, 
-          at = c(0, scale.SCARB2.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D50 I
-ATAC_TH.pos_D50_I_SCARB2 = plotSignal(
-  data = bw.SCARB2.TH.pos_D50_1, 
-  params = region.p.SCARB2,
-  fill = "#FFA07A", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 9.5, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D50_I_SCARB2, 
-          at = c(0, scale.SCARB2.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D50 II
-ATAC_TH.pos_D50_II_SCARB2 = plotSignal(
-  data = bw.SCARB2.TH.pos_D50_2, 
-  params = region.p.SCARB2,
-  fill = "#FA8072", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 9.5, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D50_II_SCARB2, 
-          at = c(0, scale.SCARB2.max),
-          fontsize = 6)
-
-# ATACseq signal TH positive neurons D50 III
-ATAC_TH.pos_D50_III_SCARB2 = plotSignal(
-  data = bw.SCARB2.TH.pos_D50_3, 
-  params = region.p.SCARB2,
-  fill = "#E9967A", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 9.5, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = ATAC_TH.pos_D50_III_SCARB2, 
-          at = c(0, scale.SCARB2.max),
-          fontsize = 6)
-
-# Gene track
-plotGenes(
-  chrom = "chr4",
-  chromstart = 76173717,
-  chromend = 76253717,
-  assembly = assembly(Genome = "hg38refGene", 
-                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
-                      OrgDb = "org.Hs.eg.db"),
-  fontcolor = "black",
-  fill = "black",
-  x = 0.75,
-  y = 9.875,
-  width = 4.0,
-  height = 0.375,
-  just = c("left", "top"),
-  default.units = "inches")
-
-# Add the samples name
-plotText(label = "smNPC", 
-         fontsize = 6, 
-         fontcolor = "#A9A9A9",
-         fontfamily = "Helvetica",
-         x = 0.75, 
-         y = 8.375, 
-         just = c("left", "top"),
-         default.units = "inches",
-         fontface = "bold")
-
-plotText(label = "mDAN D15", 
-         fontsize = 6, 
-         fontcolor = "#B22222",
-         fontfamily = "Helvetica",
-         x = 0.75, 
-         y = 8.75, 
-         just = c("left", "top"),
-         default.units = "inches",
-         fontface = "bold")
-
-plotText(label = "mDAN D30", 
-         fontsize = 6, 
-         fontcolor = "#DC143C",
-         fontfamily = "Helvetica",
-         x = 0.75, 
-         y = 9.125, 
-         just = c("left", "top"),
-         default.units = "inches",
-         fontface = "bold")
-
-plotText(label = "mDAN D50", 
-         fontsize = 6, 
-         fontcolor = "#E9967A",
-         fontfamily = "Helvetica",
-         x = 0.75, 
-         y = 9.5, 
-         just = c("left", "top"),
-         default.units = "inches",
-         fontface = "bold")
-
-# text F
-plotText(label = "F", 
-         fontsize = 12,
-         fontfamily = "Helvetica",
-         x = 5.0, 
-         y = 8.0, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
-
-SCARB2.NR2C2.exp = ggboxplot(dat.RPKM.filt %>% 
-                            dplyr::filter(gene_name %in% c("SCARB2", "NR2C2", "FAM47E")) %>% 
-                              mutate(gene_name = factor(gene_name,
-                                                        levels = c("SCARB2", "NR2C2", "FAM47E"))),
-                          x = "Cond", 
-                          y = "RPKM", 
-                          add = "jitter", 
-                          fill = "Cond", 
-                          palette = c("#A9A9A9", "#B22222", "#DC143C", "#E9967A"),
-                          facet.by = "gene_name",
-                          xlab = "", 
-                          ylab = "Reads Per Kilobase Million (RPKM)") +
-  scale_x_discrete(labels = c("smNPC",
-                              "mDAN D15",
-                              "mDAN D30",
-                              "mDAN D50")) +
-  theme(legend.position = "none",
-        axis.text.x = element_text(angle = 90))
-
-# Place the plot
-plotGG(plot = SCARB2.NR2C2.exp, 
-       x = 5.25, 
-       y = 7.875, 
-       width = 3, 
-       height = 3.5,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-# Add the transcription factor binding motif (TFBS) for NR2C2
-pfm.NR2C2 = getMatrixByID(JASPAR2020, 
-                         ID = "MA1536.1")
-
-# Reverse to position weight matrix as the SNP is on the reverse strand
-pfm.NR2C2 = reverseComplement(pfm.NR2C2)
-
-NR2C2 = new.env()
-
-NR2C2$NR2C2 = pfm.NR2C2@profileMatrix
-
-NR2C2 = as.list(NR2C2)
-
-# Remove nucleotide
-NR2C2_TFBS = ggseqlogo(NR2C2) +
-  annotate("rect", 
-           xmin = 3.5, 
-           xmax = 4.5, 
-           ymin = -0.05, 
-           ymax = 2.0, 
-           alpha = .1, 
-           col = "black", 
-           fill = "#404788FF") +
-  theme(axis.text.x = element_blank())
-
-# Place the plot
-plotGG(plot = NR2C2_TFBS, 
-       x = 1.8475, 
-       y = 10.375, 
-       width = 1.5, 
-       height = 1.5,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-dev.off()
-```
-
-### FIGURE 3
-```{r fig3, eval = FALSE, echo = TRUE}
-########## FIGURE 3 ##########
-##############################
-# Save as a PDF and as TIF
-pdf("/home/vagrant/Manuscript_1/FIGURE3/FIGURE3.pdf",
-    paper = "a4",
-    family = "Helvetica")
-
-# Save as TIFF, 300 dpi
-tiff("/home/vagrant/Manuscript_1/FIGURE3/FIGURE3.tiff",
-     width = 8.27,
-     height = 11.67,
-     units = "in",
-     res = 300,
-     compression = "lzw")
-
-# Create a A4 blank page
-pageCreate(width = 8.27, 
-           height = 11.67, 
-           default.units = "inches",
-           showGuides = FALSE)
-
-# text Figure 3
-plotText(label = "Figure 3", 
-         fontsize = 14,
-         fontface = "bold",
-         fontfamily = "Helvetica",
-         x = 0.25, 
-         y = 0.25, 
-         just = "left", 
-         default.units = "inches")
-
-#### PANEL A - Scheme of transduction for knockdown and luciferase
-# text A
-plotText(label = "A", 
-         fontsize = 12,
-         fontface = "bold",
-         fontfamily = "Helvetica",
-         x = 0.25, 
-         y = 0.5, 
-         just = "left", 
-         default.units = "inches")
-
-# Fig3A
-fig3A = readPNG("/home/vagrant/Manuscript_1/FIGURE3/Fig3A_BIORENDER.png")
-#fig3A = readPNG("/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE3/Fig3A_BIORENDER.png")
-
-plotRaster(image = fig3A,
-           x = 0.25, 
-           y = 1, 
-           width = 8.0, 
-           height = 1.0, 
-           just = "left",
-           interpolate = TRUE)
-
-#### PANEL B - luciferase barplots with statistics
-# text B
-plotText(label = "B", 
-         fontsize = 12,
-         fontface = "bold",
-         fontfamily = "Helvetica",
-         x = 0.25, 
-         y = 2.0, 
-         just = "left", 
-         default.units = "inches")
-
-Gluc_signal = tibble(Sample = c("BAG3-WT", "BAG3-MUT", "IDUA-WT", "IDUA-MUT", "SCARB2-WT", "SCARB2-MUT", "miniCMV", "Neg_CTRL"),
-                     GLUC_n1_rep1 = c(319, 240, 154, 196, 379, 211, 431, 33),
-                     GLUC_n1_rep2 = c(323, 237, 161, 205, 371, 224, 459, 33),
-                     GLUC_n2_rep1 = c(201, 143, 121, 128, 278, 172, 253, 31),
-                     GLUC_n2_rep2 = c(191, 149, 119, 126, 278, 162, 249, 31),
-                     GLUC_n3_rep1 = c(249, 146, 136, 142, 223, 175, 212, 32),
-                     GLUC_n3_rep2 = c(203, 152, 121, 125, 209, 168, 190, 33),
-                     GLUC_n4_rep1 = c(348, 333, 220, 185, 396, 244, 319, 31),
-                     GLUC_n4_rep2 = c(322, 306, 229, 186, 369, 227, 294, 32),
-                     SEAP_n1_rep1 = c(72, 78, 54, 67, 99, 75, 128, 32),
-                     SEAP_n1_rep2 = c(69, 70, 49, 66, 97, 79, 132, 29),
-                     SEAP_n2_rep1 = c(50, 52, 45, 45, 76, 64, 80, 32),
-                     SEAP_n2_rep2 = c(50, 52, 45, 51, 85, 63, 80, 32),
-                     SEAP_n3_rep1 = c(52, 50, 43, 50, 66, 55, 68, 32),
-                     SEAP_n3_rep2 = c(49, 53, 48, 46, 66, 62, 69, 31),
-                     SEAP_n4_rep1 = c(64, 75, 58, 54, 103, 75, 111, 33),
-                     SEAP_n4_rep2 = c(61, 74, 62, 56, 108, 77, 111, 31)) %>% 
-  pivot_longer(!Sample, names_to = "Meas", values_to = "Abs_val") %>% 
-  mutate(Meas2 = gsub("^([^_]*_[^_]*)_.*", "\\1", Meas)) %>% 
-  group_by(Sample, Meas2) %>% 
-  mutate(AVG = mean(Abs_val, na.rm = TRUE))
-
-# Calculate ratio Gluc over SEAP
-Gluc_signal_ratio = Gluc_signal %>% 
-  dplyr::select(-Meas, -Abs_val) %>% 
-  distinct(Meas2, .keep_all = TRUE) %>% 
-  pivot_wider(names_from = "Meas2", values_from = "AVG") %>% 
-  mutate(Ratio_within_bio_rep1 = GLUC_n1/SEAP_n1,
-         Ratio_within_bio_rep2 = GLUC_n2/SEAP_n2,
-         Ratio_within_bio_rep3 = GLUC_n3/SEAP_n3,
-         Ratio_within_bio_rep4 = GLUC_n4/SEAP_n4) %>% 
-  dplyr::select(Sample, Ratio_within_bio_rep1:Ratio_within_bio_rep4) %>% 
-  pivot_longer(cols = c("Ratio_within_bio_rep1", "Ratio_within_bio_rep2", "Ratio_within_bio_rep3",
-                        "Ratio_within_bio_rep4"),
-               names_to = "Ratio",
-               values_to = "value") %>% 
-  mutate(Genes = gsub("(.*)-.*", "\\1", Sample))
-
-# Calculate statistics - T-test
-GLUC_stat = compare_means(value ~ Sample,
-                          data = Gluc_signal_ratio %>% 
-                            ungroup(),
-                          method = "t.test")
-
-# Plot for BAG3
-GLUC_BAG3 = ggbarplot(Gluc_signal_ratio %>% 
-                        dplyr::filter(Sample %in% c("BAG3-WT",
-                                                     "BAG3-MUT",
-                                                     "miniCMV",
-                                                     "Neg_CTRL")), 
-                      x = "Sample", 
-                      y = "value",
-                      width = 0.25,
-                      add = c("mean_se", 
-                              "jitter"),
-                      fill = "grey",
-                      xlab = "",
-                      ylab = "Ratio Gluc/SEAP",
-                      position = position_dodge(0.9)) +
-  theme(legend.position = "none",
-        axis.text.x = element_text(angle = 90, hjust = 1.0, size = 9, face = "bold", family = "Helvetica"),
-        axis.text.y = element_text(size = 9, face = "bold"),
-        axis.title.y = element_text(size = 10, face = "bold")) +
-  scale_y_continuous(expand = c(0, 0),
-                     limits = c(0, 6.0)) +
-  scale_x_discrete(labels = c("BAG3 other allele",
-                              "BAG3 effect allele",
-                              "Positive control",
-                              "Negative control")) +
-  stat_pvalue_manual(GLUC_stat %>% 
-                       dplyr::filter(group1 == "BAG3-WT",
-                              group2 == "BAG3-MUT"),
-                     label = "p = {p.format}",
-                     y.position = 5.6,
-                     size = 3.0)
-
-# Place the plot
-plotGG(plot = GLUC_BAG3, 
-       x = 0.50, 
-       y = 2.25, 
-       width = 2, 
-       height = 4.25,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-# Plot for IDUA
-GLUC_IDUA = ggbarplot(Gluc_signal_ratio %>% 
-                        dplyr::filter(Sample %in% c("IDUA-WT",
-                                                    "IDUA-MUT",
-                                                    "miniCMV",
-                                                    "Neg_CTRL")), 
-                      x = "Sample", 
-                      y = "value",
-          width = 0.25,
-          add = c("mean_se", 
-                  "jitter"),
-          fill = "grey",
-          xlab = "",
-          ylab = "Ratio Gluc/SEAP",
-          position = position_dodge(0.9)) +
-  theme(legend.position = "none",
-        axis.text.x = element_text(angle = 90, hjust = 1.0, size = 9, face = "bold"),
-        axis.text.y = element_text(size = 9, face = "bold"),
-        axis.title.y = element_text(size = 10, face = "bold")) +
-  scale_x_discrete(labels = c("IDUA other allele",
-                              "IDUA effect allele",
-                              "Positive control",
-                              "Negative control")) +
-  scale_y_continuous(expand = c(0, 0),
-                     limits = c(0, 6.0)) +
-  stat_pvalue_manual(GLUC_stat %>% 
-                       dplyr::filter(group1 == "IDUA-WT",
-                              group2 == "IDUA-MUT"),
-                     label = "p = {p.format}",
-                     y.position = 4.0,
-                     size = 3.0)
-
-# Place the plot
-plotGG(plot = GLUC_IDUA, 
-       x = 3.0, 
-       y = 2.25, 
-       width = 2, 
-       height = 4.25,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-# Plot for SCARB2
-GLUC_SCARB2 = ggbarplot(Gluc_signal_ratio %>% 
-                          dplyr::filter(Sample %in% c("SCARB2-WT",
-                                                     "SCARB2-MUT",
-                                                     "miniCMV",
-                                                     "Neg_CTRL")), 
-                        x = "Sample", 
-                        y = "value",
-          width = 0.25,
-          add = c("mean_se", 
-                  "jitter"),
-          fill = "grey",
-          xlab = "",
-          ylab = "Ratio Gluc/SEAP",
-          position = position_dodge(0.9)) +
-  theme(legend.position = "none",
-        axis.text.x = element_text(angle = 90, hjust = 1.0, size = 9, face = "bold"),
-        axis.text.y = element_text(size = 9, face = "bold"),
-        axis.title.y = element_text(size = 10, face = "bold")) +
-  scale_x_discrete(labels = c("SCARB2 other allele",
-                              "SCARB2 effect allele",
-                              "Positive control",
-                              "Negative control")) +
-  scale_y_continuous(expand = c(0, 0),
-                     limits = c(0, 6.0)) +
-  stat_pvalue_manual(GLUC_stat %>% 
-                       dplyr::filter(group1 == "SCARB2-WT",
-                              group2 == "SCARB2-MUT"),
-                     label = "p = {p.format}",
-                     y.position = 4.0,
-                      size = 3.0)
-
-# Place the plot
-plotGG(plot = GLUC_SCARB2, 
-       x = 5.5, 
-       y = 2.25, 
-       width = 2, 
-       height = 4.25,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-#### PANEL C - knockdown barplots with statistics
-# text C
-plotText(label = "C", 
-         fontsize = 12,
-         fontfamily = "Helvetica",
-         x = 0.25, 
-         y = 6.75, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
-
-# Knockdown of LHX1 and quantification of LHX1 and BAG3 expression 3 days post transduction
-KD.BAG3.LHX1.3days = tibble(Sple = rep("shLHX1", 6),
-                            Gene = c(rep("LHX1", 3),
-                                     rep("BAG3", 3)),
-                            Exp = c(0.411253539,
-                                    0.359459217,
-                                    0.367190337,
-                                    0.972688658,
-                                    0.965902853,
-                                    0.88813445))
-
-# Stats
-KD.BAG3.LHX1.3days.stats = tibble(Sple = c(rep("shLHX1", 6),
-                                           rep("shCTRL", 6)),
-                                  Gene = rep(c(rep("LHX1", 3),
-                                           rep("BAG3", 3)), 2),
-                                  Exp = c(9.5167,
-                                          8.39675,
-                                          8.1855,
-                                          9.13605,
-                                          8.33795,
-                                          8.76415,
-                                          8.2348,
-                                          6.92065,
-                                          6.7401,
-                                          9.0961,
-                                          8.2879,
-                                          8.593))
-
-stat_LHX1.KD = compare_means(Exp ~ Sple,
-                          data = KD.BAG3.LHX1.3days.stats,
-                          group.by = "Gene",
-                          method = "t.test",
-                          paired = TRUE)
-# Plot
-pl.KD_BAG3_LHX1 = KD.BAG3.LHX1.3days %>% 
-  mutate(Gene = factor(Gene, levels = c("LHX1", "BAG3"))) %>% 
-  ggbarplot(.,
-            x = "Gene",
-            y = "Exp",
-            fill = c("Gene"),
-            position = position_dodge(0.9),
-            palette = c("#440154FF", "#287C8EFF"),
-            add = c("mean_se", "jitter"),
-            xlab = "",
-            ylab = "Relative expression to shSCRAMBLE",
-            title = "shLHX1 - 3 days") +
-  geom_hline(yintercept = 1.0, lty = "dashed", color = "black") +
-  theme(axis.title.y = element_text(face = "bold", size = 10),
-        axis.text.x = element_text(face = "bold.italic", size = 10, angle = 90, family = "Helvetica"),
-        axis.text.y = element_text(face = "bold", size = 10),
-        legend.position = "none",
-        plot.title = element_text(face = "bold", size = 10, hjust = 0.5)) +
-  scale_y_continuous(expand = c(0, 0),
-                     limits = c(0, 1.8)) +
-  stat_pvalue_manual(stat_LHX1.KD,
-                     label = "p = {p.format}",
-                     x = "Gene",
-                     y.position = c(0.5, 1.2),
-                     size = 3.0,
-                     hide.ns = FALSE)
-
-plotGG(plot = pl.KD_BAG3_LHX1, 
-       x = 0.5, 
-       y = 7.0, 
-       width = 1.75, 
-       height = 4.25,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-# Knockdown of ZBTB14 and quantification of ZBTB14 and IDUA expression 3 days post transduction
-KD.IDUA.ZBTB14.3days = tibble(Sple = rep("shZBTB14", 6),
-                            Gene = c(rep("ZBTB14", 3),
-                                     rep("IDUA", 3)),
-                            Exp = c(0.334134302,
-                                    0.316834205,
-                                    0.294206291,
-                                    0.663813558,
-                                    1.259979272,
-                                    1.774054093))
-
-# Stats
-KD.IDUA.ZBTB14.3days.stats = tibble(Sple = c(rep("shZBTB14", 6),
-                                           rep("shCTRL", 6)),
-                                  Gene = rep(c(rep("ZBTB14", 3),
-                                           rep("IDUA", 3)), 2),
-                                  Exp = c(11.39125,
-                                          10.4813,
-                                          10.5062,
-                                          11.56275,
-                                          10.1455,
-                                          9.76485,
-                                          9.80975,
-                                          8.8231,
-                                          8.7411,
-                                          10.9716,
-                                          10.4789,
-                                          10.5919))
-
-stat_ZBTB14.KD = compare_means(Exp ~ Sple,
-                          data = KD.IDUA.ZBTB14.3days.stats,
-                          group.by = "Gene",
-                          method = "t.test",
-                          paired = TRUE)
-
-# Plot
-pl.KD_IDUA_ZBTB14 = KD.IDUA.ZBTB14.3days %>% 
-  mutate(Gene = factor(Gene, levels = c("ZBTB14", "IDUA"))) %>% 
-  ggbarplot(.,
-            x = "Gene",
-            y = "Exp",
-            fill = c("Gene"),
-            position = position_dodge(0.9),
-            palette = c("#440154FF", "#287C8EFF"),
-            add = c("mean_se", "jitter"),
-            xlab = "",
-            ylab = "Relative expression to shSCRAMBLE",
-            title = "shZBTB14 - 3 days") +
-  geom_hline(yintercept = 1.0, lty = "dashed", color = "black") +
-  theme(axis.title.y = element_text(face = "bold", size = 10),
-        axis.text.x = element_text(face = "bold.italic", size = 10, angle = 90, family = "Helvetica"),
-        axis.text.y = element_text(face = "bold", size = 10),
-        legend.position = "none",
-        plot.title = element_text(face = "bold", size = 10, hjust = 0.5)) +
-  scale_y_continuous(expand = c(0, 0),
-                     limits = c(0, 1.9)) +
-  stat_pvalue_manual(stat_ZBTB14.KD,
-                     label = "p = {p.format}",
-                     x = "Gene",
-                     y.position = c(0.5, 1.6),
-                     size = 3.0,
-                     hide.ns = FALSE)
-
-plotGG(plot = pl.KD_IDUA_ZBTB14, 
-       x = 2.375, 
-       y = 7.0, 
-       width = 1.75, 
-       height = 4.25,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-# Knockdown of NR2C2 and quantification of NR2C2 and SCARB2 expression 3 days post transduction
-KD.SCARB2.NR2C2.3days = tibble(Sple = rep("shNR2C2", 6),
-                            Gene = c(rep("NR2C2", 3),
-                                     rep("SCARB2", 3)),
-                            Exp = c(0.345210918,
-                                    0.512864636,
-                                    0.548665969,
-                                    1.239922544,
-                                    1.130295504,
-                                    1.170885498))
-
-# Stats
-KD.SCARB2.NR2C2.3days.stats = tibble(Sple = c(rep("shNR2C2", 6),
-                                           rep("shCTRL", 6)),
-                                  Gene = rep(c(rep("NR2C2", 3),
-                                           rep("SCARB2", 3)), 2),
-                                  Exp = c(9.43575,
-                                          9.3043,
-                                          9.263,
-                                          5.6841,
-                                          5.92295,
-                                          5.9289,
-                                          7.9013,
-                                          8.34095,
-                                          8.397,
-                                          5.99435,
-                                          6.09965,
-                                          6.1565))
-
-stat_NR2C2.KD = compare_means(Exp ~ Sple,
-                          data = KD.SCARB2.NR2C2.3days.stats,
-                          group.by = "Gene",
-                          method = "t.test",
-                          paired = TRUE)
-
-# Plot
-pl.KD_SCARB2_NR2C2 = KD.SCARB2.NR2C2.3days %>% 
-  mutate(Gene = factor(Gene, levels = c("NR2C2", "SCARB2"))) %>% 
-  ggbarplot(.,
-            x = "Gene",
-            y = "Exp",
-            fill = c("Gene"),
-            position = position_dodge(0.9),
-            palette = c("#440154FF", "#287C8EFF"),
-            add = c("mean_se", "jitter"),
-            xlab = "",
-            ylab = "Relative expression to shSCRAMBLE",
-            title = "shNR2C2 - 3 days") +
-  geom_hline(yintercept = 1.0, lty = "dashed", color = "black") +
-  theme(axis.title.y = element_text(face = "bold", size = 10),
-        axis.text.x = element_text(face = "bold.italic", size = 10, angle = 90, family = "Helvetica"),
-        axis.text.y = element_text(face = "bold", size = 10),
-        legend.position = "none",
-        plot.title = element_text(face = "bold", size = 10, hjust = 0.5)) +
-  scale_y_continuous(expand = c(0, 0),
-                     limits = c(0, 1.8)) +
-  stat_pvalue_manual(stat_NR2C2.KD,
-                     label = "p = {p.format}",
-                     x = "Gene",
-                     y.position = c(0.65, 1.5),
-                     size = 3.0,
-                     hide.ns = FALSE)
-
-plotGG(plot = pl.KD_SCARB2_NR2C2, 
-       x = 4.25, 
-       y = 7.0, 
-       width = 1.75, 
-       height = 4.25,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-# Knockdown of NR2C2 and quantification of NR2C2 and SCARB2 expression 6 days post transduction
-KD.SCARB2.NR2C2.6days = tibble(Sple = rep("shNR2C2", 6),
-                            Gene = c(rep("NR2C2", 3),
-                                     rep("SCARB2", 3)),
-                            Exp = c(0.662710186,
-                                    0.456029798,
-                                    0.787662775,
-                                    1.410640142,
-                                    1.425976296,
-                                    1.332143962))
-
-# Stats
-KD.SCARB2.NR2C2.6days.stats = tibble(Sple = c(rep("shNR2C2", 6),
-                                           rep("shCTRL", 6)),
-                                  Gene = rep(c(rep("NR2C2", 3),
-                                           rep("SCARB2", 3)), 2),
-                                  Exp = c(8.34355,
-                                          9.0917,
-                                          8.32445,
-                                          5.3595,
-                                          5.19535,
-                                          6.5266,
-                                          7.75,
-                                          7.9589,
-                                          7.9801,
-                                          5.85585,
-                                          5.7073,
-                                          6.94035))
-
-stat_NR2C2.KD.6days = compare_means(Exp ~ Sple,
-                          data = KD.SCARB2.NR2C2.6days.stats,
-                          group.by = "Gene",
-                          method = "t.test",
-                          paired = TRUE)
-
-# Plot
-pl.KD_SCARB2_NR2C2_6days = KD.SCARB2.NR2C2.6days %>% 
-  mutate(Gene = factor(Gene, levels = c("NR2C2", "SCARB2"))) %>% 
-  ggbarplot(.,
-            x = "Gene",
-            y = "Exp",
-            fill = c("Gene"),
-            position = position_dodge(0.9),
-            palette = c("#440154FF", "#287C8EFF"),
-            add = c("mean_se", "jitter"),
-            xlab = "",
-            ylab = "Relative expression to shSCRAMBLE",
-            title = "shNR2C2 - 6 days") +
-  geom_hline(yintercept = 1.0, lty = "dashed", color = "black") +
-  theme(axis.title.y = element_text(face = "bold", size = 10),
-        axis.text.x = element_text(face = "bold.italic", size = 10, angle = 90, family = "Helvetica"),
-        axis.text.y = element_text(face = "bold", size = 10),
-        legend.position = "none",
-        plot.title = element_text(face = "bold", size = 10, hjust = 0.5)) +
-  scale_y_continuous(expand = c(0, 0),
-                     limits = c(0, 1.8)) +
-  stat_pvalue_manual(stat_NR2C2.KD.6days,
-                     label = "p = {p.format}",
-                     x = "Gene",
-                     y.position = c(0.85, 1.5),
-                     size = 3.0,
-                     hide.ns = FALSE)
-
-plotGG(plot = pl.KD_SCARB2_NR2C2_6days, 
-       x = 6.125, 
-       y = 7.0, 
-       width = 1.75, 
-       height = 4.25,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-dev.off()
-```
-
-### FIGURE 4
-Allelic imbalance at rs1465922 in ATACseq of differentiated TH REP1 cell line.  
-```{bash, eval = FALSE, echo = TRUE}
-# Copy the ATACseq BAM locally 
-rsync -avzPhu --no-p iris-cluster://work/projects/epifunc/merged_bam/ /Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE4/
-```
-
-Within R
-```{r, eval = FALSE, echo = TRUE}
-# Since TH REP1 cell line is heterozygous for rs1465922 check around that position for chromatin allelic imbalance in ATACseq data
-# hg38
-searchArea = GRanges(seqnames = c("chr4"), 
-                     ranges = IRanges(start = c(76213716), 
-                                      end = c(76213726)))
-
-# Path where the ATACseq BAM files are
-pathToFiles = "/home/vagrant/Manuscript_1/FIGURE4/"
-
-# Import a specific region (10bp around rs1465922) from the BAM files
-reads = impBamGAL(pathToFiles, 
-                  searchArea, 
-                  verbose = TRUE)
-
-# Identify the position of rs1465922 in the BAM files
-heterozygotePositions = scanForHeterozygotes(reads, 
-                                             verbose = TRUE)
-
-# Count the number of reads for the 2 different alleles at that position
-countList = getAlleleCounts(reads, 
-                            heterozygotePositions, 
-                            verbose = FALSE)
-
-# Save as a rds file for loading later if necessary
-saveRDS(countList, 
-        file = "/home/vagrant/Manuscript_1/FIGURE4/SCARB2_het_counts_THREP1_ATACseq.rds")
-```
-
-```{r fig4, eval = FALSE, echo = TRUE}
-########## FIGURE 4 ##########
-##############################
-# Save as a PDF
-pdf("/home/vagrant/Manuscript_1/FIGURE4/FIGURE4.pdf",
-    width = 8.3, 
-    height = 11.7)
-
-# Save as TIFF, 300 dpi
-tiff("/home/vagrant/Manuscript_1/FIGURE4/FIGURE4.tiff",
-     width = 8.27,
-     height = 11.67,
-     units = "in",
-     res = 300,
-     compression = "lzw")
-
-# Create a A4 blank page
-pageCreate(width = 8.27, 
-           height = 11.67, 
-           default.units = "inches",
-           showGuides = FALSE)
-
-plotText(label = "Figure 4", 
-         fontsize = 14,
-         fontface = "bold",
-         fontfamily = "Helvetica",
-         x = 0.25, 
-         y = 0.25, 
-         just = "left", 
-         default.units = "inches")
-
-#### PANEL A - Chromatin imbalance in TH REP1 mCHERRY cell line at rs1465922 
-# text A
-plotText(label = "A", 
-         fontsize = 12,
-         fontface = "bold",
-         fontfamily = "Helvetica",
-         x = 0.25, 
-         y = 0.5, 
-         just = "left", 
-         default.units = "inches")
-
-# Chromatin imbalance values as calculated by the AllelicImbalance R package
-countList = readRDS("/home/vagrant/Manuscript_1/FIGURE4/SCARB2_het_counts_THREP1_ATACseq.rds")
-
-# Extract and reformat for positively sorted TH population
-AI_ATAC = countList$chr4_76213717 %>% 
-  as_tibble() %>% 
-  mutate(Sample = rownames(countList$chr4_76213717)) %>% 
-  pivot_longer(cols = c(A, C, G, T), names_to = "Base", values_to = "Reads") %>% 
-  mutate(Sample.n = case_when(str_detect(Sample, "astrocytes") ~ "Astrocytes",
-                              str_detect(Sample, "D15_neg") ~ "Negative DAN D15",
-                              str_detect(Sample, "D15_pos") ~ "mDAN D15",
-                              str_detect(Sample, "D30_pos") ~ "mDAN D30",
-                              str_detect(Sample, "D50_neg") ~ "Negative DAN D50",
-                              str_detect(Sample, "D50_pos") ~ "mDAN D50",
-                              TRUE ~ "smNPCs")) %>% 
-  dplyr::filter(!str_detect(Sample, "neg"),
-                Base %in% c("A", "G")) %>% 
-  mutate(Sample.n = factor(Sample.n,
-                           levels = c("smNPCs",
-                                      "mDAN D15",
-                                      "mDAN D30",
-                                      "mDAN D50",
-                                      "Astrocytes")),
-         Allele = case_when(Base == "A" ~ "PD allele",
-                            TRUE ~ "Other allele"))
-
-# Plot
-chrom_AI = ggplot(AI_ATAC,
-                  aes(Sample.n, 
-                      Reads, 
-                      fill = interaction(Sample.n, Base)), 
-                  alpha = Base) +
-  geom_bar(stat = "identity",
-           position = "dodge",
-           width = 0.5,
-           colour = "black") +
-  geom_text(aes(label = format(c(paste0("p = ",
-                                        0.3),
-                          "",
-                          paste0("p = ",
-                                 0.3),
-                          "",
-                          paste0("p = ",
-                                 0.003),
-                          "",
-                          paste0("p = ",
-                                 0.0000003),
-                          "",
-                          paste0("p = ",
-                                 0.2),
-                          ""),
-                          scientific = TRUE),
-                 y = Reads + 100),
-            vjust = 0) +
-  scale_fill_manual(aesthetics = "fill",
-                    values = c("#D3D3D3",
-                               "#B22222",
-                               "#FF6347",
-                               "#FFA07A",
-                               "#b8627db2",
-                               "#C0C0C0",
-                               "#A52A2A",
-                               "#FF0000",
-                               "#FA8072",
-                               "#cc6a70b2")) +
-  coord_flip() +
-  theme_classic() +
-  scale_y_continuous(expand = c(0, 0),
-                     limits = c(0, 330)) +
-  xlab("") +
-  theme(axis.text = element_text(face = "bold", colour = "black"),
-        axis.title.x = element_text(face = "bold", colour = "black"),
-        legend.position = "none") 
-#######################################################################
-
-ggplot(AI_ATAC,
-       aes(Allele, 
-           Reads,
-           fill = Sample.n,
-           alpha = Base)) +
-  # geom_col(position = position_dodge(),
-  #          width = 1.0,
-  #          colour = "black") +
-  geom_bar(stat = "identity",
-           position = "dodge",
-           width = 0.5,
-           colour = "black") +
-  facet_wrap(~Sample.n,
-             strip.position = "bottom") +
-  theme_classic() +
-  theme(strip.placement = "outside") +
-  scale_fill_manual(values = c("#A9A9A9",
-                               "#B22222",
-                               "#DC143C", 
-                               "#E9967A",
-                               "#CC6A70B2")) +
-  scale_y_continuous(expand = c(0, 0),
-                     limits = c(0, 330)) +
-  theme(legend.position = "none") +
-  xlab("") +
-  #coord_flip()
-  geom_text(aes(label = format(c(0.3,
-                          "",
-                          0.3,
-                          "",
-                          0.003,
-                          "",
-                          0.0000003,
-                          "",
-                          0.2,
-                          ""),
-                          scientific = TRUE),
-                 y = Reads + 100),
-            vjust = 0) +
-  scale_fill_manual(aesthetics = "fill",
-                    values = c("#D3D3D3",
-                               "#B22222",
-                               "#FF6347",
-                               "#FFA07A",
-                               "#b8627db2",
-                               "#C0C0C0",
-                               "#A52A2A",
-                               "#FF0000",
-                               "#FA8072",
-                               "#cc6a70b2")) +
-  coord_flip() +
-  theme_classic() +
-  scale_y_continuous(expand = c(0, 0),
-                     limits = c(0, 330)) +
-  xlab("") +
-  theme(axis.text = element_text(face = "bold", colour = "black"),
-        axis.title.x = element_text(face = "bold", colour = "black"),
-        legend.position = "none")
-
-AI_ATAC = AI_ATAC %>%
-  mutate(term.i = as.factor(paste(Sample.n, Base)))
-
-chrom_AI = ggbarplot(AI_ATAC,
-                     x = "Sample.n",
-                     y = "Reads",
-                     fill = "Allele",
-                     position = position_dodge(0.7),
-                     xlab = "",
-                     ylab = "Reads",
-                     title = "Read at SCARB2 promoter overlapping rs1465922 (SCARB2)",
-                     label = format(c(paste0("p = ",
-                                        0.3),
-                          "",
-                          paste0("p = ",
-                                 0.3),
-                          "",
-                          paste0("p = ",
-                                 0.003),
-                          "",
-                          paste0("p = ",
-                                 0.0000003),
-                          "",
-                          paste0("p = ",
-                                 0.2),
-                          ""),
-                          scientific = TRUE),
-                     label.pos = "out",
-                     lab.size = 3,
-                     lab.vjust = 0.5,
-                     lab.hjust = -0.5,
-                     orientation = "horiz") +
-  theme(legend.position = "right",
-        axis.text.x = element_text(angle = 45, hjust = 1.0, face = "bold", size = 10),
-        axis.text.y = element_text(face = "bold", size = 10),
-        axis.title.y = element_text(face = "bold", size = 10),
-        axis.title.x = element_text(face = "bold", size = 10),
-        legend.text = element_text(face = "bold", size = 10),
-        legend.title = element_text(face = "bold", size = 10),
-        plot.title = element_text(hjust = 0.5)) +
-  scale_fill_manual(values = c("#80A44F", "#427F96")) +
-  scale_y_continuous(expand = c(0, 0),
-                     limits = c(0, 330))
-
-# Place the plot
-plotGG(plot = chrom_AI, 
-       x = 0.5, 
-       y = 0.75, 
-       width = 7, 
-       height = 4,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-# text B
-plotText(label = "B", 
-         fontsize = 12,
-         fontfamily = "Helvetica",
-         x = 0.25, 
-         y = 5.0, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
-
-# GTEX_SNPs_interest = read_delim("/Volumes/deborah.gerard/Documents/epifunc/eQTpLot/20230117_GTEX_data.csv",
-#               delim = ";",
-#              col_names = TRUE)
-
-GTEX_SNPs_interest = read_delim("/home/vagrant/epifunc/eQTpLot/20230117_GTEX_data.csv",
-               delim = ";",
-               col_names = TRUE)
-
-GTEX_SNPs_SCARB2_brain = GTEX_SNPs_interest %>% 
-  mutate(GTEX_sig = if_else(P.Value < 0.05, "*", "")) %>% 
-  dplyr::filter(str_detect(Tissue, "Brain"),
-         Gene.Symbol == "SCARB2") %>% 
-  mutate(SNP.Id = factor(SNP.Id,
-                         levels = c("rs6825004",
-                                    "rs7697073",
-                                    "rs11547135",
-                                    "rs6812193",
-                                    "rs1465922")))
-
-GTEX_eqtl = ggplot(data = GTEX_SNPs_SCARB2_brain, 
-                   mapping = aes(x = SNP.Id,
-                                 y = Tissue,
-                                 fill = NES)) + 
-  geom_tile() +
-  theme_classic() +
-  theme(axis.text.x = element_text(angle = 60, hjust = 1, face = "bold", size = 10),
-        axis.title.x = element_blank(),
-        axis.text.y = element_text(face = "bold", size = 10),
-        axis.title.y = element_blank(),
-        legend.text = element_text(face = "bold", size = 10),
-        legend.title = element_text(face = "bold", size = 10)) +
-  scale_fill_gradient2(
-    low = muted("blue"),
-    mid = "white",
-    high = muted("red"),
-    midpoint = 0,
-    name = "eQTL \neffect size") +
-  geom_text(aes(label = GTEX_sig))
-
-plotGG(plot = GTEX_eqtl, 
-       x = 0.5, 
-       y = 5.25, 
-       width = 7, 
-       height = 6,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-dev.off()
-```
-
-### FIGURE 5
-```{r fig5, eval = FALSE, echo = TRUE}
-########## FIGURE 5 ##########
-##############################
-# Save as a PDF
-pdf("/home/vagrant/Manuscript_1/FIGURE5/FIGURE5.pdf",
-    width = 8.3, 
-    height = 11.7)
-
-# Save as TIFF, 300 ppi
-tiff("/home/vagrant/Manuscript_1/FIGURE5/FIGURE5.tiff",
-     width = 8.27,
-     height = 11.67,
-     units = "in",
-     res = 300,
-     compression = "lzw")
-
-# Create a A4 blank page
-pageCreate(width = 8.3, 
-           height = 11.7, 
-           default.units = "inches",
-           showGuides = FALSE)
-
-#### PANEL A - 
-# text Figure 5
-plotText(label = "Figure 5", 
-         fontsize = 14,
-
-         x = 0.25, 
-         y = 0.25, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
-# text A
-plotText(label = "A", 
-         fontsize = 12,
-         x = 0.25, 
-         y = 0.5, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
-
-GCase_signal = tibble(Sample = c("shSCARB2", "shNR2C2", "shSCRAMBLE"),
-                     n1_rep1 = c(11577, 9485, 9903),
-                     n1_rep2 = c(11329, 9685, 9574),
-                     n2_rep1 = c(8979, 9443, 9489),
-                     n2_rep2 = c(9489, 9440, 11333),
-                     n3_rep1 = c(9209, 10130, 10353),
-                     n3_rep2 = c(10104, 11158, 14640),
-                     n4_rep1 = c(15255, 15551, 15611),
-                     n4_rep2 = c(14964, 16078, 16352)) %>% 
-  pivot_longer(!Sample, names_to = "Meas", values_to = "Abs_val") %>% 
-  mutate(Meas2 = gsub("\\_.*", "\\1", Meas)) %>% 
-  group_by(Sample, Meas2) %>% 
-  mutate(AVG = mean(Abs_val, na.rm = TRUE)) %>% 
-  ungroup() %>% 
-  dplyr::select(-Meas, -Abs_val, -Meas2) %>%
-  distinct(AVG, .keep_all = TRUE)
-
-# Plot 
-GCase.pl = ggbarplot(GCase_signal, 
-                      x = "Sample", 
-                      y = "AVG",
-                      width = 0.25,
-                      add = c("mean_se", 
-                              "jitter"),
-                      fill = "grey",
-                      xlab = "",
-                      ylab = "GCase absolute fluorescence value",
-                      position = position_dodge(0.9)) +
-  theme(legend.position = "none",
-        axis.text.x = element_text(angle = 90, hjust = 1.0, size = 9, face = "bold", family = "Helvetica"),
-        axis.text.y = element_text(size = 9, face = "bold"),
-        axis.title.y = element_text(size = 10, face = "bold")) +
-  scale_y_continuous(expand = c(0, 0),
-                     limits = c(0, 17000.0))
-
-# Place the plot
-plotGG(plot = GCase.pl, 
-       x = 0.50, 
-       y = 0.5, 
-       width = 2, 
-       height = 4.25,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-dev.off()
-
-############ WILL BE SUPP #####
-
-KD_TH_lev = tibble(Sple = rep("shNR2C2", 3),
-                   Rep = 1:3,
-                   days = "6 days",
-                   Gene = "TH",
-                   Exp = c(1.705920009,
-                           2.196566231,
-                           1.107610012))
-
-#TH levels in knockdown of NR2C2 6 days#
-TH_lev_KD = KD_TH_lev %>% 
-  ggbarplot(.,
-            x = "Gene",
-            y = "Exp",
-            fill = c("days"),
-            facet.by = "Sple",
-            position = position_dodge(0.9),
-            palette = c("#287C8EFF"),
-            add = c("mean_se"),
-            xlab = "",
-            ylab = "Relative expression to shSCRAMBLE") +
-  geom_hline(yintercept = 1.0, lty = "dashed", color = "black") +
-  theme(axis.title.y = element_text(face = "bold", size = 10),
-        axis.text.x = element_text(face = "bold", size = 10, angle = 90),
-        axis.text.y = element_text(face = "bold", size = 10),
-        legend.position = "none")
-
-plotGG(plot = TH_lev_KD, 
-       x = 0.5, 
-       y = 0.5, 
-       width = 2, 
-       height = 4.25,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-### DEXOMAG - 3 biological repliactes ###
-GCase = read_excel("/Volumes/deborah.gerard/Documents/Wetlab/epifunc/DEXOMAG_shSCARB2_shNR2C2_shCTRL_N1_N2_N3/20231214_DEXOMAG_KD_SCARB2_NR2C2_SCRAMBLE_N1_N2_N3_ANALYSIS.xlsx")
-
-GCase %>% 
-  dplyr::select(GCase, `GCase MEAN`, ...10, ...11) %>% 
-  drop_na() %>% 
-  dplyr::rename(Sample = GCase,
-                N1 = `GCase MEAN`,
-                N2 = ...10,
-                N3 = ...11) %>% 
-  pivot_longer(N1:N3, names_to = "Rep.bio", values_to = "norm.fluo.value") %>% 
-  mutate(norm.fluo.value = as.numeric(norm.fluo.value)) %>% 
-  #dplyr::filter(Sample != "Whole Gcase NT") %>% 
-  ggbarplot(.,
-            x = "Sample",
-            y = "norm.fluo.value",
-            add = c("mean_se", "jitter"),
-            xlab = "",
-            ylab = "GCase activity (normalised fluorescence values)") +
-  scale_x_discrete(labels = c("SCARB2 KD",
-                              "NR2C2 KD",
-                              "SCRAMBLE",
-                              "Not transduced + dexomag",
-                              "Not transduced - dexomag",
-                              "Whole cell lysate")) +
-  theme(axis.text.x = element_text(angle = 45, face = "bold", hjust = 1.0),
-        axis.text.y = element_text(face = "bold"),
-        axis.title.y = element_text(face = "bold")) +
-  stat_compare_means(comparisons = list(c("shSCARB2", "shSCRAMBLE")),
-                     method = "t.test",
-                     size = 4,
-                     label = "p.format") +
-  stat_compare_means(comparisons = list(c("shNR2C2", "shSCRAMBLE")),
-                     method = "t.test",
-                     size = 4,
-                     label = "p.format")
-
-dev.off()
-```
-
-### SUPPLEMENTARY FIGURE 1
-Plot genes of interest from the TH REP2 mCHERRY cell line RNAseq data to demonstrate that expression is similar.  
-In addition, do the same for FOUNDIN-PD.
-```{r suppFig2, eval = FALSE, echo = TRUE}
-############################################
-########## SUPPLEMENTARY FIGURE 1 ##########
-############################################
-
-# Save as a PDF
-pdf("/home/vagrant/Manuscript_1/SUPPLEMENTARY_FIGURE1/SUPPLEMENTARY_FIGURE1.pdf",
-    width = 13, 
-    height = 15)
-
-# Save as TIFF, 300 dpi
-tiff("/home/vagrant/Manuscript_1/SUPPLEMENTARY_FIGURE1/SUPPLEMENTARY_FIGURE1.tiff",
-     width = 8.27,
-     height = 11.67,
-     units = "in",
-     res = 300)
-
-# Create a A4 blank page
-pageCreate(width = 8.27, 
-           height = 11.67, 
-           default.units = "inches",
-           showGuides = FALSE)
-
-#### PANEL A - 
-# text Supplementary Figure 1
-plotText(label = "Supplementary Figure 1", 
-         fontsize = 14,
-         x = 0.25, 
-         y = 0.25, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
-# text A
-plotText(label = "A", 
-         fontsize = 12,
-         x = 0.25, 
-         y = 0.5, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
-
-# Load data
-dat.THREP2.FPKM = read_delim("/home/vagrant/epifunc/RNAseq/TH_REP2_mCHERRY/180604_HT-Rep2_fpkm.tsv",
-                      delim = "\t", 
-                      col_names = TRUE)
-
-dat.THREP2.FPKM = read_delim("/Volumes/deborah.gerard/Documents/epifunc/RNAseq/TH_REP2_mCHERRY/180604_HT-Rep2_fpkm.tsv",
-                     delim = "\t",
-                     col_names = TRUE)
-
-# Filter for genes of interest - BAG3 and LHX1 - IDUA, ZBTB14, SLC26A1 - SCARB2, NR2C2, FAM47E
-BAG3.LHX1 = c("BAG3",
-              "LHX1")
-
-IDUA.ZBTB14 = c("IDUA",
-                "ZBTB14",
-                "SLC26A1")
-
-SCARB2.NR2C2 = c("SCARB2",
-                 "NR2C2",
-                 "FAM47E")
-
-# Reformat the matrix and take only positively sorted neurons
-dat.THREP2.FPKM = dat.THREP2.FPKM %>% 
-  pivot_longer(starts_with("TH"), 
-               names_to = "Samples",
-               values_to = "FPKM") %>% 
-  #dplyr::filter(str_detect(Samples, paste("SmNPC", "pos", sep = "|"))) %>% 
-  mutate(Cond = case_when(str_detect(Samples, "D15pos") ~ "Positively sorted neurons D15",
-                          str_detect(Samples, "D15neg") ~ "Negatively sorted neurons D15",
-                          str_detect(Samples, "D30pos") ~ "Positively sorted neurons D30",
-                          str_detect(Samples, "D30neg") ~ "Negatively sorted neurons D30",
-                          TRUE ~ "smNPCs"),
-         Cond = factor(Cond, 
-                       levels = c("smNPCs", 
-                                  "Negatively sorted neurons D15",
-                                  "Positively sorted neurons D15",
-                                  "Negatively sorted neurons D30",
-                                  "Positively sorted neurons D30")))
-
-# GBA expression in TH REP2 cell line
-ggboxplot(dat.THREP2.FPKM %>% 
-                            dplyr::filter(str_detect(gene_id, "ENSG00000177628")),
-                          x = "Cond", 
-                          y = "FPKM", 
-                          add = "jitter", 
-                          fill = "Cond", 
-                          facet.by = "gene_name",
-                          xlab = "", 
-                          ylab = "Fragments Per Kilobase Million (FPKM)",
-          title = "GBA expression in TH REP2 cell line") +
-  scale_x_discrete(labels = c("smNPCs",
-                              "Negatively sorted neurons D15",
-                              "Positively sorted neurons D15",
-                              "Negatively sorted neurons D30",
-                              "Positively sorted neurons D30")) +
-  theme(legend.position = "none",
-        axis.text.x = element_text(angle = 45, hjust = 1.0))
-
-ggboxplot(dat.RPKM.filt %>% 
-                            dplyr::filter(str_detect(gene_id, "ENSG00000177628")),
-                          x = "Cond", 
-                          y = "RPKM", 
-                          add = "jitter", 
-                          fill = "Cond", 
-                          palette = c("#A9A9A9", "#B22222", "#DC143C", "#E9967A"),
-                          facet.by = "gene_name",
-                          xlab = "", 
-                          ylab = "Reads Per Kilobase Million (RPKM)") +
-  scale_x_discrete(labels = c("smNPC",
-                              expression("mDAN D15"),
-                              expression("mDAN D30"),
-                              expression("mDAN D50"))) +
-  theme(legend.position = "none",
-        axis.text.x = element_text(angle = 90))
-
-# Plot the expression of BAG3 and LHX1
-TH.REP2_BAG3.LHX1.exp = ggboxplot(dat.THREP2.FPKM %>% 
-                            dplyr::filter(gene_name %in% BAG3.LHX1),
-                          x = "Cond", 
-                          y = "FPKM", 
-                          add = "jitter", 
-                          fill = "Cond", 
-                          palette = c("#A9A9A9", "#B22222", "#DC143C"),
-                          facet.by = "gene_name",
-                          xlab = "", 
-                          ylab = "Fragments Per Kilobase Million (FPKM)") +
-  scale_x_discrete(labels = c("smNPC",
-                              expression("mDAN D15"),
-                              expression("mDAN D30"))) +
-  theme(legend.position = "none",
-        axis.text.x = element_text(angle = 90))
-
-# Place the plot  
-plotGG(plot = TH.REP2_BAG3.LHX1.exp, 
-      x = 0.5, 
-       y = 0.625, 
-       width = 2, 
-       height = 3.5,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-# Plot the expression of IDUA and ZBTB14
-TH.REP2_IDUA.ZBTB14.exp = ggboxplot(dat.THREP2.FPKM %>% 
-                            dplyr::filter(gene_name %in% IDUA.ZBTB14) %>% 
-                              mutate(gene_name = factor(gene_name,
-                                                        levels = c("IDUA", "ZBTB14", "SLC26A1"))),
-                          x = "Cond", 
-                          y = "FPKM", 
-                          add = "jitter", 
-                          fill = "Cond", 
-                          palette = c("#A9A9A9", "#B22222", "#DC143C"),
-                          facet.by = "gene_name",
-                          xlab = "", 
-                          ylab = "Fragments Per Kilobase Million (FPKM)") +
-  scale_x_discrete(labels = c("smNPC",
-                              expression("mDAN D15"),
-                              expression("mDAN D30"))) +
-  theme(legend.position = "none",
-        axis.text.x = element_text(angle = 90))
-
-# Place the plot  
-plotGG(plot = TH.REP2_IDUA.ZBTB14.exp, 
-       x = 2.75, 
-       y = 0.625, 
-       width = 2.5, 
-       height = 3.5,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-# Plot the expression of SCARB2 and NR2C2
-TH.REP2_SCARB2.NR2C2.exp = ggboxplot(dat.THREP2.FPKM %>% 
-                            dplyr::filter(gene_name %in% SCARB2.NR2C2) %>% 
-                              mutate(gene_name = factor(gene_name,
-                                                        levels = c("SCARB2", "NR2C2", "FAM47E"))),
-                          x = "Cond", 
-                          y = "FPKM", 
-                          add = "jitter", 
-                          fill = "Cond", 
-                          palette = c("#A9A9A9", "#B22222", "#DC143C"),
-                          facet.by = "gene_name",
-                          xlab = "", 
-                          ylab = "Fragments Per Kilobase Million (FPKM)") +
-  scale_x_discrete(labels = c("smNPC",
-                              expression("mDAN D15"),
-                              expression("mDAN D30"))) +
-  theme(legend.position = "none",
-        axis.text.x = element_text(angle = 90))
-
-# Place the plot  
-plotGG(plot = TH.REP2_SCARB2.NR2C2.exp, 
-       x = 5.5, 
-       y = 0.625, 
-       width = 2.5, 
-       height = 3.5,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-#### PANEL B - 
-# text B
-plotText(label = "B", 
-         fontsize = 12,
-         x = 0.25, 
-         y = 4.5, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
-
-# FOUNDIN-PD data
-# Load
-FIPD = read_delim("/home/vagrant/epifunc/PPMI_data/FOUNDIN-PD_150.9_RNAB/aggregated_expression/cpmTable.tsv",
-                  delim = "\t",
-                  col_names = TRUE)
-
-FIPD = read_delim("/Volumes/deborah.gerard/Documents/epifunc/PPMI_data/FOUNDIN-PD_150.9_RNAB/aggregated_expression/cpmTable.tsv",
-                  delim = "\t",
-                  col_names = TRUE)
-
-# Filter for genes of interest and get the ensembl and gene names
-goi_ens = select(org.Hs.eg.db, 
-                 keys = c("BAG3",
-                          "LHX1",
-                          "IDUA",
-                          "ZBTB14",
-                          "SLC26A1",
-                          "SCARB1",
-                          "SCARB2",
-                          "SCARB3",
-                          "CD36",
-                          "NR2C2",
-                          "FAM47E",
-                          "TH",
-                          "GAPDH",
-                          "ACTB",
-                          "GBA1",
-                          "PSAP",
-                          "CTSD"), 
-                 columns = c("SYMBOL",
-                             "ENSEMBL"), 
-                 keytype = "SYMBOL")
-
-# 2 LHX1 ensembl IDs came back. Check on the Ensembl website which one is correct
-goi_ens = goi_ens %>% 
-  as_tibble() %>% 
-  dplyr::filter(!ENSEMBL %in% c("ENSG00000274577",
-                                "ENSG00000262446")) %>% 
-  dplyr::rename(ENSEMBL.not.dot = ENSEMBL)
-
-# Filter the matrix of expression for my genes of interest
-FIPD.fin = FIPD %>% 
-  dplyr::filter(str_detect(Geneid, paste(goi_ens$ENSEMBL.not.dot, collapse = "|"))) %>% 
-  dplyr::rename(ENSEMBL = Geneid) %>% 
-  mutate(ENSEMBL.not.dot = gsub("\\..*", "", ENSEMBL)) %>% 
-  dplyr::select(ENSEMBL, ENSEMBL.not.dot, everything()) %>% 
-  pivot_longer(cols = starts_with("RNAB"), names_to = "Samples", values_to = "CPM") %>% 
-  mutate(Day = str_extract(Samples, "da+\\d+")) %>% 
-  left_join(goi_ens, 
-            by = "ENSEMBL.not.dot") %>% 
-  dplyr::select(SYMBOL, Day, CPM)
-
-# Anova
-BAG3.aov = FIPD.fin %>% 
-  dplyr::filter(SYMBOL %in% BAG3.LHX1) %>% 
-  group_by(SYMBOL) %>% 
-  anova_test(CPM ~ Day)
-
-# Tukey post-hoc test
-BAG3.ph = FIPD.fin %>% 
-  dplyr::filter(SYMBOL %in% BAG3.LHX1) %>% 
-  group_by(SYMBOL) %>% 
-  tukey_hsd(CPM ~ Day) %>% 
-  add_xy_position(x = "Day")
-
-# Plot expression of BAG3 and LHX1
-FIPD.exp_BAG3.LHX1 = ggboxplot(FIPD.fin %>% 
-                          dplyr::filter(SYMBOL %in% BAG3.LHX1),
-                     x = "Day", 
-                     y = "CPM", 
-                     add = "jitter", 
-                     fill = "Day", 
-                     palette = c("#482677FF", "#2D708EFF", "#29AF7FFF"),
-                     facet.by = "SYMBOL",
-                     xlab = "", 
-                     ylab = "Counts per Million (CPM)",
-                     add.params = list(size = 0.1)) +
-  scale_x_discrete(labels = c("Day 0",
-                              "Day 25",
-                              "Day 65")) +
-  theme(legend.position = "none",
-        axis.text.x = element_text(angle = 90))
-  # stat_pvalue_manual(BAG3.ph, 
-  #                    hide.ns = TRUE,
-  #                    label = "p.adj") +
-  # labs(subtitle = get_test_label(BAG3.aov, 
-  #                                detailed = FALSE))
-
-# Place the plot  
-plotGG(plot = FIPD.exp_BAG3.LHX1, 
-       x = 0.5, 
-       y = 4.75 ,
-       width = 2.5, 
-       height = 3.5,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-# Anova
-IDUA.aov = FIPD.fin %>% 
-  dplyr::filter(SYMBOL %in% IDUA.ZBTB14) %>% 
-  group_by(SYMBOL) %>% 
-  anova_test(CPM ~ Day)
-
-# Tukey post-hoc test
-IDUA.ph = FIPD.fin %>% 
-  dplyr::filter(SYMBOL %in% IDUA.ZBTB14) %>% 
-  group_by(SYMBOL) %>% 
-  tukey_hsd(CPM ~ Day) %>% 
-  add_xy_position(x = "Day")
-
-# Plot expression of IDUA and ZBTB14
-FIPD.exp_IDUA.ZBTB14 = ggboxplot(FIPD.fin %>% 
-                                   dplyr::filter(SYMBOL %in% IDUA.ZBTB14) %>% 
-                            mutate(SYMBOL = factor(SYMBOL, levels = c("IDUA", "ZBTB14", "SLC26A1"))),
-                     x = "Day", 
-                     y = "CPM", 
-                     add = "jitter", 
-                     fill = "Day", 
-                     palette = c("#482677FF", "#2D708EFF", "#29AF7FFF"),
-                     facet.by = "SYMBOL",
-                     xlab = "", 
-                     ylab = "Counts per Million (CPM)",
-                     add.params = list(size = 0.1)) +
-  scale_x_discrete(labels = c("Day 0",
-                              "Day 25",
-                              "Day 65")) +
-  theme(legend.position = "none",
-        axis.text.x = element_text(angle = 90))
-  # stat_pvalue_manual(IDUA.ph, 
-  #                    hide.ns = TRUE,
-  #                    label = "p.adj") +
-  # labs(subtitle = get_test_label(IDUA.aov, 
-  #                                detailed = FALSE))
-
-# Place the plot  
-plotGG(plot = FIPD.exp_IDUA.ZBTB14, 
-       x = 3.125, 
-       y = 4.75 ,
-       width = 2.5, 
-       height = 3.5,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-# Anova
-SCARB2.aov = FIPD.fin %>% 
-  dplyr::filter(SYMBOL %in% SCARB2.NR2C2) %>% 
-  group_by(SYMBOL) %>% 
-  anova_test(CPM ~ Day)
-
-# Tukey post-hoc test
-SCARB2.ph = FIPD.fin %>% 
-  dplyr::filter(SYMBOL %in% SCARB2.NR2C2) %>% 
-  group_by(SYMBOL) %>% 
-  tukey_hsd(CPM ~ Day) %>% 
-  add_xy_position(x = "Day")
-
-# Plot expression of SCARB2 and NR2C2
-FIPD.exp_SCARB2.NR2C2 = ggboxplot(FIPD.fin %>% 
-                                   dplyr::filter(SYMBOL %in% SCARB2.NR2C2) %>% 
-                            mutate(SYMBOL = factor(SYMBOL, levels = c("SCARB2", "NR2C2", "FAM47E"))),
-                     x = "Day", 
-                     y = "CPM", 
-                     add = "jitter", 
-                     fill = "Day", 
-                     palette = c("#482677FF", "#2D708EFF", "#29AF7FFF"),
-                     facet.by = "SYMBOL",
-                     xlab = "", 
-                     ylab = "Counts per Million (CPM)",
-                     add.params = list(size = 0.1)) +
-  scale_x_discrete(labels = c("Day 0",
-                              "Day 25",
-                              "Day 65")) +
-  theme(legend.position = "none",
-        axis.text.x = element_text(angle = 90))
-  # stat_pvalue_manual(SCARB2.ph, 
-  #                    hide.ns = TRUE,
-  #                    label = "p.adj") +
-  # labs(subtitle = get_test_label(SCARB2.aov, 
-  #                                detailed = FALSE))
-
-# Place the plot  
-plotGG(plot = FIPD.exp_SCARB2.NR2C2, 
-       x = 5.625, 
-       y = 4.75 ,
-       width = 2.5, 
-       height = 3.5,
-       just = c("left", "top"), 
-       default.units = "inches")
-
-dev.off()
-
-## GBA expression in FOUNDIN-PD
-ggboxplot(FIPD.fin %>% 
-            dplyr::filter(SYMBOL == "GBA1"),
-                     x = "Day", 
-                     y = "CPM", 
-                     add = "jitter", 
-                     fill = "Day", 
-                     palette = c("#482677FF", "#2D708EFF", "#29AF7FFF"),
-                     facet.by = "SYMBOL",
-                     xlab = "", 
-                     ylab = "Counts per Million (CPM)",
-                     add.params = list(size = 0.1),
-          title = "GBA expression in FOUNDIN-PD cell lines") +
-  scale_x_discrete(labels = c("Day 0",
-                              "Day 25",
-                              "Day 65")) +
-  theme(legend.position = "none",
-        axis.text.x = element_text(angle = 90))
-
-FIPD %>% 
-  dplyr::filter(str_detect(Geneid, "ENSG00000177628")) %>% 
-  pivot_longer(cols = starts_with("RNAB"), names_to = "Sample",
-               values_to = "CPM") %>%
-
-```
-
-### SUPPLEMENTARY FIGURE 2
-IHEC consortium has one sample of substantia nigra for H3K27me3, H3K9me3, H3K4me1, H3K4me3 and H3K36me3 from a healthy brain for BAG3, IDUA and SCARB2 loci
-```{r suppFig1, eval = FALSE, echo = TRUE}
-############################################
-########## SUPPLEMENTARY FIGURE 2 ##########
-############################################
-
-# Save as a PDF
-pdf("/home/vagrant/Manuscript_1/SUPPLEMENTARY_FIGURE2/SUPPLEMENTARY_FIGURE2.pdf",
-    width = 8.3, 
-    height = 11.7)
-
-# Save as TIFF, 300 dpi
-tiff("/home/vagrant/Manuscript_1/SUPPLEMENTARY_FIGURE2/SUPPLEMENTARY_FIGURE2.tiff",
-     width = 8.27,
-     height = 11.67,
-     units = "in",
-     res = 300)
-
-# Create a A4 blank page
-pageCreate(width = 8.27, 
-           height = 11.67, 
-           default.units = "inches",
-           showGuides = FALSE)
-
-#### PANEL A - 
-# text Supplementary Figure 2
-plotText(label = "Supplementary Figure 2", 
-         fontsize = 14,
-         x = 0.25, 
-         y = 0.25, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
-# text A
-plotText(label = "A", 
-         fontsize = 12,
-         x = 0.25, 
-         y = 0.5, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
-
-# ChIP-seq signal BAG3
-# path where bigwig files are
-bw.IHEC.path = "/home/vagrant/Documents/IHEC/ChIP_Seq/BIGWIG/"
-
-# Reads BIGWIG file at BAG3 location - H3K4me1
-bw.BAG3.H3K4me1 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6a1889bf-7312-4e41-b1cc-e2f3be7a8076.fc.signal.bigwig"),
-                               chrom = "chr10",
-                               chromstart = 119611305,
-                               chromend = 119691505)
-
-# Reads BIGWIG file at BAG3 location - H3K4me3
-bw.BAG3.H3K4me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.4cb9300f-9097-4374-8f2a-4afd8ff855fb.fc.signal.bigwig"),
-                               chrom = "chr10",
-                               chromstart = 119611305,
-                               chromend = 119691505)
-
-# Reads BIGWIG file at BAG3 location - H3K36me3
-bw.BAG3.H3K36me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6586e624-852f-4cac-83df-2325cee19699.fc.signal.bigwig"),
-                               chrom = "chr10",
-                               chromstart = 119611305,
-                               chromend = 119691505)
-
-# Reads BIGWIG file at BAG3 location - H3K9me3
-bw.BAG3.H3K9me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.e8fe7664-906e-4d87-8f3a-6ce88dbeadc6.fc.signal.bigwig"),
-                               chrom = "chr10",
-                               chromstart = 119611305,
-                               chromend = 119691505)
-
-# Reads BIGWIG file at BAG3 location - H3K27me3
-bw.BAG3.H3K27me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.5f5024a9-2e3f-4527-82ec-0ed04bf4a848.fc.signal.bigwig"),
-                               chrom = "chr10",
-                               chromstart = 119611305,
-                               chromend = 119691505)
-
-# Add a scale next to the bigwig files - check the maximum to choose
-scale.IHEC.BAG3.max = max(c(bw.BAG3.H3K4me1$score,
-                              bw.BAG3.H3K4me3$score,
-                              bw.BAG3.H3K36me3$score,
-                              bw.BAG3.H3K9me3$score,
-                              bw.BAG3.H3K27me3$score)) %>% 
-  round(.,
-        digits = 1.0)
-
-print(scale.IHEC.BAG3.max)
-
-# Define parameters for the regions
-region.p.IHEC.BAG3 = pgParams(chrom = "chr10",
-                         chromstart = 119611405,
-                         chromend = 119691405,
-                         assembly = "hg38",
-                         range = c(0, scale.IHEC.BAG3.max))
-
-# Add the genomic label
-plotGenomeLabel(
-  chrom = "chr10",
-  chromstart = 119611405,
-  chromend = 119691405,
-  assembly = "hg38",
-  x = 0.75,
-  y = 0.625,
-  length = 4.0,
-  default.units = "inches",
-  scale = "Mb")
-
-# ChIPseq signal H3K4me1
-H3K4me1_BAG3 = plotSignal(
-  data = bw.BAG3.H3K4me1, 
-  params = region.p.IHEC.BAG3,
-  fill = "#b5de2b", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 0.875, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K4me1_BAG3, 
-          at = c(0, scale.IHEC.BAG3.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K4me3
-H3K4me3_BAG3 = plotSignal(
-  data = bw.BAG3.H3K4me3, 
-  params = region.p.IHEC.BAG3,
-  fill = "#35b779", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 1.25, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K4me3_BAG3, 
-          at = c(0, scale.IHEC.BAG3.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K36me3
-H3K36me3_BAG3 = plotSignal(
-  data = bw.BAG3.H3K36me3, 
-  params = region.p.IHEC.BAG3,
-  fill = "#26828e", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 1.625, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K36me3_BAG3, 
-          at = c(0, scale.IHEC.BAG3.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K9me3
-H3K9me3_BAG3 = plotSignal(
-  data = bw.BAG3.H3K9me3, 
-  params = region.p.IHEC.BAG3,
-  fill = "#3e4989", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 2.0, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K9me3_BAG3, 
-          at = c(0, scale.IHEC.BAG3.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K27me3
-H3K27me3_BAG3 = plotSignal(
-  data = bw.BAG3.H3K27me3, 
-  params = region.p.IHEC.BAG3,
-  fill = "#440154", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 2.375, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K27me3_BAG3, 
-          at = c(0, scale.IHEC.BAG3.max),
-          fontsize = 6)
-
-# Gene track
-plotGenes(
-  chrom = "chr10",
-  chromstart = 119611405,
-  chromend = 119691405,
-  assembly = assembly(Genome = "hg38refGene", 
-                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
-                      OrgDb = "org.Hs.eg.db"),
-  fontcolor = "black",
-  fill = "black",
-  x = 0.75,
-  y = 2.75,
-  width = 4.0,
-  height = 0.375,
-  just = c("left", "top"),
-  default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K4me1", 
-         fontsize = 6, 
-         fontcolor = "#b5de2b",
-         x = 0.75,
-         y = 0.875, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K4me3", 
-         fontsize = 6, 
-         fontcolor = "#35b779",
-         x = 0.75,
-         y = 1.25, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K36me3", 
-         fontsize = 6, 
-         fontcolor = "#26828e",
-         x = 0.75,
-         y = 1.625, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K9me3", 
-         fontsize = 6, 
-         fontcolor = "#3e4989",
-         x = 0.75,
-         y = 2.0, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K27me3", 
-         fontsize = 6, 
-         fontcolor = "#440154",
-         x = 0.75,
-         y = 2.375, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Reads BIGWIG file at IDUA location - H3K4me1
-bw.IDUA.H3K4me1 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6a1889bf-7312-4e41-b1cc-e2f3be7a8076.fc.signal.bigwig"),
-                               chrom = "chr4",
-                               chromstart = 947008,
-                               chromend = 1027208)
-
-# Reads BIGWIG file at IDUA location - H3K4me3
-bw.IDUA.H3K4me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.4cb9300f-9097-4374-8f2a-4afd8ff855fb.fc.signal.bigwig"),
-                               chrom = "chr4",
-                               chromstart = 947008,
-                               chromend = 1027208)
-
-# Reads BIGWIG file at IDUA location - H3K36me3
-bw.IDUA.H3K36me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6586e624-852f-4cac-83df-2325cee19699.fc.signal.bigwig"),
-                               chrom = "chr4",
-                               chromstart = 947008,
-                               chromend = 1027208)
-
-# Reads BIGWIG file at IDUA location - H3K9me3
-bw.IDUA.H3K9me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.e8fe7664-906e-4d87-8f3a-6ce88dbeadc6.fc.signal.bigwig"),
-                               chrom = "chr4",
-                               chromstart = 947008,
-                               chromend = 1027208)
-
-# Reads BIGWIG file at IDUA location - H3K27me3
-bw.IDUA.H3K27me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.5f5024a9-2e3f-4527-82ec-0ed04bf4a848.fc.signal.bigwig"),
-                               chrom = "chr4",
-                               chromstart = 947008,
-                               chromend = 1027208)
-
-# Add a scale next to the bigwig files - check the maximum to choose
-scale.IHEC.IDUA.max = max(c(bw.IDUA.H3K4me1$score,
-                              bw.IDUA.H3K4me3$score,
-                              bw.IDUA.H3K36me3$score,
-                              bw.IDUA.H3K9me3$score,
-                              bw.IDUA.H3K27me3$score)) %>% 
-  round(.,
-        digits = 1.0)
-
-print(scale.IHEC.IDUA.max)
-
-# Define parameters for the regions
-region.p.IHEC.IDUA = pgParams(chrom = "chr4",
-                         chromstart = 947108,
-                         chromend = 1027108,
-                         assembly = "hg38",
-                         range = c(0, scale.IHEC.IDUA.max))
-
-# Add the genomic label
-plotGenomeLabel(
-  chrom = "chr4",
-  chromstart = 947108,
-  chromend = 1027108,
-  assembly = "hg38",
-  x = 0.75,
-  y = 3.5,
-  length = 4.0,
-  default.units = "inches",
-  scale = "Mb")
-
-# ChIPseq signal H3K4me1
-H3K4me1_IDUA = plotSignal(
-  data = bw.IDUA.H3K4me1, 
-  params = region.p.IHEC.IDUA,
-  fill = "#b5de2b", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 3.75, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K4me1_IDUA, 
-          at = c(0, scale.IHEC.IDUA.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K4me3
-H3K4me3_IDUA = plotSignal(
-  data = bw.IDUA.H3K4me3, 
-  params = region.p.IHEC.IDUA,
-  fill = "#35b779", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 4.125, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K4me3_IDUA, 
-          at = c(0, scale.IHEC.IDUA.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K36me3
-H3K36me3_IDUA = plotSignal(
-  data = bw.IDUA.H3K36me3, 
-  params = region.p.IHEC.IDUA,
-  fill = "#26828e", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 4.5, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K36me3_IDUA, 
-          at = c(0, scale.IHEC.IDUA.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K9me3
-H3K9me3_IDUA = plotSignal(
-  data = bw.IDUA.H3K9me3, 
-  params = region.p.IHEC.IDUA,
-  fill = "#3e4989", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 4.875, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K9me3_IDUA, 
-          at = c(0, scale.IHEC.IDUA.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K27me3
-H3K27me3_IDUA = plotSignal(
-  data = bw.IDUA.H3K27me3, 
-  params = region.p.IHEC.IDUA,
-  fill = "#440154", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 5.25, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K27me3_IDUA, 
-          at = c(0, scale.IHEC.IDUA.max),
-          fontsize = 6)
-
-# Gene track
-plotGenes(
-  chrom = "chr4",
-  chromstart = 947108,
-  chromend = 1027108,
-  assembly = assembly(Genome = "hg38refGene", 
-                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
-                      OrgDb = "org.Hs.eg.db"),
-  fontcolor = "black",
-  fill = "black",
-  x = 0.75,
-  y = 5.625,
-  width = 4.0,
-  height = 0.375,
-  just = c("left", "top"),
-  default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K4me1", 
-         fontsize = 6, 
-         fontcolor = "#b5de2b",
-         x = 0.75,
-         y = 3.75, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K4me3", 
-         fontsize = 6, 
-         fontcolor = "#35b779",
-         x = 0.75,
-         y = 4.125, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K36me3", 
-         fontsize = 6, 
-         fontcolor = "#26828e",
-         x = 0.75,
-         y = 4.5, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K9me3", 
-         fontsize = 6, 
-         fontcolor = "#3e4989",
-         x = 0.75,
-         y = 4.875, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K27me3", 
-         fontsize = 6, 
-         fontcolor = "#440154",
-         x = 0.75,
-         y = 5.25, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# ChIP-seq signal SCARB2
-# Reads BIGWIG file at SCARB2 location - H3K4me1
-bw.SCARB2.H3K4me1 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6a1889bf-7312-4e41-b1cc-e2f3be7a8076.fc.signal.bigwig"),
-                               chrom = "chr4",
-                               chromstart = 76173617,
-                               chromend = 76253817)
-
-# Reads BIGWIG file at SCARB2 location - H3K4me3
-bw.SCARB2.H3K4me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.4cb9300f-9097-4374-8f2a-4afd8ff855fb.fc.signal.bigwig"),
-                               chrom = "chr4",
-                               chromstart = 76173617,
-                               chromend = 76253817)
-
-# Reads BIGWIG file at SCARB2 location - H3K36me3
-bw.SCARB2.H3K36me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.6586e624-852f-4cac-83df-2325cee19699.fc.signal.bigwig"),
-                               chrom = "chr4",
-                               chromstart = 76173617,
-                               chromend = 76253817)
-
-# Reads BIGWIG file at SCARB2 location - H3K9me3
-bw.SCARB2.H3K9me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.e8fe7664-906e-4d87-8f3a-6ce88dbeadc6.fc.signal.bigwig"),
-                               chrom = "chr4",
-                               chromstart = 76173617,
-                               chromend = 76253817)
-
-# Reads BIGWIG file at SCARB2 location - H3K27me3
-bw.SCARB2.H3K27me3 = readBigwig(file = paste0(bw.IHEC.path,
-                                             "ihec.chipseq.ihec-chipseq-containerv1.1.4.IHECRE00000986.6.5f5024a9-2e3f-4527-82ec-0ed04bf4a848.fc.signal.bigwig"),
-                               chrom = "chr4",
-                               chromstart = 76173617,
-                               chromend = 76253817)
-
-# Add a scale next to the bigwig files - check the maximum to choose
-scale.IHEC.SCARB2.max = max(c(bw.SCARB2.H3K4me1$score,
-                              bw.SCARB2.H3K4me3$score,
-                              bw.SCARB2.H3K36me3$score,
-                              bw.SCARB2.H3K9me3$score,
-                              bw.SCARB2.H3K27me3$score)) %>% 
-  round(.,
-        digits = 1.0)
-
-print(scale.IHEC.SCARB2.max)
-
-# Define parameters for the regions
-region.p.IHEC.SCARB2 = pgParams(chrom = "chr4",
-                         chromstart = 76173717,
-                         chromend = 76253717,
-                         assembly = "hg38",
-                         range = c(0, scale.IHEC.SCARB2.max))
-
-# Add the genomic label
-plotGenomeLabel(
-  chrom = "chr4",
-  chromstart = 76173717,
-  chromend = 76253717,
-  assembly = "hg38",
-  x = 0.75,
-  y = 6.5,
-  length = 4.0,
-  default.units = "inches",
-  scale = "Mb")
-
-# ChIPseq signal H3K4me1
-H3K4me1_SCARB2 = plotSignal(
-  data = bw.SCARB2.H3K4me1, 
-  params = region.p.IHEC.SCARB2,
-  fill = "#b5de2b", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 6.75, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K4me1_SCARB2, 
-          at = c(0, scale.IHEC.SCARB2.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K4me3
-H3K4me3_SCARB2 = plotSignal(
-  data = bw.SCARB2.H3K4me3, 
-  params = region.p.IHEC.SCARB2,
-  fill = "#35b779", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 7.125, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K4me3_SCARB2, 
-          at = c(0, scale.IHEC.SCARB2.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K36me3
-H3K36me3_SCARB2 = plotSignal(
-  data = bw.SCARB2.H3K36me3, 
-  params = region.p.IHEC.SCARB2,
-  fill = "#26828e", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 7.5, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K36me3_SCARB2, 
-          at = c(0, scale.IHEC.SCARB2.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K9me3
-H3K9me3_SCARB2 = plotSignal(
-  data = bw.SCARB2.H3K9me3, 
-  params = region.p.IHEC.SCARB2,
-  fill = "#3e4989", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 7.875, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K9me3_SCARB2, 
-          at = c(0, scale.IHEC.SCARB2.max),
-          fontsize = 6)
-
-# ChIPseq signal H3K27me3
-H3K27me3_SCARB2 = plotSignal(
-  data = bw.SCARB2.H3K27me3, 
-  params = region.p.IHEC.SCARB2,
-  fill = "#440154", 
-  alpha = 0.7, 
-  linecolor = NA,
-  x = 0.75, 
-  y = 8.25, 
-  width = 4.0, 
-  height = 0.25,
-  just = c("left", "top"), 
-  default.units = "inches")
-
-annoYaxis(plot = H3K27me3_SCARB2, 
-          at = c(0, scale.IHEC.SCARB2.max),
-          fontsize = 6)
-
-# Gene track
-plotGenes(
-  chrom = "chr4",
-  chromstart = 76173717,
-  chromend = 76253717,
-  assembly = assembly(Genome = "hg38refGene", 
-                      TxDb = "TxDb.Hsapiens.UCSC.hg38.refGene", 
-                      OrgDb = "org.Hs.eg.db"),
-  fontcolor = "black",
-  fill = "black",
-  x = 0.75,
-  y = 8.625,
-  width = 4.0,
-  height = 0.375,
-  just = c("left", "top"),
-  default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K4me1", 
-         fontsize = 6, 
-         fontcolor = "#b5de2b",
-         x = 0.75,
-         y = 6.75, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K4me3", 
-         fontsize = 6, 
-         fontcolor = "#35b779",
-         x = 0.75,
-         y = 7.125, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K36me3", 
-         fontsize = 6, 
-         fontcolor = "#26828e",
-         x = 0.75,
-         y = 7.5, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K9me3", 
-         fontsize = 6, 
-         fontcolor = "#3e4989",
-         x = 0.75,
-         y = 7.875, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-# Add the samples name
-plotText(label = "H3K27me3", 
-         fontsize = 6, 
-         fontcolor = "#440154",
-         x = 0.75,
-         y = 8.25, 
-         just = c("left", "top"),
-         default.units = "inches")
-
-#### PANEL B - 
-# text Supplementary Figure 1
-# text B
-plotText(label = "B", 
-         fontsize = 12,
-         x = 0.25, 
-         y = 8.5, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
-
-# Load IHEC RNA-seq data (TPM)
-IHEC.exp = read_delim("/home/vagrant/Documents/IHEC/RNA_seq/genes_tpm.csv",
-                      delim = ",",
-                      col_names = TRUE)
-
-# Genes of interest to be plotted
-goi_ens.filt = goi_ens %>% 
-  as_tibble() %>% 
-  dplyr::filter(ENSEMBL != "ENSG00000274577")
-
-IHEC.exp %>% 
-  # Remove the dot and number in Ensembl IDS
-  mutate(id_col = gsub("\\..*", 
-                       "", 
-                       id_col)) %>% 
-  dplyr:::filter(id_col %in% goi_ens.filt$ENSEMBL) %>% 
-  pivot_longer(cols = starts_with("IHEC"),
-               names_to = "Sample",
-               values_to = "TPM") %>% 
-  mutate(Sample = gsub("",
-                       "",
-                       Sample))
-
-dev.off()
-```
-
-### SUPPLEMENTARY FIGURE 3
-Plot FACS results for experiments where knockdown were performed at day 9 and samples collected 3 and 6 days post-transduction
-```{r suupFig3, eval = FALSE, echo = TRUE}
-############################################
-########## SUPPLEMENTARY FIGURE 3 ##########
-############################################
-
-# Save as a PDF
-pdf("/home/vagrant/Manuscript_1/SUPPLEMENTARY_FIGURE3/SUPPLEMENTARY_FIGURE3.pdf",
-    width = 13, 
-    height = 15)
-
-# Save as TIFF, 300 ppi
-tiff("/home/vagrant/Manuscript_1/SUPPLEMENTARY_FIGURE3/SUPPLEMENTARY_FIGURE3.tiff",
-     width = 8.27,
-     height = 11.67,
-     units = "in",
-     res = 300)
-
-# Create a A4 blank page
-pageCreate(width = 8.27, 
-           height = 11.67, 
-           default.units = "inches",
-           showGuides = TRUE)
-
-#### PANEL A - 
-# text Supplementary Figure 3
-plotText(label = "Supplementary Figure 3", 
-         fontsize = 14,
-         x = 0.25, 
-         y = 0.25, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
-# text A
-plotText(label = "A", 
-         fontsize = 12,
-         x = 0.25, 
-         y = 0.5, 
-         just = "left", 
-         default.units = "inches",
-         fontface = "bold")
-
-# Read the facs files (.fcs)
-#facs.path = "/home/vagrant/Documents/Wetlab/epifunc/"
-facs.path = "/Volumes/deborah.gerard/Documents/Wetlab/epifunc/"
-
-facs_6days_PT_N1.fs = read.flowSet(path = paste0(facs.path,
-                                              "2022.11_DG_KD_SCARB2_NR2C2_1/FACS/RAW_DATA/NEW_EXPORT_06122022_1624/2022.11_DG_KD_SCARB2_NR2C2_1/"),
-                                pattern = ".fcs",
-                               alter.names = TRUE,
-                               truncate_max_range = FALSE)
-
-# Check what channels are present
-colnames(facs_6days_PT_N1.fs)
-
-# Check sample
-pData(facs_6days_PT_N1.fs)
-
-# Rename some for clarity
-colnames(facs_6days_PT_N1.fs)[colnames(facs_6days_PT_N1.fs) == "FITC.A"] = "GFP"
-colnames(facs_6days_PT_N1.fs)[colnames(facs_6days_PT_N1.fs) == "mCherry..A"] = "mCHERRY"
-colnames(facs_6days_PT_N1.fs)[colnames(facs_6days_PT_N1.fs) == "SYTOX_BLUE..A"] = "SYTOX BLUE"
-
-# To be able to add gates, the object must be transformed as a GatingSet object
-facs_6days_PT_N1.gs = GatingSet(facs_6days_PT_N1.fs)
-
-# Define neurons gate
-dead.neur.gate = polygonGate(filterId = "Neurons",
-                        "FSC.A" = c(5e4, 2e5, 2e5, 5e4),
-                        "SSC.A" = c(0e4, 125e3, 2.e5, 1e5))
-
-# Plot SYTOX BLUE positive CTRL
-ggcyto(facs_6days_PT_N1.gs[[1]],
-       aes(x = FSC.A, 
-           y = SSC.A),
-       subset = "root") + 
-  geom_hex(bins = 200) +
-  geom_gate(dead.neur.gate) +
-  ggcyto_par_set(limits = "instrument")
-
-# The gate for dead neurons has been defined -> add the gate to the gateset and recompute
-add(facs_6days_PT_N1.gs,
-    dead.neur.gate)
-
-recompute(facs_6days_PT_N1.gs)
-
-dev.off()
-```
-
-SCARB2 snp (rs1465922) for samples with whole genome sequencing data (75 cases)
-```{r, eval= FALSE, echo = TRUE}
-# Load data
-SCARB2.SNP.WGS.75 = read_excel("/Volumes/deborah.gerard/Documents/epifunc/Final.WGS.SCARB2.OK_from_Sinthu.xlsx")
-
-# Filter for rs1465922
-SCARB2.SNP.WGS.75 %>% 
-  filter(avsnp150 == "rs1465922") %>% 
-  dplyr::select(samples) %>% 
-  separate(samples,
-           sep = ", ",
-           into = )
-
-```
-
-```{r, eval = FALSE, echo = TRUE}
-sessionInfo()
-```
-
-```{r, eval = FALSE, echo = TRUE}
-library("tidyverse")
-library("readxl")
-library("AnnotationDbi")
-library("EnsDb.Hsapiens.v86")
-
-# Load data
-TFlist = read_excel("/Volumes/deborah.gerard/Documents/Elena/Human_TF_list.xls",
-                    skip = 1,
-                    col_names = TRUE)
-
-# Add gene symbol
-TFlist.GN = select(EnsDb.Hsapiens.v86, 
-       keys = as.character(TFlist$EntrezID), 
-       columns = c("ENTREZID", "GENENAME"), 
-       keytype = "ENTREZID")
-
-TFlist.GN %>% 
-  as_tibble() %>% 
-  distinct(GENENAME)
-  write_delim(.,
-              "/Volumes/deborah.gerard/Documents/Elena/Human_TF_list_geneName.txt",
-              col_names = TRUE,
-              delim = "\t")
-
-```
-
-### TEST GBA and SNPs
-```{r, eval = FALSE, echo = TRUE}
-# Load the genotype of rs1465922 from the PPMI data
-GT_PPMI = read_delim("/Volumes/deborah.gerard/Documents/epifunc/PPMI_data/VCF/ppmi.july2018.chr4.vqsr_with_my_snps.vcf",
-                     delim = "\t",
-                     comment = "##",
-                     col_names = TRUE)
-
-# Filter for rs1465922 only and assign genotype for that snp
-GT_PPMI.filt = GT_PPMI %>% 
-  filter(ID == "rs1465922") %>% 
-  dplyr::select(-QUAL:-FORMAT) %>% 
-  pivot_longer(cols = starts_with("PPMI"),
-               names_to = "Sample",
-               values_to = "Genotype.plus") %>% 
-  mutate(Genotype = gsub("\\:.*", "", Genotype.plus),
-         Genotype.l = case_when(Genotype == "1/1" ~ "A/A",
-                                Genotype == "0/1" ~ "G/A",
-                                Genotype == "0/0" ~ "G/G"),
-         Sample = gsub("SI", "", Sample)) %>%
-  dplyr::select(ID, Sample, Genotype.l)
-
-# Expression for SCARB2, NR2C2, TH, GAPDH and ACTIN
-FIPD.fin2 = FIPD %>% 
-  #dplyr::filter(str_detect(Geneid, paste(goi_ens$ENSEMBL.not.dot, collapse = "|"))) %>% 
-  dplyr::filter(str_detect(Geneid, paste(goi_ens$ENSEMBL.not.dot, 
-                                         collapse = "|"))) %>% 
-  dplyr::rename(ENSEMBL = Geneid) %>% 
-  mutate(ENSEMBL.not.dot = gsub("\\..*", "", ENSEMBL)) %>% 
-  dplyr::select(ENSEMBL, ENSEMBL.not.dot, everything()) %>% 
-  pivot_longer(cols = starts_with("RNAB"), names_to = "Samples", values_to = "CPM") %>% 
-  mutate(Day = str_extract(Samples, "da+\\d+")) %>% 
-  left_join(goi_ens, 
-            by = "ENSEMBL.not.dot") %>% 
-  dplyr::select(SYMBOL, Samples, Day, CPM) %>% 
-  #dplyr::filter(SYMBOL %in% c("SCARB2", "NR2C2", "TH", "ACTB", "GAPDH", "FAM47E", "GBA1")) %>% 
-  mutate(Sample = str_extract(Samples, "PPMI+\\d+")) %>% 
-  left_join(GT_PPMI.filt,
-            by = "Sample")
-
-# How many samples are heterozygous for rs1465922
-FIPD.fin2 %>% 
-  dplyr::select(Sample:Genotype.l) %>% 
-  filter(Genotype.l == "G/A") %>% 
-  dplyr::select(Sample) %>% 
-  distinct(Sample) %>% 
-  summarise(count = n())
-
-# Number of samples
-FIPD.fin2 %>% 
-  dplyr::select(Sample) %>% 
-  distinct(Sample) %>% 
-  summarise(count = n())
-
-# Plot for SCARB2
-ggboxplot(FIPD.fin2 %>% 
-            dplyr::filter(SYMBOL == "SCARB2"),
-          x = "Genotype.l",
-          y = "CPM",
-          facet.by = "Day",
-          title = "SCARB2 expression associated to rs1465922 genotype") + 
-  stat_compare_means(method = "anova",
-                     label.y = 1500) +
-  stat_compare_means(comparisons = list(c("A/A", "G/A"),
-                                        c("A/A", "G/G"),
-                                        c("G/A", "G/G")))
-
-# Plot for NR2C2
-ggboxplot(FIPD.fin2 %>% 
-            dplyr::filter(SYMBOL == "NR2C2"),
-          x = "Genotype.l",
-          y = "CPM",
-          facet.by = "Day",
-          title = "NR2C2 expression associated to rs1465922 genotype") + 
-  stat_compare_means(method = "anova",
-                     label.y = 100) +
-  stat_compare_means(comparisons = list(c("A/A", "G/A"),
-                                        c("A/A", "G/G"),
-                                        c("G/A", "G/G")))
-
-# Plot for TH
-ggboxplot(FIPD.fin2 %>% 
-            dplyr::filter(SYMBOL == "TH"),
-          x = "Genotype.l",
-          y = "CPM",
-          facet.by = "Day",
-          title = "TH expression associated to rs1465922 genotype") + 
-  stat_compare_means(method = "anova",
-                     label.y = 100) +
-  stat_compare_means(comparisons = list(c("A/A", "G/A"),
-                                        c("A/A", "G/G"),
-                                        c("G/A", "G/G")))
-
-# Plot for FAM47E
-ggboxplot(FIPD.fin2 %>% 
-            dplyr::filter(SYMBOL == "FAM47E"),
-          x = "Genotype.l",
-          y = "CPM",
-          facet.by = "Day",
-          title = "FAM47E expression associated to rs1465922 genotype") + 
-  stat_compare_means(method = "anova",
-                     label.y = 30) +
-  stat_compare_means(comparisons = list(c("A/A", "G/A"),
-                                        c("A/A", "G/G"),
-                                        c("G/A", "G/G")))
-
-# Plot for GAPDH
-ggboxplot(FIPD.fin2 %>% 
-            dplyr::filter(SYMBOL == "GAPDH"),
-          x = "Genotype.l",
-          y = "CPM",
-          facet.by = "Day",
-          title = "GAPDH expression associated to rs1465922 genotype") + 
-  stat_compare_means(method = "anova",
-                     label.y = 4500) +
-  stat_compare_means(comparisons = list(c("A/A", "G/A"),
-                                        c("A/A", "G/G"),
-                                        c("G/A", "G/G")))
-
-# Plot for ACTB
-ggboxplot(FIPD.fin2 %>% 
-            dplyr::filter(SYMBOL == "ACTB"),
-          x = "Genotype.l",
-          y = "CPM",
-          facet.by = "Day",
-          title = "ACTB expression associated to rs1465922 genotype") + 
-  stat_compare_means(method = "anova",
-                     label.y = 10000) +
-  stat_compare_means(comparisons = list(c("A/A", "G/A"),
-                                        c("A/A", "G/G"),
-                                        c("G/A", "G/G")))
-
-# Plot for GBA1
-ggboxplot(FIPD.fin2 %>% 
-            dplyr::filter(SYMBOL == "GBA1"),
-          x = "Genotype.l",
-          y = "CPM",
-          facet.by = "Day",
-          title = "GBA1 expression associated to rs1465922 genotype") + 
-  stat_compare_means(method = "anova",
-                     label.y = 100) +
-  stat_compare_means(comparisons = list(c("A/A", "G/A"),
-                                        c("A/A", "G/G"),
-                                        c("G/A", "G/G")))
-
-# Plot for PSAP
-ggboxplot(FIPD.fin2 %>% 
-            dplyr::filter(SYMBOL == "PSAP"),
-          x = "Genotype.l",
-          y = "CPM",
-          facet.by = "Day",
-          title = "PSAP expression associated to rs1465922 genotype") + 
-  stat_compare_means(method = "anova",
-                     label.y = 100) +
-  stat_compare_means(comparisons = list(c("A/A", "G/A"),
-                                        c("A/A", "G/G"),
-                                        c("G/A", "G/G")))
-
-# Scatterplot of GBA1 and SCARB2 independtly of the genotype
-FIPD.fin2 %>% 
-  dplyr::filter(SYMBOL %in% c("GBA1", "SCARB2")) %>% 
-  pivot_wider(names_from = SYMBOL, values_from = CPM) %>% 
-  ggscatter(x = "SCARB2",
-            y = "GBA1",
-            color = "Genotype.l",
-            facet.by = c("Day", "Genotype.l"),
-            add = "reg.line",
-            cor.coef = TRUE,
-            cor.coeff.args = list(method = "pearson", label.x = 3, label.sep = "\n"),
-            xlab = "SCARB2 expression (CPM)",
-            ylab = "GBA1 expression (CPM)") +
-  theme(legend.position = "right")
-
-# Scatterplot of NR2C2 and SCARB2 independtly of the genotype
-FIPD.fin2 %>% 
-  dplyr::filter(SYMBOL %in% c("NR2C2", "SCARB2")) %>% 
-  pivot_wider(names_from = SYMBOL, values_from = CPM) %>% 
-  ggscatter(x = "SCARB2",
-            y = "NR2C2",
-            color = "Genotype.l",
-            facet.by = c("Day", "Genotype.l"),
-            add = "reg.line",
-            cor.coef = TRUE,
-            cor.coeff.args = list(method = "pearson", label.x = 3, label.sep = "\n"),
-            xlab = "SCARB2 expression (CPM)",
-            ylab = "NR2C2 expression (CPM)") +
-  theme(legend.position = "right")
-
-dat.RPKM = read_delim("/Volumes/deborah.gerard/Documents/epifunc/RNAseq/RPKM_genename",
-                      delim = "\t",
-                      col_names = TRUE)
-
-dat.RPKM %>% 
-  #mutate(gene_id = gsub("\\..*", "", gene_id)) %>% 
-  dplyr::filter(str_detect(gene_id, "ENSG00000177628")) %>% 
-  pivot_longer(cols = contains("reads"), names_to = "Sample", values_to = "RPKM") %>% 
-  mutate(Cond = case_when(str_detect(Sample, "D15_possort") ~ "Positively sorted neurons D15",
-                         str_detect(Sample, "D30_possort") ~ "Positively sorted neurons D30",
-                         str_detect(Sample, "D50_possort") ~ "Positively sorted neurons D50",
-                         str_detect(Sample, "D15_negsort") ~ "Negatively sorted neurons D15",
-                         str_detect(Sample, "D50_negsort") ~ "Negatively sorted neurons D50",
-                         str_detect(Sample, "ASTRO") ~ "Astrocytes D65",
-                         TRUE ~ "smNPCs"),
-         Cond = factor(Cond, levels = c("smNPCs", 
-                                        "Negatively sorted neurons D15",
-                                        "Positively sorted neurons D15",
-                                        "Positively sorted neurons D30",
-                                        "Negatively sorted neurons D50",
-                                        "Positively sorted neurons D50",
-                                        "Astrocytes D65"))) %>% 
-  ggboxplot(.,
-            x = "Cond",
-            y = "RPKM",
-            fill = "Cond",
-            facet.by = "gene_name",
-            title = "GBA expression in TH REP1 cell line") +
-  theme(legend.position = "none",
-        axis.text.x = element_text(angle = 45, hjust = 1))
-
-## TH REP1 RNA feature counts
-THREP1.rawCount = read_rds("/Volumes/deborah.gerard/Documents/epifunc/RNAseq/fc_hs_q30RNA.rds")
-
-# TH REP1 reads assigned
-THREP1.seqDepth = THREP1.rawCount$stat %>% 
-  dplyr::slice(1) %>% 
-  as_tibble() %>% 
-  pivot_longer(cols = contains("bam"), names_to = "Sample", values_to = "seqDepthInSple") %>% 
-  #dplyr::filter(!str_detect(Sample, "ASTRO")) %>% 
-  dplyr::select(-Status)
-
-# TH REP1 raw read counts
-THREP1.rawCount$counts %>% 
- as.data.frame() %>% 
-  rownames_to_column(var = "gene_id") %>% 
-  as_tibble() %>% 
-  filter(str_detect(gene_id, "ENSG00000177628")) %>% 
-  pivot_longer(cols = contains("bam"), names_to = "Sample", values_to = "rawCounts") %>% 
-  #dplyr::filter(!str_detect(Sample, "ASTRO")) %>% 
-  left_join(THREP1.seqDepth, by = "Sample") %>% 
-  mutate(CPM = (rawCounts/seqDepthInSple)*10^6) %>% 
-  mutate(Cond = case_when(str_detect(Sample, "D15_pos") ~ "Positively sorted neurons D15",
-                          str_detect(Sample, "D15_neg") ~ "Negatively sorted neurons D15",
-                          str_detect(Sample, "D30_pos") ~ "Positively sorted neurons D30",
-                          str_detect(Sample, "D50_neg") ~ "Negatively sorted neurons D50",
-                          str_detect(Sample, "D50_pos") ~ "Positively sorted neurons D50",
-                          str_detect(Sample, "ASTRO") ~ "Astrocytes D65",
-                          TRUE ~ "smNPCs"),
-         Cond = factor(Cond, 
-                       levels = c("smNPCs", 
-                                  "Negatively sorted neurons D15",
-                                  "Positively sorted neurons D15",
-                                  "Negatively sorted neurons D30",
-                                  "Positively sorted neurons D30",
-                                  "Negatively sorted neurons D50",
-                                  "Positively sorted neurons D50",
-                                  "Astrocytes D65"))) %>% 
-  ggboxplot(.,
-            x = "Cond",
-            y = "CPM",
-            facet.by = "gene_id",
-            fill = "Cond",
-            title = "GBA expression (as CPM) in TH REP1 cell line") +
-  theme(legend.position = "none",
-        axis.text.x = element_text(angle = 45, hjust = 1))
-
-# TEST IF GBA is mutated in TH REP1 from WGS
-THREP1.wgs = read_rds("/Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/E19D017a78.merge.qc.SNP_INDEL.hg19.annotated.rds")
-
-THREP1.wgs %>% 
-  dplyr::filter(str_detect(Gene.refGene, "GBA"),
-                CHR == 1) %>% 
-  View()
-```
-
-##TEST 28 SNPs
-```{bash, eval = FALSE, echo = TRUE}
-# Concatenate all output files from Nina
-# smNPC
-awk 'BEGIN{ FS = OFS = "\t" } { print $0, (NR==1?
-"Sample" : "smNPC") }' /Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/PD_smNPC_0.01_0.5.txt > /Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/REPRO/PD_smNPC_0.01_0.5_SAMPLE_NAME.txt
-
-# mDAN D15
-awk 'BEGIN{ FS = OFS = "\t" } { print $0, (NR==1?
-"Sample" : "mDAN_D15") }' /Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/PD_D15_pos_0.01_0.5.txt > /Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/REPRO/PD_D15_pos_0.01_0.5_SAMPLE_NAME.txt
-
-# mDAN D30
-awk 'BEGIN{ FS = OFS = "\t" } { print $0, (NR==1?
-"Sample" : "mDAN_D30") }' /Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/PD_D30_pos_0.01_0.5_new_20210308.txt > /Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/REPRO/PD_D30_pos_0.01_0.5_new_20210308_SAMPLE_NAME.txt
-
-# mDAN D50
-awk 'BEGIN{ FS = OFS = "\t" } { print $0, (NR==1?
-"Sample" : "mDAN_D50") }' /Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/PD_D50_pos_0.01_0.5.txt > /Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/REPRO/PD_D50_pos_0.01_0.5_SAMPLE_NAME.txt
-
-# Astro
-awk 'BEGIN{ FS = OFS = "\t" } { print $0, (NR==1?
-"Sample" : "astro") }' /Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/PD_astro_0.01_0.5.txt > /Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/REPRO/PD_astro_0.01_0.5_SAMPLE_NAME.txt
-
-# Concatenate them all together
-cat /Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/REPRO/PD_smNPC_0.01_0.5_SAMPLE_NAME.txt \
-/Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/REPRO/PD_D15_pos_0.01_0.5_SAMPLE_NAME.txt \
-/Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/REPRO/PD_D30_pos_0.01_0.5_new_20210308_SAMPLE_NAME.txt \
-/Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/REPRO/PD_D50_pos_0.01_0.5_SAMPLE_NAME.txt \
-/Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/REPRO/PD_astro_0.01_0.5_SAMPLE_NAME.txt > /Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/REPRO/SNEEP_PD.txt
-```
-
-Load the PD GWAS data (hg38)
-```{r, eval = FALSE, echo = TRUE}
-nalls_allSNPs.HG38.GR = readRDS(
-"/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/nalls_allSNPs.HG38.GR.rds")
-
-nalls_allSNPs.HG38.GR.pvalFilt = nalls_allSNPs.HG38.GR %>% 
-  as_tibble() %>% 
-  dplyr::select(seqnames:end, p, effect_allele:other_allele) %>% 
-  unite(col = "tmp", c(seqnames, start), sep = ":", remove = FALSE) %>% 
-  unite(col = "SNP_position", c(tmp, end), sep = "-", remove = TRUE) %>% 
-  dplyr::filter(p < 5e-08)
-
-nalls_allSNPs.HG38.GR.pvalFilt106 = nalls_allSNPs.HG38.GR %>% 
-  as_tibble() %>% 
-  dplyr::select(seqnames:end, p, effect_allele:other_allele) %>% 
-  unite(col = "tmp", c(seqnames, start), sep = ":", remove = FALSE) %>% 
-  unite(col = "SNP_position", c(tmp, end), sep = "-", remove = TRUE) %>% 
-  dplyr::filter(p < 5e-06)
-
-SNEEP_out_all = read_delim("/Volumes/deborah.gerard/Documents/epifunc/SNPs_overlap/Ninas_files/REPRO/SNEEP_PD.txt",
-                           delim = "\t",
-                           col_names = TRUE)
-
-SNEEP_out_all %>% 
-  dplyr::filter(SNP_position %in% nalls_allSNPs.HG38.GR.pvalFilt$SNP_position) %>% 
-  distinct(SNP_position, .keep_all = TRUE) %>% 
-  View()
-
-SNEEP_out_all %>% 
-  dplyr::filter(SNP_position %in% nalls_allSNPs.HG38.GR.pvalFilt106$SNP_position) %>% 
-  distinct(SNP_position, .keep_all = TRUE) %>% 
-  View()
-
-strawr::readHicChroms("/Volumes/deborah.gerard/Documents/Wetlab/epifunc/LOW_C/LowCO/LowCO/FANC_output_mixedNeur/hic/binned/FANC_opti_mixed_neur_100kb.hic")
-```

### 2025-01-31 FIGURE1/scripts/FANC_in_silico_digestion.sh
Add the different scripts for the Low-C

@@ -1,0 +1,27 @@
+#!/bin/bash -l
+#SBATCH -J N1_smNPC_mDAN_in_silico_digestion
+#SBATCH --mail-type=begin,end,fail
+#SBATCH --mail-user=deborah.gerard@uni.lu
+#SBATCH -N 1
+#SBATCH --exclusive
+#SBATCH -p batch
+#SBATCH --qos=normal
+#SBATCH --time=06:00:00
+
+# This script is for performing in silico digestion of the genome using the restriction enzyme MboI (the same enzyme that been used for the wetlab experiment) #
+# Load modlue containing python3
+module load lang/Python/3.8.6-GCCcore-10.2.0
+
+# Activate the python environment for FAN-C
+source ~/Environment/FANC/bin/activate
+
+# Check FAN-C version
+fanc --version
+
+# Run in-silico genome digestion
+fanc fragments -c 'chr1,chr2,chr3,chr4,chr5,chr6,chr7,chr8,chr9,chr10,chr11,chr12,chr13,chr14,chr15,chr16,chr17,chr18,chr19,chr20,chr21,chr22,chrX,chrY' \
+$SCRATCH/bwa_index/GRCh38.genome.fa.gz \
+'MboI' \
+$SCRATCH/FANC_hg38.p1.cano.chr.bed
+
+deactivate

### 2025-01-31 FIGURE1/scripts/fastqc.sh
Add the different scripts for the Low-C

@@ -1,0 +1,20 @@
+#!/bin/bash -l
+#SBATCH -J N1_smNPC_mDAN_fastqc
+#SBATCH --mail-type=begin,end,fail
+#SBATCH --mail-user=deborah.gerard@uni.lu
+#SBATCH -N 1
+#SBATCH --time=08:00:00
+#SBATCH -p batch
+#SBATCH --qos=normal
+
+# Load module containing fastqc
+module load bio/FastQC/0.11.9-Java-11
+
+# Check fastqc version
+fastqc --v
+
+# Perform quality control using fastqc module.
+for i in $SCRATCH/LowC_smNPC_THpos_neur/fastq/*.gz
+do
+	fastqc -o $SCRATCH/LowC_smNPC_THpos_neur/FASTQC_res/ $i
+done

### 2025-01-31 FIGURE1/scripts/FANC_hic_to_juicer.sh
Update of the script for Figure 1 and upload of the Low-C scripts

@@ -1,0 +1,49 @@
+#!/bin/bash -l
+#SBATCH -J FANC_hic_to_juicer
+#SBATCH --mail-type=begin,end,fail
+#SBATCH --mail-user=deborah.gerard@uni.lu
+#SBATCH -N 1
+#SBATCH --exclusive
+#SBATCH --time=03:00:00
+#SBATCH -p batch
+#SBATCH --qos=long
+
+# Load module containing python3
+module load lang/Python/3.8.6-GCCcore-10.2.0
+
+# Activate the python environment for FAN-C
+source ~/Environment/FANC/bin/activate
+
+# Check FAN-C version
+fanc --version
+
+# As FAN-C needs bwa for the mapping step, load the module containing bwa
+module load bio/BWA/0.7.17-GCC-10.2.0
+
+# And check version
+bwa
+
+# Remove tempfiles and set a TMPDIR variable
+rm -rf $SCRATCH/tempfiles/*
+export TMPDIR=$SCRATCH/tempfiles/
+echo $TMPDIR
+
+# Pairs files are in SCRATCH
+cd $SCRATCH
+
+# 5kb resolution
+#parallel -j 4 "fanc to-juicer {} {.}.juicer.5kb.hic --juicer-tools-jar $HOME/juicer_tools.2.20.00.jar -tmp -r 5000" ::: *.pairs
+
+# 10kb resolution
+#parallel -j 4 "fanc to-juicer {} {.}.juicer.10kb.hic --juicer-tools-jar $HOME/juicer_tools.2.20.00.jar -tmp -r 10000" ::: *.pairs
+
+# 25kb resolution
+#parallel -j 4 "fanc to-juicer {} {.}.juicer.25kb.hic --juicer-tools-jar $HOME/juicer_tools.2.20.00.jar -tmp -r 25000" ::: *.pairs
+
+# 50kb resolution
+parallel -j 4 "fanc to-juicer {} {.}.juicer.50kb.hic --juicer-tools-jar $HOME/juicer_tools.2.20.00.jar -tmp -r 50000" ::: *.pairs
+
+echo "Remove first temporary files previously written"
+rm -rf $SCRATCH/tempfiles/*
+
+deactivate

### 2025-01-31 FIGURE1/scripts/FANC_launcher_N1.sh

@@ -1,0 +1,54 @@
+#!/bin/bash -l
+#SBATCH -J FANC_N2_smNPC_N1_mDAN_smNPC_Op
+#SBATCH --mail-type=begin,end,fail
+#SBATCH --mail-user=deborah.gerard@uni.lu
+#SBATCH -N 1
+#SBATCH --exclusive
+#SBATCH --time=96:00:00
+#SBATCH -p batch
+#SBATCH --qos=long
+
+# Load modlue containing python3
+module load lang/Python/3.8.6-GCCcore-10.2.0
+
+# Activate the python environment for FAN-C
+source ~/Environment/FANC/bin/activate
+
+# Check FAN-C version
+fanc --version
+
+# As FAN-C needs bwa for the mapping step, load the module containing bwa
+module load bio/BWA/0.7.17-GCC-10.2.0
+
+# And check version
+bwa
+
+# Set a TMPDIR variable
+export TMPDIR=$SCRATCH/tempfiles/
+echo $TMPDIR
+
+echo "Remove first temporary files previously written"
+rm -rf $SCRATCH/tempfiles/*
+
+# Run FAN-C in automatic mode smNPC - Biological replicate 1 - Normalisation method is Knight-Ruiz
+fanc auto $SCRATCH/LowC_smNPC_THpos_neur/fastq/N1_TH_REP1_mCHERRY_smNPC_LOW_C_LowTH_SB_S2_R1_001.fastq.gz \
+$SCRATCH/LowC_smNPC_THpos_neur/fastq/N1_TH_REP1_mCHERRY_smNPC_LOW_C_LowTH_SB_S2_R2_001.fastq.gz \
+$SCRATCH/LowC_smNPC_THpos_neur/FANC_output_N1_smNPC \
+-g $SCRATCH/FANC_hg38.p1.cano.chr.bed \
+-i $SCRATCH/bwa_index/GRCh38.genome.fa.gz \
+-r MboI \
+-n N1_smNPC \
+-t 14 \
+--le-inward-cutoff 5000 \
+--le-outward-cutoff 5000 \
+--fanc-parallel \
+--norm-method KR \
+--iterative \
+--split-ligation-junction \
+-q 3 \
+-tmp
+
+echo "Remove first temporary files previously written"
+rm -rf $SCRATCH/tempfiles/*
+
+deactivate

### 2025-01-31 FIGURE1/scripts/FANC_launcher_N1_TH_N2_smNPC.sh

@@ -1,0 +1,93 @@
+#!/bin/bash -l
+#SBATCH -J FANC_N2_smNPC_N1_mDAN_smNPC_Op
+#SBATCH --mail-type=begin,end,fail
+#SBATCH --mail-user=deborah.gerard@uni.lu
+#SBATCH -N 1
+#SBATCH --exclusive
+#SBATCH --time=96:00:00
+#SBATCH -p batch
+#SBATCH --qos=long
+
+# Load modlue containing python3
+module load lang/Python/3.8.6-GCCcore-10.2.0
+
+# Activate the python environment for FAN-C
+source ~/Environment/FANC/bin/activate
+
+# Check FAN-C version
+fanc --version
+
+# As FAN-C needs bwa for the mapping step, load the module containing bwa
+module load bio/BWA/0.7.17-GCC-10.2.0
+
+# And check version
+bwa
+
+# Set a TMPDIR variable
+export TMPDIR=$SCRATCH/tempfiles/
+echo $TMPDIR
+
+echo "Remove first temporary files previously written"
+rm -rf $SCRATCH/tempfiles/*
+
+# Run FAN-C in automatic mode for mDAN neurons day 30 - Biological replicate 1 - Normalisation method is Knight-Ruiz
+fanc auto $SCRATCH/LowC_smNPC_THpos_neur/fastq/N1_TH_REP1_mCHERRY_TH_Neur_day30_LOW_C_LowTH_SB_S1_R1_001.fastq.gz \
+$SCRATCH/LowC_smNPC_THpos_neur/fastq/N1_TH_REP1_mCHERRY_TH_Neur_day30_LOW_C_LowTH_SB_S1_R2_001.fastq.gz \
+$SCRATCH/LowC_smNPC_THpos_neur/FANC_output_N1_mDAN_D30 \
+-g $SCRATCH/FANC_hg38.p1.cano.chr.bed \
+-i $SCRATCH/bwa_index/GRCh38.genome.fa.gz \
+-r MboI \
+-n N1_mDAN_D30 \
+-t 14 \
+--le-inward-cutoff 5000 \
+--le-outward-cutoff 5000 \
+--fanc-parallel \
+--norm-method KR \
+--iterative \
+--split-ligation-junction \
+-q 3 \
+-tmp
+
+echo "Remove first temporary files previously written"
[…]

### 2025-01-31 FIGURE1/scripts/FANC_replicate_merge_smNPC.sh

@@ -1,0 +1,44 @@
+#!/bin/bash -l
+#SBATCH -J FANC_merge_replicate_smNPC
+#SBATCH --mail-type=begin,end,fail
+#SBATCH --mail-user=deborah.gerard@uni.lu
+#SBATCH -N 1
+#SBATCH --exclusive
+#SBATCH --time=96:00:00
+#SBATCH -p batch
+#SBATCH --qos=long
+
+# Load modlue containing python3
+module load lang/Python/3.8.6-GCCcore-10.2.0
+
+# Activate the python environment for FAN-C
+source ~/Environment/FANC/bin/activate
+
+# Check FAN-C version
+fanc --version
+
+# As FAN-C needs bwa for the mapping step, load the module containing bwa
+module load bio/BWA/0.7.17-GCC-10.2.0
+
+# And check version
+bwa
+
+# Set a TMPDIR variable
+export TMPDIR=$SCRATCH/tempfiles/
+echo $TMPDIR
+
+echo "Remove first temporary files previously written"
+rm -rf $SCRATCH/tempfiles/*
+
+# Run FAN-C in automatic mode for merging hic files for smNPCs (3 biological replicates)
+fanc auto $SCRATCH/LowC_smNPC_THpos_neur/FANC_output_N1_smNPC/hic/N1_smNPC.hic \
+$SCRATCH/LowC_smNPC_THpos_neur/FANC_output_N2_smNPC/hic/N2_smNPC.hic \
+$SCRATCH/LowC_smNPC_THpos_neur/FANC_output_opti_smNPC/hic/opti_smNPC.hic \
+$SCRATCH/LowC_smNPC_THpos_neur/FANC_merged_smNPC \
+-n merged_smNPC \
+-t 14
+
+echo "Remove first temporary files previously written"
+rm -rf $SCRATCH/tempfiles/*
+
+deactivate

### 2025-01-31 FIGURE1/scripts/FANC_hic_expected.sh
Update of the script for Figure 1 and upload of the Low-C scripts

@@ -1,0 +1,218 @@
+#!/bin/bash -l
+#SBATCH -J FANC_hic_O/E
+#SBATCH --mail-type=begin,end,fail
+#SBATCH --mail-user=deborah.gerard@uni.lu
+#SBATCH -N 1
+#SBATCH --exclusive
+#SBATCH --time=60:00:00
+#SBATCH -p batch
+#SBATCH --qos=long
+
+# Load module containing python3
+module load lang/Python/3.8.6-GCCcore-10.2.0
+
+# Activate the python environment for FAN-C
+source ~/Environment/FANC/bin/activate
+
+# Check FAN-C version
+fanc --version
+
+# As FAN-C needs bwa for the mapping step, load the module containing bwa
+module load bio/BWA/0.7.17-GCC-10.2.0
+
+# And check version
+bwa
+
+# Remove tempfiles and set a TMPDIR variable
+rm -rf $SCRATCH/tempfiles/*
+export TMPDIR=$SCRATCH/tempfiles/
+echo $TMPDIR
+
+# Run fan-c expected command for every hic files and resolutions
+## N1-smNPC and N1-mDAN D30
+### 1 mb resolution
+echo "Calculating expected values for the 1mb resolution on N1-smNPCs and N1-mDAN D30"
+fanc expected -l "N1-smNPCs_1mb" "N1-mDAN D30_1mb" \
+-p $SCRATCH/LowC_smNPC_THpos_neur/Obs_Expected_res/1mb_N1-smNPC_N1-mDAN-D30_OE.pdf \
+-tmp \
+$SCRATCH/LowC_smNPC_THpos_neur/FANC_output_N1_smNPC/hic/binned/N1_smNPC_1mb.hic \
+$SCRATCH/LowC_smNPC_THpos_neur/FANC_output_N1_mDAN_D30/hic/binned/N1_mDAN_D30_1mb.hic \
+$SCRATCH/LowC_smNPC_THpos_neur/Obs_Expected_res/1mb_N1-smNPC_N1-mDAN-D30_OE.txt
+
+### 2 mb resolution
+echo "Calculating expected values for the 2mb resolution on N1-smNPCs and N1-mDAN D30"
[…]

### 2025-01-31 FIGURE1/scripts/FANC_hic_to_txt_and_bin_nolog.sh

@@ -1,0 +1,44 @@
+#!/bin/bash -l
+#SBATCH -J FANC_from_hic_to_txt_and_bin_nolog
+#SBATCH --mail-type=begin,end,fail
+#SBATCH --mail-user=deborah.gerard@uni.lu
+#SBATCH -N 1
+#SBATCH --exclusive
+#SBATCH -p batch
+#SBATCH --qos=normal
+#SBATCH --time=02:00:00
+
+# This script is for converting a hic file from 3 hic files into a text file#
+# Load modlue containing python3
+module load lang/Python/3.8.6-GCCcore-10.2.0
+
+# Activate the python environment for FAN-C
+source ~/Environment/FANC/bin/activate
+
+# Check FAN-C version
+fanc --version
+
+# Set a TMPDIR variable
+export TMPDIR=$SCRATCH/tempfiles/
+echo $TMPDIR
+
+echo "Remove first temporary files previously written"
+rm -rf $SCRATCH/tempfiles/*
+
+# Run the fan dump command using the 5kb and 10 kb bins for Dennis
+# 5kb
+fanc dump -tmp \
+$SCRATCH/LowC_smNPC_THpos_neur/FANC_merged_smNPC/hic/binned/merged_smNPC_5kb.hic \
+$SCRATCH/LowC_smNPC_THpos_neur/FANC_merged_smNPC/hic/binned/merged_smNPC_5kb_matrix_noOE_nolog.txt \
+$SCRATCH/LowC_smNPC_THpos_neur/FANC_merged_smNPC/hic/binned/merged_smNPC_5kb_bins_noOE_nolog.txt
+
+echo "Remove first temporary files previously written"
+rm -rf $SCRATCH/tempfiles/*
+
+# 10kb
+fanc dump -tmp \
+$SCRATCH/LowC_smNPC_THpos_neur/FANC_merged_smNPC/hic/binned/merged_smNPC_10kb.hic \
+$SCRATCH/LowC_smNPC_THpos_neur/FANC_merged_smNPC/hic/binned/merged_smNPC_10kb_matrix_noOE_nolog.txt \
+$SCRATCH/LowC_smNPC_THpos_neur/FANC_merged_smNPC/hic/binned/merged_smNPC_10kb_bins_noOE_nolog.txt
+
+deactivate
